### 2022-12-27 paper/main.tex
added paper

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%This is a template for producing LIPIcs articles. 
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{What's in a Name? Linear Temporal Logic Literally Represents Time Lines} %TODO Please add

%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line

\author{Runming Li\thanks{These authors contributed equally to this work}}{Carnegie Mellon University, USA}{runmingl@andrew.cmu.edu}{https://orcid.org/0000-0001-7600-9069}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional. Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.

\author{Keerthana Gurushankar\footnotemark[1]}{Carnegie Mellon University, USA}{kgurusha@andrew.cmu.edu}{[orcid]}{}

\authorrunning{Li and Gurushankar} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Runming Li and Keerthana Gurushankar} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003752.10003766.10003770</concept_id>
       <concept_desc>Theory of computation~Automata over infinite objects</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10003752.10003766.10003776</concept_id>
       <concept_desc>Theory of computation~Regular languages</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
   <concept>
       <concept_id>10003752.10003790.10003793</concept_id>
       <concept_desc>Theory of computation~Modal and temporal logics</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10003752.10003790.10002990</concept_id>
       <concept_desc>Theory of computation~Logic and verification</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Automata over infinite objects}
\ccsdesc[300]{Theory of computation~Regular languages}
\ccsdesc[500]{Theory of computation~Modal and temporal logics}
\ccsdesc[300]{Theory of computation~Logic and verification}

\keywords{Linear Temporal Logic, \Buchi automata, $\omega$-regular expression, model checking, visualization} %TODO mandatory; please add comma-separated list of keywords

\category{} %optional, e.g. invited paper

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversiondetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g. Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional

%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
%\supplementdetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g. Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\nolinenumbers %uncomment to disable line numbering

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{}
\EventNoEds{1}
\EventLongTitle{}
\EventShortTitle{}
\EventAcronym{}
\EventYear{}
\EventDate{}
\EventLocation{}
\EventLogo{}
\SeriesVolume{}
\ArticleNo{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{algorithm, algpseudocode, amsmath, amsfonts, scalerel}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,  
    urlcolor=blue,
    linkcolor=blue,
    citecolor=blue,
    pdfpagemode=FullScreen,
    }
\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}
\crefname{algocf}{alg.}{algs.}
\Crefname{algocf}{Algorithm}{Algorithms}

\newcommand{\AP}{\mathcal{AP}}
\newcommand{\always}{\Box}
\newcommand{\eventually}{\Diamond}
\newcommand{\nextt}{\mathcal{X}}
\newcommand{\limplies}{\rightarrow}
\newcommand{\ltl}{\textit{LTL}}

\newcommand{\Buchi}{B\"{u}chi }
\newcommand{\stronguntil}{\hspace{0.1cm} \mathcal{U}  \hspace{0.1cm}}
\newcommand{\strongrelease}{\hspace{0.1cm} \mathcal{M} \hspace{0.1cm}}
\newcommand{\weakuntil}{\hspace{0.1cm} \mathcal{W} \hspace{0.1cm}}
\newcommand{\weakrelease}{\hspace{0.1cm} \mathcal{R} \hspace{0.1cm}}
\newcommand{\liff}{\leftrightarrow}
\DeclareMathOperator*{\bigplus}{\scalerel*{+}{\sum}}

% hyperref must go last
\usepackage{hyperref}
% but cleveref goes "laster" than hyperref
\usepackage[capitalise,noabbrev]{cleveref}
\providecommand\algorithmname{algorithm}
\crefname{algocf}{alg.}{algs.}
\Crefname{algocf}{Algorithm}{Algorithms}

\begin{document}

\maketitle

%TODO mandatory: add short abstract of the document
\begin{abstract}
    Linear Temporal Logic (\ltl) is widely used to specify requirements in safety-critical systems.
    However, like many formal verification techniques, it is known to be unintuitive and error-prone for human practitioners to specify and validate.
    In this paper, we provide a new timeline tool for visualizing \ltl-based specifications, which is effective at intuitively representing a wide range of formulas.
    Our tool generates timeline visualizations by translating \ltl\ formulae to intermediate representations as \Buchi automata and then $\omega$-regular expressions, and finally simplifying and visualizing the expressions.
    We provide an algorithm for this visualization, a theoretical soundness analysis, and an implementation.
\end{abstract}

\section{Introduction}

Formal methods, including Linear Temporal Logic (\ltl), are widely used in the specification and analysis of safety-critical systems, such as those found in the aerospace industry. These methods provide powerful tools for rigorously verifying the correctness of system designs, from early design-time model checking to on-board runtime verification. However, these methods can be difficult for humans to understand and use, leading to the possibility of errors and misunderstandings.

There has been recent work aimed at making the use of formal methods more intuitive for humans, such as NASA's FRET (Formal Requirements Engineering Tool) \cite{GPMS20} which uses structured natural language to bridge the gap between natural language and formal semantics.

However, \ltl\ is a literally a language of timelines, so timeline visualizations have the potential to be a powerful tool for representing \ltl\ formulas in an intuitive manner. In this paper, we propose such a timeline visualization tool, using regular expressions, to effectively represent a wide range of \ltl-based formulas.

\section{Setting the stage}

\subsection{Linear temporal logic (LTL)}

\begin{definition}[Linear Temporal Logic (LTL)]
    % cite Kristin's survey paper
    The syntax of an LTL formula over a set of atomic propositions $\AP$, where $p\in\AP$ is a propositional variable, is given by the following grammar:
    \begin{align*}
        \Phi ::= p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi
    \end{align*}\label{ltl-defn}
\end{definition}
Intuitively, $\always \Phi$ says that formula $\Phi$ is true at every time step; $\eventually \Phi$ says that formula $\Phi$ is true either now or at sometime in the future time step; and $\nextt \Phi$ says formula $\Phi$ is true at the next time step immediately after the current one.
\begin{remark}
    The definition of \ltl\ can be extended to allow release and until as shown below, but they are definable using connectives in \ref{ltl-defn}, hence they are omitted in the definition. The tool we present in this paper, however, does support those operators.
    \begin{align*}
        \Phi ::= \cdots \mid \Phi \strongrelease \Phi \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi \mid \Phi \weakuntil \Phi 
    \end{align*}
\end{remark}

\begin{definition}[Semantics of \ltl\ formula]
    The semantics of \ltl\ formula is defined via judgement $\pi, i \models \Phi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step. The semantics follows exactly from \cite{Roz11}.
\end{definition}

\subsection{State-based \Buchi automata (BA)}
\begin{definition}[$\omega$-word]
    An $\omega$-word or infinite run of $\Sigma$, is an infinite string $s = (s_0, s_1, s_2, \dots)$ where each $s_i\in \Sigma$
\end{definition}
\begin{definition}[\Buchi automaton]
    A \Buchi automaton is a $5$-tuple, $G = (Q, \Sigma, \delta, s, F)$ consisting of
    \begin{enumerate}
        \item a finite set of states $Q$
        \item a finite alphabet of input symbols called the alphabet $\Sigma$
        \item a partial function $\delta : Q\times \Sigma \to Q$, called the transition function
        \item an initial or start stae called $s\in Q$
        \item a set of accept states $F \subseteq Q$
    \end{enumerate}
    $G$ accepts an infinite run iff at least one of its infinitely visited states is in $F$
\end{definition}
\subsection{$\omega$-regular expression}
\begin{definition}[Regular expression]
    For word $a \in \Sigma$, regular expression is defined by the following grammar:
    \begin{align*}
        A ::= \emptyset \mid \epsilon \mid a \mid AA \mid A + A \mid A^*
    \end{align*}
\end{definition}
\begin{definition}[Semantics of regular expression]
    Let $L(A)$ denote the language accepted by regular expression $A$. Then $L(A)$ is inductively defined as
    \begin{align*}
        L(\emptyset) & = \emptyset \\
        L(\epsilon) & = \{\epsilon\} \\
        L(a) & = \{a\} \\
        L(A_1A_2) & = \{s_1s_2 \mid s_1 \in L(A_1) \text{ and } s_2 \in L(A_2)\} \\
        L(A_1 + A_2) & = L(A_1) \cup L(A_2) \\
        L^{(0)}(A) & = \{\epsilon\} \\
        L^{(i + 1)}(A) & = \{s_1s_2 \mid s_1 \in L(A) \text{ and } s_2 \in L^{(i)}(A)\} \\\
        L(A^*) & = \bigcup_{i \ge 0} L^{(i)}(A)
    \end{align*}
\end{definition}

\begin{remark}
    For the purpose of our tool, $\Sigma$ is the set of propositional logic formula defined as
    \[
    \Psi ::= p \mid \neg \Psi \mid \Psi \land \Psi \mid \Psi \lor \Psi \mid \Psi \limplies \Psi
    \]
\end{remark}

\begin{definition}[$\omega$-regular expression]
    Regular expression concerns only finite-length strings. However, since \ltl\ formulas reason about events that happen over an infinite-length timeline, we need to model it using infinite regular expressions (i.e. $\omega$-regular expression). $\omega$-regular expression is defined by the following grammar:
    \begin{align*}
        B ::= A^{\omega} \mid AB \mid B + B
    \end{align*}
\end{definition}
\begin{definition}[Semantics of $\omega$-regular expression]\label{def:omega-semantics}
    Let $\Sigma^{\omega}$ denote the set of infinite-length string over fixed alphabet $\Sigma$. Let $L_{\omega}(B)$ denote the $\omega$-language accepted by $\omega$-regular expression $B$. Then $L_{\omega}(B)$ is inductively defined as
    \begin{align*}
        L_{\omega}(A^{\omega}) & = \{s_1s_2s_3\cdots \mid s_i \in L(A) \text{ and } i \ge 1\} \\
        L_{\omega}(AB) & = \{s_1s_2 \mid s_1 \in L(A) \text{ and } s_2 \in L_{\omega}(B)\} \\
        L_{\omega}(B_1 + B_2) &= L_{\omega}(B_1) \cup L_{\omega}(B_2) 
    \end{align*}
\end{definition}

\subsection{Timeline}
We present timelines as graphic visualizations. It contains the following features:
\begin{itemize}
    \item Every timeline starts with a node named ``start''.
    \item Every node represents one time step, and each node has a propositional logic formula $\Psi$, which specifies the behavior of atomic propositions at that time step. The formula $\Psi$ must be true at that time step. If $\Psi = 1$, that means all atomic propositions can behave arbitrarily.
    \item A node with label ``$\cdots$'' means to repeat the node prior to it and after it finitely many times.
    \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its starting point.
\end{itemize}

\begin{example}
    In figure \ref{fig:ex2}, one can reason about two timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$. Then at the end of the grey box, we reenter the box, with the next time step being $!p$, and so on. The lower timeline starts with one step of $!p$ and one step of $p$ outside the grey box, and then enter the infinite run of $!p$ and $p$ repeating. 
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.4]{examples/ex2/ex2.gv.png}
        \caption{Example timeline for specification ``$p$ oscillates every time step''}
        \label{fig:ex2}
    \end{figure}
\end{example}

\section{Algorithm}
On a high level, our algorithm of converting \ltl\ formula into timeline visualization works as follows:
\begin{enumerate}
    \item Convert \ltl\ formula to its corresponding \Buchi automata \ref{ltl2aut}
    \item Derive the $\omega$-regular expression corresponding to the \Buchi automata \ref{aut2regex}
    \item Simplify the derived $\omega$-regular expression \ref{regex-simplify}
    \item Visualize the $\omega$-regular expression according to its structure \ref{regex2timeline}
\end{enumerate}
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{img/algo-flowchart.png}
    \caption{Algorithm outline}
    \label{fig:algo}
\end{figure}
\subsection{LTL to BA} \label{ltl2aut}
The translation from LTL formulas to \Buchi automata is provided by SPOT\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.}.

\subsection{BA to $\omega$-regex} \label{aut2regex}

We translate \Buchi automata to $\omega$-regular expressions by first finding the regular expressions for paths from the start state to some final state (say $r_{sf}$), and for those for paths for looping from the final state back to itself (say $r_{ff}$), and finally combining those to form the $\omega$-expression for valid runs ($\bigplus_{f\in F} r_{sf}r_{ff}^\omega$). The regular expressions for finite paths are in turn found by iteratively deleting interior nodes in digraph of the automaton.

The algorithm is outlined below (see Algorithms 1 - 4). %\cref{alg:ba2wregex}

\begin{algorithm}[h!]
    \caption{reduce\_dfa}
    \begin{algorithmic}
        \Require ($G, v$), a DFA with state $v$ that is not initial or final
        \Ensure Deletes state $v$ from $G$ while ensuring the same language is recognized
        \For{ every $u\xrightarrow{r_{in}} v, v \xrightarrow{r_{out}} w$ }
            \If {$v$ has a self-edge  $v\xrightarrow{r_{loop}}v$}
                \State replace edges $u\xrightarrow{r_{in}} v, v \xrightarrow{r_{out}} w$ with $u \xrightarrow{r_{in} r_{loop}* r_{out}} w$
            \Else
                \State replace edges $u\xrightarrow{r_{in}} v, v \xrightarrow{r_{out}} w$ with $u \xrightarrow{r_{in}  r_{out}} w$
            \EndIf
        \EndFor
        %\State \Return the reduced graph $G$
    \end{algorithmic}
\end{algorithm}
\begin{algorithm}[h!]
    \caption{dfa2regex}
    \begin{algorithmic}
        \Require ($G, s, f$), a DFA with initial state $s$ and final state $f$
        \Ensure The regular expression corresponding to all paths from $s$ to $f$
        % WHile there exists any edge except r_sf
        \While{ there exists an interior vertex $v$ }
            \State reduce\_dfa($G, v$)
            \State combine multiedges, i.e. $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
        \EndWhile
        \State \Return $(r_{ss}| r_{sf} r_{ff}^* r_{fs})^* r_{sf} r_{ff}$
        % if called by first visit, this is r_{ss}* r_{sf}
        % if called by ba2wregex, s=f, this is r_{ff}
        % consider modularizing fns differently
        % \State \Return regexp labelling the edge $s\to f$
    \end{algorithmic}
\end{algorithm}
\begin{algorithm}[h!]
    \caption{dfa2regex\_firstvisit}
    \begin{algorithmic}
        \Require ($G, s, f$), a DFA with initial state $s$ and final state $f$
        \Ensure The regular expression of all paths from $s$ reaching $f$ for the first time
        \State delete all out edges from $f$ in $G$
        \State \Return dfa2regex($G, s, f$)
    \end{algorithmic}
\end{algorithm}
\begin{algorithm}[h!]
    \label{alg:ba2wregex}
    \caption{ba2wregex}
    \begin{algorithmic}
        \Require $G$, a \Buchi automaton
        \Ensure The $\omega$-regular expression recognized by $G$
        \State \Return $\bigcup_{f \in F}\left({\verb|dfa2regex_firstvisit|}(G, s, f){\verb|^dfa2regex|}(G, f, f) \right) $
    \end{algorithmic}
\end{algorithm}

\subsection{$\omega$-regex simplification} \label{regex-simplify}
The $\omega$-regular expression generated in \ref{aut2regex} may not be the ``simplest'' for the purpose of visualizing the timeline. We have observed multiple patterns in the resulting $\omega$-regular expression that could be simplified. For example, an $\omega$-regular expression in the form of $r^*r^{\omega}$ represents the same timeline as $r^{\omega}$, but the latter is more intuitive. For this purpose, we devised some simplification rules in our tool, based on our observation of common patterns in the generated $\omega$-regular expression.
\paragraph*{Rule-based simplification}
Here we show a demonstrating subset of simplification rules we encoded.
\begin{alignat*}{2}
        & r_1 + r_1r_2^* && \Longrightarrow r_1r_2^* \\
        & r + r && \Longrightarrow r \\
        & r_1 + r_2^*r_1 && \Longrightarrow r_2^*r_1 \\
        & (r^*)^{\omega} && \Longrightarrow r^{\omega} \\
        & (r_1r_2^*)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & (r_1r_2)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & r^*r^{\omega} && \Longrightarrow r^{\omega} \\
        & rr^{\omega} && \Longrightarrow r^{\omega}
\end{alignat*}
\paragraph*{Result of simplification}
Those simplification rules lead to more intuitive representation of timelines. Here we demonstrate their effects using an example. 
\begin{example}
    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((!a) | ((aa^*(!a)))((!a) | ((aa^*(!a)))^{\omega}$, and simplified version $((!a) | ((aa^*(!a)))^{\omega}$, which corresponds to the two timelines in figure \ref{fig:unsimplified} and \ref{fig:simplified}.
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.gv.png}
        \caption{Timeline for un-simplified $\omega$-regular expression $((!a) | ((aa^*(!a)))((!a) | ((aa^*(!a)))^{\omega}$}
        \label{fig:unsimplified}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.3]{examples/ex9/ex9.gv.png}
        \caption{Timeline for simplified $\omega$-regular expression $((!a) | ((aa^*(!a)))^{\omega}$}
        \label{fig:simplified}
    \end{figure}
\end{example}

\begin{remark}
    Both simplified and un-simplified $\omega$-regular expression would generate correct timeline representations. Correct as they faithfully represent the set of satisfying traces of the original \ltl\ formula $\Phi$. Nonetheless, we, as human user, oftentimes find the simplified version more intuitive to reason about.
\end{remark}

\subsection{$\omega$-regex to timeline} \label{regex2timeline}
Our tool uses Graphviz\cite{Ellson2001GraphvizO} to achieve the timeline visualization step. By construction of our algorithm, every $\omega$-regular expression is in the form of 
\[
    A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}
\]
where $A_i$ are regular expressions, and $A_{2i-1}$ could be $\epsilon$. On a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input. We view each union operator as parallel timelines, and each $A_{2i-1}$ is concatenated with $A_{2i}$ repeated infinitely many times, as represented in the grey box. Figure \ref{fig:timeline} presents a generic timeline resulting from this form of construction.
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{img/timeline.png}
    \caption{Generic timeline construction from $A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}$}
    \label{fig:timeline}
\end{figure}

\section{Theoretical Analyses}
\subsection{Correctness of Regex Translation}
\begin{lemma}
    % reduce_dfa does its input to output behaviour
    For any DFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_dfa}$(G, v)$ preserves the regular language accepted by $G$
\end{lemma}
\begin{proof}
    Let $G'$ be the graph of $G$ post reduction by the application of \textbf{reduce\_dfa}$(G, v)$. We show that the trace of every path accepted by $G$ is also accepted by $G'$. Suppose a path accepted by $G$ does not pass through $v$, clearly this is true. Else, suppose it passes through $v$, since $v$ is an interior node, $v$ cannot be the first or last in the path. Thus, for every pass through $v$, let $u\neq v$ be the last node passed before entering $v$, and likewise $w$ be the first node after exiting $v$. We show that the regular language of sub-traces from $u$ to $w$ in $G$ (shown in \cref{fig:uvw-dfa}) is identical to that in $G'$. 
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.5]{img/uvw-dfa.png}
        \caption{$u$ to $w$ path in $G$}
        \label{fig:uvw-dfa}
    \end{figure}
    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_{uv}}v\xrightarrow{r_{vw}}w$, with the trace $r=r_{uv}r_{vw}$. If there is a loop edge $r_{vv}$, this edge can be travelled any number of times before exiting $v$, thus the regular expression is $r=r_{uv}r_{vv}^*r_{vw}$. This edge $u\xrightarrow{r}w$ is added in $G'$. Thus, for every path accepted by $G$, for every subpath entering and exiting $v$ from some $u$ to $w$, there exists a corresponding subpath from $u$ to $w$ in $G'$, and thus a corresponding path accepted by $G'$. 
\end{proof}

\begin{lemma}
    For any DFA $G$ with start state $s$ and (exactly one) final state $f$, \textbf{dfa2regex}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$ (i.e., the language accepted by $G$)
\end{lemma}
\begin{proof}
    The while loop clearly terminates since the number of interior nodes is strictly decreasing, and upon termination, $G$ is a DFA containing only the nodes $s$ and $f$. Now, every non-terminal visit from $s$ to $f$ and back to $s$, can be replaced by an edge $s\xrightarrow{r_{sf}r_{ff}^* r_{fs}} s$, instead of the edge $f\to s$. This DFA yields the regular language $(r_{ss}|r_{sf}r_{ff}^* r_{fs})^* r_{sf} r_{ff}$, as outputted by the algorithm. 
\end{proof}

\begin{lemma}
    For any DFA $G$ with start state $s$ and (exactly one) final state $f$, \\\textbf{dfa2regex\_firstvisit}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$, visiting $f$ for the first time.
\end{lemma}
\begin{proof}
    Let $G'$ be $G$ with all out-edge (including loops) from $f$ deleted. We claim that $L(G')$ is equal to the language $L'$ of all paths from $s$ reaching $f$ for the first time.

    First we show $L(G') \subseteq L'$, i.e., every path accepted by $G'$ starts in $s$ and ends by reaching $f$ for the first time. Since $s$ and $f$ are the initial and final states of $G'$ respectively, clearly every path accepted by $G$ must start in $s$ and end in $f$. Further, as $f$ has no out-edges in $G$, any accepted path must end immediately once it reaches $f$. Thus it must end once it reaches $f$ for the first time.

    Also, we show $L' \subseteq L(G')$, i.e., every path starting in $s$ and ending by $f$ reaching $f$ for the first time is accepted by $G'$. If a path contains an out-edge of $f$, it cannot be in $L'$ as the trace continues beyond the first time step at $f$. Thus, every trace in $L'$ only uses edges in $G'$, and is thus accepted by $G$ iff it is accepted by $G'$. 
\end{proof}

\begin{theorem}
    For any \Buchi automaton $G$ with start state $s$ and final states $F$, \textbf{ba2wregex}$(G)$ outputs the $\omega$-regular language accepted by $G$
\end{theorem}
\begin{proof}
    We show that $L = \bigcup_{f\in F} \textbf{dfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{dfa2regex\_firstvisit}(G, f, f)\right)^\omega$ and the $\omega$-language accepted by $G$, $L_\omega(G)$ are identical.

    First, $L\subseteq L_\omega(G)$ since for every infinite run in $L$, clearly by definition of $L$, there is some $f\in F$ such that passes through $f$ infinitely often. The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often, thus the run is in $\textbf{dfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{dfa2regex\_firstvisit}(G, f, f)\right)^\omega$
\end{proof}
\subsection{Correctness of Rewrite Rules}
\begin{lemma}
    For all regular expressions $r_1, r_2, r$, each of the following rewrite rules preserve the regular or $\omega$-regular language represented by the expressions:
    \begin{alignat}{2}
        & r_1 + r_1r_2^* && \Longrightarrow r_1r_2^* \\
        & r + r && \Longrightarrow r \\
        & r_1 + r_2^*r_1 && \Longrightarrow r_2^*r_1 \\
        & (r^*)^{\omega} && \Longrightarrow r^{\omega} \\
        & (r_1r_2^*)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & (r_1r_2)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & r^*r^{\omega} && \Longrightarrow r^{\omega} \\
        & rr^{\omega} && \Longrightarrow r^{\omega}
    \end{alignat}
\end{lemma}

The soundness of each of these translations can be proven by reasoning about the  semantics detailed in \cref{def:omega-semantics}. A full proof is not provided at this time.

%\begin{theorem}
%    For any LTL formula $\phi$, 
%\end{theorem}

\section{Tool showcase}
To demonstrate the result of our tool, we present two examples, one from a real-world model checking example in \cite{ZR14} and one from a randomly generated \ltl\ formula.

\begin{example}
    \cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula 
    \[
    \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
    \]
    For simplicity, we swap the concrete atomic proposition to $a, b, c$ and get
    \[
    \always (a \land b \limplies \nextt (\neg b))
    \]
    For this \ltl\ formula, our tool generates the timeline representation in figure \ref{fig:ex14}.
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.3]{examples/ex14/ex14.gv.png}
        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
        \label{fig:ex14}
    \end{figure}
\end{example}

\begin{example}
    Spot \cite{SPOT-online} presents command-line tool for random \ltl\ formula generator \texttt{randltl}\cite{duret.13.atva}. The following \ltl\ formula is generated from this tool. 
    \[
    p_2 \land (\eventually (\always p_0 \strongrelease  1) \weakrelease \nextt(\always p_1 \land ((p_0 \liff p_2) \stronguntil \eventually p_0)))
    \]
    This formula is reasonably complicated, and hard for human to reason about directly. For this \ltl\ formula, our tool generates the timeline representation in figure \ref{fig:ex13}.
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.3]{examples/ex13/ex13.gv.png}
        \caption{Timeline for $p_2 \land (\eventually (\always p_0 \strongrelease  1) \weakrelease \nextt(\always p_1 \land ((p_0 \liff p_2) \stronguntil \eventually p_0)))$}
        \label{fig:ex13}
    \end{figure}
\end{example}
\begin{remark}
    These two examples show that our tool can generate reasonably clear diagrams for both real-world formula and randomly generated formula.
\end{remark}

\section{Artifact availability}
The tool we present in this paper is available at 
\[
\text{\url{https://github.com/EULIR/ltl-explainability}}
\]
which comes with two command-line tools, \texttt{ltl2regex} and \texttt{ltl2timeline}. The specific usage of the tool can be found  \href{https://github.com/EULIR/ltl-explainability#usage}{here}.

\section{Future work}
Based on our results, we raise the following questions as future works:
\begin{itemize}
    \item Can there be more simplifications methods as described in \ref{regex-simplify}? The answer is definitely positive. On one hand, more rule-based simplifications can be discovered by finding more patterns in the generated $\omega$-regular expressions. On the other hand, other simplification are possible: for example, if the generated $\omega$-regular expression is $r_1 + r_2$ where $r_1, r_2$ are not syntactically equivalent (or equivalent up to algebraic rules) $\omega$-regular expressions, but they accepts the same set of infinite-length strings, then we can simplify this down to just $r_1$. This reduce the problem to equivalence test on $\omega$-regular expressions, which is decidable. In the similar vein, many more simplifications can be used, but the question is how efficient are they? In the end, one have to balance trade-off between the efficiency of the tool and the simplicity of the result.
    %\item Our tool is effective at translating a wide range of LTL formulas. Even with LTL formulae with complex nesting structure are represented by relatively readable timeline visualizations. 
    \item Can we define timeline more formally so that one can do this process reversely (i.e. a tool that converts timeline representation to its corresponding \ltl\ formula)? That would be a very useful tool in practice. However, a direct reverse of the algorithm we presented in this paper may not be viable.
\end{itemize}

\section{Acknowledgement}
We sincerely appreciate the guidance of Professors Kristin Yvonne Rozier and Marijn Heule throughout our project.

\bibliography{Related Work}
% \cite{*} %?
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Typesetting instructions -- Summary}
\label{sec:typesetting-summary}

LIPIcs is a series of open access high-quality conference proceedings across all fields in informatics established in cooperation with Schloss Dagstuhl. 
In order to do justice to the high scientific quality of the conferences that publish their proceedings in the LIPIcs series, which is ensured by the thorough review process of the respective events, we believe that LIPIcs proceedings must have an attractive and consistent layout matching the standard of the series.
Moreover, the quality of the metadata, the typesetting and the layout must also meet the requirements of other external parties such as indexing service, DOI registry, funding agencies, among others. The guidelines contained in this document serve as the baseline for the authors, editors, and the publisher to create documents that meet as many different requirements as possible.

Please comply with the following instructions when preparing your article for a LIPIcs proceedings volume. 
\paragraph*{Minimum requirements}

\begin{itemize}
\item Use pdflatex and an up-to-date \LaTeX{} system.
\item Use further \LaTeX{} packages and custom made macros carefully and only if required.
\item Use the provided sectioning macros: \verb+\section+, \verb+\subsection+, \verb+\subsubsection+, \linebreak \verb+\paragraph+, \verb+\paragraph*+, and \verb+\subparagraph*+.
\item Provide suitable graphics of at least 300dpi (preferably in PDF format).
\item Use BibTeX and keep the standard style (\verb+plainurl+) for the bibliography.
\item Please try to keep the warnings log as small as possible. Avoid overfull \verb+\hboxes+ and any kind of warnings/errors with the referenced BibTeX entries.
\item Use a spellchecker to correct typos.
\end{itemize}

\paragraph*{Mandatory metadata macros}
Please set the values of the metadata macros carefully since the information parsed from these macros will be passed to publication servers, catalogues and search engines.
Avoid placing macros inside the metadata macros. The following metadata macros/environments are mandatory:
\begin{itemize}
\item \verb+\title+ and, in case of long titles, \verb+\titlerunning+.
\item \verb+\author+, one for each author, even if two or more authors have the same affiliation.
\item \verb+\authorrunning+ and \verb+\Copyright+ (concatenated author names)\\
The \verb+\author+ macros and the \verb+\Copyright+ macro should contain full author names (especially with regard to the first name), while \verb+\authorrunning+ should contain abbreviated first names.
\item \verb+\ccsdesc+ (ACM classification, see \url{https://www.acm.org/publications/class-2012}).
\item \verb+\keywords+ (a comma-separated list of keywords).
\item \verb+\relatedversion+ (if there is a related version, typically the ``full version''); please make sure to provide a persistent URL, e.\,g., at arXiv.
\item \verb+\begin{abstract}...\end{abstract}+ .
\end{itemize}

\paragraph*{Please do not \ldots} %Do not override the \texttt{\seriesstyle}-defaults}
Generally speaking, please do not override the \texttt{lipics-v2021}-style defaults. To be more specific, a short checklist also used by Dagstuhl Publishing during the final typesetting is given below.
In case of \textbf{non-compliance} with these rules Dagstuhl Publishing will remove the corresponding parts of \LaTeX{} code and \textbf{replace it with the \texttt{lipics-v2021} defaults}. In serious cases, we may reject the LaTeX-source and expect the corresponding author to revise the relevant parts.
\begin{itemize}
\item Do not use a different main font. (For example, the \texttt{times} package is forbidden.)
\item Do not alter the spacing of the \texttt{lipics-v2021.cls} style file.
\item Do not use \verb+enumitem+ and \verb+paralist+. (The \texttt{enumerate} package is preloaded, so you can use
 \verb+\begin{enumerate}[(a)]+ or the like.)
\item Do not use ``self-made'' sectioning commands (e.\,g., \verb+\noindent{\bf My+ \verb+Paragraph}+).
\item Do not hide large text blocks using comments or \verb+\iffalse+ $\ldots$ \verb+\fi+ constructions. 
\item Do not use conditional structures to include/exclude content. Instead, please provide only the content that should be published -- in one file -- and nothing else.
\item Do not wrap figures and tables with text. In particular, the package \texttt{wrapfig} is not supported.
\item Do not change the bibliography style. In particular, do not use author-year citations. (The
\texttt{natbib} package is not supported.)
\end{itemize}

\enlargethispage{\baselineskip}

This is only a summary containing the most relevant details. Please read the complete document ``LIPIcs: Instructions for Authors and the \texttt{lipics-v2021} Class'' for all details and don't hesitate to contact Dagstuhl Publishing (\url{mailto:publishing@dagstuhl.de}) in case of questions or comments:
\href{http://drops.dagstuhl.de/styles/lipics-v2021/lipics-v2021-authors/lipics-v2021-authors-guidelines.pdf}{\texttt{http://drops.dagstuhl.de/styles/lipics-v2021/\newline lipics-v2021-authors/lipics-v2021-authors-guidelines.pdf}}

\section{Lorem ipsum dolor sit amet}

Lorem ipsum dolor sit amet, consectetur adipiscing elit \cite{DBLP:journals/cacm/Knuth74}. Praesent convallis orci arcu, eu mollis dolor. Aliquam eleifend suscipit lacinia. Maecenas quam mi, porta ut lacinia sed, convallis ac dui. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse potenti. Donec eget odio et magna ullamcorper vehicula ut vitae libero. Maecenas lectus nulla, auctor nec varius ac, ultricies et turpis. Pellentesque id ante erat. In hac habitasse platea dictumst. Curabitur a scelerisque odio. Pellentesque elit risus, posuere quis elementum at, pellentesque ut diam. Quisque aliquam libero id mi imperdiet quis convallis turpis eleifend.

\begin{lemma}[Lorem ipsum]
\label{lemma:lorem}
Vestibulum sodales dolor et dui cursus iaculis. Nullam ullamcorper purus vel turpis lobortis eu tempus lorem semper. Proin facilisis gravida rutrum. Etiam sed sollicitudin lorem. Proin pellentesque risus at elit hendrerit pharetra. Integer at turpis varius libero rhoncus fermentum vitae vitae metus.
\end{lemma}

\begin{proof}
Cras purus lorem, pulvinar et fermentum sagittis, suscipit quis magna.

\proofsubparagraph*{Just some paragraph within the proof.}
Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
\begin{claim}
content...
\end{claim}
\begin{claimproof}
content...
    \begin{enumerate}
        \item abc abc abc \claimqedhere{}
    \end{enumerate}
\end{claimproof}

\end{proof}

\begin{corollary}[Curabitur pulvinar, \cite{DBLP:books/mk/GrayR93}]
\label{lemma:curabitur}
Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
\end{corollary}

\begin{proposition}\label{prop1}
This is a proposition
\end{proposition}

\autoref{prop1} and \cref{prop1} \ldots

\subsection{Curabitur dictum felis id sapien}

Curabitur dictum \cref{lemma:curabitur} felis id sapien \autoref{lemma:curabitur} mollis ut venenatis tortor feugiat. Curabitur sed velit diam. Integer aliquam, nunc ac egestas lacinia, nibh est vehicula nibh, ac auctor velit tellus non arcu. Vestibulum lacinia ipsum vitae nisi ultrices eget gravida turpis laoreet. Duis rutrum dapibus ornare. Nulla vehicula vulputate iaculis. Proin a consequat neque. Donec ut rutrum urna. Morbi scelerisque turpis sed elit sagittis eu scelerisque quam condimentum. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nec faucibus leo. Cras ut nisl odio, non tincidunt lorem. Integer purus ligula, venenatis et convallis lacinia, scelerisque at erat. Fusce risus libero, convallis at fermentum in, dignissim sed sem. Ut dapibus orci vitae nisl viverra nec adipiscing tortor condimentum \cite{DBLP:journals/cacm/Dijkstra68a}. Donec non suscipit lorem. Nam sit amet enim vitae nisl accumsan pretium.

\begin{lstlisting}[caption={Useless code.},label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount]
for i:=maxint to 0 do 
begin 
    j:=square(root(i));
end;
\end{lstlisting}

\subsection{Proin ac fermentum augue}

Proin ac fermentum augue. Nullam bibendum enim sollicitudin tellus egestas lacinia euismod orci mollis. Nulla facilisi. Vivamus volutpat venenatis sapien, vitae feugiat arcu fringilla ac. Mauris sapien tortor, sagittis eget auctor at, vulputate pharetra magna. Sed congue, dui nec vulputate convallis, sem nunc adipiscing dui, vel venenatis mauris sem in dui. Praesent a pretium quam. Mauris non mauris sit amet eros rutrum aliquam id ut sapien. Nulla aliquet fringilla sagittis. Pellentesque eu metus posuere nunc tincidunt dignissim in tempor dolor. Nulla cursus aliquet enim. Cras sapien risus, accumsan eu cursus ut, commodo vel velit. Praesent aliquet consectetur ligula, vitae iaculis ligula interdum vel. Integer faucibus faucibus felis.

\begin{itemize}
\item Ut vitae diam augue. 
\item Integer lacus ante, pellentesque sed sollicitudin et, pulvinar adipiscing sem. 
\item Maecenas facilisis, leo quis tincidunt egestas, magna ipsum condimentum orci, vitae facilisis nibh turpis et elit. 
\end{itemize}

\begin{remark}
content...
\end{remark}

\section{Pellentesque quis tortor}

Nec urna malesuada sollicitudin. Nulla facilisi. Vivamus aliquam tempus ligula eget ornare. Praesent eget magna ut turpis mattis cursus. Aliquam vel condimentum orci. Nunc congue, libero in gravida convallis \cite{DBLP:conf/focs/HopcroftPV75}, orci nibh sodales quam, id egestas felis mi nec nisi. Suspendisse tincidunt, est ac vestibulum posuere, justo odio bibendum urna, rutrum bibendum dolor sem nec tellus.

\begin{lemma} [Quisque blandit tempus nunc]
Sed interdum nisl pretium non. Mauris sodales consequat risus vel consectetur. Aliquam erat volutpat. Nunc sed sapien ligula. Proin faucibus sapien luctus nisl feugiat convallis faucibus elit cursus. Nunc vestibulum nunc ac massa pretium pharetra. Nulla facilisis turpis id augue venenatis blandit. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
\end{lemma}

Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.

\section{Morbi eros magna}

Morbi eros magna, vestibulum non posuere non, porta eu quam. Maecenas vitae orci risus, eget imperdiet mauris. Donec massa mauris, pellentesque vel lobortis eu, molestie ac turpis. Sed condimentum convallis dolor, a dignissim est ultrices eu. Donec consectetur volutpat eros, et ornare dui ultricies id. Vivamus eu augue eget dolor euismod ultrices et sit amet nisi. Vivamus malesuada leo ac leo ullamcorper tempor. Donec justo mi, tempor vitae aliquet non, faucibus eu lacus. Donec dictum gravida neque, non porta turpis imperdiet eget. Curabitur quis euismod ligula.

%%
%% Bibliography
%%

%% Please use bibtex,

\bibliography{RelatedWork}

\appendix

\section{Styles of lists, enumerations, and descriptions}\label{sec:itemStyles}

List of different predefined enumeration styles:

\begin{itemize}
\item \verb|\begin{itemize}...\end{itemize}|
\item \dots
\item \dots
%\item \dots
\end{itemize}

\begin{enumerate}
\item \verb|\begin{enumerate}...\end{enumerate}|
\item \dots
\item \dots
%\item \dots
\end{enumerate}

\begin{alphaenumerate}
\item \verb|\begin{alphaenumerate}...\end{alphaenumerate}|
\item \dots
\item \dots
%\item \dots
\end{alphaenumerate}

\begin{romanenumerate}
\item \verb|\begin{romanenumerate}...\end{romanenumerate}|
\item \dots
\item \dots
%\item \dots
\end{romanenumerate}

\begin{bracketenumerate}
\item \verb|\begin{bracketenumerate}...\end{bracketenumerate}|
\item \dots
\item \dots
%\item \dots
\end{bracketenumerate}

\begin{description}
\item[Description 1] \verb|\begin{description} \item[Description 1]  ...\end{description}|
\item[Description 2] Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\item[Description 3]  \dots
%\item \dots
\end{description}

\cref{testenv-proposition} and \autoref{testenv-proposition} ...

\section{Theorem-like environments}\label{sec:theorem-environments}

List of different predefined enumeration styles:

\begin{theorem}\label{testenv-theorem}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{theorem}

\begin{lemma}\label{testenv-lemma}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{lemma}

\begin{corollary}\label{testenv-corollary}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{corollary}

\begin{proposition}\label{testenv-proposition}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{proposition}

\begin{conjecture}\label{testenv-conjecture}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{conjecture}

\begin{observation}\label{testenv-observation}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{observation}

\begin{exercise}\label{testenv-exercise}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{exercise}

\begin{definition}\label{testenv-definition}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{definition}

\begin{example}\label{testenv-example}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{example}

\begin{note}\label{testenv-note}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{note}

\begin{note*}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{note*}

\begin{remark}\label{testenv-remark}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{remark}

\begin{remark*}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{remark*}

\begin{claim}\label{testenv-claim}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{claim}

\begin{claim*}\label{testenv-claim2}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{claim*}

\begin{proof}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{proof}

\begin{claimproof}
Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\end{claimproof}

\end{document}
Footer
© 2022 GitHub, Inc.
Footer navigation

    Terms
    Privacy
    Security
    Status
    Docs
    Contact GitHub
    Pricing
    API
    Training
    Blog
    About

styles/lipics-v2021-sample-article.tex at master · dagstuhl-publishing/styles

### 2022-12-27 paper/slide.tex
added paper

\documentclass[handout]{beamer}
\usetheme{Boadilla}
\usepackage[backend=biber,style=numeric-comp,isbn=true]{biblatex}

\addbibresource{RelatedWork.bib}
\setbeamercolor*{bibliography entry title}{parent=palette primary}

\usepackage{mathpartir}
\usepackage{listings}
\usepackage{tikz}
\usepackage{wasysym}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{scalerel}

\usetikzlibrary{arrows.meta,
                chains,
                positioning,
                shapes.geometric
                }

\lstdefinelanguage{dtt}{
    keywords={contract, library, function, public, storage, memory, msg, sender, payable, return, revert, if, event, indexed, external, emit},
    keywordstyle=\color{blue}\bfseries,
    ndkeywords={uint, address, bool, mapping, bytes, uint256},
    ndkeywordstyle=\color{purple},
    identifierstyle=\color{black},
    sensitive=false,
    comment=[l]{//},
    morecomment=[s]{(*}{*)},
    commentstyle=\color{brown}\ttfamily,
    stringstyle=\color{red}\ttfamily,
    morestring=[b]',
    morestring=[b]",
    showstringspaces=false,
    literate={->}{$\rightarrow\ $}1
}

\lstset{
    basicstyle=\ttfamily\tiny,
    language=dtt
}
\newcommand{\code}[1]{\lstinline!#1!}
\newcommand{\colorcite}[2]{\textcolor{blue}{\cite[#1]{#2}}}
\newcommand{\always}{\textcolor{red}{\text{ALWAYS }}}
\newcommand{\nextt}{\textcolor{red}{\text{NEXT }}}
\newcommand{\even}{\textcolor{red}{\text{EVENTUALLY }}}
\newcommand{\alwaysf}{\Box}
\newcommand{\nexttf}{\mathcal{X}}
\newcommand{\evenf}{\Diamond}
\newcommand{\stronguntil}{\hspace{0.1cm} \mathcal{U}  \hspace{0.1cm}}
\newcommand{\strongrelease}{\hspace{0.1cm} \mathcal{M} \hspace{0.1cm}}
\newcommand{\weakuntil}{\hspace{0.1cm} \mathcal{W} \hspace{0.1cm}}
\newcommand{\weakrelease}{\hspace{0.1cm} \mathcal{R} \hspace{0.1cm}}
\newcommand{\Buchi}{B\"{u}chi }
\newcommand{\limplies}{\rightarrow}
\newcommand{\liff}{\leftrightarrow}
\DeclareMathOperator*{\bigplus}{\scalerel*{+}{\sum}}

% section slides
\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

\makeatother
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor%~~(\insertshortinstitute)
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot} Linear Temporal Logic Visualization
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
    \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
    \insertframenumber{} / \inserttotalframenumber\hspace*{2ex}
  \end{beamercolorbox}}%
  \vskip0pt%
}
\makeatletter

\title{What's in a Name? Linear Temporal Logic Literally Represents Time Lines}
\subtitle{Project Report for 15-816}
\author{Runming Li \& Keerthana Gurushankar}
\institute[]{Carnegie Mellon University \\ \{runmingl, kgurusha\}@andrew.cmu.edu\\
Mentored by Kristin Yvonne Rozier \& Marijn Heule}
\date{December 14, 2022}

\begin{document}
\maketitle

\begin{frame}{What is LTL?}
    \begin{align*}
        a ::= & p \mid q \mid r \mid \cdots \tag{atomic propositions} \\
        \Phi ::= & a \tag{atomic} \\
        \mid & \neg \Phi \tag{negation} \\ 
        \mid & \Phi \vee \Phi \tag{disjunction} \\
        \mid & \Phi \wedge \Phi \tag{conjunction} \\
        \mid & \Phi \rightarrow \Phi \tag{implication} \\
        \mid & \alwaysf \Phi \tag{always} \\
        \mid & \evenf \Phi \tag{eventually} \\
        \mid & \nexttf \Phi \tag{next}
    \end{align*}
    $\alwaysf \Phi = \Phi$ is \always true \\
    $\evenf \Phi = \Phi$ is \even true \\
    $\nexttf \Phi = \Phi$ is true in the \nextt time step\footnote{Other temporal connectives untils ($\stronguntil, \weakuntil$) and releases ($\strongrelease, \weakrelease$) are omitted} 
\end{frame}

\begin{frame}{Can you tell the difference?\footnote{slide adapted from Rozier}}
A NASA Rocket Scientist was given this English specification:

``\textbf{p oscillates every time step}''

She wrote two possible LTL formulas:
\[
    \Phi = \always ((p \wedge \nextt \neg p) \vee (\neg p \wedge \nextt p))
\]
\[
    \Psi = \always ((p \wedge \nextt \neg p) \wedge (\neg p \wedge \nextt p))
\]

Which one is correct?    
\end{frame}

\begin{frame}{Which one is correct?}
    $\Phi =$
    \begin{figure}
        \centering
        \includegraphics[scale=0.6]{examples/ex2/ex2.gv.png}
        \caption{Timeline representation for formula $\Phi$}
    \end{figure}

    $\Psi =$

   \begin{figure}
        \centering
        \includegraphics[scale=0.6]{examples/ex3/ex3.gv.png}
        \caption{Timeline representation for formula $\Psi$}
    \end{figure}
\end{frame}

\begin{frame}{LTL to Timeline Conversion}
    Our contribution: an algorithm and a tool that converts any LTL formula into its corresponding timeline
    \begin{itemize}
        \item LTL to state-based \Buchi Automata (BA)
        \item BA to $\omega$-regular expression
        \item Heuristics based $\omega$-regular expression simplification
        \item $\omega$-regular expression to timeline
    \end{itemize}
    \begin{figure}
        \centering
        \includegraphics[scale=0.45]{img/algo-flowchart.png}
        %\caption{Caption}
        \label{fig:my_label}
    \end{figure}
\end{frame}

\begin{frame}{LTL to state-based \Buchi Automata (BA)}
    \Buchi Automata: the normal automata you know, except for the accepting condition

    \begin{figure}
        \centering
        \includegraphics[scale=0.5]{img/buchi-ex.png}
        \caption{Example \Buchi Automata for $\alwaysf ((p \wedge \nexttf \neg p) \vee (\neg p \wedge \nexttf p))$}
    \end{figure}

    This step is very well-studied \cite{Dur22} and our tool uses \textit{Spot}.
\end{frame}

\begin{frame}{BA to $\omega$-regular expression}
    \begin{definition}{Regular expression \& $\omega$-regular expression}
        \begin{align*}
            A & ::= \epsilon \mid \emptyset \mid p (\in \Sigma) \mid AA \mid A + A \mid A^* \\
            B & ::= A^{\omega} \mid AB \mid B + B
        \end{align*}
        Our $\Sigma$ is the set of propositional logic formula.
    \end{definition}

    \begin{definition}
        $A_{(s, f)}^0$ represents the regular expression that corresponds to all paths from state $s$ reaching state $f$ for the first time

        $A_{(s, f)}^1$ represents the regular expression that corresponds to all paths from state $s$ reaching state $f$
    \end{definition}
\end{frame}

\begin{frame}{BA to $\omega$-regular expression, cont}
    \[
        B = \bigplus_{f \in F} A_{(s, f)}^0 (A_{(f, f)}^1)^{\omega}
    \]
    \begin{example}
        \begin{figure}
        \centering
        \includegraphics[scale=0.5]{img/buchi-ex.png}
        \caption{Example \Buchi Automata for $\alwaysf ((p \wedge \nexttf \neg p) \vee (\neg p \wedge \nexttf p))$}
    \end{figure}
    Generated $\omega$-regular expression:
    \[
        (p(!pp)^{\omega}) + (!p(p!p)^{\omega})
    \]
    \end{example}
\end{frame}

\begin{frame}{Heuristics based $\omega$-regular expression simplification}
    The $\omega$-regular expression generated may not be the ``simplest'' to visualize.
    \begin{alignat*}{2}
        & r_1 + r_1r_2^* && \Longrightarrow r_1r_2^* \\
        & r + r && \Longrightarrow r \\
        & r_1 + r_2^*r_1 && \Longrightarrow r_2^*r_1 \\
        & (r^*)^{\omega} && \Longrightarrow r^{\omega} \\
        & (r_1r_2^*)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & (r_1r_2)r_2^{\omega} && \Longrightarrow r_1r_2^{\omega} \\
        & r^*r^{\omega} && \Longrightarrow r^{\omega} \\
        & rr^{\omega} && \Longrightarrow r^{\omega}
    \end{alignat*}
\end{frame}

\begin{frame}{Heuristics based $\omega$-regular expression simplification, cont}
    \begin{example}
        $\Phi = \alwaysf (a \limplies \evenf (\neg a))$
    \begin{figure}
        \centering
        \includegraphics[scale=0.25]{examples/ex9/ex9-unsimplified.gv.png}
        \caption{Timeline for un-simplified $\omega$-regex $((!a) | ((aa^*(!a)))((!a) | ((aa^*(!a)))^{\omega}$}
    \end{figure}
    \begin{figure}
        \centering
        \includegraphics[scale=0.25]{examples/ex9/ex9.gv.png}
        \caption{Timeline for simplified $\omega$-regex $((!a) | ((aa^*(!a)))^{\omega}$}
    \end{figure}
    \end{example}
\end{frame}

\begin{frame}{$\omega$-regular expression to timeline}
    Every $\omega$-regular we generate is the form of 
    \[
        A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}
    \]
    % Every regular expression $A_i$ is visualized as a set of finite length strings.
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{img/timeline.png}
        \caption{Generic timeline representation for arbitrary $\omega$-regular expression}
    \end{figure}
    Out tool uses Graphviz \cite{Ellson2001GraphvizO} for visualization. 
\end{frame}

\begin{frame}{Tool showcase}
    \begin{example}
        $\Phi = \alwaysf (a \limplies \nexttf b)$

        ``A message on the controllers monitor indicates when the aircraft has cleared the conflict and control of the aircraft is handed off to the controllers.''\cite{ZR14}

        \begin{figure}
            \centering
            \includegraphics[scale=0.25]{examples/ex4/ex4.gv.png}
            \caption{Timeline for $\Phi = \alwaysf (a \limplies \nexttf b)$}
            \label{fig:my_label}
        \end{figure}
    \end{example}
\end{frame}

\begin{frame}{Tool showcase, cont}
    \begin{example}
        $\Phi = p_2 \land (\evenf (\alwaysf p_0 \strongrelease  1) \weakrelease \nexttf(\alwaysf p_1 \land ((p_0 \liff p_2) \stronguntil \evenf p_0)))$

        A randomly generated LTL formula

        \begin{figure}
            \centering
            \includegraphics[scale=0.25]{examples/ex13/ex13.gv.png}
            \caption{Timeline for $\Phi = p_2 \land (\evenf (\alwaysf p_0 \strongrelease  1) \weakrelease \nexttf(\alwaysf p_1 \land ((p_0 \liff p_2) \stronguntil \evenf p_0)))$}
        \end{figure}
    \end{example}
\end{frame}

\begin{frame}
    \frametitle{References}
    \printbibliography
\end{frame}

\end{document}

### 2022-12-28 paper/main.tex
figs 2, 6 to graphviz
port to elsarticle style

@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
-%This is a template for producing LIPIcs articles. 
-%See lipics-v2021-authors-guidelines.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling cleveref support, use "cleveref"
-%for enabling autoref support, use "autoref"
-%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
-%for enabling thm-restate support, use "thm-restate"
-%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
-%for producing a PDF according the PDF/A standard, add "pdfa"
+\documentclass[preprint,12pt]{elsarticle}
+\journal{Journal of Computer Languages}
 
-%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+\usepackage{amsmath, amssymb, amsthm}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{lemma}{Lemma}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{example}{Example}[section]
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}[section]
 
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
-
-\title{What's in a Name? Linear Temporal Logic Literally Represents Time Lines} %TODO Please add
-
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
-
-\author{Runming Li\thanks{These authors contributed equally to this work}}{Carnegie Mellon University, USA}{runmingl@andrew.cmu.edu}{https://orcid.org/0000-0001-7600-9069}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
-Please provide at least the name of the affiliation and the country.
-The full address is optional.
-Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.
-
-\author{Keerthana Gurushankar\footnotemark[1]}{Carnegie Mellon University, USA}{kgurusha@andrew.cmu.edu}{[orcid]}{}
-
-\authorrunning{Li and Gurushankar} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
-
-\Copyright{Runming Li and Keerthana Gurushankar} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\begin{CCSXML}
-<ccs2012>
-   <concept>
-       <concept_id>10003752.10003766.10003770</concept_id>
-       <concept_desc>Theory of computation~Automata over infinite objects</concept_desc>
-       <concept_significance>500</concept_significance>
-       </concept>
-   <concept>
-       <concept_id>10003752.10003766.10003776</concept_id>
-       <concept_desc>Theory of computation~Regular languages</concept_desc>
-       <concept_significance>300</concept_significance>
-       </concept>
-   <concept>
-       <concept_id>10003752.10003790.10003793</concept_id>
-       <concept_desc>Theory of computation~Modal and temporal logics</concept_desc>
-       <concept_significance>500</concept_significance>
-       </concept>
-   <concept>
-       <concept_id>10003752.10003790.10002990</concept_id>
-       <concept_desc>Theory of computation~Logic and verification</concept_desc>
-       <concept_significance>300</concept_significance>
-       </concept>
- </ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Theory of computation~Automata over infinite objects}
-\ccsdesc[300]{Theory of computation~Regular languages}
-\ccsdesc[500]{Theory of computation~Modal and temporal logics}
-\ccsdesc[300]{Theory of computation~Logic and verification}
-
-\keywords{Linear Temporal Logic, \Buchi automata, $\omega$-regular expression, model checking, visualization} %TODO mandatory; please add comma-separated list of keywords
-
-\category{} %optional, e.g. invited paper
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{}
-\EventNoEds{1}
-\EventLongTitle{}
-\EventShortTitle{}
-\EventAcronym{}
-\EventYear{}
-\EventDate{}
-\EventLocation{}
-\EventLogo{}
-\SeriesVolume{}
-\ArticleNo{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{algorithm, algpseudocode, amsmath, amsfonts, scalerel}
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,  
-    urlcolor=blue,
-    linkcolor=blue,
-    citecolor=blue,
-    pdfpagemode=FullScreen,
-    }
+\usepackage{algorithm, algpseudocode}
 \algrenewcommand\algorithmicrequire{\textbf{Input:}}
 \algrenewcommand\algorithmicensure{\textbf{Output:}}
-\crefname{algocf}{alg.}{algs.}
-\Crefname{algocf}{Algorithm}{Algorithms}
+
+\usepackage{scalerel}
+\DeclareMathOperator*{\bigplus}{\scalerel*{+}{\sum}}
+
+\usepackage[strings]{underscore} % fixes doi underscores
+
+\usepackage{hyperref} % brings up so many errors
+\usepackage[capitalise, noabbrev]{cleveref}
 
@@
 \newcommand{\liff}{\leftrightarrow}
-\DeclareMathOperator*{\bigplus}{\scalerel*{+}{\sum}}
-
-% hyperref must go last
-\usepackage{hyperref}
-% but cleveref goes "laster" than hyperref
-\usepackage[capitalise,noabbrev]{cleveref}
-\providecommand\algorithmname{algorithm}
-\crefname{algocf}{alg.}{algs.}
-\Crefname{algocf}{Algorithm}{Algorithms}
 
@@
 
-\maketitle
+\begin{frontmatter}
+    \title{What's in a Name? Linear Temporal Logic Literally Represents Time Lines}
 
-%TODO mandatory: add short abstract of the document
+    \author[inst1]{Runming Li}
+    \ead{runmingl@andrew.cmu.edu}
+
+    \author[inst1]{Keerthana Gurushankar}
+    \ead{kgurusha@andrew.cmu.edu}
+
+    \author[inst2]{Kristin Y. Rozier}
+    \ead{kyrozier@iastate.edu}
+
+    \author[inst1]{Marijn Heule \corref{cor1}}
+    \ead{marijn@cmu.edu}
+
+    \affiliation[inst1]{organization={Carnegie Mellon University},%Department and Organization
+                addressline={5032 Forbes Ave}, 
+                city={Pittsburgh},
+                postcode={15213}, 
+                state={PA},
+                country={USA}}
+
+    \affiliation[inst2]{organization={Iowa State University},%Department and Organization
+                %addressline={Address Two}, 
+                city={Ames},
+                postcode={50010}, 
+                state={IA},
+                country={USA}}
+
+    \cortext[cor1]{Corresponding author}
+
     \begin{abstract}
@@
     \end{abstract}
+
+    \begin{highlights} %TODO
+        \item Research highlight 1
+        \item Research highlight 2
+    \end{highlights}
+
+    \begin{keyword}
+        Modal and Temporal Logics 
+        \sep Logic and Verification
+        \sep Regular languages
+    \end{keyword}
+\end{frontmatter}
 
@@
 
-However, \ltl\ is a literally a language of timelines, so timeline visualizations have the potential to be a powerful tool for representing \ltl\ formulas in an intuitive manner.
+However, \ltl\ is literally a language of timelines, so timeline visualizations have the potential to be a powerful tool for representing \ltl\ formulas in an intuitive manner.
 In this paper, we propose such a timeline visualization tool, using regular expressions, to effectively represent a wide range of \ltl-based formulas.
@@
 \begin{remark}
-    The definition of \ltl\ can be extended to allow release and until as shown below, but they are definable using connectives in \ref{ltl-defn}, hence they are omitted in the definition.
+    The definition of \ltl\ can be extended to allow release and until as shown below, but they are definable using connectives in \cref{ltl-defn}, hence they are omitted in the definition.
 The tool we present in this paper, however, does support those operators.
@@
         \item a partial function $\delta : Q\times \Sigma \to Q$, called the transition function
-        \item an initial or start stae called $s\in Q$
+        \item an initial or start state called $s\in Q$
         \item a set of accept states $F \subseteq Q$
@@
 \end{definition}
+
 \subsection{$\omega$-regular expression}
@@
 The lower timeline starts with one step of $!p$ and one step of $p$ outside the grey box, and then enter the infinite run of $!p$ and $p$ repeating.
-    \begin{figure}[h!]
+    \begin{figure}[!h]
         \centering
@@
 \section{Algorithm}
-On a high level, our algorithm of converting \ltl\ formula into timeline visualization works as follows:
+On a high level, our algorithm of converting \ltl\ formulas into timeline visualization works as follows:
 \begin{enumerate}
-    \item Convert \ltl\ formula to its corresponding \Buchi automata \ref{ltl2aut}
-    \item Derive the $\omega$-regular expression corresponding to the \Buchi automata \ref{aut2regex}
-    \item Simplify the derived $\omega$-regular expression \ref{regex-simplify}
-    \item Visualize the $\omega$-regular expression according to its structure \ref{regex2timeline}
+    \item Convert the given \ltl\ formula to its corresponding \Buchi automata % (as detailed in \cref{ltl2aut})
+    \item Derive the $\omega$-regular expression corresponding to the \Buchi automata % (in \cref{aut2regex})
+    \item Simplify the derived $\omega$-regular expression % (in \cref{regex-simplify})
+    \item Visualize the $\omega$-regular expression according to its structure %(in \cref{regex2timeline})
 \end{enumerate}
@@
     \centering
-    \includegraphics[scale=0.5]{img/algo-flowchart.png}
+    \includegraphics[width=\textwidth, trim=1cm 3cm 1cm 3cm, clip]{img/algorithm_outline.gv.pdf}
     \caption{Algorithm outline}
@@
 \end{figure}
+
 \subsection{LTL to BA} \label{ltl2aut}
-The translation from LTL formulas to \Buchi automata is provided by SPOT\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.}.
+The translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.}.
 
 \subsection{BA to $\omega$-regex} \label{aut2regex}
-
 We translate \Buchi automata to $\omega$-regular expressions by first finding the regular expressions for paths from the start state to some final state (say $r_{sf}$), and for those for paths for looping from the final state back to itself (say $r_{ff}$), and finally combining those to form the $\omega$-expression for valid runs ($\bigplus_{f\in F} r_{sf}r_{ff}^\omega$).
@@
 \end{algorithm}
+
 \begin{algorithm}[h!]
@@
         \Ensure The $\omega$-regular expression recognized by $G$
-        \State \Return $\bigcup_{f \in F}\left({\verb|dfa2regex_firstvisit|}(G, s, f){\verb|^dfa2regex|}(G, f, f) \right) $
+        \State \Return $\bigcup_{f \in F}\left(\text{dfa2regex\_firstvisit}(G, s, f)\text{\^{}dfa2regex}(G, f, f) \right) $
     \end{algorithmic}
@@
 \subsection{$\omega$-regex simplification} \label{regex-simplify}
-The $\omega$-regular expression generated in \ref{aut2regex} may not be the ``simplest'' for the purpose of visualizing the timeline.
+
+The $\omega$-regular expression generated in \cref{aut2regex} may not be the ``simplest'' for the purpose of visualizing the timeline.
 We have observed multiple patterns in the resulting $\omega$-regular expression that could be simplified.
@@
 For this purpose, we devised some simplification rules in our tool, based on our observation of common patterns in the generated $\omega$-regular expression.
+
 \paragraph*{Rule-based simplification}
@@
 \end{alignat*}
+
 \paragraph*{Result of simplification}
 Those simplification rules lead to more intuitive representation of timelines. Here we demonstrate their effects using an example.
+
 \begin{example}
-    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((!a) | ((aa^*(!a)))((!a) | ((aa^*(!a)))^{\omega}$, and simplified version $((!a) | ((aa^*(!a)))^{\omega}$, which corresponds to the two timelines in figure \ref{fig:unsimplified} and \ref{fig:simplified}.
+    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((!a) | ((aa^*(!a)))((!a) | ((aa^*(!a)))^{\omega}$, and simplified version $((!a) | ((aa^*(!a)))^{\omega}$, which corresponds to the two timelines in figure \cref{fig:unsimplified} and \cref{fig:simplified}.
     \begin{figure}[h!]
@@
 \subsection{$\omega$-regex to timeline} \label{regex2timeline}
-Our tool uses Graphviz\cite{Ellson2001GraphvizO} to achieve the timeline visualization step. By construction of our algorithm, every $\omega$-regular expression is in the form of 
+Our tool uses Graphviz~\cite{Ellson2001GraphvizO} to achieve the timeline visualization step. By construction of our algorithm, every $\omega$-regular expression is in the form of 
 \[
@@
 We view each union operator as parallel timelines, and each $A_{2i-1}$ is concatenated with $A_{2i}$ repeated infinitely many times, as represented in the grey box.
-Figure \ref{fig:timeline} presents a generic timeline resulting from this form of construction.
+\cref{fig:timeline} presents a generic timeline resulting from this form of construction.
 \begin{figure}[h!]
@@
         \centering
-        \includegraphics[scale=0.5]{img/uvw-dfa.png}
+        \includegraphics[scale=0.75]{img/uvw_dfa.gv.pdf}
         \caption{$u$ to $w$ path in $G$}
@@
 \begin{lemma}
-    For any DFA $G$ with start state $s$ and (exactly one) final state $f$, \\\textbf{dfa2regex\_firstvisit}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$, visiting $f$ for the first time.
+    For any DFA $G$ with start state $s$ and (exactly one) final state $f$, \textbf{dfa2regex\_firstvisit}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$, visiting $f$ for the first time.
 \end{lemma}
@@
 \begin{proof}
-    We show that $L = \bigcup_{f\in F} \textbf{dfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{dfa2regex\_firstvisit}(G, f, f)\right)^\omega$ and the $\omega$-language accepted by $G$, $L_\omega(G)$ are identical.
+    We show that 
+    \[
+        L = \bigcup_{f\in F} \textbf{dfa2regex}(G, s, f) \verb|^| \left(\textbf{dfa2regex\_firstvisit}(G, f, f)\right)^\omega
+    \]
+    and the $\omega$-language accepted by $G$, $L_\omega(G)$ are identical.
 
@@
 The soundness of each of these translations can be proven by reasoning about the  semantics detailed in \cref{def:omega-semantics}. A full proof is not provided at this time.
-
-%\begin{theorem}
-%    For any LTL formula $\phi$, 
-%\end{theorem}
 
@@
 \begin{example}
-    Spot \cite{SPOT-online} presents command-line tool for random \ltl\ formula generator \texttt{randltl}\cite{duret.13.atva}. The following \ltl\ formula is generated from this tool. 
+    Spot~\cite{SPOT-online} presents command-line tool for random \ltl\ formula generator \texttt{randltl}~\cite{duret.13.atva}. The following \ltl\ formula is generated from this tool. 
     \[
@@
     \]
-    This formula is reasonably complicated, and hard for human to reason about directly. For this \ltl\ formula, our tool generates the timeline representation in figure \ref{fig:ex13}.
+    This formula is reasonably complicated, and hard for human to reason about directly. For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex13}.
     \begin{figure}[h!]
@@
 \[
-\text{\url{https://github.com/EULIR/ltl-explainability}}
+    \texttt{\url{https://github.com/EULIR/ltl-explainability}}
 \]
@@
 
-\section{Acknowledgement}
-We sincerely appreciate the guidance of Professors Kristin Yvonne Rozier and Marijn Heule throughout our project.
+\section{Conclusion}
+To add. % Journal also asks for a Discussion section
 
-\bibliography{Related Work}
-% \cite{*} %?
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Typesetting instructions -- Summary}
-\label{sec:typesetting-summary}
-
-LIPIcs is a series of open access high-quality conference proceedings across all fields in informatics established in cooperation with Schloss Dagstuhl. 
-In order to do justice to the high scientific quality of the conferences that publish their proceedings in the LIPIcs series, which is ensured by the thorough review process of the respective events, we believe that LIPIcs proceedings must have an attractive and consistent layout matching the standard of the series.
-Moreover, the quality of the metadata, the typesetting and the layout must also meet the requirements of other external parties such as indexing service, DOI registry, funding agencies, among others.
-The guidelines contained in this document serve as the baseline for the authors, editors, and the publisher to create documents that meet as many different requirements as possible.
-
-Please comply with the following instructions when preparing your article for a LIPIcs proceedings volume. 
-\paragraph*{Minimum requirements}
-
-\begin{itemize}
-\item Use pdflatex and an up-to-date \LaTeX{} system.
-\item Use further \LaTeX{} packages and custom made macros carefully and only if required.
-\item Use the provided sectioning macros: \verb+\section+, \verb+\subsection+, \verb+\subsubsection+, \linebreak \verb+\paragraph+, \verb+\paragraph*+, and \verb+\subparagraph*+.
-\item Provide suitable graphics of at least 300dpi (preferably in PDF format).
-\item Use BibTeX and keep the standard style (\verb+plainurl+) for the bibliography.
-\item Please try to keep the warnings log as small as possible. Avoid overfull \verb+\hboxes+ and any kind of warnings/errors with the referenced BibTeX entries.
-\item Use a spellchecker to correct typos.
-\end{itemize}
-
-\paragraph*{Mandatory metadata macros}
-Please set the values of the metadata macros carefully since the information parsed from these macros will be passed to publication servers, catalogues and search engines.
-Avoid placing macros inside the metadata macros. The following metadata macros/environments are mandatory:
-\begin{itemize}
-\item \verb+\title+ and, in case of long titles, \verb+\titlerunning+.
-\item \verb+\author+, one for each author, even if two or more authors have the same affiliation.
-\item \verb+\authorrunning+ and \verb+\Copyright+ (concatenated author names)\\
-The \verb+\author+ macros and the \verb+\Copyright+ macro should contain full author names (especially with regard to the first name), while \verb+\authorrunning+ should contain abbreviated first names.
-\item \verb+\ccsdesc+ (ACM classification, see \url{https://www.acm.org/publications/class-2012}).
-\item \verb+\keywords+ (a comma-separated list of keywords).
-\item \verb+\relatedversion+ (if there is a related version, typically the ``full version''); please make sure to provide a persistent URL, e.\,g., at arXiv.
-\item \verb+\begin{abstract}...\end{abstract}+ .
-\end{itemize}
-
-\paragraph*{Please do not \ldots} %Do not override the \texttt{\seriesstyle}-defaults}
-Generally speaking, please do not override the \texttt{lipics-v2021}-style defaults.
-To be more specific, a short checklist also used by Dagstuhl Publishing during the final typesetting is given below.
-In case of \textbf{non-compliance} with these rules Dagstuhl Publishing will remove the corresponding parts of \LaTeX{} code and \textbf{replace it with the \texttt{lipics-v2021} defaults}.
-In serious cases, we may reject the LaTeX-source and expect the corresponding author to revise the relevant parts.
-\begin{itemize}
-\item Do not use a different main font. (For example, the \texttt{times} package is forbidden.)
-\item Do not alter the spacing of the \texttt{lipics-v2021.cls} style file.
-\item Do not use \verb+enumitem+ and \verb+paralist+. (The \texttt{enumerate} package is preloaded, so you can use
- \verb+\begin{enumerate}[(a)]+ or the like.)
-\item Do not use ``self-made'' sectioning commands (e.\,g., \verb+\noindent{\bf My+ \verb+Paragraph}+).
-\item Do not hide large text blocks using comments or \verb+\iffalse+ $\ldots$ \verb+\fi+ constructions. 
-\item Do not use conditional structures to include/exclude content. Instead, please provide only the content that should be published -- in one file -- and nothing else.
-\item Do not wrap figures and tables with text. In particular, the package \texttt{wrapfig} is not supported.
-\item Do not change the bibliography style. In particular, do not use author-year citations. (The
-\texttt{natbib} package is not supported.)
-\end{itemize}
-
-\enlargethispage{\baselineskip}
-
-This is only a summary containing the most relevant details.
-Please read the complete document ``LIPIcs: Instructions for Authors and the \texttt{lipics-v2021} Class'' for all details and don't hesitate to contact Dagstuhl Publishing (\url{mailto:publishing@dagstuhl.de}) in case of questions or comments:
-\href{http://drops.dagstuhl.de/styles/lipics-v2021/lipics-v2021-authors/lipics-v2021-authors-guidelines.pdf}{\texttt{http://drops.dagstuhl.de/styles/lipics-v2021/\newline lipics-v2021-authors/lipics-v2021-authors-guidelines.pdf}}
-
-\section{Lorem ipsum dolor sit amet}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit \cite{DBLP:journals/cacm/Knuth74}.
-Praesent convallis orci arcu, eu mollis dolor.
-Aliquam eleifend suscipit lacinia.
-Maecenas quam mi, porta ut lacinia sed, convallis ac dui.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Suspendisse potenti.
-Donec eget odio et magna ullamcorper vehicula ut vitae libero.
-Maecenas lectus nulla, auctor nec varius ac, ultricies et turpis.
-Pellentesque id ante erat.
-In hac habitasse platea dictumst.
-Curabitur a scelerisque odio.
-Pellentesque elit risus, posuere quis elementum at, pellentesque ut diam.
-Quisque aliquam libero id mi imperdiet quis convallis turpis eleifend.
-
-\begin{lemma}[Lorem ipsum]
-\label{lemma:lorem}
-Vestibulum sodales dolor et dui cursus iaculis.
-Nullam ullamcorper purus vel turpis lobortis eu tempus lorem semper.
-Proin facilisis gravida rutrum.
-Etiam sed sollicitudin lorem.
-Proin pellentesque risus at elit hendrerit pharetra.
-Integer at turpis varius libero rhoncus fermentum vitae vitae metus.
-\end{lemma}
-
-\begin{proof}
-Cras purus lorem, pulvinar et fermentum sagittis, suscipit quis magna.
-
-\proofsubparagraph*{Just some paragraph within the proof.}
-Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-\begin{claim}
-content...
-\end{claim}
-\begin{claimproof}
-content...
-    \begin{enumerate}
-        \item abc abc abc \claimqedhere{}
-    \end{enumerate}
-\end{claimproof}
-
-\end{proof}
-
-\begin{corollary}[Curabitur pulvinar, \cite{DBLP:books/mk/GrayR93}]
-\label{lemma:curabitur}
-Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-\end{corollary}
-
-\begin{proposition}\label{prop1}
-This is a proposition
-\end{proposition}
-
-\autoref{prop1} and \cref{prop1} \ldots
-
-\subsection{Curabitur dictum felis id sapien}
-
-Curabitur dictum \cref{lemma:curabitur} felis id sapien \autoref{lemma:curabitur} mollis ut venenatis tortor feugiat.
-Curabitur sed velit diam.
-Integer aliquam, nunc ac egestas lacinia, nibh est vehicula nibh, ac auctor velit tellus non arcu.
-Vestibulum lacinia ipsum vitae nisi ultrices eget gravida turpis laoreet.
-Duis rutrum dapibus ornare.
-Nulla vehicula vulputate iaculis.
-Proin a consequat neque.
-Donec ut rutrum urna.
-Morbi scelerisque turpis sed elit sagittis eu scelerisque quam condimentum.
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-Aenean nec faucibus leo.
-Cras ut nisl odio, non tincidunt lorem.
-Integer purus ligula, venenatis et convallis lacinia, scelerisque at erat.
-Fusce risus libero, convallis at fermentum in, dignissim sed sem.
-Ut dapibus orci vitae nisl viverra nec adipiscing tortor condimentum \cite{DBLP:journals/cacm/Dijkstra68a}.
-Donec non suscipit lorem.
-Nam sit amet enim vitae nisl accumsan pretium.
-
-\begin{lstlisting}[caption={Useless code.},label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount]
-for i:=maxint to 0 do 
-begin 
-    j:=square(root(i));
-end;
-\end{lstlisting}
-
-\subsection{Proin ac fermentum augue}
-
-Proin ac fermentum augue.
-Nullam bibendum enim sollicitudin tellus egestas lacinia euismod orci mollis.
-Nulla facilisi.
-Vivamus volutpat venenatis sapien, vitae feugiat arcu fringilla ac.
-Mauris sapien tortor, sagittis eget auctor at, vulputate pharetra magna.
-Sed congue, dui nec vulputate convallis, sem nunc adipiscing dui, vel venenatis mauris sem in dui.
-Praesent a pretium quam.
-Mauris non mauris sit amet eros rutrum aliquam id ut sapien.
-Nulla aliquet fringilla sagittis.
-Pellentesque eu metus posuere nunc tincidunt dignissim in tempor dolor.
-Nulla cursus aliquet enim.
-Cras sapien risus, accumsan eu cursus ut, commodo vel velit.
-Praesent aliquet consectetur ligula, vitae iaculis ligula interdum vel.
-Integer faucibus faucibus felis.
-
-\begin{itemize}
-\item Ut vitae diam augue. 
-\item Integer lacus ante, pellentesque sed sollicitudin et, pulvinar adipiscing sem. 
-\item Maecenas facilisis, leo quis tincidunt egestas, magna ipsum condimentum orci, vitae facilisis nibh turpis et elit. 
-\end{itemize}
-
-\begin{remark}
-content...
-\end{remark}
-
-\section{Pellentesque quis tortor}
-
-Nec urna malesuada sollicitudin.
-Nulla facilisi.
-Vivamus aliquam tempus ligula eget ornare.
-Praesent eget magna ut turpis mattis cursus.
-Aliquam vel condimentum orci.
-Nunc congue, libero in gravida convallis \cite{DBLP:conf/focs/HopcroftPV75}, orci nibh sodales quam, id egestas felis mi nec nisi.
-Suspendisse tincidunt, est ac vestibulum posuere, justo odio bibendum urna, rutrum bibendum dolor sem nec tellus.
-
-\begin{lemma} [Quisque blandit tempus nunc]
-Sed interdum nisl pretium non.
-Mauris sodales consequat risus vel consectetur.
-Aliquam erat volutpat.
-Nunc sed sapien ligula.
-Proin faucibus sapien luctus nisl feugiat convallis faucibus elit cursus.
-Nunc vestibulum nunc ac massa pretium pharetra.
-Nulla facilisis turpis id augue venenatis blandit.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-\end{lemma}
-
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-
-\section{Morbi eros magna}
-
-Morbi eros magna, vestibulum non posuere non, porta eu quam.
-Maecenas vitae orci risus, eget imperdiet mauris.
-Donec massa mauris, pellentesque vel lobortis eu, molestie ac turpis.
-Sed condimentum convallis dolor, a dignissim est ultrices eu.
-Donec consectetur volutpat eros, et ornare dui ultricies id.
-Vivamus eu augue eget dolor euismod ultrices et sit amet nisi.
-Vivamus malesuada leo ac leo ullamcorper tempor.
-Donec justo mi, tempor vitae aliquet non, faucibus eu lacus.
-Donec dictum gravida neque, non porta turpis imperdiet eget.
-Curabitur quis euismod ligula.
-
-%%
-%% Bibliography
-%%
-
-%% Please use bibtex,
-
+\bibliographystyle{elsarticle-num} 
 \bibliography{RelatedWork}
 
-\appendix
-
-\section{Styles of lists, enumerations, and descriptions}\label{sec:itemStyles}
-
-List of different predefined enumeration styles:
-
-\begin{itemize}
-\item \verb|\begin{itemize}...\end{itemize}|
-\item \dots
-\item \dots
-%\item \dots
-\end{itemize}
-
-\begin{enumerate}
-\item \verb|\begin{enumerate}...\end{enumerate}|
-\item \dots
-\item \dots
-%\item \dots
-\end{enumerate}
-
-\begin{alphaenumerate}
-\item \verb|\begin{alphaenumerate}...\end{alphaenumerate}|
-\item \dots
-\item \dots
-%\item \dots
-\end{alphaenumerate}
-
-\begin{romanenumerate}
-\item \verb|\begin{romanenumerate}...\end{romanenumerate}|
-\item \dots
-\item \dots
-%\item \dots
-\end{romanenumerate}
-
-\begin{bracketenumerate}
-\item \verb|\begin{bracketenumerate}...\end{bracketenumerate}|
-\item \dots
-\item \dots
-%\item \dots
-\end{bracketenumerate}
-
-\begin{description}
-\item[Description 1] \verb|\begin{description} \item[Description 1]  ...\end{description}|
-\item[Description 2] Fusce eu leo nisi.
-Cras eget orci neque, eleifend dapibus felis.
-Duis et leo dui.
-Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\item[Description 3]  \dots
-%\item \dots
-\end{description}
-
-\cref{testenv-proposition} and \autoref{testenv-proposition} ...
-
-\section{Theorem-like environments}\label{sec:theorem-environments}
-
-List of different predefined enumeration styles:
-
-\begin{theorem}\label{testenv-theorem}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{theorem}
-
-\begin{lemma}\label{testenv-lemma}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{lemma}
-
-\begin{corollary}\label{testenv-corollary}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{corollary}
-
-\begin{proposition}\label{testenv-proposition}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{proposition}
-
-\begin{conjecture}\label{testenv-conjecture}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{conjecture}
-
-\begin{observation}\label{testenv-observation}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{observation}
-
-\begin{exercise}\label{testenv-exercise}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{exercise}
-
-\begin{definition}\label{testenv-definition}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{definition}
-
-\begin{example}\label{testenv-example}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{example}
-
-\begin{note}\label{testenv-note}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{note}
-
-\begin{note*}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{note*}
-
-\begin{remark}\label{testenv-remark}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{remark}
-
-\begin{remark*}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{remark*}
-
-\begin{claim}\label{testenv-claim}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{claim}
-
-\begin{claim*}\label{testenv-claim2}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{claim*}
-
-\begin{proof}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{proof}
-
-\begin{claimproof}
-Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
-\end{claimproof}
-
 \end{document}
-Footer
-© 2022 GitHub, Inc.
-Footer navigation
-
-    Terms
-    Privacy
-    Security
-    Status
-    Docs
-    Contact GitHub
-    Pricing
-    API
-    Training
-    Blog
-    About
-
-styles/lipics-v2021-sample-article.tex at master · dagstuhl-publishing/styles

### 2022-12-28 paper/main.tex
some minor changes

@@
 
-    \author[inst1]{Marijn Heule \corref{cor1}}
+    \author[inst1]{Marijn Heule\corref{cor1}}
     \ead{marijn@cmu.edu}
@@
     \affiliation[inst1]{organization={Carnegie Mellon University},%Department and Organization
-                addressline={5032 Forbes Ave}, 
+                addressline={5000 Forbes Ave},
                 city={Pittsburgh},
@@
 \begin{example}
-    In figure \ref{fig:ex2}, one can reason about two timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$.
+    In \cref{fig:ex2}, one can reason about two timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$.
 Then at the end of the grey box, we reenter the box, with the next time step being $!p$, and so on.
@@
 \begin{example}
-    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((!a) | ((aa^*(!a)))((!a) | ((aa^*(!a)))^{\omega}$, and simplified version $((!a) | ((aa^*(!a)))^{\omega}$, which corresponds to the two timelines in figure \cref{fig:unsimplified} and \cref{fig:simplified}.
+    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((!a) | (aa^*(!a)))((!a) | (aa^*(!a)))^{\omega}$, and simplified version $((!a) | (aa^*(!a)))^{\omega}$, which corresponds to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
     \begin{figure}[h!]
@@
         \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.gv.png}
-        \caption{Timeline for un-simplified $\omega$-regular expression $((!a) | ((aa^*(!a)))((!a) | ((aa^*(!a)))^{\omega}$}
+        \caption{Timeline for un-simplified $\omega$-regular expression $((!a) | (aa^*(!a)))((!a) | (aa^*(!a)))^{\omega}$}
         \label{fig:unsimplified}
@@
         \includegraphics[scale=0.3]{examples/ex9/ex9.gv.png}
-        \caption{Timeline for simplified $\omega$-regular expression $((!a) | ((aa^*(!a)))^{\omega}$}
+        \caption{Timeline for simplified $\omega$-regular expression $((!a) | (aa^*(!a)))^{\omega}$}
         \label{fig:simplified}
@@
     \]
-    For this \ltl\ formula, our tool generates the timeline representation in figure \ref{fig:ex14}.
+    For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex14}.
     \begin{figure}[h!]
@@
 \begin{itemize}
-    \item Can there be more simplifications methods as described in \ref{regex-simplify}?
+    \item Can there be more simplifications methods as described in Section \ref{regex-simplify}?
 The answer is definitely positive.

### 2022-12-28 paper/main.tex
images

@@
         \centering
-        \includegraphics[scale=0.4]{examples/ex2/ex2.gv.png}
+        \includegraphics[scale=0.4]{examples/ex2/ex2.png}
         \caption{Example timeline for specification ``$p$ oscillates every time step''}
@@
     \centering
-    \includegraphics[width=\textwidth, trim=1cm 3cm 1cm 3cm, clip]{img/algorithm_outline.gv.pdf}
+    \includegraphics[width=\textwidth, trim=1cm 3cm 1cm 3cm, clip]{img/algorithm_outline.pdf}
     \caption{Algorithm outline}
@@
         \centering
-        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.gv.png}
+        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
         \caption{Timeline for un-simplified $\omega$-regular expression $((!a) | (aa^*(!a)))((!a) | (aa^*(!a)))^{\omega}$}
@@
         \centering
-        \includegraphics[scale=0.3]{examples/ex9/ex9.gv.png}
+        \includegraphics[scale=0.3]{examples/ex9/ex9.png}
         \caption{Timeline for simplified $\omega$-regular expression $((!a) | (aa^*(!a)))^{\omega}$}
@@
         \centering
-        \includegraphics[scale=0.75]{img/uvw_dfa.gv.pdf}
+        \includegraphics[scale=0.75]{img/uvw_dfa.pdf}
         \caption{$u$ to $w$ path in $G$}
@@
         \centering
-        \includegraphics[scale=0.3]{examples/ex14/ex14.gv.png}
+        \includegraphics[scale=0.3]{examples/ex14/ex14.png}
         \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
@@
         \centering
-        \includegraphics[scale=0.3]{examples/ex13/ex13.gv.png}
+        \includegraphics[scale=0.3]{examples/ex13/ex13.png}
         \caption{Timeline for $p_2 \land (\eventually (\always p_0 \strongrelease  1) \weakrelease \nextt(\always p_1 \land ((p_0 \liff p_2) \stronguntil \eventually p_0)))$}

### 2022-12-28 paper/main.tex
added cls and bst files

@@
 \usepackage[strings]{underscore} % fixes doi underscores
+
+\usepackage{graphicx}
 
@@
 
-    \author[inst1]{Runming Li}
+	\author[inst1]{Runming Li\corref{cor1}}
     \ead{runmingl@andrew.cmu.edu}
 
-    \author[inst1]{Keerthana Gurushankar}
+	\author[inst1]{Keerthana Gurushankar\corref{cor1}}
     \ead{kgurusha@andrew.cmu.edu}
@@
 
-    \author[inst1]{Marijn Heule\corref{cor1}}
+    \author[inst1]{Marijn Heule\corref{cor2}}
     \ead{marijn@cmu.edu}
@@
 
-    \cortext[cor1]{Corresponding author}
+	\cortext[cor1]{These authors contributed equally to this work}
+    \cortext[cor2]{Corresponding author}
 
@@
 
-    \begin{highlights} %TODO
+    \begin{highlights} %TODO ~ Highly encouraged but not mandatory
         \item Research highlight 1
@@
 \end{enumerate}
-\begin{figure}[h!]
+\begin{figure}[!h]
     \centering
@@
 \subsection{BA to $\omega$-regex} \label{aut2regex}
-We translate \Buchi automata to $\omega$-regular expressions by first finding the regular expressions for paths from the start state to some final state (say $r_{sf}$), and for those for paths for looping from the final state back to itself (say $r_{ff}$), and finally combining those to form the $\omega$-expression for valid runs ($\bigplus_{f\in F} r_{sf}r_{ff}^\omega$).
+We translate \Buchi automata to $\omega$-regular expressions by first finding the regular expressions for paths from the start state to some final state (say $r_\mathrm{sf}$), and for those for paths for looping from the final state back to itself (say $r_\mathrm{ff}$), and finally combining those to form the $\omega$-expression for valid runs ($\bigplus_{f\in F} r_\mathrm{sf}r_\mathrm{ff}^\omega$).
 The regular expressions for finite paths are in turn found by iteratively deleting interior nodes in digraph of the automaton.
@@
         \Ensure Deletes state $v$ from $G$ while ensuring the same language is recognized
-        \For{ every $u\xrightarrow{r_{in}} v, v \xrightarrow{r_{out}} w$ }
-            \If {$v$ has a self-edge  $v\xrightarrow{r_{loop}}v$}
-                \State replace edges $u\xrightarrow{r_{in}} v, v \xrightarrow{r_{out}} w$ with $u \xrightarrow{r_{in} r_{loop}* r_{out}} w$
+        \For{ every $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ }
+            \If {$v$ has a self-edge  $v\xrightarrow{r_\mathrm{loop}}v$}
+                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in} r_\mathrm{loop}* r_\mathrm{out}} w$
             \Else
-                \State replace edges $u\xrightarrow{r_{in}} v, v \xrightarrow{r_{out}} w$ with $u \xrightarrow{r_{in}  r_{out}} w$
+                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in}  r_\mathrm{out}} w$
             \EndIf
@@
         \EndWhile
-        \State \Return $(r_{ss}| r_{sf} r_{ff}^* r_{fs})^* r_{sf} r_{ff}$
-        % if called by first visit, this is r_{ss}* r_{sf}
-        % if called by ba2wregex, s=f, this is r_{ff}
+        \State \Return $(r_\mathrm{ss}| r_\mathrm{sf} r_\mathrm{ff}^* r_\mathrm{fs})^* r_\mathrm{sf} r_\mathrm{ff}$
+        % if called by first visit, this is r_\mathrm{ss}* r_\mathrm{sf}
+        % if called by ba2wregex, s=f, this is r_\mathrm{ff}
         % consider modularizing fns differently
@@
     \end{figure}
-    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_{uv}}v\xrightarrow{r_{vw}}w$, with the trace $r=r_{uv}r_{vw}$.
-If there is a loop edge $r_{vv}$, this edge can be travelled any number of times before exiting $v$, thus the regular expression is $r=r_{uv}r_{vv}^*r_{vw}$.
+    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_\mathrm{uv}}v\xrightarrow{r_\mathrm{vw}}w$, with the trace $r=r_\mathrm{uv}r_\mathrm{vw}$.
+If there is a loop edge $r_\mathrm{vv}$, this edge can be travelled any number of times before exiting $v$, thus the regular expression is $r=r_\mathrm{uv}r_\mathrm{vv}^*r_\mathrm{vw}$.
 This edge $u\xrightarrow{r}w$ is added in $G'$.
@@
     The while loop clearly terminates since the number of interior nodes is strictly decreasing, and upon termination, $G$ is a DFA containing only the nodes $s$ and $f$.
-Now, every non-terminal visit from $s$ to $f$ and back to $s$, can be replaced by an edge $s\xrightarrow{r_{sf}r_{ff}^* r_{fs}} s$, instead of the edge $f\to s$.
-This DFA yields the regular language $(r_{ss}|r_{sf}r_{ff}^* r_{fs})^* r_{sf} r_{ff}$, as outputted by the algorithm.
+Now, every non-terminal visit from $s$ to $f$ and back to $s$, can be replaced by an edge $s\xrightarrow{r_\mathrm{sf}r_\mathrm{ff}^* r_\mathrm{fs}} s$, instead of the edge $f\to s$.
+This DFA yields the regular language $(r_\mathrm{ss}|r_\mathrm{sf}r_\mathrm{ff}^* r_\mathrm{fs})^* r_\mathrm{sf} r_\mathrm{ff}$, as outputted by the algorithm.
 \end{proof}
@@
 \section{Tool showcase}
-To demonstrate the result of our tool, we present two examples, one from a real-world model checking example in \cite{ZR14} and one from a randomly generated \ltl\ formula.
+To demonstrate the result of our tool, we present two examples, one from a real-world model checking example from Zhao and Rozier~\cite{ZR14} and one from a randomly generated \ltl\ formula.
 
 \begin{example}
-    \cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula
+    Zhao and Rozier~\cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula
     \[

### 2022-12-30 paper/main.tex
some things
add one more example

@@
 
-    \author[inst1]{Marijn Heule\corref{cor2}}
+    \author[inst1]{Marijn~J.H.~Heule\corref{cor2}}
     \ead{marijn@cmu.edu}
@@
 \begin{example}
-    In \cref{fig:ex2}, one can reason about two timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$.
+    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$.
 Then at the end of the grey box, we reenter the box, with the next time step being $!p$, and so on.
@@
         \label{fig:ex2}
+    \end{figure}
+\end{example}
+
+\begin{example}
+    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by two nodes with $!a$ separated by $\cdots$ (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $1$ (true) in the grey box.
+    \begin{figure}[!h]
+        \centering
+        \includegraphics[scale=0.4]{examples/ex15/ex15.gv.png}
+        \caption{Example timeline for specification ``$a$ is eventually true''}
+        \label{fig:ex15}
     \end{figure}
@@
     \]
-    For simplicity, we swap the concrete atomic proposition to $a, b, c$ and get
+    For simplicity, we swap the concrete atomic proposition to $a,b$ and get
     \[

### 2022-12-30 paper/main.tex
png
update on examples

@@
     \begin{align*}
-        \Phi ::= p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi
+        \Phi ::= p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
     \end{align*}\label{ltl-defn}
 \end{definition}
-Intuitively, $\always \Phi$ says that formula $\Phi$ is true at every time step; $\eventually \Phi$ says that formula $\Phi$ is true either now or at sometime in the future time step; and $\nextt \Phi$ says formula $\Phi$ is true at the next time step immediately after the current one.
+
 \begin{remark}
-    The definition of \ltl\ can be extended to allow release and until as shown below, but they are definable using connectives in \cref{ltl-defn}, hence they are omitted in the definition.
-The tool we present in this paper, however, does support those operators.
-    \begin{align*}
-        \Phi ::= \cdots \mid \Phi \strongrelease \Phi \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi \mid \Phi \weakuntil \Phi
-    \end{align*}
+    Intuitively, $\always \Phi$ says that formula $\Phi$ is true at every time step; $\eventually \Phi$ says that formula $\Phi$ is true either now or at sometime in the future time step; and $\nextt \Phi$ says formula $\Phi$ is true at the next time step immediately after the current one; $\Phi \stronguntil \Psi$ says that formula $\Phi$ is true \textit{until} such time formula $\Psi$ becomes true; $\Phi \weakrelease \Psi$ says that formula $\Psi$ must be true now and remain true until formula $\Phi$ becomes true, after which point \textit{release} $\Psi$ (if formula $\Phi$ is never true, then formula $\Psi$ must remain true at all time).
+\end{remark}
+
+\begin{remark}
+    The tool we provide in this paper uses a set of concrete syntax to represent those logical connectives, in order to avoid the difficulty of typesetting connectives such as $\always$ and $\eventually$.
+The concrete syntax is defined in \ref{sec:concrete-syntax}.
 \end{remark}
@@
     The semantics of \ltl\ formula is defined via judgement $\pi, i \models \Phi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step.
-The semantics follows exactly from \cite{Roz11}.
+The semantics follows exactly from Rozier~\cite{Roz11}.
 \end{definition}
@@
         \centering
-        \includegraphics[scale=0.4]{examples/ex15/ex15.gv.png}
+        \includegraphics[scale=0.4]{examples/ex15/ex15.png}
         \caption{Example timeline for specification ``$a$ is eventually true''}
@@
     \centering
-    \includegraphics[width=\textwidth, trim=1cm 3cm 1cm 3cm, clip]{img/algorithm_outline.pdf}
+    \includegraphics[width=\textwidth]{img/algorithm_outline.pdf}
     \caption{Algorithm outline}
@@
     \[
-    p_2 \land (\eventually (\always p_0 \strongrelease  1) \weakrelease \nextt(\always p_1 \land ((p_0 \liff p_2) \stronguntil \eventually p_0)))
+    p_2 \land (\eventually \always p_0 \weakrelease \nextt(\always p_1 \land ((p_0 \limplies p_2 \land p_2 \limplies p_0) \stronguntil \eventually p_0)))
     \]
@@
         \includegraphics[scale=0.3]{examples/ex13/ex13.png}
-        \caption{Timeline for $p_2 \land (\eventually (\always p_0 \strongrelease  1) \weakrelease \nextt(\always p_1 \land ((p_0 \liff p_2) \stronguntil \eventually p_0)))$}
+        \caption{Timeline for $p_2 \land (\eventually \always p_0 \weakrelease \nextt(\always p_1 \land ((p_0 \limplies p_2 \land p_2 \limplies p_0) \stronguntil \eventually p_0)))$}
         \label{fig:ex13}
@@
 
-\section{Future work}
-Based on our results, we raise the following questions as future works:
+\section{Discussion}
+Based on our results, we propose the following questions for discussions and future works:
 \begin{itemize}
@@
 
+\appendix
+\section{Concrete Syntax of \texttt{ltl2timeline}} \label{sec:concrete-syntax}
+Recall from \ref{ltl-defn} that we define \ltl\ formula as
+\begin{align*}
+    \Phi ::= p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
+\end{align*}
+where $p \in \AP$. In our tool \texttt{ltl2timeline}, we use the following concrete syntax to represent \ltl\ formulae.
+\[
+    \begin{array}{c r l l l@{\qquad} l}
+         &      & \textit{abstract syntax}              & \textit{concrete syntax}                       & \textit{description} \\
+    \Phi & ::=  & p                                     & \texttt{p}                                     & \text{atomic proposition} \\
+         & \mid & \neg \Phi                             & \texttt{!} \Phi                                & \text{negation} \\
+         & \mid & \Phi \land \Phi                       & \Phi \texttt{ \& } \Phi                        & \text{conjunction} \\
+         & \mid & \Phi \lor \Phi                        & \Phi \texttt{ | } \Phi                         & \text{disjunction} \\
+         & \mid & \Phi \limplies \Phi                   & \Phi \texttt{ -> } \Phi                        & \text{implication} \\
+         & \mid & \always \Phi                          & \texttt{G} \Phi                                & \text{globally} \\
+         & \mid & \eventually \Phi                      & \texttt{F} \Phi                                & \text{finally} \\
+         & \mid & \nextt \Phi                           & \texttt{X} \Phi                                & \text{next} \\
+         & \mid & \Phi \stronguntil \Phi                & \Phi \texttt{ U } \Phi                         & \text{until} \\
+         & \mid & \Phi \weakrelease \Phi                & \Phi \texttt{ R } \Phi                         & \text{release} \\
+    \end{array}
+\]
+
 \bibliographystyle{elsarticle-num}

### 2022-12-31 paper/intro-draft.tex
upload intro-draft which expands text

--- 2022-12-30 paper/main.tex
@@
     \begin{highlights} %TODO ~ Highly encouraged but not mandatory
-        \item Research highlight 1
-        \item Research highlight 2
+        \item We transform Linear Temporal Logic (LTL) formulas to timeline visualizations for the set of satisfying traces.
+        \item We translate LTL formulas to \Buchi automata, then to $\omega$-regular expressions, then simplify them and use graph visualization tools to draw timelines.
+        \item Our algorithm is sound and complete. 
+        \item Our tool, \texttt{ltl2timeline}, effectively constructs small timeline visualizations for a range of LTL formulas.
     \end{highlights}
@@
 
-Formal methods, including Linear Temporal Logic (\ltl), are widely used in the specification and analysis of safety-critical systems, such as those found in the aerospace industry.
-These methods provide powerful tools for rigorously verifying the correctness of system designs, from early design-time model checking to on-board runtime verification.
-However, these methods can be difficult for humans to understand and use, leading to the possibility of errors and misunderstandings.
+Requirement specification is a central step in the development of safety-critical systems.
+As a first step, requirements are typically written in natural language.
+For example, here is a real-world requirement specification from an air traffic control system ~\cite{ZR14}
+\begin{center}
+    "If a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft"
+\end{center}
+Such natural language requirements are often ambiguous and not amenable to formal analysis, so requirements must often be specified using rigorous formalized semantics for the purpose of verification and validation.
+The above requirement, when translated to Linear Temporal Logic (detailed in Section 2.1), may be expressed as follows:
+\begin{align*}
+    \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \\
+    \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
+\end{align*}
+Several tools have been developed to reason about formal specifications written with such LTL formulas, like R2U2 and FRET \cite{GPMS20}.
+However, these formalized semantics are unintintuitive and error-prone for human practitioners, and the tools are much less useful when system designers can't validate input specifications.
+Thus, a significant hurdle remains: how can we convincingly demonstrate to the humans in the loop, from system designers to certifiers, that the analyzed formulas truly represent the desired system requirements?
+% quote MLTL paper?
 
-There has been recent work aimed at making the use of formal methods more intuitive for humans, such as NASA's FRET (Formal Requirements Engineering Tool) \cite{GPMS20} which uses structured natural language to bridge the gap between natural language and formal semantics.
+We take a simple idiomatic approach to address this problem.
+As Linear Temporal Logic formulas are temporal information, we devise a tool, \texttt{ltl2timeline}, which can draw timelines to depict the satisfying traces of the LTL formula, and thereby represent the specified behaviour in a more natural human-intelligible form.
 
-However, \ltl\ is literally a language of timelines, so timeline visualizations have the potential to be a powerful tool for representing \ltl\ formulas in an intuitive manner.
-In this paper, we propose such a timeline visualization tool, using regular expressions, to effectively represent a wide range of \ltl-based formulas.
+Our tool, \texttt{ltl2timeline}, uses a remarkably simple algorithm: transforming an input LTL formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of LTL formulas.
+It would visualize the above air traffic control requirement behaviour with the following timeline:
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\textwidth]{examples/ex10/ex10.gv.png}
+    \caption{[TODO: make fig with variables, explain a, b, c or just use oscillating example if that's easier]}
+\end{figure}
+
+We make the following contributions in our paper:
+\begin{itemize}
+    \item We provide the tool, \texttt{ltl2timeline}, which takes LTL formulas and synthesizes timeline visualizations for them
+    \item We prove correctness in Section 4. We show that for every LTL formula, the timeline outputted indeed represents the set of satisfying traces.
+    \item We showcase the results of our tool on a range of example formulas in Section 5, including discussing the air traffic example above. 
+\end{itemize}
 
 \section{Setting the stage}
+
+We must begin by setting up the prerequisite definitions involved in our work. 
+First, we provide the definition and semantics for LTL.
+In the following subsections, we define (state-based) \Buchi automata and $\omega$-regular expressions, which are generalizations of the well-known deterministic finite automata (DFAs) and regular expressions, for the case of infinite words.
+Lastly, we describe the graphic visualizations we will use to depict timelines.
 
@@
 The translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.}.
+SPOT is a C++ library that provides a variety of tools to generate, convert and translate LTL formulas and $\omega$-automata.
+To aid our tool, we only use its function to translate LTL formulas to state-based \Buchi automata.
+% write about how spot works?
 
@@
 \section{Discussion}
+% Questions we were asked during the talk
+% Where there formulas we had trouble representing
+% Going from timelines to LTL
+% It would be helpful to have benchmarks beyond showcase because what is cool is timelines being remarkably short
+% Also a theoretical discussion of same with star height
+
 Based on our results, we propose the following questions for discussions and future works:
@@
 \section{Conclusion}
-To add. % Journal also asks for a Discussion section
+Making formal methods, such as LTL, easier for humans in the loop is an important problem today, in making systems safer with verification. 
+In this paper, we present a novel tool to visualize LTL specification behavior and aid in validating their correctness.
+We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for LTL.
 

### 2022-12-31 paper/main.tex
added Playing It Out section with draft bits

@@
 \newcommand{\liff}{\leftrightarrow}
+
+\newcommand{\tool}{\texttt{ltl2timeline}}
 
@@
 
+\section{Playing it out} %KYR: may swap order with the next section on artifact availability?
+
+We quantify the useability and performance of \tool by compiling an extensive set of LTL formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of all real-life LTL formulas over those metrics.
+We release the set of real-life LTL formulas as a benchmark set for the research community.
+Our experimental evaluation conclusively demonstrates that \tool scales to provide helpful visualizations of LTL formulas written by humans.
+
+\subsection{Set of Real LTL Formulas}
+
+We collect the LTL formulas from a covering set of publicly-available case studies that use LTL in the analysis of real-life safety-critical systems.
+As some formulas are redundant (i.e., common properties occur in many different case studies), it is not necessary to include every paper that has ever used LTL in a real setting; we instead opt for the largest and most unique formulas to cover the space of realistic use of LTL.
+
+\subsection{Timeline Metrics}
+
+Define size, length, height, complexity, etc. here.
+
+\subsection{Experimental Analysis} %We could come up with a less-generic name for this, which would be nicer...
+
+Here we nicely summarize (with pictures as much as possible) all of the statistics and results we gathered.
+
+<image>
+caption: For all of the <large number> of real LTL formulas historically used to analyze real systems, \tool efficiently yields useable, readable timeine visualizations.
+
 \section{Artifact availability}
@@
 which comes with two command-line tools, \texttt{ltl2regex} and \texttt{ltl2timeline}. The specific usage of the tool can be found  \href{https://github.com/EULIR/ltl-explainability#usage}{here}.
+
+KYR: link LTL database here too.
 

### 2022-12-31 paper/main.tex
updates to experiments section; small fixes (spell check) throughout

@@
 
+    \author[inst1]{Marijn~J.H.~Heule\corref{cor2}}
+    \ead{marijn@cmu.edu}
+
     \author[inst2]{Kristin Y. Rozier}
     \ead{kyrozier@iastate.edu}
-
-    \author[inst1]{Marijn~J.H.~Heule\corref{cor2}}
-    \ead{marijn@cmu.edu}
 
@@
 \begin{definition}[Semantics of \ltl\ formula]
-    The semantics of \ltl\ formula is defined via judgement $\pi, i \models \Phi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step.
+    The semantics of \ltl\ formula is defined via judgment $\pi, i \models \Phi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step.
 The semantics follows exactly from Rozier~\cite{Roz11}.
@@
     Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_\mathrm{uv}}v\xrightarrow{r_\mathrm{vw}}w$, with the trace $r=r_\mathrm{uv}r_\mathrm{vw}$.
-If there is a loop edge $r_\mathrm{vv}$, this edge can be travelled any number of times before exiting $v$, thus the regular expression is $r=r_\mathrm{uv}r_\mathrm{vv}^*r_\mathrm{vw}$.
+If there is a loop edge $r_\mathrm{vv}$, this edge can be traveled any number of times before exiting $v$, thus the regular expression is $r=r_\mathrm{uv}r_\mathrm{vv}^*r_\mathrm{vw}$.
 This edge $u\xrightarrow{r}w$ is added in $G'$.
@@
 
-We quantify the useability and performance of \tool by compiling an extensive set of LTL formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of all real-life LTL formulas over those metrics.
+We quantify the usability and performance of \tool by compiling an extensive set of LTL formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of all real-life LTL formulas over those metrics.
 We release the set of real-life LTL formulas as a benchmark set for the research community.
@@
 
+Given the tremendous popularity of LTL as a specification language for industrial analysis, surprisingly few real-life system analysis case studies publicly release their LTL formula specifications, largely to protect proprietary system information.
+We purposely avoid using the random or machine-generated formulas from published benchmarks because the purpose of \tool is helping humans understand and validate LTL formulas.
+Thus, we gather an extensive, representative set of formulas humans have written or needed to understand.
+Our LTL formula collection is as follows.
+
+%Purpose & \# formulas & source
+
 \subsection{Timeline Metrics}
+\label{sec:metrics}
 
-Define size, length, height, complexity, etc. here.
+KYR: Define size, length, height, complexity, etc. here.
 
@@
 
-Here we nicely summarize (with pictures as much as possible) all of the statistics and results we gathered.
+KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
+
+\paragraph{Scalability}
+KYR: Here we characterize the size of the timeline as a function of the number of bits of a binary counter for each of the four binary counter LTL formulas.
+The point is that these four are the only (unboundedly) scalable formulas that describe something real (i.e., they describe a binary counter for any number of bits) that have ever been published in the literature.
+These would throw off our metrics about the set of real LTL formulas if we included them in there.
+Thus, we analyze them separately, and can define the timeline size as a function of the number of bits for each of the four formulas.
+We can give an example or two here, such as two pictures of timelines for a 2-bit and a 3-bit counter from two different formulas, one with U's and one with X's; one with carry and one without (such as a 2-bit w/carry X formula and a 3-bit no carry U formula).
+The scalable counter formulas are from \cite{RV10}.
+
+\paragraph{Denouement}
+KYR: aggregate and summarize all experiments here.
 
 <image>
-caption: For all of the <large number> of real LTL formulas historically used to analyze real systems, \tool efficiently yields useable, readable timeine visualizations.
+caption: For all of the <large number> of real LTL formulas historically used to analyze real systems, \tool efficiently yields usable, readable timeline visualizations.
 

### 2022-12-31 paper/main.tex
added table of LTL formulas and some of the formulas

@@
 
-\newcommand{\tool}{\texttt{ltl2timeline}}
+\newcommand{\tool}{\hspace{0.1cm}\texttt{ltl2timeline}\hspace{0.1cm}}
 
@@
 
-%Purpose & \# formulas & source
+\noindent
+\begin{tabular}{p{3.6in}|c|c}
+  \hline
+  Purpose & \# formulas & Source \\
+  \hline
+  Design space for NASA's AAC (Automated Airspace Concept) & 20,250 & \cite{GCMTR16} \\
+  \hline
+  Safety specificatons for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
+  \hline
+  Requirements for model checking NASA's AAC high-level architecture & 6 & \cite{ZR14} \\
+  \hline
+  Real formulas collected from all publicly-available, pre-2011 case studies &  & \cite{RV11} \\
+  \hline
+\end{tabular}
 

### 2022-12-31 ltl-formulas/RV10patterns/Sformula.pl
added LTL formulas

@@ -1,0 +1,53 @@
+#!/usr/bin/perl
+
+# Sformula.pl
+#
+# Input: n = the number of operands of the form "G F pi" in the output formula
+# 
+# Output: an LTL formula of the form S(n) = || _{i=1} ^{n} G pi
+#
+# Usage: Sformula.pl n
+#
+
+# System Description
+#
+# - n variables: p1 .. pn
+
+# Purpose: to create scaleable formulas as described in "Larger Automata and Less Work for LTL Model Checking" by Geldenhuys and Hansen
+
+
+
+#################### Argument Setup ####################
+
+#Check for correct number and type of command line arguments
+if ($ARGV[0] =~ /^-v?/) {
+    $verbose = 1;
+    shift(@ARGV);
+} #end if
+else {
+    $verbose = 0;
+} #end else
+
+if (@ARGV != 1) {
+    die "Usage: Sformula.pl n\n\tproduces an n-part formula of the form S(n) = || _{i=1} ^{n} G pi\n\tUse flag -v for verbose, human-readable output.\n";
+} #end if
+
+$n = $ARGV[0];
+
+#Check that we have an integer
+if (($n !~ /^\d+?/) || ($n <= 0)) {
+    die "Error: Expecting a positive integer as input; Got $n\n";
+} #end if
+
+
+#################### Generation of the Formula ####################
+$pattern = "(G (p1))"; #initialize the pattern
+
+for ($i = 2; $i <= $n; $i++) {
+    $pattern = "($pattern || (G (p$i)))";
+} #end for
+
+if ($verbose == 1) {
+    print "\nComputer readable: ";
+} #end if
+print "$pattern\n";

### 2022-12-31 ltl-formulas/RV10patterns/Uformula.pl

@@ -1,0 +1,54 @@
+#!/usr/bin/perl
+
+# Uformula.pl
+#
+# Input: n = the number of variables arranged in the output formula of the form
+#            "(...((p1 U p2) U ... ) U pn)"
+# 
+# Output: an LTL formula of the form U(n) = (...((p1 U p2) U ... ) U pn)
+#
+# Usage: Uformula.pl n
+#
+
+# System Description
+#
+# - n variables: p1 .. pn
+
+# Purpose: to create scaleable formulas as described in "Larger Automata and Less Work for LTL Model Checking" by Geldenhuys and Hansen
+
+
+
+#################### Argument Setup ####################
+
+#Check for correct number and type of command line arguments
+if ($ARGV[0] =~ /^-v?/) {
+    $verbose = 1;
+    shift(@ARGV);
+} #end if
+else {
+    $verbose = 0;
+} #end else
+
+if (@ARGV != 1) {
+    die "Usage: Uformula.pl n\n\tproduces an n-part formula of the form U(n) = (...((p1 U p2) U ... ) U pn)\n\tUse flag -v for verbose, human-readable output.\n";
+} #end if
+
+$n = $ARGV[0];
+
+#Check that we have an integer
+if (($n !~ /^\d+?/) || ($n < 2)) {
+    die "Error: Expecting a positive integer (at least 2) as input; Got $n\n";
+} #end if
+
+
+#################### Generation of the Formula ####################
+$pattern = "(p1 U p2)"; #initialize the pattern
+
+for ($i = 3; $i <= $n; $i++) {
+    $pattern = "($pattern U p$i)";
+} #end for
+
+if ($verbose == 1) {
+    print "\nComputer readable: ";
+} #end if
+print "$pattern\n";

### 2022-12-31 ltl-formulas/ApplicationBenchmarks/acacia_orig_source/acacia/Makefile.PL
added application benchmarks from RV11

@@ -1,0 +1,12 @@
+use 5.010000;
+use ExtUtils::MakeMaker;
+# See lib/ExtUtils/MakeMaker.pm for details of how to influence
+# the contents of the Makefile that is written.
+WriteMakefile(
+    NAME              => 'acacia',
+    VERSION_FROM      => 'lib/Acacia.pm', # finds $VERSION
+    PREREQ_PM         => {}, # e.g., Module::Name => 1.1
+    ($] >= 5.005 ?     ## Add these new keywords supported since 5.005
+      (ABSTRACT_FROM  => 'lib/Acacia.pm', # retrieve abstract from module
+       AUTHOR         => 'Naiyong Jin <naiyjin@ulb.ac.be>') : ()),
+);

### 2023-01-01 paper/main.tex
small update to main
added metric defs

@@
 
+\newcommand{\tllen}{\text{tllen}}
+
 \begin{document}
@@
 
-    \begin{highlights} %TODO ~ Highly encouraged but not mandatory
-        \item Research highlight 1
-        \item Research highlight 2
+    \begin{highlights} 
+        \item We transform Linear Temporal Logic (LTL) formulas to timeline visualizations for the set of satisfying traces.
+        \item We translate LTL formulas to \Buchi automata, then to $\omega$-regular expressions, then simplify them and use graph visualization tools to draw timelines.
+        \item Our algorithm is sound and complete. 
+        \item Our tool, \texttt{ltl2timeline}, effectively constructs small timeline visualizations for a range of LTL formulas.
     \end{highlights}
@@
   \hline
-  Real formulas collected from all publicly-available, pre-2011 case studies &  & \cite{RV11} \\
+  Real formulas collected from all publicly-available, pre-2011 case studies & 63 & \cite{RV11} \\
   \hline
@@
 
-KYR: Define size, length, height, complexity, etc. here.
+%KYR: Define size, length, height, complexity, etc. here.
+
+We use two measures of complexity for timeline visualizations: timeline length and star height.
+
+We use timeline length, defined below, to capture the length of our timeline visualization graphs.
+Since Kleene stars are the trickiest operator to depict in timelines, we also use star height, a well-studied measure for the structural complexity of regular expressions, to measure the complexity of our visualizations.
+
+\begin{definition}[Timeline Length]
+    We define the timeline length of a regular expression $\tllen(A)$ recursively as follows
+    \begin{align*}
+        \tllen(\emptyset)   &= -\infty\\
+        \tllen(\epsilon)        &= 0\\
+        \tllen(a)           &= 1\\
+        \tllen(A_1 A_2)     &= \tllen(A_1) + \tllen(A_2)\\
+        \tllen(A_1 + A_2)   &= \max(\tllen(A_1, A_2))\\
+        \tllen(A^*)         &= 2\tllen(A) + 1 
+    \end{align*}
+    We also extend this definition to $\omega$-regular expressions as follows
+    \begin{align*}
+        \tllen(A^\omega)    &= \tllen(A)\\
+        \tllen(AB)          &= \tllen(A) + \tllen(B)\\
+        \tllen(B_1 + B_2)   &= \max(\tllen(B_1), \tllen(B_2))
+    \end{align*}
+    This quantity $\tllen$ captures the length of the longest path in our timeline graph visualization.
+\end{definition}
+
+\begin{definition}[Star height]
+    We define the star height of regular and $\omega$-regular expressions to be the star-nesting depth in the (unsimplified) expression. Namely,
+    \begin{align*}
+        h(\emptyset) = h(\epsilon) = h(a) &= 0\\
+        h(A_1 A_2) = h(A_1 + A_2) &= \max(h(A_1), h(A_2))\\
+        h(A^*) &= 1 + h(A)\\
+        h(A^\omega) &= h(A)\\
+        h(A B) &= \max(h(A), h(B))\\
+        h(B_1 + B_2) &= \max(h(B_1), h(B_2))
+    \end{align*}
+
+\end{definition}
 

### 2023-01-01 ltl-formulas/benchmark.py
added regex_tllen to src

@@ -1,0 +1,14 @@
+import sys
+sys.path.append('/home/kgurusha/Documents/CMU/15816/ltl-explainability/src')
+
+from main import Ltl2Regex
+tl = Ltl2Regex()
+
+aac_file = open('AAC_Communication_Protocol.ltl', 'r')
+specs = aac_file.readlines()
+ltls = [spec.split(' ', 1)[1] for spec in specs]
+regexs = [tl.ltl2regex(ltl) for ltl in ltls]
+tllens = [len(wregex) for wregex in regexs]
+
+print("AAC timeline lengths", tllens)
+

### 2023-01-01 src/ltl_regex.py

@@ -6,6 +6,9 @@ class Regex:
     def __str__(self) -> str:
         return regex_to_string(self)
 
+    def __len__(self) -> int:
+        return regex_tllen(self)
+
 
 @dataclass(eq=True, frozen=True)
 class Epsilon(Regex):
@@ -54,6 +57,24 @@ def regex_to_string(regex: Regex) -> str:
         case Star(r):
             return f'({regex_to_string(r)})*'
         case _:
+            raise Typeerror(f'Unknown regex type: {type(regex)}')
+
+def regex_tllen(regex: Regex) -> int:
+    # currently returns timeline length of regex
+    match regex:
+        case Epsilon():
+            return 0
+        case Empty():
+            return -1
+        case Symbol(s):
+            return 1
+        case Concat(r1, r2):
+            return regex_tllen(r1) + regex_tllen(r2)
+        case Union(r1, r2):
+            return max(regex_tllen(r1), regex_tllen(r2))
+        case Star(r):
+            return 2 * regex_tllen(r) + 1
+        case _:
             raise TypeError(f'Unknown regex type: {type(regex)}')
 
 
@@ -61,7 +82,8 @@ def regex_to_string(regex: Regex) -> str:
 class OmegaRegex:
     def __str__(self) -> str:
         return omega_regex_to_string(self)
-
+    def __len__(self) -> int:
+        return omega_regex_tllen(self)
 
 @dataclass(eq=True, frozen=True)
 class Repeat(OmegaRegex):
@@ -88,5 +110,17 @@ def omega_regex_to_string(omega_regex: OmegaRegex) -> str:
             return f'({regex_to_string(r1)}{omega_regex_to_string(r2)})'
         case UnionOmega(r1, r2):
             return f'({omega_regex_to_string(r1)}|{omega_regex_to_string(r2)})'
+        case _:
+            raise TypeError(f'Unknown omega regex type: {type(omega_regex)}')
+
+
+def omega_regex_tllen(omega_regex: OmegaRegex) -> int:
+    match omega_regex:
+        case Repeat(r):
+            return regex_tllen(r)
+        case ConcatOmega(r1, r2):
+            return regex_tllen(r1) + omega_regex_tllen(r2)
+        case UnionOmega(r1, r2):
+            return max(omega_regex_tllen(r1), omega_regex_tllen(r2))
         case _:
             raise TypeError(f'Unknown omega regex type: {type(omega_regex)}')

### 2023-01-01 src/ltl_regex.py
fix typo

@@ -57,7 +57,7 @@ def regex_to_string(regex: Regex) -> str:
         case Star(r):
             return f'({regex_to_string(r)})*'
         case _:
-            raise Typeerror(f'Unknown regex type: {type(regex)}')
+            raise TypeError(f'Unknown regex type: {type(regex)}')
 
 def regex_tllen(regex: Regex) -> int:
     # currently returns timeline length of regex

### 2023-01-01 ltl-formulas/benchmark.py
acacia and tacas formulas

@@ -4,11 +4,41 @@ sys.path.append('/home/kgurusha/Documents/CMU/15816/ltl-explainability/src')
 from main import Ltl2Regex
 tl = Ltl2Regex()
 
+import numpy as np
+
+# AAC formulas
 aac_file = open('AAC_Communication_Protocol.ltl', 'r')
-specs = aac_file.readlines()
-ltls = [spec.split(' ', 1)[1] for spec in specs]
+aac_specs = aac_file.readlines()
+aac_ltls = [spec.split(' ', 1)[1] for spec in aac_specs]
+print("Found AAC formulas: ", len(aac_ltls))
+
+# RV11 formulas
+
+# tacas08 counter formulas 
+base_path = 'ApplicationBenchmarks/AlaskaBenchmarks/tacas08_experiments/counter/'
+
+tacas_counter_ltls = []
+for i in range(2, 17):
+    f = open(base_path + 'counter_' + str(i) + '.ltl', 'r')
+    tacas_counter_ltls.append(f.read())
+print("Found TACAS counter formulas: ", len(tacas_counter_ltls)) # very long formulas, 1000+ chars
+
+# acacia formulas
+base_path = 'ApplicationBenchmarks/acacia_orig_source/acacia/examples/example/'
+
+acacia_ltls = []
+for i in range(1,24):
+    f = open(base_path + 'demo-v' + str(i) + '.ltl', 'r')
+    acacia_ltls.append(f.read())
+print("Found acacia formulas: ", len(acacia_ltls))
+
+
+ltls = aac_ltls #+ acacia_ltls (needs formatting) #+ tacas_counter_ltls (takes too long to compute)
 regexs = [tl.ltl2regex(ltl) for ltl in ltls]
 tllens = [len(wregex) for wregex in regexs]
 
-print("AAC timeline lengths", tllens)
+print("\n")
+print("Number of formulas: ", len(ltls))
+print("Mean timeline length: ", np.mean(tllens))
+
 

### 2023-01-01 ltl-formulas/benchmark.py
acacia and tacas formulas

@@ -33,7 +33,7 @@ for i in range(1,24):
 print("Found acacia formulas: ", len(acacia_ltls))
 
 
-ltls = aac_ltls #+ acacia_ltls (needs formatting) #+ tacas_counter_ltls (takes too long to compute)
+ltls = aac_ltls # + acacia_ltls (needs formatting) # + tacas_counter_ltls (takes too long to compute)
 regexs = [tl.ltl2regex(ltl) for ltl in ltls]
 tllens = [len(wregex) for wregex in regexs]
 

### 2023-01-01 ltl-formulas/benchmark.py
got table of metrics for acacia

@@ -1,7 +1,7 @@
 import sys
 sys.path.append('/home/kgurusha/Documents/CMU/15816/ltl-explainability/src')
 
-from main import Ltl2Regex
+from main import *
 tl = Ltl2Regex()
 
 import numpy as np
@@ -21,24 +21,40 @@ tacas_counter_ltls = []
 for i in range(2, 17):
     f = open(base_path + 'counter_' + str(i) + '.ltl', 'r')
     tacas_counter_ltls.append(f.read())
-print("Found TACAS counter formulas: ", len(tacas_counter_ltls)) # very long formulas, 1000+ chars
+print("Found TACAS counter formulas: ", len(tacas_counter_ltls), ". Didn't use") # very long formulas, 1000+ chars, not useful
 
-# acacia formulas
+# acacsia formulas
 base_path = 'ApplicationBenchmarks/acacia_orig_source/acacia/examples/example/'
 
 acacia_ltls = []
-for i in range(1,24):
+for i in range(1,24): 
     f = open(base_path + 'demo-v' + str(i) + '.ltl', 'r')
-    acacia_ltls.append(f.read())
+    lines = f.readlines()
+    # strip comments, clause 'assume' tags and '\n's
+    lines = [line.split('#', 1)[0].replace('assume', '').strip() for line in lines]
+    # formulas are semicolon seperated 
+    ltls = " ".join(lines).split(';')[:-1]
+    # treat each formula (within examples) as seperate case (is this what we want?) 
+    acacia_ltls += ltls 
+    
 print("Found acacia formulas: ", len(acacia_ltls))
 
+ltls = aac_ltls # + tacas_counter_ltls (takes too long to compute)
+ltls += [ltl for ltl in acacia_ltls if len(ltl) < 170] # len > takes too long
+# use len < 120 for nice plot, use len < 170 for computable cases that blow up
 
[…]

### 2023-01-01 paper/main.tex
small fixes

@@
 
-    \author[inst2]{Kristin Y. Rozier}
+    \author[inst2]{Kristin~Y.~Rozier}
     \ead{kyrozier@iastate.edu}
@@
     \end{figure}
-    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_\mathrm{uv}}v\xrightarrow{r_\mathrm{vw}}w$, with the trace $r=r_\mathrm{uv}r_\mathrm{vw}$.
-If there is a loop edge $r_\mathrm{vv}$, this edge can be traveled any number of times before exiting $v$, thus the regular expression is $r=r_\mathrm{uv}r_\mathrm{vv}^*r_\mathrm{vw}$.
+    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_{uv}}v\xrightarrow{r_{vw}}w$, with the trace $r=r_{uv}r_{vw}$.
+If there is a loop edge $r_{vv}$, this edge can be traveled any number of times before exiting $v$, thus the regular expression is $r=r_{uv}r_{vv}^*r_{vw}$.
 This edge $u\xrightarrow{r}w$ is added in $G'$.
@@
   \hline
-  Safety specificatons for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
+  Safety specifications for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
   \hline

### 2023-01-01 paper/main.tex
tikz

@@
 
-\usepackage{amsmath, amssymb, amsthm}
+\usepackage{amsmath, amssymb, amsthm,tikz}
+\usetikzlibrary{positioning,shapes,quotes}
+
 \newtheorem{theorem}{Theorem}[section]
@@
         \centering
-        \includegraphics[scale=0.75]{img/uvw_dfa.pdf}
-        \caption{$u$ to $w$ path in $G$}
+        \begin{tikzpicture}
+	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (u) {$u$};
+	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (v) [right=of u] {$v$};
+	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (w) [right=of v] {$w$};
+	\draw[thick] (u) edge["$r_{uv}$",-latex] (v) (v) edge["$r_{vv}$",-latex,loop above] (v) (v) edge["$r_{vw}$",-latex] (w); 
+        \end{tikzpicture}
+ %       \includegraphics[scale=0.75]{img/uvw_dfa.pdf}
+        \caption{A path from $u$ to $w$ in $G$}
         \label{fig:uvw-dfa}
@@
 \noindent
+\begin{table}[h]
 \begin{tabular}{p{3.6in}|c|c}
@@
 \end{tabular}
+\end{table}
 

### 2023-01-01 paper/main.tex
tikz fig 6

@@
 \usepackage{amsmath, amssymb, amsthm,tikz}
-\usetikzlibrary{positioning,shapes,quotes}
+\usetikzlibrary{positioning,shapes,quotes,calc}
 
@@
     \centering
-    \includegraphics[scale=0.5]{img/timeline.png}
+    \begin{tikzpicture}
+    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {$A_1$};
+    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a2g) [right= 0.85cm of a1] {};
+    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [right= 1cm of a1] {$A_2$};
+    \node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [below= 0.4cm of a1] {$A_3$};
+    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a4g) [right= 0.85cm of a3] {};
+    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 1cm of a3] {$A_4$};
+    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [below= 0.4cm of a3] {...};
+    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a7) [below= 0.4cm of a5] {\!\!\!$A_{2n-1}$\!\!\!};
+    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a8g) [right= 0.85cm of a7] {};
+    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a8) [right= 1cm of a7] {\!\!\!$A_{2n}$\!\!\!};
+    \node (m) at ($(a1)!0.5!(a7)$) {};
+    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 1.5cm of m] {\!\!\!\!start\!\!\!\!};
+    \draw[thick] (s) edge[-latex] (a1) (s) edge[-latex] (a3) (s) edge[-latex] (a5) (s) edge[-latex] (a7);
+    \draw[thick] (a1) edge[-latex] (a2) (a3) edge[-latex] (a4) (a7) edge[-latex] (a8);
+    \end{tikzpicture}
+%    \includegraphics[scale=0.5]{img/timeline.png}
     \caption{Generic timeline construction from $A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}$}

### 2023-01-01 paper/main.tex
fig 1

@@
         \centering
-        \includegraphics[scale=0.4]{examples/ex2/ex2.png}
+        \begin{tikzpicture}
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [below=0.4cm of p1] {\!\!\!$p$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
+        \node (m) at ($(p1)!0.5!(p2)$) {};
+        \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.5cm}] (g) [right= 1.35cm of m] {};
+
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p4) [right= 1.5cm of m] {\!\!\!$\lnot p$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p5) [right= 1cm of p4] {\!\!\!$p$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 4cm of m] {\!\!\!start\!\!\!};
+        \draw[thick] (s) edge[-latex] (p1) (s) edge[-latex] (p3) (p3) edge[-latex] (p2) (p1) edge[-latex] (p4) (p2) edge[-latex] (p4) (p4) edge[-latex] (p5);
+
+        \end{tikzpicture}
+   %     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
         \caption{Example timeline for specification ``$p$ oscillates every time step''}
@@
         \begin{tikzpicture}
-	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (u) {$u$};
-	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (v) [right=of u] {$v$};
-	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm}] (w) [right=of v] {$w$};
+	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (u) {$u$};
+	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (v) [right=of u] {$v$};
+	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (w) [right=of v] {$w$};
 	\draw[thick] (u) edge["$r_{uv}$",-latex] (v) (v) edge["$r_{vv}$",-latex,loop above] (v) (v) edge["$r_{vw}$",-latex] (w); 

### 2023-01-01 paper/main.tex
fig 4 and fig 5

@@
         \centering
+                \resizebox{\textwidth}{!}{
+        \begin{tikzpicture}
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
+        \node (m) at ($(a1)!0.5!(a2)$) {};
+        \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=3cm}] (g) [right= -1.1cm of m] {};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$\dots$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a6) [right= 0.75cm of a5] {\!\!\!$\lnot a$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 12.5cm of m] {\!\!\!start\!\!\!};
+
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a7) [left= .75cm of a1] {\!\!\!$\lnot a$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a8) [left= .75cm of a2] {\!\!\!$\lnot a$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a9) [left= .75cm of a8] {\!\!\!$a$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a10) [left= .75cm of a9] {\!\!\!$\dots$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a11) [left= .75cm of a10] {\!\!\!$a$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a12) [left= .75cm of a11] {\!\!\!$a$\!\!\!};
+
+        \draw[thick] (s) edge[-latex] (a12) (s) edge[-latex] (a7) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
+        \draw[thick] (a12) edge[-latex] (a11) (a11) edge[-latex] (a10) (a10) edge[-latex] (a9) (a9) edge[-latex] (a8) (a8) edge[-latex] (a1) (a8) edge[-latex] (a2) (a7) edge[-latex] (a1) (a7) edge[-latex] (a2);
+
+        \end{tikzpicture}}
         \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
@@
         \centering
+        \resizebox{.8\textwidth}{!}{
+        \begin{tikzpicture}
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
+  %      \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
+        \node (m) at ($(a1)!0.5!(a2)$) {};
+        \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=3cm}] (g) [right= -1.1cm of m] {};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$\dots$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$a$\!\!\!};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a6) [right= 0.75cm of a5] {\!\!\!$\lnot a$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 2cm of m] {\!\!\!start\!\!\!};
+        \draw[thick] (s) edge[-latex] (a1) (s) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
+        \end{tikzpicture}}
         \includegraphics[scale=0.3]{examples/ex9/ex9.png}

### 2023-01-01 paper/main.tex
line width

@@
 
-        \draw[thick] (s) edge[-latex] (a12) (s) edge[-latex] (a7) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
-        \draw[thick] (a12) edge[-latex] (a11) (a11) edge[-latex] (a10) (a10) edge[-latex] (a9) (a9) edge[-latex] (a8) (a8) edge[-latex] (a1) (a8) edge[-latex] (a2) (a7) edge[-latex] (a1) (a7) edge[-latex] (a2);
+        \draw[thick, line width=1.25] (s) edge[-latex] (a12) (s) edge[-latex] (a7) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
+        \draw[thick, line width=1.25] (a12) edge[-latex] (a11) (a11) edge[-latex] (a10) (a10) edge[-latex] (a9) (a9) edge[-latex] (a8) (a8) edge[-latex] (a1) (a8) edge[-latex] (a2) (a7) edge[-latex] (a1) (a7) edge[-latex] (a2);
 
@@
         \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 2cm of m] {\!\!\!start\!\!\!};
-        \draw[thick] (s) edge[-latex] (a1) (s) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
+        \draw[thick, line width=1.25] (s) edge[-latex] (a1) (s) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
         \end{tikzpicture}}

### 2023-01-01 src/ltl_regex.py
star height def

@@ -9,6 +9,9 @@ class Regex:
     def __len__(self) -> int:
         return regex_tllen(self)
 
+    def star_height(self) -> int:
+        return regex_star_height(self)
+
 
 @dataclass(eq=True, frozen=True)
 class Epsilon(Regex):
@@ -60,7 +63,7 @@ def regex_to_string(regex: Regex) -> str:
             raise TypeError(f'Unknown regex type: {type(regex)}')
 
 def regex_tllen(regex: Regex) -> int:
-    # currently returns timeline length of regex
+    # returns timeline length of regex
     match regex:
         case Epsilon():
             return 0
@@ -77,6 +80,23 @@ def regex_tllen(regex: Regex) -> int:
         case _:
             raise TypeError(f'Unknown regex type: {type(regex)}')
 
+def regex_star_height(regex: Regex) -> int:
+    # currently returns timeline length of regex
+    match regex:
+        case Epsilon():
+            return 0
+        case Empty():
+            return 0
+        case Symbol(s):
+            return 0
+        case Concat(r1, r2):
+            return max(regex_star_height(r1), regex_star_height(r2))
+        case Union(r1, r2):
+            return max(regex_star_height(r1), regex_star_height(r2))
+        case Star(r):
+            return regex_star_height(r) + 1
+        case _:
+            raise TypeError(f'Unknown regex type: {type(regex)}')
 
 @dataclass(eq=True, frozen=True)
 class OmegaRegex:
@@ -84,6 +104,8 @@ class OmegaRegex:
         return omega_regex_to_string(self)
     def __len__(self) -> int:
         return omega_regex_tllen(self)
+    def star_height(self) -> int:
+        return omega_regex_star_height(self)
 
 @dataclass(eq=True, frozen=True)
 class Repeat(OmegaRegex):
@@ -122,5 +144,17 @@ def omega_regex_tllen(omega_regex: OmegaRegex) -> int:
             return regex_tllen(r1) + omega_regex_tllen(r2)
         case UnionOmega(r1, r2):
             return max(omega_regex_tllen(r1), omega_regex_tllen(r2))
+        case _:
+            raise TypeError(f'Unknown omega regex type: {type(omega_regex)}')
+
+
+def omega_regex_star_height(omega_regex: OmegaRegex) -> int:
+    match omega_regex:
+        case Repeat(r):
+            return regex_star_height(r)
+        case ConcatOmega(r1, r2):
[…]

### 2023-01-01 ltl-formulas/benchmark.py
write to txt file

@@ -23,7 +23,7 @@ for i in range(2, 17):
     tacas_counter_ltls.append(f.read())
 print("Found TACAS counter formulas: ", len(tacas_counter_ltls), ". Didn't use") # very long formulas, 1000+ chars, not useful
 
-# acacsia formulas
+# acacia formulas
 base_path = 'ApplicationBenchmarks/acacia_orig_source/acacia/examples/example/'
 
 acacia_ltls = []
@@ -42,17 +42,26 @@ print("Found acacia formulas: ", len(acacia_ltls))
 ltls = aac_ltls # + tacas_counter_ltls (takes too long to compute)
 ltls += [ltl for ltl in acacia_ltls if len(ltl) < 170] # len > takes too long
 # use len < 120 for nice plot, use len < 170 for computable cases that blow up
+ltls = [ltl.strip() for ltl in ltls]
 
-ltllens = [len(ltl.strip()) for ltl in ltls]
+ltllens = [len(ltl) for ltl in ltls]
 regexs = [tl.ltl2regex(ltl) for ltl in ltls]
 tllens = [len(wregex) for wregex in regexs]
 star_heights = [OmegaRegex.star_height(wregex) for wregex in regexs]
+
 
 print("\nNumber of formulas: ", len(ltls))
 print("\nLTL Formula lengths: ", ltllens)
 print("\nTimeline lengths: ", tllens)
 print("\nStar heights: ", star_heights)
 print("\nMean timeline length: ", np.mean(tllens))
+
+
+file = open('benchmark-ltls.txt','w')
+for ltl in ltls:
+	file.write(ltl+";\n")
+file.close()
+print("\nWrote ltl-formulas to benchmark-ltls.txt")
 
[…]

### 2023-01-01 paper/main.tex
no duplicate images
add more details in ltl2ba

@@
 \subsection{LTL to BA} \label{ltl2aut}
-The translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.}.
+The automata-theoretic approach \cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} of studying \ltl\ (i.e.
+reducing \ltl\ formulas to their corresponding \Buchi automata) has been well-studied.
+Many algorithms and optimizations have been studied such as \cite{DGV99, F03}.
+Our tool \tool uses SPOT~\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.} for this step, which provides an implementation of the translation from LTL formulas to \Buchi automata.
 
@@
         \end{tikzpicture}}
-        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
+%        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
         \caption{Timeline for un-simplified $\omega$-regular expression $((!a) | (aa^*(!a)))((!a) | (aa^*(!a)))^{\omega}$}
@@
         \end{tikzpicture}}
-        \includegraphics[scale=0.3]{examples/ex9/ex9.png}
+  %      \includegraphics[scale=0.3]{examples/ex9/ex9.png}
         \caption{Timeline for simplified $\omega$-regular expression $((!a) | (aa^*(!a)))^{\omega}$}

### 2023-01-01 paper/main.tex
add link to formulas

@@
 
-\section{Playing it out} %KYR: may swap order with the next section on artifact availability?
+\section{Playing it out} \label{sec:playing}%KYR: may swap order with the next section on artifact availability?
 
@@
 
-KYR: link LTL database here too.
+The set of \ltl\ formulas we used to evaluate our tool in \cref{sec:playing} can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas}{here}.
 

### 2023-01-01 paper/main.tex
intro, conclusion and minor changes

@@
 \usepackage[strings]{underscore} % fixes doi underscores
-
-\usepackage{graphicx}
-
 \usepackage{hyperref} % brings up so many errors
@@
 \end{frontmatter}
-
 \section{Introduction}
 
-Formal methods, including Linear Temporal Logic (\ltl), are widely used in the specification and analysis of safety-critical systems, such as those found in the aerospace industry.
-These methods provide powerful tools for rigorously verifying the correctness of system designs, from early design-time model checking to on-board runtime verification.
-However, these methods can be difficult for humans to understand and use, leading to the possibility of errors and misunderstandings.
+Requirement specification is a central step in the development of safety-critical systems.
+As a first step, requirements are typically written in natural language.
+For example, here is a real-world requirement specification from an air traffic control system ~\cite{ZR14}
+\begin{center}
+    "If a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft"
+\end{center}
+Such natural language requirements are often ambiguous and not amenable to formal analysis, so requirements must often be specified using rigorous formalized semantics for the purpose of verification and validation.
+The above requirement, when translated to Linear Temporal Logic (detailed in Section 2.1), may be expressed as follows:
+\begin{align*}
+    \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \\
+    \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
+\end{align*}
+Several tools have been developed to reason about formal specifications written with such LTL formulas, like R2U2 and FRET \cite{GPMS20}.
+However, these formalized semantics are unintintuitive and error-prone for human practitioners, and the tools are much less useful when system designers can't validate input specifications.
+Thus, a significant hurdle remains: how can we convincingly demonstrate to the humans in the loop, from system designers to certifiers, that the analyzed formulas truly represent the desired system requirements?
+% quote MLTL paper?
 
-There has been recent work aimed at making the use of formal methods more intuitive for humans, such as NASA's FRET (Formal Requirements Engineering Tool) \cite{GPMS20} which uses structured natural language to bridge the gap between natural language and formal semantics.
+We take a simple idiomatic approach to address this problem.
+As Linear Temporal Logic formulas are temporal information, we devise a tool, \texttt{ltl2timeline}, which can draw timelines to depict the satisfying traces of the LTL formula, and thereby represent the specified behaviour in a more natural human-intelligible form.
 
-However, \ltl\ is literally a language of timelines, so timeline visualizations have the potential to be a powerful tool for representing \ltl\ formulas in an intuitive manner.
-In this paper, we propose such a timeline visualization tool, using regular expressions, to effectively represent a wide range of \ltl-based formulas.
+Our tool, \texttt{ltl2timeline}, uses a remarkably simple algorithm: transforming an input LTL formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of LTL formulas.
+It would visualize the above air traffic control requirement behaviour with the following timeline:
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\textwidth]{examples/ex14/ex14.png}
+    \caption{[TODO: make fig with variables, explain a, b or just use oscillating example if that's easier]}
+\end{figure}
+
+We make the following contributions in our paper:
+\begin{itemize}
+    \item We provide the tool, \texttt{ltl2timeline}, which takes LTL formulas and synthesizes timeline visualizations for them
+    \item We prove correctness in Section 4. We show that for every LTL formula, the timeline outputted indeed represents the set of satisfying traces.
+    \item We showcase the results of our tool on a range of example formulas in Section 5, including discussing the air traffic example above. 
+\end{itemize}
 
 \section{Setting the stage}
+
+We must begin by setting up the prerequisite definitions involved in our work. 
+First, we provide the definition and semantics for LTL.
+In the following subsections, we define (state-based) \Buchi automata and $\omega$-regular expressions, which are generalizations of the well-known deterministic finite automata (DFAs) and regular expressions, for the case of infinite words.
+Lastly, we describe the graphic visualizations we will use to depict timelines.
 
@@
     Zhao and Rozier~\cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula
-    \[
-        \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
-    \]
+    \begin{align*}
+        \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \\
+        \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
+    \end{align*}
     For simplicity, we swap the concrete atomic proposition to $a,b$ and get

### 2023-01-01 paper/main.tex
minor change

--- 2023-01-01 paper/main.tex
@@
         L(\emptyset) & = \emptyset \\
-        L(\epsilon) & = \{\epsilon\} \\
+        L(\epsilon) & = \{\epsilon\} \tag{$\epsilon$ denotes the empty string}\\
         L(a) & = \{a\} \\

### 2023-01-01 paper/main.tex
minor change

@@
         \item Our algorithm is sound and complete.
-        \item Our tool, \texttt{ltl2timeline}, effectively constructs small timeline visualizations for a range of LTL formulas.
+        \item Our tool, \tool, effectively constructs small timeline visualizations for a range of LTL formulas.
     \end{highlights}
@@
 \begin{center}
-    "If a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft"
+    ``If a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft''
 \end{center}
@@
 We take a simple idiomatic approach to address this problem.
-As Linear Temporal Logic formulas are temporal information, we devise a tool, \texttt{ltl2timeline}, which can draw timelines to depict the satisfying traces of the LTL formula, and thereby represent the specified behaviour in a more natural human-intelligible form.
+As Linear Temporal Logic formulas are temporal information, we devise a tool, \tool, which can draw timelines to depict the satisfying traces of the LTL formula, and thereby represent the specified behaviour in a more natural human-intelligible form.
 
-Our tool, \texttt{ltl2timeline}, uses a remarkably simple algorithm: transforming an input LTL formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of LTL formulas.
+Our tool, \tool, uses a remarkably simple algorithm: transforming an input LTL formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of LTL formulas.
 It would visualize the above air traffic control requirement behaviour with the following timeline:
@@
 \begin{itemize}
-    \item We provide the tool, \texttt{ltl2timeline}, which takes LTL formulas and synthesizes timeline visualizations for them
+    \item We provide the tool, \tool, which takes LTL formulas and synthesizes timeline visualizations for them
     \item We prove correctness in Section 4. We show that for every LTL formula, the timeline outputted indeed represents the set of satisfying traces.
@@
 \]
-which comes with two command-line tools, \texttt{ltl2regex} and \texttt{ltl2timeline}. The specific usage of the tool can be found  \href{https://github.com/EULIR/ltl-explainability#usage}{here}.
+which comes with two command-line tools, \texttt{ltl2regex} and \tool. The specific usage of the tool can be found  \href{https://github.com/EULIR/ltl-explainability#usage}{here}.
 
@@
 \appendix
-\section{Concrete Syntax of \texttt{ltl2timeline}} \label{sec:concrete-syntax}
+\section{Concrete Syntax of \tool} \label{sec:concrete-syntax}
 Recall from \ref{ltl-defn} that we define \ltl\ formula as
@@
 \end{align*}
-where $p \in \AP$. In our tool \texttt{ltl2timeline}, we use the following concrete syntax to represent \ltl\ formulae.
+where $p \in \AP$. In our tool \tool, we use the following concrete syntax to represent \ltl\ formulae.
 \[

### 2023-01-01 paper/main.tex
typo

@@
 Such natural language requirements are often ambiguous and not amenable to formal analysis, so requirements must often be specified using rigorous formalized semantics for the purpose of verification and validation.
-The above requirement, when translated to Linear Temporal Logic (detailed in Section 2.1), may be expressed as follows:
+The above requirement, when translated to Linear Temporal Logic (detailed in \cref{sec:ltl}), may be expressed as follows:
 \begin{align*}
@@
 \end{align*}
-Several tools have been developed to reason about formal specifications written with such LTL formulas, like R2U2 and FRET \cite{GPMS20}.
-However, these formalized semantics are unintintuitive and error-prone for human practitioners, and the tools are much less useful when system designers can't validate input specifications.
+Several tools have been developed to reason about formal specifications written with such \ltl\ formulas, like R2U2 and FRET \cite{GPMS20}.
+However, these formalized semantics are unintuitive and error-prone for human practitioners, and the tools are much less useful when system designers can't validate input specifications.
 Thus, a significant hurdle remains: how can we convincingly demonstrate to the humans in the loop, from system designers to certifiers, that the analyzed formulas truly represent the desired system requirements?
@@
 We take a simple idiomatic approach to address this problem.
-As Linear Temporal Logic formulas are temporal information, we devise a tool, \tool, which can draw timelines to depict the satisfying traces of the LTL formula, and thereby represent the specified behaviour in a more natural human-intelligible form.
+As Linear Temporal Logic formulas are temporal information, we devise a tool, \tool, which can draw timelines to depict the satisfying traces of the \ltl\ formula, and thereby represent the specified behavior in a more natural human-intelligible form.
 
-Our tool, \tool, uses a remarkably simple algorithm: transforming an input LTL formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of LTL formulas.
-It would visualize the above air traffic control requirement behaviour with the following timeline:
+Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of \ltl formulas.
+It would visualize the above air traffic control requirement behavior with the following timeline:
 \begin{figure}[!h]
@@
 \begin{itemize}
-    \item We provide the tool, \tool, which takes LTL formulas and synthesizes timeline visualizations for them
-    \item We prove correctness in Section 4. We show that for every LTL formula, the timeline outputted indeed represents the set of satisfying traces.
-    \item We showcase the results of our tool on a range of example formulas in Section 5, including discussing the air traffic example above.
+    \item We provide the tool, \tool, which takes \ltl\ formulas and synthesizes timeline visualizations for them.
+    \item We prove correctness in \cref{sec:analysis}. We show that for every \ltl\ formula, the timeline outputted indeed represents the set of satisfying traces.
+    \item We showcase the results of our tool on a range of example formulas in \cref{sec:tool-showcase} and \cref{sec:playing}, including discussing the air traffic example above.
 \end{itemize}
@@
 We must begin by setting up the prerequisite definitions involved in our work.
-First, we provide the definition and semantics for LTL.
+First, we provide the definition and semantics for \ltl.
 In the following subsections, we define (state-based) \Buchi automata and $\omega$-regular expressions, which are generalizations of the well-known deterministic finite automata (DFAs) and regular expressions, for the case of infinite words.
@@
 
-\subsection{Linear temporal logic (LTL)}
+\subsection{Linear temporal logic (LTL)} \label{sec:ltl}
 
@@
 Many algorithms and optimizations have been studied such as \cite{DGV99, F03}.
-Our tool \tool uses SPOT~\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.} for this step, which provides an implementation of the translation from LTL formulas to \Buchi automata.
+Our tool \tool uses SPOT~\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.} for this step, which provides an implementation of the translation from \ltl\ formulas to \Buchi automata.
 
@@
 
-\section{Theoretical Analyses}
+\section{Theoretical Analyses} \label{sec:analysis}
 \subsection{Correctness of Regex Translation}
@@
 
-\section{Tool showcase}
+\section{Tool showcase} \label{sec:tool-showcase}
 To demonstrate the result of our tool, we present two examples, one from a real-world model checking example from Zhao and Rozier~\cite{ZR14} and one from a randomly generated \ltl\ formula.
@@
 
-We quantify the usability and performance of \tool by compiling an extensive set of LTL formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of all real-life LTL formulas over those metrics.
-We release the set of real-life LTL formulas as a benchmark set for the research community.
-Our experimental evaluation conclusively demonstrates that \tool scales to provide helpful visualizations of LTL formulas written by humans.
+We quantify the usability and performance of \tool by compiling an extensive set of \ltl\ formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of all real-life \ltl\ formulas over those metrics.
+We release the set of real-life \ltl\ formulas as a benchmark set for the research community.
+Our experimental evaluation conclusively demonstrates that \tool scales to provide helpful visualizations of \ltl\ formulas written by humans.
 
@@
 
-We collect the LTL formulas from a covering set of publicly-available case studies that use LTL in the analysis of real-life safety-critical systems.
-As some formulas are redundant (i.e., common properties occur in many different case studies), it is not necessary to include every paper that has ever used LTL in a real setting; we instead opt for the largest and most unique formulas to cover the space of realistic use of LTL.
+We collect the \ltl\ formulas from a covering set of publicly-available case studies that use \ltl\ in the analysis of real-life safety-critical systems.
+As some formulas are redundant (i.e., common properties occur in many different case studies), it is not necessary to include every paper that has ever used \ltl\ in a real setting; we instead opt for the largest and most unique formulas to cover the space of realistic use of \ltl.
 
-Given the tremendous popularity of LTL as a specification language for industrial analysis, surprisingly few real-life system analysis case studies publicly release their LTL formula specifications, largely to protect proprietary system information.
-We purposely avoid using the random or machine-generated formulas from published benchmarks because the purpose of \tool is helping humans understand and validate LTL formulas.
+Given the tremendous popularity of \ltl\ as a specification language for industrial analysis, surprisingly few real-life system analysis case studies publicly release their \ltl\ formula specifications, largely to protect proprietary system information.
+We purposely avoid using the random or machine-generated formulas from published benchmarks because the purpose of \tool is helping humans understand and validate \ltl\ formulas.
 Thus, we gather an extensive, representative set of formulas humans have written or needed to understand.
-Our LTL formula collection is as follows.
+Our \ltl\ formula collection is as follows.
 
@@
 \paragraph{Scalability}
-KYR: Here we characterize the size of the timeline as a function of the number of bits of a binary counter for each of the four binary counter LTL formulas.
+KYR: Here we characterize the size of the timeline as a function of the number of bits of a binary counter for each of the four binary counter \ltl\ formulas.
 The point is that these four are the only (unboundedly) scalable formulas that describe something real (i.e., they describe a binary counter for any number of bits) that have ever been published in the literature.
-These would throw off our metrics about the set of real LTL formulas if we included them in there.
+These would throw off our metrics about the set of real \ltl\ formulas if we included them in there.
 Thus, we analyze them separately, and can define the timeline size as a function of the number of bits for each of the four formulas.
@@
 \section{Conclusion}
-Making formal methods, such as LTL, easier for humans in the loop is an important problem today, in making systems safer with verification.
-In this paper, we present a novel tool to visualize LTL specification behavior and aid in validating their correctness.
-We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for LTL.
+Making formal methods, such as \ltl, easier for humans in the loop is an important problem today, in making systems safer with verification.
+In this paper, we present a novel tool to visualize \ltl\ specification behavior and aid in validating their correctness.
+We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for \ltl.
 

### 2023-01-01 paper/main.tex
minor change

@@
 
-Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of \ltl formulas.
-It would visualize the above air traffic control requirement behavior with the following timeline:
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=\textwidth]{examples/ex14/ex14.png}
-    \caption{[TODO: make fig with variables, explain a, b or just use oscillating example if that's easier]}
-\end{figure}
+Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of \ltl\ formulas.
+It would visualize the above air traffic control requirement behavior with the timeline shown in \cref{example:air}.
 
@@
 
-\begin{example}
+\begin{example} \label{example:air}
     Zhao and Rozier~\cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula

### 2023-01-01 paper/main.tex
add scalibility paragraph

@@
 Correct as they faithfully represent the set of satisfying traces of the original \ltl\ formula $\Phi$.
-Nonetheless, we, as human user, oftentimes find the simplified version more intuitive to reason about.
+Nonetheless, we, as human users, oftentimes find the simplified version more intuitive to reason about.
 \end{remark}
@@
 \paragraph{Scalability}
-KYR: Here we characterize the size of the timeline as a function of the number of bits of a binary counter for each of the four binary counter \ltl\ formulas.
+We measure the scalability of our tool by running it against a set of scalable \ltl\ formulas.
+We define a scalable \ltl\ formula as one that describes an $n$-bit number using a binary counter \cite{RV10}.
+As $n$ gets larger, the \ltl\ formula used to encode the $n$-bit counter scales in size, but it remains practical.
+The result is shown in \cref{fig:scalability}.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[scale=0.7]{img/scale.png}
+    \caption{Scalability measured with binary counter examples from Rozier and Vardi \cite{RV10}}
+    \label{fig:scalability}
+\end{figure}
+
+% KYR: Here we characterize the size of the timeline as a function of the number of bits of a binary counter for each of the four binary counter \ltl\ formulas.
 The point is that these four are the only (unboundedly) scalable formulas that describe something real (i.e., they describe a binary counter for any number of bits) that have ever been published in the literature.

### 2023-01-02 paper/main.tex
minor algo1 fix
update scalability

@@
         \EndFor
+	\State delete node $v$ from $G$
         %\State \Return the reduced graph $G$
@@
 The result is shown in \cref{fig:scalability}.
+In this analysis, the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi \cite{RV10}.
+
+In \cref{fig:scalability}, the x-axis ranges from $1$ to $6$, after which point it hits the $30$ seconds timeout we set, as the timeline length grows exponentially fast.
+
 \begin{figure}[h!]

### 2023-01-02 paper/main.tex
added a new conclusion, more citations

@@
 \section{Conclusion}
-Making formal methods, such as \ltl, easier for humans in the loop is an important problem today, in making systems safer with verification.
-In this paper, we present a novel tool to visualize \ltl\ specification behavior and aid in validating their correctness.
-We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for \ltl.
+The Achilles heel of formal verification is specification; formal methods are only as effective at verification as their specifications are at describing the essential properties to verify.
+Yet, specification remains the biggest bottleneck to the use of formal methods \cite{Roz16}.
+LTL is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway \cite{DBR21}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system \cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS) \cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept \cite{CDRWRWL22} just to name a few.
+ %
+Yet the humans that need to use formal verification tools and deeply understand their results struggle to validate that LTL formulas capture the specifications they are meant to capture.
+A major contributor to LTL's popularity is the propensity of humans to think of requirements in terms of timelines.
+This inspired the creation of LTL in the first place, as a logic that ``intuitively'' represents timelines.
+Our work serves to reinforce that connection, enabling visualization of most realistic LTL formulas as timelines.
+By releasing \tool, we contribute to better validation capabilities for LTL specifications and aid the effort to make formal verification more accessible and wide-spread.
+%We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for \ltl.
+
+Future extensions of this work include optimizations to the algorithm and implementation to improve performance and scalability.
+While we have chosen visual elements that succinctly represent timelines, it would be informative to conduct a study on different possible visualizations and which of the many ways of representing different timeline elements humans find most intuitive.
+It is possible that factors of context, such as the type of requirement an LTL formula describes, change its optimal timeline representation.
 

### 2023-01-02 paper/main.tex
added realworld tests

--- 2023-01-02 paper/main.tex
@@
 
-\usepackage{amsmath, amssymb, amsthm,tikz}
+\usepackage{amsmath, amssymb, amsthm,tikz, subfig}
 \usetikzlibrary{positioning,shapes,quotes,calc}
@@
 KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
+\paragraph{Real-world datasets} We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
+
+We gather a test suite of 91 formulas used in real-world requirement specification.
+We take $6$ specifications from NASA's Automated Airspace Concept (AAC)\cite{GCMTR16}.
+We also collect formulas from the Acacia suite of examples \cite{RV10}.
+We reap $85$ formulas from the suit of $23$ examples, by generating seperate visualizations for each line of specification.
+% We choose to visualize each formula specifically, rather than complete specifications, as
+
+We run \texttt{ltl2regex} on these $91$ examples, the tool completes execution (within timeout of $20$s) on $87$.
+Within the $87$, two examples have regular expressions of star height $8$ and are intractible to generate graph visualizations of.
+We are able to generate tractible visualization on the $85$, or over $93\%$ of benchmarks tested.
+The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.
+
+\begin{figure}[h!]
+    \centering
+    \subfloat{{\includegraphics[width=6.5cm]{img/naive-ltl2tl-scatterplot-omit-big-values.png} }}%
+    \quad % [\centering label 1]
+    \subfloat{{\includegraphics[width=6.5cm]{img/star-height-scatter-plot.png}}}
+    \caption{Visualization complexity metrics for formulas collected from Acacia \cite{RV10} and NASA's  AAC \cite{GCMTR16}}
+    \label{fig:real-world}
+\end{figure}
 

### 2023-01-02 paper/main.tex
cleaned up section 6

@@
 
-The soundness of each of these translations can be proven by reasoning about the  semantics detailed in \cref{def:omega-semantics}. A full proof is not provided at this time.
+The soundness of each of these translations can be proven by reasoning about the  semantics detailed in \cref{def:omega-semantics}. A full proof is not provided here.
 
@@
 
-\subsection{Set of Real LTL Formulas}
-
-We collect the \ltl\ formulas from a covering set of publicly-available case studies that use \ltl\ in the analysis of real-life safety-critical systems.
-As some formulas are redundant (i.e., common properties occur in many different case studies), it is not necessary to include every paper that has ever used \ltl\ in a real setting; we instead opt for the largest and most unique formulas to cover the space of realistic use of \ltl.
-
-Given the tremendous popularity of \ltl\ as a specification language for industrial analysis, surprisingly few real-life system analysis case studies publicly release their \ltl\ formula specifications, largely to protect proprietary system information.
-We purposely avoid using the random or machine-generated formulas from published benchmarks because the purpose of \tool is helping humans understand and validate \ltl\ formulas.
-Thus, we gather an extensive, representative set of formulas humans have written or needed to understand.
-Our \ltl\ formula collection is as follows.
-
-\noindent
-\begin{table}[h]
-\begin{tabular}{p{3.6in}|c|c}
-  \hline
-  Purpose & \# formulas & Source \\
-  \hline
-  Design space for NASA's AAC (Automated Airspace Concept) & 20,250 & \cite{GCMTR16} \\
-  \hline
-  Safety specifications for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
-  \hline
-  Requirements for model checking NASA's AAC high-level architecture & 6 & \cite{ZR14} \\
-  \hline
-  Real formulas collected from all publicly-available, pre-2011 case studies & 63 & \cite{RV11} \\
-  \hline
-\end{tabular}
-\end{table}
-
 \subsection{Timeline Metrics}
@@
 
-KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
+%KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
 \paragraph{Real-world datasets} We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
@@
 
-\paragraph{Denouement}
-KYR: aggregate and summarize all experiments here.
+%\paragraph{Denouement}
+%KYR: aggregate and summarize all experiments here.
 
-<image>
-caption: For all of the <large number> of real LTL formulas historically used to analyze real systems, \tool efficiently yields usable, readable timeline visualizations.
+%<image>
+%caption: For all of the <large number> of real LTL formulas historically used to analyze real systems, \tool efficiently yields usable, readable timeline visualizations.
 
@@
 \end{document}
+
+\subsection{Set of Real LTL Formulas}
+
+We collect the \ltl\ formulas from a covering set of publicly-available case studies that use \ltl\ in the analysis of real-life safety-critical systems.
+As some formulas are redundant (i.e., common properties occur in many different case studies), it is not necessary to include every paper that has ever used \ltl\ in a real setting; we instead opt for the largest and most unique formulas to cover the space of realistic use of \ltl.
+
+Given the tremendous popularity of \ltl\ as a specification language for industrial analysis, surprisingly few real-life system analysis case studies publicly release their \ltl\ formula specifications, largely to protect proprietary system information.
+We purposely avoid using the random or machine-generated formulas from published benchmarks because the purpose of \tool is helping humans understand and validate \ltl\ formulas.
+Thus, we gather an extensive, representative set of formulas humans have written or needed to understand.
+Our \ltl\ formula collection is as follows.
+
+\noindent
+\begin{table}[h]
+\begin{tabular}{p{3.6in}|c|c}
+  \hline
+  Purpose & \# formulas & Source \\
+  \hline
+  Design space for NASA's AAC (Automated Airspace Concept) & 20,250 & \cite{GCMTR16} \\
+  \hline
+  Safety specifications for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
+  \hline
+  Requirements for model checking NASA's AAC high-level architecture & 6 & \cite{ZR14} \\
+  \hline
+  Real formulas collected from all publicly-available, pre-2011 case studies & 63 & \cite{RV11} \\
+  \hline
+\end{tabular}
+\end{table}

### 2023-01-02 paper/main.tex
minor edit to sec 6

@@
 
-We quantify the usability and performance of \tool by compiling an extensive set of \ltl\ formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of all real-life \ltl\ formulas over those metrics.
-We release the set of real-life \ltl\ formulas as a benchmark set for the research community.
+We quantify the usability and performance of \tool by compiling an extensive set of \ltl\ formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of real-life \ltl\ formulas over those metrics.
+% We release the set of real-life \ltl\ formulas as a benchmark set for the research community. 
 Our experimental evaluation conclusively demonstrates that \tool scales to provide helpful visualizations of \ltl\ formulas written by humans.

### 2023-01-02 paper/main.tex
fix typo
minor change

@@
     \begin{highlights}
-        \item We transform Linear Temporal Logic (LTL) formulas to timeline visualizations for the set of satisfying traces.
-        \item We translate LTL formulas to \Buchi automata, then to $\omega$-regular expressions, then simplify them and use graph visualization tools to draw timelines.
+        \item We transform Linear Temporal Logic (\ltl) formulas to timeline visualizations for the set of satisfying traces.
+        \item We translate \ltl\ formulas to \Buchi automata, then to $\omega$-regular expressions, then simplify them and use graph visualization tools to draw timelines.
         \item Our algorithm is sound and complete.
-        \item Our tool, \tool, effectively constructs small timeline visualizations for a range of LTL formulas.
+        \item Our tool, \tool, effectively constructs small timeline visualizations for a range of \ltl\ formulas.
     \end{highlights}
@@
     % cite Kristin's survey paper
-    The syntax of an LTL formula over a set of atomic propositions $\AP$, where $p\in\AP$ is a propositional variable, is given by the following grammar:
+    The syntax of an \ltl\ formula over a set of atomic propositions $\AP$, where $p\in\AP$ is a propositional variable, is given by the following grammar:
     \begin{align*}
@@
 %KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
-\paragraph{Real-world datasets} We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
+\paragraph{Real-world datasets} We study the feasibility of our tool on a benchmark suite of \ltl\ formulas gathered from real world use cases.
 
@@
 
-In \cref{fig:scalability}, the x-axis ranges from $1$ to $6$, after which point it hits the $30$ seconds timeout we set, as the timeline length grows exponentially fast.
+In \cref{fig:scalability}, the $x$-axis ranges from $1$ to $6$, after which point it hits the $30$ seconds timeout we set, as the timeline length grows exponentially fast.
 
@@
     \centering
-    \includegraphics[scale=0.7]{img/scale.png}
+    \includegraphics[scale=0.6]{img/scale.png}
     \caption{Scalability measured with binary counter examples from Rozier and Vardi \cite{RV10}}
@@
 Yet, specification remains the biggest bottleneck to the use of formal methods \cite{Roz16}.
-LTL is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway \cite{DBR21}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system \cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS) \cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept \cite{CDRWRWL22} just to name a few.
+\ltl\ is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway \cite{DBR21}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system \cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS) \cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept \cite{CDRWRWL22} just to name a few.
  %
-Yet the humans that need to use formal verification tools and deeply understand their results struggle to validate that LTL formulas capture the specifications they are meant to capture.
-A major contributor to LTL's popularity is the propensity of humans to think of requirements in terms of timelines.
-This inspired the creation of LTL in the first place, as a logic that ``intuitively'' represents timelines.
-Our work serves to reinforce that connection, enabling visualization of most realistic LTL formulas as timelines.
-By releasing \tool, we contribute to better validation capabilities for LTL specifications and aid the effort to make formal verification more accessible and wide-spread.
+Yet the humans that need to use formal verification tools and deeply understand their results struggle to validate that \ltl\ formulas capture the specifications they are meant to capture.
+A major contributor to \ltl's popularity is the propensity of humans to think of requirements in terms of timelines.
+This inspired the creation of \ltl\ in the first place, as a logic that ``intuitively'' represents timelines.
+Our work serves to reinforce that connection, enabling visualization of most realistic \ltl\ formulas as timelines.
+By releasing \tool, we contribute to better validation capabilities for \ltl\ specifications and aid the effort to make formal verification more accessible and wide-spread.
 %We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for \ltl.
@@
 While we have chosen visual elements that succinctly represent timelines, it would be informative to conduct a study on different possible visualizations and which of the many ways of representing different timeline elements humans find most intuitive.
-It is possible that factors of context, such as the type of requirement an LTL formula describes, change its optimal timeline representation.
+It is possible that factors of context, such as the type of requirement an \ltl\ formula describes, change its optimal timeline representation.
 

### 2023-01-02 paper/main.tex
typo

@@
 We also collect formulas from the Acacia suite of examples \cite{RV10}.
-We reap $85$ formulas from the suit of $23$ examples, by generating seperate visualizations for each line of specification.
+We reap $85$ formulas from the suite of $23$ examples, by generating separate visualizations for each line of specification.
 % We choose to visualize each formula specifically, rather than complete specifications, as
@@
 We run \texttt{ltl2regex} on these $91$ examples, the tool completes execution (within timeout of $20$s) on $87$.
-Within the $87$, two examples have regular expressions of star height $8$ and are intractible to generate graph visualizations of.
-We are able to generate tractible visualization on the $85$, or over $93\%$ of benchmarks tested.
+Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of.
+We are able to generate tractable visualization on the $85$, or over $93\%$, of benchmarks tested.
 The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.
@@
 \]
-
+%\nocite{*}
 \bibliographystyle{elsarticle-num}

### 2023-01-02 paper/main.tex
small change

@@
 We reap $85$ formulas from the suite of $23$ examples, by generating separate visualizations for each line of specification.
+We choose to visualize each formula specifically, rather than complete specifications, as complete specifications may describe large complex systems, and we only intend the use case of validating individual specification formulas.
 % We choose to visualize each formula specifically, rather than complete specifications, as
@@
 Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of.
-We are able to generate tractable visualization on the $85$, or over $93\%$, of benchmarks tested.
+We are able to generate tractable visualization on the remaining $85$, or over $93\%$ of benchmarks tested.
 The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.

### 2023-01-02 paper/main.tex
typo fix
getting rid of bang

@@
 \begin{example}
-    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by two nodes with $!a$ separated by $\cdots$ (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $1$ (true) in the grey box.
+    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by two nodes with $\lnot a$ separated by $\cdots$ (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $1$ (true) in the grey box.
     \begin{figure}[!h]
@@
 \begin{example}
-    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((!a) | (aa^*(!a)))((!a) | (aa^*(!a)))^{\omega}$, and simplified version $((!a) | (aa^*(!a)))^{\omega}$, which corresponds to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
+    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which corresponds to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
     \begin{figure}[h!]
@@
 %        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
-        \caption{Timeline for un-simplified $\omega$-regular expression $((!a) | (aa^*(!a)))((!a) | (aa^*(!a)))^{\omega}$}
+        \caption{Timeline for %un-simplified 
+        $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
         \label{fig:unsimplified}
@@
   %      \includegraphics[scale=0.3]{examples/ex9/ex9.png}
-        \caption{Timeline for simplified $\omega$-regular expression $((!a) | (aa^*(!a)))^{\omega}$}
+        \caption{Timeline for simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
         \label{fig:simplified}
@@
         \tllen(A_1 A_2)     &= \tllen(A_1) + \tllen(A_2)\\
-        \tllen(A_1 + A_2)   &= \max(\tllen(A_1, A_2))\\
+        \tllen(A_1 + A_2)   &= \max(\tllen(A_1), \tllen(A_2))\\
         \tllen(A^*)         &= 2\tllen(A) + 1

### 2023-01-02 paper/main.tex
figures

@@
 
+\newcommand{\tand}{\land}
+\newcommand{\tor}{\lor}
+\newcommand{\tnot}{\lnot}
+
 \newcommand{\Buchi}{B\"{u}chi }
@@
     \affiliation[inst1]{organization={Carnegie Mellon University},%Department and Organization
-                addressline={5000 Forbes Ave},
+                %addressline={5000 Forbes Ave},
                 city={Pittsburgh},
-                postcode={15213},
+                %postcode={15213},
                 state={PA},
@@
                 city={Ames},
-                postcode={50010},
+                %postcode={50010},
                 state={IA},
@@
         \node (m) at ($(p1)!0.5!(p2)$) {};
-        \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.5cm}] (g) [right= 1.35cm of m] {};
+        \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.25cm}] (g) [right= 1.35cm of m] {};
 
@@
         \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 4cm of m] {\!\!\!start\!\!\!};
-        \draw[thick] (s) edge[-latex] (p1) (s) edge[-latex] (p3) (p3) edge[-latex] (p2) (p1) edge[-latex] (p4) (p2) edge[-latex] (p4) (p4) edge[-latex] (p5);
+        \draw[thick, line width=1.25] (s) edge[-latex] (p1) (s) edge[-latex] (p3) (p3) edge[-latex] (p2) (p1) edge[-latex] (p4) (p2) edge[-latex] (p4) (p4) edge[-latex] (p5);
 
@@
         \centering
-        \includegraphics[scale=0.4]{examples/ex15/ex15.png}
+        \begin{tikzpicture}
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) {\!\!\!start\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) [right= 0.75cm of s] {\!\!\!$\lnot a$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [right= 0.75cm of a1] {\!\!\!$\dots$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$\lnot a$\!\!\!};
+        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$a$\!\!\!};
+        \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.25cm}] (g) [right= 0.6cm of a4] {};
+        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$1$\!\!\!};
+        \draw[thick, line width=1.25] (s) edge[-latex] (a1) (a1) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5);
+
+        \end{tikzpicture}
+    %    \includegraphics[scale=0.4]{examples/ex15/ex15.png}
         \caption{Example timeline for specification ``$a$ is eventually true''}
@@
         \centering
-        \includegraphics[scale=0.3]{examples/ex14/ex14.png}
+        \resizebox{\textwidth}{!}{
+        \begin{tikzpicture}
+            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) {\!\!\!\!start\!\!\!\!};
+            \node[shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab1) [right= of s]{\!\!\!\!$a \tand b$\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!$a \tand b$\!\!\!\!};
+            \node (m) at ($(ab1)!0.5!(ab2)$) {};
+            \node[shape=rectangle, fill=gray!30!white, style={minimum width=4cm, minimum height=3cm}] (g2) [right= -1cm of m] {};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab1) [right= of s]{\!\!\!\!$a \tand b$\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!$a \tand b$\!\!\!\!};
+            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab3) [below= 0.6cm  of ab1]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (b1) [right= 0.75cm  of ab1]{\!\!\!\!\!\!\!\!$\tnot b$\!\!\!\!\!\!\!\!};
+            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab4) [right= .75cm of ab3]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
+            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab5) [right= .75cm of ab4]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab6) [right= .75cm of ab5]{\!\!\!\!\!\!\!\!$a \tand b$\!\!\!\!\!\!\!\!};
+            \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=1.3cm}] (g2) [right= 0.6cm of ab6] {};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab7) [right= .75cm of ab6]{\!\!\!\!\!\!\!\!$\tnot b$\!\!\!\!\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab8) [right= .75cm of ab7]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab9) [right= .75cm of ab8]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab10) [right= .75cm of ab9]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab11) [right= .75cm of ab10]{\!\!\!\!\!\!\!\!$a \tand b$\!\!\!\!\!\!\!\!};
+
+        \draw[thick, line width=1.25] (s) edge[-latex] (ab1) (s) edge[-latex] (ab2) (s) edge[-latex] (ab3) (ab3) edge[-latex] (ab4) (ab4) edge[-latex] (ab5) (ab5) edge[-latex] (ab6) (ab1) edge[-latex] (b1);
+        \draw[thick, line width=1.25] (ab6) edge[-latex] (ab7) (ab6) edge[-latex] (ab7) (ab7) edge[-latex] (ab8) (ab8) edge[-latex] (ab9) (ab9) edge[-latex] (ab10) (ab10) edge[-latex] (ab11);
+
+        \end{tikzpicture}}
+
+     %   \includegraphics[scale=0.3]{examples/ex14/ex14.png}
         \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
@@
         \centering
-        \includegraphics[scale=0.3]{examples/ex13/ex13.png}
+        \resizebox{\textwidth}{!}{
+        \begin{tikzpicture}
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) {\!\!\!\!start\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) [right= .75cm of s]{\!\!\!\!\!\!\!\!$p_2$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [right= .75cm of p1]{\!\!\!\!\!\!\!\!$\tnot p_0 \! \tand \!  p_1$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [right= .75cm of p2]{\!\!\!\!\!\!\!\!$\tnot p_0 \! \tand \!  p_1$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p4) [right= .75cm of p3]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p5) [right= .75cm of p4]{\!\!\!\!\!\!\!\!$\tnot p_0 \! \tand \!  p_1$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p6) [right= .75cm of p5]{\!\!\!\!\!\!\!\!$p_0 \! \tand \! p_1$\!\!\!\!\!\!\!\!};
+
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p7) [above= .6cm of p1]{\!\!\!\!\!\!\!\!$p_2$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p8) [above= .6cm of p6]{\!\!\!\!\!\!\!\!$p_0 \! \tand \! p_1$\!\!\!\!\!\!\!\!};
+            \node (m) at ($(p6)!0.5!(p8)$) {};
+            \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.25cm}] (g1) [right= 1cm of m] {};
+           \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (o1) [right= 1.15cm of m]{\!\!\!\!\!\!\!\!$p_1$\!\!\!\!\!\!\!\!};
+
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p9) [below= .6cm of p1]{\!\!\!\!\!\!\!\!$p_2$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p10) [below= .6cm of p2]{\!\!\!\!\!\!\!\!$1$\!\!\!\!\!\!\!\!};
+	   \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p11) [below= .6cm of p3]{\!\!\!\!\!\!\!\!$1$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p12) [below= .6cm of p4]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
+           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p13) [below= .6cm of p5]{\!\!\!\!\!\!\!\!$1$\!\!\!\!\!\!\!\!};
+           \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.25cm}] (g2) [right= 0.6cm of p13] {};
+
+           \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p14) [below= .6cm of p6]{\!\!\!\!\!\!\!\!$p_0 \! \tand \! p_1$\!\!\!\!\!\!\!\!};
+
+           \draw[thick, line width=1.25] (s) edge[-latex] (p1) (s) edge[-latex] (p7) (s) edge[-latex] (p9) (p1) edge[-latex] (p2) (p2) edge[-latex] (p3) (p3) edge[-latex] (p4) (p4) edge[-latex] (p5) (p5) edge[-latex] (p6) (p7) edge[-latex] (p8);
+           \draw[thick, line width=1.25] (p8) edge[-latex] (o1) (p6) edge[-latex] (o1) (p9) edge[-latex] (p10) (p10) edge[-latex] (p11) (p11) edge[-latex] (p12) (p12) edge[-latex] (p13) (p13) edge[-latex] (p14);
+
+        \end{tikzpicture}}
+
+   %     \includegraphics[scale=0.3]{examples/ex13/ex13.png}
         \caption{Timeline for $p_2 \land (\eventually \always p_0 \weakrelease \nextt(\always p_1 \land ((p_0 \limplies p_2 \land p_2 \limplies p_0) \stronguntil \eventually p_0)))$}

### 2023-01-02 paper/main.tex
bib

@@
 \begin{example}
-    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$.
-Then at the end of the grey box, we reenter the box, with the next time step being $!p$, and so on.
-The lower timeline starts with one step of $!p$ and one step of $p$ outside the grey box, and then enter the infinite run of $!p$ and $p$ repeating.
+    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $\lnot p$ and one step of $p$.
+Then at the end of the grey box, we reenter the box, with the next time step being $\lnot p$, and so on.
+The lower timeline starts with one step of $\lnot p$ and one step of $p$ outside the grey box, and then enter the infinite run of $\lnot p$ and $p$ repeating.
     \begin{figure}[!h]

### 2023-01-12 paper/main.tex
Added visualization discussion

@@
 
+Going forward, it will become important to conduct a user survey to gather data from a representative audience of system engineers regarding what timeline visualizations help most with formula validation.
+Specifically, we list the following questions regarding the intuitive aesthetics of timelines.
+\begin{itemize}
+\item {\bf Can lines in timelines be curved or do they need to be straight?} If a timeline has a curved line is that still visually, intuitively a line?
+Does the placement of the line matter as to whether it is intuitive for the line to be straight or curved (e.g., to save space or reduce possible visual clutter)?
+
+\item {\bf Can there be back edges in a limited fashion (i.e., to simplify formulas) in timelines?} Most of our formulas have star-height of 1, so if we limit the back-edge representation to only surrounding a single node, that would simplify most formulas.
+We can then use the expanded notation for stared formulas larger than a single proposition, thus navigating a trade-off between small representation and limiting the visual complication.
+Do the back edges in a limited capacity cause confusion between timeline and automata representatins?
+
+\item {\bf What are intuitive representations of star-formulas and do they change depending on the formula?} There are two ways to represent stars in regular expressions \cite{Runming where did you find these?}.
+We can represent a stared formula inside a box \cite{where?} or with a back edge \cite{where?}.
+Does using the box cause confusion with respect to the LTL $\Box$ operator?
+What is the most intuitive way to remind users of the corner case where the starred formula occurs zero times?
+
+\item {\bf When do we choose to unroll for clarity?
+When do we merge parallel parts of timelines?} To merge parts of lines, we have to check for logical equivalence of the parts of the timelines we want to merge.
+By our algorithm, we generate parallel lines only when the formulas are not syntactically equivalent, so we would be guaranteed to run the more complex check for logical equivalence.
+In some cases, this could provide a clarifying simplification, with the cost of a repetitive computationally expensive check.
+Would it make sense to offer an ``optimizing'' compilation option to users that takes longer to create a timeline representation but checks for smaller representations via logical equivalence?
+\end{itemize}
+KYR note: we should include a figure here with the different visual options we brainstormed and reference it in the bullets above.
+
 \section{Conclusion}

### 2023-01-13 ltl-formulas/benchmark.py
boing ltls + replot with ltllen

@@ -4,7 +4,9 @@ sys.path.append('/home/kgurusha/Documents/CMU/15816/ltl-explainability/src')
 from main import *
 tl = Ltl2Regex()
 
+import re
 import numpy as np
+import matplotlib.pyplot as plt
 
 # AAC formulas
 aac_file = open('AAC_Communication_Protocol.ltl', 'r')
@@ -13,7 +15,6 @@ aac_ltls = [spec.split(' ', 1)[1] for spec in aac_specs]
 print("Found AAC formulas: ", len(aac_ltls))
 
 # RV11 formulas
-
 # tacas08 counter formulas 
 base_path = 'ApplicationBenchmarks/AlaskaBenchmarks/tacas08_experiments/counter/'
 
@@ -39,16 +40,36 @@ for i in range(1,24):
     
 print("Found acacia formulas: ", len(acacia_ltls))
 
-ltls = aac_ltls # + tacas_counter_ltls (takes too long to compute)
-ltls += [ltl for ltl in acacia_ltls if len(ltl) < 170] # len > takes too long
-# use len < 120 for nice plot, use len < 170 for computable cases that blow up
+
+# Boeing formulas
+f = open('wbs-ltlspecs.txt', 'r')
+lines = f.readlines()
+wbs_ltls = [line.split(':= ',1)[1][:-2] for line in lines]
+wbs_ltls = list(set(wbs_ltls))
+
+def clean_ltl(ltl):
+    ltl = re.sub(r'(\w+)\s*(>|<|>=|<=|=|!=)\s*(\w+)', r'\1_cmp_\3', ltl) # var1 <cmp> var2/num => var1_cmp_var2
+    ltl = ltl.replace('next', 'X') 
+    ltl = ltl.replace('= rolling', '') # wheel status = rolling is treated as wheel status is true
+    ltl = re.sub(r'([\w()]+)\s*=\s*stopped', r'!\1', ltl) # 'stopped' wheel status is false
+    return ltl
+
[…]

### 2023-01-27 paper/main.tex
merge

--- 2023-01-02 paper/main.tex
@@
 \newcommand{\tllen}{\text{tllen}}
+
+\tikzset{
+    partial ellipse/.style args={#1:#2:#3}{
+        insert path={+ (#1:#3) arc (#1:#2:#3)}
+    }
+}
 
@@
 \end{frontmatter}
+
 \section{Introduction}
+
+\begin{figure}[h]
+  \centering
+  \begin{tikzpicture}
+        \node[fill=white!50!gray, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
+        \node (p0) [left= 0.5cm of p1] {};
+        \node (p2) [right= 0.5cm of p1] {};
+        \draw[-latex, thick] (p0) edge (p1) (p1) edge (p2);
+
+%        \draw[thick, black, -latex] (0,0) [partial ellipse=180:90:0.75cm and 0.5cm];
+%        \draw[thick, black, -] (0,0) [partial ellipse=90:0:0.75cm and 0.5cm];
+%
+%        \draw[thick, black, -latex] (0,0) [partial ellipse=360:270:0.75cm and 0.5cm];
+%        \draw[thick, black, -] (0,0) [partial ellipse=270:180:0.75cm and 0.5cm];
+
+   \end{tikzpicture}
+   ~~~~~
+    \begin{tikzpicture}
+        \node[fill=white!50!gray, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
+        \node (p0) [left= 0.5cm of p1] {};
+        \node (p2) [right= 0.5cm of p1] {};
+        \draw[-latex, thick] (p0) edge (p1) (p1) edge (p2);
+
+%        \draw[thick, black, -latex] (0,0) [partial ellipse=180:90:0.75cm and 0.5cm];
+%        \draw[thick, black, -] (0,0) [partial ellipse=90:0:0.75cm and 0.5cm];
+
+        \draw[thick, black, -latex] (-0.15,0) [partial ellipse=360:270:1cm and 0.7cm];
+        \draw[thick, black, -] (-0.15,0) [partial ellipse=270:180:1cm and 0.7cm];
+
+  \end{tikzpicture}
+  ~~~~~~
+  \begin{tikzpicture}
+        \node[fill=white!50!gray, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
+        \node (p0) [left= 0.5cm of p1] {};
+        \node (p2) [right= 0.5cm of p1] {};
+        \draw[-latex, thick] (p0) edge (p1) (p1) edge (p2);
+
+        \draw[thick, black, -latex] (-0.05cm,0) [partial ellipse=180:90:1cm and 0.7cm];
+        \draw[thick, black, -] (-0.05cm,0) [partial ellipse=90:0:1cm and 0.7cm];
+
+        \draw[thick, black, -latex] (-0.15,0) [partial ellipse=360:270:1cm and 0.7cm];
+        \draw[thick, black, -] (-0.15,0) [partial ellipse=270:180:1cm and 0.7cm];
+
+%        \draw[thick, black, -latex] (0,0) [partial ellipse=360:270:0.75cm and 0.5cm];
+%        \draw[thick, black, -] (0,0) [partial ellipse=270:180:0.75cm and 0.5cm];
+
+  \end{tikzpicture}
+\end{figure}
 
@@
             \node[shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab1) [right= of s]{\!\!\!\!$a \tand b$\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!$a \tand b$\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
             \node (m) at ($(ab1)!0.5!(ab2)$) {};
@@
             \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab1) [right= of s]{\!\!\!\!$a \tand b$\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!$a \tand b$\!\!\!\!};
+            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
             \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab3) [below= 0.6cm  of ab1]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};

### 2023-01-30 paper/main.tex
update graphs, citations, and descriptions

--- 2023-01-12 paper/main.tex
@@
 \journal{Journal of Computer Languages}
-
+\usepackage[x11names, svgnames, rgb]{xcolor}
+\usepackage[utf8]{inputenc}
 \usepackage{amsmath, amssymb, amsthm,tikz, subfig}
-\usetikzlibrary{positioning,shapes,quotes,calc}
+\usetikzlibrary{positioning,shapes,quotes,calc,snakes,arrows}
 
@@
 If $\Psi = 1$, that means all atomic propositions can behave arbitrarily.
-    \item A node with label ``$\cdots$'' means to repeat the node prior to it and after it finitely many times.
+    \item A node in egg shake with a caption ``repeats $0$ - $\infty$'' means to repeat the (one time step) current node for arbitrarily finitely many times.
+    \item A node with label ``$\cdots$'' means to repeat the pattern prior to it and after it arbitrarily finitely many times.
     \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its starting point.
@@
 \begin{example}
-    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by two nodes with $\lnot a$ separated by $\cdots$ (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $1$ (true) in the grey box.
+    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by the second node (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $\top$ (true) in the grey box.
     \begin{figure}[!h]
         \centering
-        \begin{tikzpicture}
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) {\!\!\!start\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) [right= 0.75cm of s] {\!\!\!$\lnot a$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [right= 0.75cm of a1] {\!\!\!$\dots$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$\lnot a$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$a$\!\!\!};
-        \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.25cm}] (g) [right= 0.6cm of a4] {};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$1$\!\!\!};
-        \draw[thick, line width=1.25] (s) edge[-latex] (a1) (a1) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5);
-
+        \begin{tikzpicture}[>=latex',line join=bevel,]
+            \pgfsetlinewidth{1bp}
+          %%
+          \begin{scope}
+            \pgfsetstrokecolor{black}
+            \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+            \pgfsetstrokecolor{strokecol}
+            \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+            \pgfsetfillcolor{fillcol}
+            \filldraw (287.84bp,8.0bp) -- (287.84bp,60.0bp) -- (357.84bp,60.0bp) -- (357.84bp,8.0bp) -- cycle;
+          \end{scope}
+            \pgfsetcolor{black}
+            % Edge: start -> 0
+            \draw [->] (54.252bp,34.0bp) .. controls (61.968bp,34.0bp) and (70.673bp,34.0bp)  .. (90.636bp,34.0bp);
+            % Edge: 0 -> 1
+            \draw [->] (169.36bp,34.0bp) .. controls (177.45bp,34.0bp) and (185.97bp,34.0bp)  .. (205.41bp,34.0bp);
+            % Edge: 1 -> 2
+            \draw [->] (260.25bp,34.0bp) .. controls (267.73bp,34.0bp) and (276.03bp,34.0bp)  .. (295.46bp,34.0bp);
+            % Node: 2
+          \begin{scope}
+            \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+            \pgfsetstrokecolor{strokecol}
+            \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+            \pgfsetfillcolor{fillcol}
+            \filldraw [opacity=1] (322.84bp,34.0bp) ellipse (27.0bp and 18.0bp);
+            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+            \pgfsetstrokecolor{strokecol}
+            \draw (322.84bp,34.0bp) node {$\top$};
+          \end{scope}
+            % Node: start
+          \begin{scope}
+            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+            \pgfsetstrokecolor{strokecol}
+            \draw (27.0bp,34.0bp) ellipse (27.0bp and 18.0bp);
+            \draw (27.0bp,34.0bp) node {start};
+          \end{scope}
+            % Node: 0
+          \begin{scope}
+            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+            \pgfsetstrokecolor{strokecol}
+            \draw (133.61bp,16.05bp) -- (136.05bp,16.15bp) -- (138.47bp,16.3bp) -- (140.85bp,16.49bp) -- (143.18bp,16.74bp) -- (145.46bp,17.03bp) -- (147.68bp,17.36bp) -- (149.83bp,17.75bp) -- (151.9bp,18.18bp) -- (153.88bp,18.65bp) -- (155.76bp,19.16bp) -- (157.54bp,19.71bp) -- (159.22bp,20.31bp) -- (160.78bp,20.94bp) -- (162.23bp,21.61bp) -- (163.56bp,22.31bp) -- (164.76bp,23.04bp) -- (165.83bp,23.8bp) -- (166.78bp,24.59bp) -- (167.59bp,25.41bp) -- (168.28bp,26.25bp) -- (168.83bp,27.11bp) -- (169.25bp,27.99bp) -- (169.55bp,28.89bp) -- (169.72bp,29.8bp) -- (169.76bp,30.72bp) -- (169.69bp,31.65bp) -- (169.5bp,32.59bp) -- (169.19bp,33.53bp) -- (168.77bp,34.47bp) -- (168.25bp,35.41bp) -- (167.63bp,36.35bp) -- (166.92bp,37.28bp) -- (166.11bp,38.2bp) -- (165.22bp,39.11bp) -- (164.26bp,40.01bp) -- (163.21bp,40.89bp) -- (162.1bp,41.75bp) -- (160.93bp,42.59bp) -- (159.7bp,43.41bp) -- (158.42bp,44.2bp) -- (157.09bp,44.96bp) -- (155.71bp,45.69bp) -- (154.3bp,46.39bp) -- (152.85bp,47.06bp) -- (151.38bp,47.69bp) -- (149.87bp,48.29bp) -- (148.35bp,48.84bp) -- (146.8bp,49.35bp) -- (145.24bp,49.82bp) -- (143.66bp,50.25bp) -- (142.07bp,50.64bp) -- (140.47bp,50.97bp) -- (138.86bp,51.26bp) -- (137.24bp,51.51bp) -- (135.62bp,51.7bp) -- (133.99bp,51.85bp) -- (132.37bp,51.95bp) -- (130.74bp,52.0bp) -- (129.11bp,52.0bp) -- (127.48bp,51.95bp) -- (125.85bp,51.85bp) -- (124.22bp,51.7bp) -- (122.6bp,51.51bp) -- (120.99bp,51.26bp) -- (119.38bp,50.97bp) -- (117.78bp,50.64bp) -- (116.19bp,50.25bp) -- (114.61bp,49.82bp) -- (113.04bp,49.35bp) -- (111.5bp,48.84bp) -- (109.97bp,48.29bp) -- (108.47bp,47.69bp) -- (106.99bp,47.06bp) -- (105.54bp,46.39bp) -- (104.13bp,45.69bp) -- (102.76bp,44.96bp) -- (101.43bp,44.2bp) -- (100.14bp,43.41bp) -- (98.91bp,42.59bp) -- (97.74bp,41.75bp) -- (96.63bp,40.89bp) -- (95.59bp,40.01bp) -- (94.62bp,39.11bp) -- (93.73bp,38.2bp) -- (92.92bp,37.28bp) -- (92.21bp,36.35bp) -- (91.59bp,35.41bp) -- (91.07bp,34.47bp) -- (90.65bp,33.53bp) -- (90.35bp,32.59bp) -- (90.15bp,31.65bp) -- (90.08bp,30.72bp) -- (90.12bp,29.8bp) -- (90.29bp,28.89bp) -- (90.59bp,27.99bp) -- (91.01bp,27.11bp) -- (91.57bp,26.25bp) -- (92.25bp,25.41bp) -- (93.07bp,24.59bp) -- (94.01bp,23.8bp) -- (95.09bp,23.04bp) -- (96.29bp,22.31bp) -- (97.61bp,21.61bp) -- (99.06bp,20.94bp) -- (100.62bp,20.31bp) -- (102.3bp,19.71bp) -- (104.08bp,19.16bp) -- (105.97bp,18.65bp) -- (107.95bp,18.18bp) -- (110.01bp,17.75bp) -- (112.16bp,17.36bp) -- (114.38bp,17.03bp) -- (116.66bp,16.74bp) -- (119.0bp,16.49bp) -- (121.38bp,16.3bp) -- (123.79bp,16.15bp) -- (126.23bp,16.05bp) -- (128.69bp,16.0bp) -- (131.15bp,16.0bp) -- cycle;
+            \draw (129.92bp,34.0bp) node [align=center] {$\neg \text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
+          \end{scope}
+            % Node: 1
+          \begin{scope}
+            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+            \pgfsetstrokecolor{strokecol}
+            \draw (232.84bp,34.0bp) ellipse (27.0bp and 18.0bp);
+            \draw (232.84bp,34.0bp) node {$\text{a}$};
+          \end{scope}
+          %
           \end{tikzpicture}
@@
                 \resizebox{\textwidth}{!}{
-        \begin{tikzpicture}
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
-        \node (m) at ($(a1)!0.5!(a2)$) {};
-        \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=3cm}] (g) [right= -1.1cm of m] {};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$\dots$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a6) [right= 0.75cm of a5] {\!\!\!$\lnot a$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 12.5cm of m] {\!\!\!start\!\!\!};
-
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a7) [left= .75cm of a1] {\!\!\!$\lnot a$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a8) [left= .75cm of a2] {\!\!\!$\lnot a$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a9) [left= .75cm of a8] {\!\!\!$a$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a10) [left= .75cm of a9] {\!\!\!$\dots$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a11) [left= .75cm of a10] {\!\!\!$a$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a12) [left= .75cm of a11] {\!\!\!$a$\!\!\!};
-
-        \draw[thick, line width=1.25] (s) edge[-latex] (a12) (s) edge[-latex] (a7) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
-        \draw[thick, line width=1.25] (a12) edge[-latex] (a11) (a11) edge[-latex] (a10) (a10) edge[-latex] (a9) (a9) edge[-latex] (a8) (a8) edge[-latex] (a1) (a8) edge[-latex] (a2) (a7) edge[-latex] (a1) (a7) edge[-latex] (a2);
-
+                    \begin{tikzpicture}[>=latex',line join=bevel,]
+                        \pgfsetlinewidth{1bp}
+                      %%
+                      \begin{scope}
+                        \pgfsetstrokecolor{black}
+                        \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+                        \pgfsetstrokecolor{strokecol}
+                        \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+                        \pgfsetfillcolor{fillcol}
+                        \filldraw (371.46bp,8.0bp) -- (371.46bp,114.0bp) -- (640.91bp,114.0bp) -- (640.91bp,8.0bp) -- cycle;
+                      \end{scope}
+                        \pgfsetcolor{black}
+                        % Edge: 5 -> 6
+                        \draw [->] (433.9bp,34.0bp) .. controls (441.44bp,34.0bp) and (449.89bp,34.0bp)  .. (469.54bp,34.0bp);
+                        % Edge: 6 -> 7
+                        \draw [->] (542.74bp,34.0bp) .. controls (550.66bp,34.0bp) and (559.09bp,34.0bp)  .. (578.42bp,34.0bp);
+                        % Edge: start -> 0
+                        \draw [->] (54.272bp,65.285bp) .. controls (105.49bp,69.739bp) and (218.83bp,79.597bp)  .. (289.35bp,85.729bp);
+                        % Edge: start -> 1
+                        \draw [->] (52.513bp,56.593bp) .. controls (61.118bp,54.344bp) and (70.969bp,51.769bp)  .. (91.313bp,46.452bp);
+                        % Edge: 0 -> 4
+                        \draw [->] (343.86bp,88.0bp) .. controls (351.34bp,88.0bp) and (359.64bp,88.0bp)  .. (379.07bp,88.0bp);
+                        % Edge: 0 -> 5
+                        \draw [->] (336.99bp,76.016bp) .. controls (348.61bp,68.885bp) and (363.57bp,59.705bp)  .. (385.98bp,45.951bp);
+                        % Edge: 1 -> 2
+                        \draw [->] (144.45bp,39.459bp) .. controls (152.06bp,39.303bp) and (160.61bp,39.128bp)  .. (180.45bp,38.722bp);
+                        % Edge: 2 -> 3
+                        \draw [->] (253.84bp,36.522bp) .. controls (261.64bp,36.203bp) and (269.9bp,35.864bp)  .. (289.26bp,35.072bp);
+                        % Edge: 3 -> 4
+                        \draw [->] (336.99bp,45.984bp) .. controls (348.61bp,53.115bp) and (363.57bp,62.295bp)  .. (385.98bp,76.049bp);
+                        % Edge: 3 -> 5
+                        \draw [->] (343.86bp,34.0bp) .. controls (351.34bp,34.0bp) and (359.64bp,34.0bp)  .. (379.07bp,34.0bp);
+                        % Node: 4
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                        \pgfsetfillcolor{fillcol}
+                        \filldraw [opacity=1] (406.46bp,88.0bp) ellipse (27.0bp and 18.0bp);
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (406.46bp,88.0bp) node {$\neg \text{a}$};
+                      \end{scope}
+                        % Node: 5
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                        \pgfsetfillcolor{fillcol}
+                        \filldraw [opacity=1] (406.46bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (406.46bp,34.0bp) node {$\text{a}$};
+                      \end{scope}
+                        % Node: 6
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                        \pgfsetfillcolor{fillcol}
+                        \filldraw (509.6bp,16.05bp) -- (511.87bp,16.15bp) -- (514.11bp,16.3bp) -- (516.32bp,16.49bp) -- (518.48bp,16.74bp) -- (520.6bp,17.03bp) -- (522.66bp,17.36bp) -- (524.65bp,17.75bp) -- (526.57bp,18.18bp) -- (528.4bp,18.65bp) -- (530.15bp,19.16bp) -- (531.8bp,19.71bp) -- (533.36bp,20.31bp) -- (534.81bp,20.94bp) -- (536.15bp,21.61bp) -- (537.38bp,22.31bp) -- (538.5bp,23.04bp) -- (539.49bp,23.8bp) -- (540.37bp,24.59bp) -- (541.12bp,25.41bp) -- (541.76bp,26.25bp) -- (542.27bp,27.11bp) -- (542.67bp,27.99bp) -- (542.94bp,28.89bp) -- (543.1bp,29.8bp) -- (543.14bp,30.72bp) -- (543.07bp,31.65bp) -- (542.89bp,32.59bp) -- (542.61bp,33.53bp) -- (542.22bp,34.47bp) -- (541.74bp,35.41bp) -- (541.16bp,36.35bp) -- (540.5bp,37.28bp) -- (539.75bp,38.2bp) -- (538.93bp,39.11bp) -- (538.03bp,40.01bp) -- (537.06bp,40.89bp) -- (536.03bp,41.75bp) -- (534.95bp,42.59bp) -- (533.8bp,43.41bp) -- (532.61bp,44.2bp) -- (531.38bp,44.96bp) -- (530.11bp,45.69bp) -- (528.8bp,46.39bp) -- (527.45bp,47.06bp) -- (526.08bp,47.69bp) -- (524.69bp,48.29bp) -- (523.27bp,48.84bp) -- (521.84bp,49.35bp) -- (520.39bp,49.82bp) -- (518.92bp,50.25bp) -- (517.45bp,50.64bp) -- (515.96bp,50.97bp) -- (514.47bp,51.26bp) -- (512.97bp,51.51bp) -- (511.47bp,51.7bp) -- (509.96bp,51.85bp) -- (508.45bp,51.95bp) -- (506.94bp,52.0bp) -- (505.43bp,52.0bp) -- (503.92bp,51.95bp) -- (502.41bp,51.85bp) -- (500.9bp,51.7bp) -- (499.39bp,51.51bp) -- (497.9bp,51.26bp) -- (496.4bp,50.97bp) -- (494.92bp,50.64bp) -- (493.44bp,50.25bp) -- (491.98bp,49.82bp) -- (490.53bp,49.35bp) -- (489.09bp,48.84bp) -- (487.68bp,48.29bp) -- (486.28bp,47.69bp) -- (484.91bp,47.06bp) -- (483.57bp,46.39bp) -- (482.26bp,45.69bp) -- (480.99bp,44.96bp) -- (479.75bp,44.2bp) -- (478.56bp,43.41bp) -- (477.42bp,42.59bp) -- (476.33bp,41.75bp) -- (475.3bp,40.89bp) -- (474.34bp,40.01bp) -- (473.44bp,39.11bp) -- (472.61bp,38.2bp) -- (471.87bp,37.28bp) -- (471.2bp,36.35bp) -- (470.63bp,35.41bp) -- (470.14bp,34.47bp) -- (469.76bp,33.53bp) -- (469.47bp,32.59bp) -- (469.3bp,31.65bp) -- (469.23bp,30.72bp) -- (469.27bp,29.8bp) -- (469.43bp,28.89bp) -- (469.7bp,27.99bp) -- (470.09bp,27.11bp) -- (470.61bp,26.25bp) -- (471.24bp,25.41bp) -- (472.0bp,24.59bp) -- (472.88bp,23.8bp) -- (473.87bp,23.04bp) -- (474.99bp,22.31bp) -- (476.21bp,21.61bp) -- (477.56bp,20.94bp) -- (479.01bp,20.31bp) -- (480.56bp,19.71bp) -- (482.22bp,19.16bp) -- (483.96bp,18.65bp) -- (485.8bp,18.18bp) -- (487.72bp,17.75bp) -- (489.71bp,17.36bp) -- (491.77bp,17.03bp) -- (493.88bp,16.74bp) -- (496.05bp,16.49bp) -- (498.26bp,16.3bp) -- (500.5bp,16.15bp) -- (502.76bp,16.05bp) -- (505.04bp,16.0bp) -- (507.32bp,16.0bp) -- cycle;
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (506.18bp,34.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
+                      \end{scope}
+                        % Node: 7
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                        \pgfsetfillcolor{fillcol}
+                        \filldraw [opacity=1] (605.91bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (605.91bp,34.0bp) node {$\neg \text{a}$};
+                      \end{scope}
+                        % Node: start
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (27.0bp,63.0bp) ellipse (27.0bp and 18.0bp);
+                        \draw (27.0bp,63.0bp) node {start};
+                      \end{scope}
+                        % Node: 0
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (316.46bp,88.0bp) ellipse (27.0bp and 18.0bp);
+                        \draw (316.46bp,88.0bp) node {$\neg \text{a}$};
+                      \end{scope}
+                        % Node: 1
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (117.0bp,40.0bp) ellipse (27.0bp and 18.0bp);
+                        \draw (117.0bp,40.0bp) node {$\text{a}$};
+                      \end{scope}
+                        % Node: 2
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (220.15bp,20.05bp) -- (222.41bp,20.15bp) -- (224.65bp,20.3bp) -- (226.86bp,20.49bp) -- (229.03bp,20.74bp) -- (231.14bp,21.03bp) -- (233.2bp,21.36bp) -- (235.19bp,21.75bp) -- (237.11bp,22.18bp) -- (238.95bp,22.65bp) -- (240.7bp,23.16bp) -- (242.35bp,23.71bp) -- (243.9bp,24.31bp) -- (245.35bp,24.94bp) -- (246.7bp,25.61bp) -- (247.93bp,26.31bp) -- (249.04bp,27.04bp) -- (250.04bp,27.8bp) -- (250.91bp,28.59bp) -- (251.67bp,29.41bp) -- (252.3bp,30.25bp) -- (252.82bp,31.11bp) -- (253.21bp,31.99bp) -- (253.49bp,32.89bp) -- (253.64bp,33.8bp) -- (253.68bp,34.72bp) -- (253.61bp,35.65bp) -- (253.44bp,36.59bp) -- (253.15bp,37.53bp) -- (252.77bp,38.47bp) -- (252.28bp,39.41bp) -- (251.71bp,40.35bp) -- (251.04bp,41.28bp) -- (250.3bp,42.2bp) -- (249.47bp,43.11bp) -- (248.57bp,44.01bp) -- (247.61bp,44.89bp) -- (246.58bp,45.75bp) -- (245.49bp,46.59bp) -- (244.35bp,47.41bp) -- (243.16bp,48.2bp) -- (241.92bp,48.96bp) -- (240.65bp,49.69bp) -- (239.34bp,50.39bp) -- (238.0bp,51.06bp) -- (236.63bp,51.69bp) -- (235.23bp,52.29bp) -- (233.82bp,52.84bp) -- (232.38bp,53.35bp) -- (230.93bp,53.82bp) -- (229.47bp,54.25bp) -- (227.99bp,54.64bp) -- (226.51bp,54.97bp) -- (225.02bp,55.26bp) -- (223.52bp,55.51bp) -- (222.01bp,55.7bp) -- (220.51bp,55.85bp) -- (219.0bp,55.95bp) -- (217.48bp,56.0bp) -- (215.97bp,56.0bp) -- (214.46bp,55.95bp) -- (212.95bp,55.85bp) -- (211.44bp,55.7bp) -- (209.94bp,55.51bp) -- (208.44bp,55.26bp) -- (206.95bp,54.97bp) -- (205.46bp,54.64bp) -- (203.99bp,54.25bp) -- (202.52bp,53.82bp) -- (201.07bp,53.35bp) -- (199.64bp,52.84bp) -- (198.22bp,52.29bp) -- (196.83bp,51.69bp) -- (195.46bp,51.06bp) -- (194.12bp,50.39bp) -- (192.81bp,49.69bp) -- (191.53bp,48.96bp) -- (190.3bp,48.2bp) -- (189.11bp,47.41bp) -- (187.97bp,46.59bp) -- (186.88bp,45.75bp) -- (185.85bp,44.89bp) -- (184.88bp,44.01bp) -- (183.98bp,43.11bp) -- (183.16bp,42.2bp) -- (182.41bp,41.28bp) -- (181.75bp,40.35bp) -- (181.17bp,39.41bp) -- (180.69bp,38.47bp) -- (180.3bp,37.53bp) -- (180.02bp,36.59bp) -- (179.84bp,35.65bp) -- (179.77bp,34.72bp) -- (179.81bp,33.8bp) -- (179.97bp,32.89bp) -- (180.24bp,31.99bp) -- (180.64bp,31.11bp) -- (181.15bp,30.25bp) -- (181.79bp,29.41bp) -- (182.54bp,28.59bp) -- (183.42bp,27.8bp) -- (184.42bp,27.04bp) -- (185.53bp,26.31bp) -- (186.76bp,25.61bp) -- (188.1bp,24.94bp) -- (189.55bp,24.31bp) -- (191.11bp,23.71bp) -- (192.76bp,23.16bp) -- (194.51bp,22.65bp) -- (196.34bp,22.18bp) -- (198.26bp,21.75bp) -- (200.25bp,21.36bp) -- (202.31bp,21.03bp) -- (204.43bp,20.74bp) -- (206.59bp,20.49bp) -- (208.8bp,20.3bp) -- (211.04bp,20.15bp) -- (213.31bp,20.05bp) -- (215.59bp,20.0bp) -- (217.87bp,20.0bp) -- cycle;
+                        \draw (216.73bp,38.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
+                      \end{scope}
+                        % Node: 3
+                      \begin{scope}
+                        \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                        \pgfsetstrokecolor{strokecol}
+                        \draw (316.46bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                        \draw (316.46bp,34.0bp) node {$\neg \text{a}$};
+                      \end{scope}
+                      %
                       \end{tikzpicture}}
@@
         \resizebox{.8\textwidth}{!}{
-        \begin{tikzpicture}
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
-  %      \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
-        \node (m) at ($(a1)!0.5!(a2)$) {};
-        \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=3cm}] (g) [right= -1.1cm of m] {};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$\dots$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$a$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a6) [right= 0.75cm of a5] {\!\!\!$\lnot a$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 2cm of m] {\!\!\!start\!\!\!};
-        \draw[thick, line width=1.25] (s) edge[-latex] (a1) (s) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
+            \begin{tikzpicture}[>=latex',line join=bevel,]
+                \pgfsetlinewidth{1bp}
+              %%
+              \begin{scope}
+                \pgfsetstrokecolor{black}
+                \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+                \pgfsetfillcolor{fillcol}
+                \filldraw (82.0bp,8.0bp) -- (82.0bp,114.0bp) -- (351.46bp,114.0bp) -- (351.46bp,8.0bp) -- cycle;
+              \end{scope}
+                \pgfsetcolor{black}
+                % Edge: 1 -> 2
+                \draw [->] (144.45bp,34.0bp) .. controls (151.99bp,34.0bp) and (160.43bp,34.0bp)  .. (180.08bp,34.0bp);
+                % Edge: 2 -> 3
+                \draw [->] (253.29bp,34.0bp) .. controls (261.21bp,34.0bp) and (269.63bp,34.0bp)  .. (288.96bp,34.0bp);
+                % Edge: start -> 0
+                \draw [->] (52.046bp,68.378bp) .. controls (60.971bp,71.116bp) and (71.285bp,74.281bp)  .. (91.983bp,80.631bp);
+                % Edge: start -> 1
+                \draw [->] (52.046bp,53.622bp) .. controls (60.971bp,50.884bp) and (71.285bp,47.719bp)  .. (91.983bp,41.369bp);
+                % Node: 0
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (117.0bp,88.0bp) ellipse (27.0bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (117.0bp,88.0bp) node {$\neg \text{a}$};
+              \end{scope}
+                % Node: 1
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (117.0bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (117.0bp,34.0bp) node {$\text{a}$};
+              \end{scope}
+                % Node: 2
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw (220.15bp,16.05bp) -- (222.41bp,16.15bp) -- (224.65bp,16.3bp) -- (226.86bp,16.49bp) -- (229.03bp,16.74bp) -- (231.14bp,17.03bp) -- (233.2bp,17.36bp) -- (235.19bp,17.75bp) -- (237.11bp,18.18bp) -- (238.95bp,18.65bp) -- (240.7bp,19.16bp) -- (242.35bp,19.71bp) -- (243.9bp,20.31bp) -- (245.35bp,20.94bp) -- (246.7bp,21.61bp) -- (247.93bp,22.31bp) -- (249.04bp,23.04bp) -- (250.04bp,23.8bp) -- (250.91bp,24.59bp) -- (251.67bp,25.41bp) -- (252.3bp,26.25bp) -- (252.82bp,27.11bp) -- (253.21bp,27.99bp) -- (253.49bp,28.89bp) -- (253.64bp,29.8bp) -- (253.68bp,30.72bp) -- (253.61bp,31.65bp) -- (253.44bp,32.59bp) -- (253.15bp,33.53bp) -- (252.77bp,34.47bp) -- (252.28bp,35.41bp) -- (251.71bp,36.35bp) -- (251.04bp,37.28bp) -- (250.3bp,38.2bp) -- (249.47bp,39.11bp) -- (248.57bp,40.01bp) -- (247.61bp,40.89bp) -- (246.58bp,41.75bp) -- (245.49bp,42.59bp) -- (244.35bp,43.41bp) -- (243.16bp,44.2bp) -- (241.92bp,44.96bp) -- (240.65bp,45.69bp) -- (239.34bp,46.39bp) -- (238.0bp,47.06bp) -- (236.63bp,47.69bp) -- (235.23bp,48.29bp) -- (233.82bp,48.84bp) -- (232.38bp,49.35bp) -- (230.93bp,49.82bp) -- (229.47bp,50.25bp) -- (227.99bp,50.64bp) -- (226.51bp,50.97bp) -- (225.02bp,51.26bp) -- (223.52bp,51.51bp) -- (222.01bp,51.7bp) -- (220.51bp,51.85bp) -- (219.0bp,51.95bp) -- (217.48bp,52.0bp) -- (215.97bp,52.0bp) -- (214.46bp,51.95bp) -- (212.95bp,51.85bp) -- (211.44bp,51.7bp) -- (209.94bp,51.51bp) -- (208.44bp,51.26bp) -- (206.95bp,50.97bp) -- (205.46bp,50.64bp) -- (203.99bp,50.25bp) -- (202.52bp,49.82bp) -- (201.07bp,49.35bp) -- (199.64bp,48.84bp) -- (198.22bp,48.29bp) -- (196.83bp,47.69bp) -- (195.46bp,47.06bp) -- (194.12bp,46.39bp) -- (192.81bp,45.69bp) -- (191.53bp,44.96bp) -- (190.3bp,44.2bp) -- (189.11bp,43.41bp) -- (187.97bp,42.59bp) -- (186.88bp,41.75bp) -- (185.85bp,40.89bp) -- (184.88bp,40.01bp) -- (183.98bp,39.11bp) -- (183.16bp,38.2bp) -- (182.41bp,37.28bp) -- (181.75bp,36.35bp) -- (181.17bp,35.41bp) -- (180.69bp,34.47bp) -- (180.3bp,33.53bp) -- (180.02bp,32.59bp) -- (179.84bp,31.65bp) -- (179.77bp,30.72bp) -- (179.81bp,29.8bp) -- (179.97bp,28.89bp) -- (180.24bp,27.99bp) -- (180.64bp,27.11bp) -- (181.15bp,26.25bp) -- (181.79bp,25.41bp) -- (182.54bp,24.59bp) -- (183.42bp,23.8bp) -- (184.42bp,23.04bp) -- (185.53bp,22.31bp) -- (186.76bp,21.61bp) -- (188.1bp,20.94bp) -- (189.55bp,20.31bp) -- (191.11bp,19.71bp) -- (192.76bp,19.16bp) -- (194.51bp,18.65bp) -- (196.34bp,18.18bp) -- (198.26bp,17.75bp) -- (200.25bp,17.36bp) -- (202.31bp,17.03bp) -- (204.43bp,16.74bp) -- (206.59bp,16.49bp) -- (208.8bp,16.3bp) -- (211.04bp,16.15bp) -- (213.31bp,16.05bp) -- (215.59bp,16.0bp) -- (217.87bp,16.0bp) -- cycle;
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (216.73bp,34.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
+              \end{scope}
+                % Node: 3
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (316.46bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (316.46bp,34.0bp) node {$\neg \text{a}$};
+              \end{scope}
+                % Node: start
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (27.0bp,61.0bp) ellipse (27.0bp and 18.0bp);
+                \draw (27.0bp,61.0bp) node {start};
+              \end{scope}
+              %
               \end{tikzpicture}}
@@
         \resizebox{\textwidth}{!}{
-        \begin{tikzpicture}
-            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) {\!\!\!\!start\!\!\!\!};
-            \node[shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab1) [right= of s]{\!\!\!\!$a \tand b$\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!$a \tand b$\!\!\!\!};
-            \node (m) at ($(ab1)!0.5!(ab2)$) {};
-            \node[shape=rectangle, fill=gray!30!white, style={minimum width=4cm, minimum height=3cm}] (g2) [right= -1cm of m] {};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab1) [right= of s]{\!\!\!\!$a \tand b$\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!$a \tand b$\!\!\!\!};
-            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab3) [below= 0.6cm  of ab1]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (b1) [right= 0.75cm  of ab1]{\!\!\!\!\!\!\!\!$\tnot b$\!\!\!\!\!\!\!\!};
-            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab4) [right= .75cm of ab3]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
-            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab5) [right= .75cm of ab4]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
-            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab6) [right= .75cm of ab5]{\!\!\!\!\!\!\!\!$a \tand b$\!\!\!\!\!\!\!\!};
-            \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=1.3cm}] (g2) [right= 0.6cm of ab6] {};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab7) [right= .75cm of ab6]{\!\!\!\!\!\!\!\!$\tnot b$\!\!\!\!\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab8) [right= .75cm of ab7]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab9) [right= .75cm of ab8]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab10) [right= .75cm of ab9]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
-            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab11) [right= .75cm of ab10]{\!\!\!\!\!\!\!\!$a \tand b$\!\!\!\!\!\!\!\!};
-
-        \draw[thick, line width=1.25] (s) edge[-latex] (ab1) (s) edge[-latex] (ab2) (s) edge[-latex] (ab3) (ab3) edge[-latex] (ab4) (ab4) edge[-latex] (ab5) (ab5) edge[-latex] (ab6) (ab1) edge[-latex] (b1);
-        \draw[thick, line width=1.25] (ab6) edge[-latex] (ab7) (ab6) edge[-latex] (ab7) (ab7) edge[-latex] (ab8) (ab8) edge[-latex] (ab9) (ab9) edge[-latex] (ab10) (ab10) edge[-latex] (ab11);
-
+            \begin{tikzpicture}[>=latex',line join=bevel,]
+                \pgfsetlinewidth{1bp}
+              %%
+              \begin{scope}
+                \pgfsetstrokecolor{black}
+                \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+                \pgfsetfillcolor{fillcol}
+                \filldraw (105.66bp,62.0bp) -- (105.66bp,168.0bp) -- (292.33bp,168.0bp) -- (292.33bp,62.0bp) -- cycle;
+              \end{scope}
+              \begin{scope}
+                \pgfsetstrokecolor{black}
+                \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+                \pgfsetfillcolor{fillcol}
+                \filldraw (312.33bp,8.0bp) -- (312.33bp,60.0bp) -- (612.66bp,60.0bp) -- (612.66bp,8.0bp) -- cycle;
+              \end{scope}
+                \pgfsetcolor{black}
+                % Edge: 1 -> 2
+                \draw [->] (169.41bp,88.0bp) .. controls (184.02bp,88.0bp) and (202.45bp,88.0bp)  .. (229.83bp,88.0bp);
+                % Edge: 5 -> 6
+                \draw [->] (374.57bp,34.0bp) .. controls (382.11bp,34.0bp) and (390.67bp,34.0bp)  .. (410.91bp,34.0bp);
+                % Edge: 6 -> 7
+                \draw [->] (514.12bp,34.0bp) .. controls (522.4bp,34.0bp) and (530.86bp,34.0bp)  .. (550.25bp,34.0bp);
+                % Edge: start -> 0
+                \draw [->] (49.552bp,98.284bp) .. controls (66.247bp,106.25bp) and (89.652bp,117.42bp)  .. (118.92bp,131.39bp);
+                % Edge: start -> 1
+                \draw [->] (54.247bp,88.0bp) .. controls (68.853bp,88.0bp) and (87.288bp,88.0bp)  .. (114.67bp,88.0bp);
+                % Edge: start -> 3
+                \draw [->] (49.489bp,77.523bp) ..
+controls (61.408bp,71.732bp) and (76.506bp,64.429bp)  ..
+(90.0bp,58.0bp) ..
+controls (93.924bp,56.131bp) and (98.021bp,54.19bp)  ..
+(112.18bp,47.52bp);
+                % Edge: 3 -> 4
+                \draw [->] (193.79bp,34.0bp) .. controls (202.07bp,34.0bp) and (210.53bp,34.0bp)  .. (229.93bp,34.0bp);
+                % Edge: 4 -> 5
+                \draw [->] (284.73bp,34.0bp) .. controls (292.21bp,34.0bp) and (300.51bp,34.0bp)  .. (319.94bp,34.0bp);
+                % Node: 0
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (142.16bp,142.0bp) ellipse (28.5bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (142.16bp,142.0bp) node {$\neg \text{a} \lor \neg \text{b}$};
+              \end{scope}
+                % Node: 1
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (142.16bp,88.0bp) ellipse (27.0bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (142.16bp,88.0bp) node {$\text{a} \land \text{b}$};
+              \end{scope}
+                % Node: 2
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (257.33bp,88.0bp) ellipse (27.0bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (257.33bp,88.0bp) node {$\neg \text{b}$};
+              \end{scope}
+                % Node: 5
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (347.33bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (347.33bp,34.0bp) node {$\neg \text{b}$};
+              \end{scope}
+                % Node: 6
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw (467.33bp,16.05bp) -- (470.54bp,16.15bp) -- (473.71bp,16.3bp) -- (476.84bp,16.49bp) -- (479.91bp,16.74bp) -- (482.9bp,17.03bp) -- (485.82bp,17.36bp) -- (488.64bp,17.75bp) -- (491.35bp,18.18bp) -- (493.95bp,18.65bp) -- (496.43bp,19.16bp) -- (498.77bp,19.71bp) -- (500.97bp,20.31bp) -- (503.03bp,20.94bp) -- (504.93bp,21.61bp) -- (506.67bp,22.31bp) -- (508.24bp,23.04bp) -- (509.65bp,23.8bp) -- (510.9bp,24.59bp) -- (511.97bp,25.41bp) -- (512.86bp,26.25bp) -- (513.59bp,27.11bp) -- (514.15bp,27.99bp) -- (514.54bp,28.89bp) -- (514.76bp,29.8bp) -- (514.82bp,30.72bp) -- (514.72bp,31.65bp) -- (514.47bp,32.59bp) -- (514.07bp,33.53bp) -- (513.52bp,34.47bp) -- (512.84bp,35.41bp) -- (512.02bp,36.35bp) -- (511.08bp,37.28bp) -- (510.03bp,38.2bp) -- (508.86bp,39.11bp) -- (507.59bp,40.01bp) -- (506.22bp,40.89bp) -- (504.76bp,41.75bp) -- (503.22bp,42.59bp) -- (501.6bp,43.41bp) -- (499.92bp,44.2bp) -- (498.17bp,44.96bp) -- (496.36bp,45.69bp) -- (494.51bp,46.39bp) -- (492.61bp,47.06bp) -- (490.67bp,47.69bp) -- (488.7bp,48.29bp) -- (486.69bp,48.84bp) -- (484.66bp,49.35bp) -- (482.61bp,49.82bp) -- (480.53bp,50.25bp) -- (478.44bp,50.64bp) -- (476.34bp,50.97bp) -- (474.23bp,51.26bp) -- (472.1bp,51.51bp) -- (469.98bp,51.7bp) -- (467.84bp,51.85bp) -- (465.7bp,51.95bp) -- (463.56bp,52.0bp) -- (461.42bp,52.0bp) -- (459.28bp,51.95bp) -- (457.14bp,51.85bp) -- (455.01bp,51.7bp) -- (452.88bp,51.51bp) -- (450.76bp,51.26bp) -- (448.64bp,50.97bp) -- (446.54bp,50.64bp) -- (444.45bp,50.25bp) -- (442.38bp,49.82bp) -- (440.33bp,49.35bp) -- (438.29bp,48.84bp) -- (436.29bp,48.29bp) -- (434.31bp,47.69bp) -- (432.37bp,47.06bp) -- (430.47bp,46.39bp) -- (428.62bp,45.69bp) -- (426.82bp,44.96bp) -- (425.07bp,44.2bp) -- (423.38bp,43.41bp) -- (421.77bp,42.59bp) -- (420.23bp,41.75bp) -- (418.77bp,40.89bp) -- (417.4bp,40.01bp) -- (416.13bp,39.11bp) -- (414.96bp,38.2bp) -- (413.9bp,37.28bp) -- (412.96bp,36.35bp) -- (412.15bp,35.41bp) -- (411.46bp,34.47bp) -- (410.92bp,33.53bp) -- (410.52bp,32.59bp) -- (410.26bp,31.65bp) -- (410.16bp,30.72bp) -- (410.22bp,29.8bp) -- (410.45bp,28.89bp) -- (410.83bp,27.99bp) -- (411.39bp,27.11bp) -- (412.12bp,26.25bp) -- (413.02bp,25.41bp) -- (414.09bp,24.59bp) -- (415.33bp,23.8bp) -- (416.74bp,23.04bp) -- (418.32bp,22.31bp) -- (420.06bp,21.61bp) -- (421.96bp,20.94bp) -- (424.01bp,20.31bp) -- (426.21bp,19.71bp) -- (428.56bp,19.16bp) -- (431.03bp,18.65bp) -- (433.63bp,18.18bp) -- (436.35bp,17.75bp) -- (439.17bp,17.36bp) -- (442.08bp,17.03bp) -- (445.08bp,16.74bp) -- (448.14bp,16.49bp) -- (451.27bp,16.3bp) -- (454.44bp,16.15bp) -- (457.65bp,16.05bp) -- (460.88bp,16.0bp) -- (464.11bp,16.0bp) -- cycle;
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (462.49bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\tiny repeats $0$ - $\infty$}};
+              \end{scope}
+                % Node: 7
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (577.66bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (577.66bp,34.0bp) node {$\text{a} \land \text{b}$};
+              \end{scope}
+                % Node: start
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (27.0bp,88.0bp) ellipse (27.0bp and 18.0bp);
+                \draw (27.0bp,88.0bp) node {start};
+              \end{scope}
+                % Node: 3
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (147.01bp,16.05bp) -- (150.21bp,16.15bp) -- (153.39bp,16.3bp) -- (156.51bp,16.49bp) -- (159.58bp,16.74bp) -- (162.58bp,17.03bp) -- (165.49bp,17.36bp) -- (168.31bp,17.75bp) -- (171.03bp,18.18bp) -- (173.63bp,18.65bp) -- (176.1bp,19.16bp) -- (178.44bp,19.71bp) -- (180.64bp,20.31bp) -- (182.7bp,20.94bp) -- (184.6bp,21.61bp) -- (186.34bp,22.31bp) -- (187.92bp,23.04bp) -- (189.33bp,23.8bp) -- (190.57bp,24.59bp) -- (191.64bp,25.41bp) -- (192.54bp,26.25bp) -- (193.26bp,27.11bp) -- (193.82bp,27.99bp) -- (194.21bp,28.89bp) -- (194.43bp,29.8bp) -- (194.49bp,30.72bp) -- (194.39bp,31.65bp) -- (194.14bp,32.59bp) -- (193.74bp,33.53bp) -- (193.19bp,34.47bp) -- (192.51bp,35.41bp) -- (191.69bp,36.35bp) -- (190.75bp,37.28bp) -- (189.7bp,38.2bp) -- (188.53bp,39.11bp) -- (187.26bp,40.01bp) -- (185.89bp,40.89bp) -- (184.43bp,41.75bp) -- (182.89bp,42.59bp) -- (181.27bp,43.41bp) -- (179.59bp,44.2bp) -- (177.84bp,44.96bp) -- (176.04bp,45.69bp) -- (174.18bp,46.39bp) -- (172.28bp,47.06bp) -- (170.34bp,47.69bp) -- (168.37bp,48.29bp) -- (166.36bp,48.84bp) -- (164.33bp,49.35bp) -- (162.28bp,49.82bp) -- (160.2bp,50.25bp) -- (158.12bp,50.64bp) -- (156.01bp,50.97bp) -- (153.9bp,51.26bp) -- (151.78bp,51.51bp) -- (149.65bp,51.7bp) -- (147.51bp,51.85bp) -- (145.37bp,51.95bp) -- (143.23bp,52.0bp) -- (141.09bp,52.0bp) -- (138.95bp,51.95bp) -- (136.82bp,51.85bp) -- (134.68bp,51.7bp) -- (132.55bp,51.51bp) -- (130.43bp,51.26bp) -- (128.32bp,50.97bp) -- (126.21bp,50.64bp) -- (124.12bp,50.25bp) -- (122.05bp,49.82bp) -- (120.0bp,49.35bp) -- (117.97bp,48.84bp) -- (115.96bp,48.29bp) -- (113.99bp,47.69bp) -- (112.05bp,47.06bp) -- (110.15bp,46.39bp) -- (108.29bp,45.69bp) -- (106.49bp,44.96bp) -- (104.74bp,44.2bp) -- (103.05bp,43.41bp) -- (101.44bp,42.59bp) -- (99.9bp,41.75bp) -- (98.44bp,40.89bp) -- (97.07bp,40.01bp) -- (95.8bp,39.11bp) -- (94.63bp,38.2bp) -- (93.57bp,37.28bp) -- (92.63bp,36.35bp) -- (91.82bp,35.41bp) -- (91.14bp,34.47bp) -- (90.59bp,33.53bp) -- (90.19bp,32.59bp) -- (89.93bp,31.65bp) -- (89.84bp,30.72bp) -- (89.9bp,29.8bp) -- (90.12bp,28.89bp) -- (90.51bp,27.99bp) -- (91.06bp,27.11bp) -- (91.79bp,26.25bp) -- (92.69bp,25.41bp) -- (93.76bp,24.59bp) -- (95.0bp,23.8bp) -- (96.41bp,23.04bp) -- (97.99bp,22.31bp) -- (99.73bp,21.61bp) -- (101.63bp,20.94bp) -- (103.68bp,20.31bp) -- (105.89bp,19.71bp) -- (108.23bp,19.16bp) -- (110.7bp,18.65bp) -- (113.3bp,18.18bp) -- (116.02bp,17.75bp) -- (118.84bp,17.36bp) -- (121.75bp,17.03bp) -- (124.75bp,16.74bp) -- (127.82bp,16.49bp) -- (130.94bp,16.3bp) -- (134.12bp,16.15bp) -- (137.32bp,16.05bp) -- (140.55bp,16.0bp) -- (143.78bp,16.0bp) -- cycle;
+                \draw (142.16bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\tiny repeats $0$ - $\infty$}};
+              \end{scope}
+                % Node: 4
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (257.33bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                \draw (257.33bp,34.0bp) node {$\text{a} \land \text{b}$};
+              \end{scope}
+              %
               \end{tikzpicture}}
@@
         \resizebox{\textwidth}{!}{
-        \begin{tikzpicture}
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) {\!\!\!\!start\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) [right= .75cm of s]{\!\!\!\!\!\!\!\!$p_2$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [right= .75cm of p1]{\!\!\!\!\!\!\!\!$\tnot p_0 \! \tand \!  p_1$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [right= .75cm of p2]{\!\!\!\!\!\!\!\!$\tnot p_0 \! \tand \!  p_1$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p4) [right= .75cm of p3]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p5) [right= .75cm of p4]{\!\!\!\!\!\!\!\!$\tnot p_0 \! \tand \!  p_1$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p6) [right= .75cm of p5]{\!\!\!\!\!\!\!\!$p_0 \! \tand \! p_1$\!\!\!\!\!\!\!\!};
-
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p7) [above= .6cm of p1]{\!\!\!\!\!\!\!\!$p_2$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p8) [above= .6cm of p6]{\!\!\!\!\!\!\!\!$p_0 \! \tand \! p_1$\!\!\!\!\!\!\!\!};
-            \node (m) at ($(p6)!0.5!(p8)$) {};
-            \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.25cm}] (g1) [right= 1cm of m] {};
-           \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (o1) [right= 1.15cm of m]{\!\!\!\!\!\!\!\!$p_1$\!\!\!\!\!\!\!\!};
-
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p9) [below= .6cm of p1]{\!\!\!\!\!\!\!\!$p_2$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p10) [below= .6cm of p2]{\!\!\!\!\!\!\!\!$1$\!\!\!\!\!\!\!\!};
-	   \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p11) [below= .6cm of p3]{\!\!\!\!\!\!\!\!$1$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p12) [below= .6cm of p4]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
-           \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p13) [below= .6cm of p5]{\!\!\!\!\!\!\!\!$1$\!\!\!\!\!\!\!\!};
-           \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.25cm}] (g2) [right= 0.6cm of p13] {};
-
-           \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p14) [below= .6cm of p6]{\!\!\!\!\!\!\!\!$p_0 \! \tand \! p_1$\!\!\!\!\!\!\!\!};
-
-           \draw[thick, line width=1.25] (s) edge[-latex] (p1) (s) edge[-latex] (p7) (s) edge[-latex] (p9) (p1) edge[-latex] (p2) (p2) edge[-latex] (p3) (p3) edge[-latex] (p4) (p4) edge[-latex] (p5) (p5) edge[-latex] (p6) (p7) edge[-latex] (p8);
-           \draw[thick, line width=1.25] (p8) edge[-latex] (o1) (p6) edge[-latex] (o1) (p9) edge[-latex] (p10) (p10) edge[-latex] (p11) (p11) edge[-latex] (p12) (p12) edge[-latex] (p13) (p13) edge[-latex] (p14);
-
+            \begin{tikzpicture}[>=latex',line join=bevel,]
+                \pgfsetlinewidth{1bp}
+              %%
+              \begin{scope}
+                \pgfsetstrokecolor{black}
+                \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+                \pgfsetfillcolor{fillcol}
+                \filldraw (504.59bp,89.0bp) -- (504.59bp,141.0bp) -- (574.59bp,141.0bp) -- (574.59bp,89.0bp) -- cycle;
+              \end{scope}
+              \begin{scope}
+                \pgfsetstrokecolor{black}
+                \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+                \pgfsetfillcolor{fillcol}
+                \filldraw (413.59bp,8.0bp) -- (413.59bp,60.0bp) -- (484.59bp,60.0bp) -- (484.59bp,8.0bp) -- cycle;
+              \end{scope}
+                \pgfsetcolor{black}
+                % Edge: start -> 0
+                \draw [->] (48.953bp,98.996bp) ..
+controls (60.709bp,104.68bp) and (75.823bp,111.21bp)  ..
+(90.0bp,115.0bp) ..
+controls (159.91bp,133.7bp) and (244.63bp,139.46bp)  ..
+(303.86bp,141.59bp);
+                % Edge: start -> 2
+                \draw [->] (54.403bp,88.0bp) .. controls (61.886bp,88.0bp) and (70.183bp,88.0bp)  .. (89.616bp,88.0bp);
+                % Edge: start -> 7
+                \draw [->] (47.53bp,76.016bp) .. controls (59.151bp,68.885bp) and (74.111bp,59.705bp)  .. (96.525bp,45.951bp);
+                % Edge: 0 -> 1
+                \draw [->] (358.57bp,142.0bp) .. controls (373.75bp,142.0bp) and (393.11bp,142.0bp)  .. (421.11bp,142.0bp);
+                % Edge: 1 -> 6
+                \draw [->] (474.27bp,134.62bp) .. controls (483.34bp,131.85bp) and (493.84bp,128.65bp)  .. (514.43bp,122.37bp);
+                % Edge: 2 -> 3
+                \draw [->] (144.47bp,88.0bp) .. controls (151.84bp,88.0bp) and (160.04bp,88.0bp)  .. (179.56bp,88.0bp);
+                % Edge: 3 -> 4
+                \draw [->] (241.48bp,88.0bp) .. controls (249.31bp,88.0bp) and (258.05bp,88.0bp)  .. (278.13bp,88.0bp);
+                % Edge: 4 -> 5
+                \draw [->] (384.77bp,88.0bp) .. controls (393.21bp,88.0bp) and (401.81bp,88.0bp)  .. (421.1bp,88.0bp);
+                % Edge: 5 -> 6
+                \draw [->] (474.27bp,95.378bp) .. controls (483.34bp,98.146bp) and (493.84bp,101.35bp)  .. (514.43bp,107.63bp);
+                % Edge: 7 -> 8
+                \draw [->] (144.47bp,34.0bp) .. controls (153.0bp,34.0bp) and (162.63bp,34.0bp)  .. (183.09bp,34.0bp);
+                % Edge: 8 -> 9
+                \draw [->] (237.86bp,34.0bp) .. controls (251.05bp,34.0bp) and (267.41bp,34.0bp)  .. (294.09bp,34.0bp);
+                % Edge: 9 -> 10
+                \draw [->] (368.61bp,34.0bp) .. controls (381.85bp,34.0bp) and (396.84bp,34.0bp)  .. (421.45bp,34.0bp);
+                % Node: 6
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (539.59bp,115.0bp) ellipse (27.0bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (539.59bp,115.0bp) node {$\text{p1}$};
+              \end{scope}
+                % Node: 10
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+                \pgfsetstrokecolor{strokecol}
+                \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+                \pgfsetfillcolor{fillcol}
+                \filldraw [opacity=1] (449.09bp,34.0bp) ellipse (27.5bp and 18.0bp);
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (449.09bp,34.0bp) node {$\text{p0} \land \text{p1}$};
+              \end{scope}
+                % Node: start
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (27.0bp,88.0bp) ellipse (27.0bp and 18.0bp);
+                \draw (27.0bp,88.0bp) node {start};
+              \end{scope}
+                % Node: 0
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (331.29bp,142.0bp) ellipse (27.0bp and 18.0bp);
+                \draw (331.29bp,142.0bp) node {$\text{p2}$};
+              \end{scope}
+                % Node: 2
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (117.0bp,88.0bp) ellipse (27.0bp and 18.0bp);
+                \draw (117.0bp,88.0bp) node {$\text{p2}$};
+              \end{scope}
+                % Node: 7
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (117.0bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                \draw (117.0bp,34.0bp) node {$\text{p2}$};
+              \end{scope}
+                % Node: 1
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (449.09bp,142.0bp) ellipse (27.5bp and 18.0bp);
+                \draw (449.09bp,142.0bp) node {$\text{p0} \land \text{p1}$};
+              \end{scope}
+                % Node: 3
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (210.5bp,88.0bp) ellipse (30.5bp and 18.0bp);
+                \draw (210.5bp,88.0bp) node {$\neg \text{p0} \land \text{p1}$};
+              \end{scope}
+                % Node: 4
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (336.3bp,70.05bp) -- (339.61bp,70.15bp) -- (342.89bp,70.3bp) -- (346.12bp,70.49bp) -- (349.29bp,70.74bp) -- (352.39bp,71.03bp) -- (355.4bp,71.36bp) -- (358.32bp,71.75bp) -- (361.12bp,72.18bp) -- (363.81bp,72.65bp) -- (366.37bp,73.16bp) -- (368.79bp,73.71bp) -- (371.07bp,74.31bp) -- (373.19bp,74.94bp) -- (375.15bp,75.61bp) -- (376.95bp,76.31bp) -- (378.58bp,77.04bp) -- (380.04bp,77.8bp) -- (381.32bp,78.59bp) -- (382.43bp,79.41bp) -- (383.36bp,80.25bp) -- (384.11bp,81.11bp) -- (384.69bp,81.99bp) -- (385.09bp,82.89bp) -- (385.32bp,83.8bp) -- (385.38bp,84.72bp) -- (385.28bp,85.65bp) -- (385.02bp,86.59bp) -- (384.6bp,87.53bp) -- (384.04bp,88.47bp) -- (383.33bp,89.41bp) -- (382.49bp,90.35bp) -- (381.52bp,91.28bp) -- (380.42bp,92.2bp) -- (379.22bp,93.11bp) -- (377.9bp,94.01bp) -- (376.49bp,94.89bp) -- (374.98bp,95.75bp) -- (373.39bp,96.59bp) -- (371.72bp,97.41bp) -- (369.98bp,98.2bp) -- (368.17bp,98.96bp) -- (366.3bp,99.69bp) -- (364.39bp,100.39bp) -- (362.42bp,101.06bp) -- (360.42bp,101.69bp) -- (358.38bp,102.29bp) -- (356.3bp,102.84bp) -- (354.21bp,103.35bp) -- (352.08bp,103.82bp) -- (349.94bp,104.25bp) -- (347.78bp,104.64bp) -- (345.61bp,104.97bp) -- (343.42bp,105.26bp) -- (341.23bp,105.51bp) -- (339.03bp,105.7bp) -- (336.82bp,105.85bp) -- (334.61bp,105.95bp) -- (332.4bp,106.0bp) -- (330.19bp,106.0bp) -- (327.97bp,105.95bp) -- (325.76bp,105.85bp) -- (323.56bp,105.7bp) -- (321.36bp,105.51bp) -- (319.16bp,105.26bp) -- (316.98bp,104.97bp) -- (314.81bp,104.64bp) -- (312.65bp,104.25bp) -- (310.5bp,103.82bp) -- (308.38bp,103.35bp) -- (306.28bp,102.84bp) -- (304.21bp,102.29bp) -- (302.17bp,101.69bp) -- (300.16bp,101.06bp) -- (298.2bp,100.39bp) -- (296.28bp,99.69bp) -- (294.42bp,98.96bp) -- (292.61bp,98.2bp) -- (290.87bp,97.41bp) -- (289.2bp,96.59bp) -- (287.61bp,95.75bp) -- (286.1bp,94.89bp) -- (284.68bp,94.01bp) -- (283.37bp,93.11bp) -- (282.16bp,92.2bp) -- (281.07bp,91.28bp) -- (280.1bp,90.35bp) -- (279.26bp,89.41bp) -- (278.55bp,88.47bp) -- (277.99bp,87.53bp) -- (277.57bp,86.59bp) -- (277.31bp,85.65bp) -- (277.21bp,84.72bp) -- (277.27bp,83.8bp) -- (277.5bp,82.89bp) -- (277.9bp,81.99bp) -- (278.48bp,81.11bp) -- (279.23bp,80.25bp) -- (280.16bp,79.41bp) -- (281.26bp,78.59bp) -- (282.55bp,77.8bp) -- (284.0bp,77.04bp) -- (285.63bp,76.31bp) -- (287.43bp,75.61bp) -- (289.4bp,74.94bp) -- (291.52bp,74.31bp) -- (293.8bp,73.71bp) -- (296.22bp,73.16bp) -- (298.77bp,72.65bp) -- (301.46bp,72.18bp) -- (304.27bp,71.75bp) -- (307.18bp,71.36bp) -- (310.19bp,71.03bp) -- (313.29bp,70.74bp) -- (316.46bp,70.49bp) -- (319.69bp,70.3bp) -- (322.97bp,70.15bp) -- (326.29bp,70.05bp) -- (329.62bp,70.0bp) -- (332.96bp,70.0bp) -- cycle;
+                \draw (331.29bp,88.0bp) node [align=center] {$\neg \text{p0} \land \text{p1}$ \\ {\tiny repeats $0$ - $\infty$}};
+              \end{scope}
+                % Node: 5
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (449.09bp,88.0bp) ellipse (27.5bp and 18.0bp);
+                \draw (449.09bp,88.0bp) node {$\text{p0} \land \text{p1}$};
+              \end{scope}
+                % Node: 8
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (210.5bp,34.0bp) ellipse (27.0bp and 18.0bp);
+                \draw (210.5bp,34.0bp) node {$\top$};
+              \end{scope}
+                % Node: 9
+              \begin{scope}
+                \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+                \pgfsetstrokecolor{strokecol}
+                \draw (334.77bp,16.05bp) -- (337.07bp,16.15bp) -- (339.35bp,16.3bp) -- (341.6bp,16.49bp) -- (343.8bp,16.74bp) -- (345.95bp,17.03bp) -- (348.05bp,17.36bp) -- (350.07bp,17.75bp) -- (352.02bp,18.18bp) -- (353.89bp,18.65bp) -- (355.67bp,19.16bp) -- (357.35bp,19.71bp) -- (358.93bp,20.31bp) -- (360.41bp,20.94bp) -- (361.77bp,21.61bp) -- (363.02bp,22.31bp) -- (364.15bp,23.04bp) -- (365.17bp,23.8bp) -- (366.06bp,24.59bp) -- (366.83bp,25.41bp) -- (367.47bp,26.25bp) -- (368.0bp,27.11bp) -- (368.4bp,27.99bp) -- (368.68bp,28.89bp) -- (368.84bp,29.8bp) -- (368.88bp,30.72bp) -- (368.81bp,31.65bp) -- (368.63bp,32.59bp) -- (368.34bp,33.53bp) -- (367.94bp,34.47bp) -- (367.45bp,35.41bp) -- (366.87bp,36.35bp) -- (366.19bp,37.28bp) -- (365.43bp,38.2bp) -- (364.6bp,39.11bp) -- (363.68bp,40.01bp) -- (362.7bp,40.89bp) -- (361.65bp,41.75bp) -- (360.55bp,42.59bp) -- (359.38bp,43.41bp) -- (358.17bp,44.2bp) -- (356.92bp,44.96bp) -- (355.62bp,45.69bp) -- (354.29bp,46.39bp) -- (352.93bp,47.06bp) -- (351.53bp,47.69bp) -- (350.11bp,48.29bp) -- (348.67bp,48.84bp) -- (347.21bp,49.35bp) -- (345.74bp,49.82bp) -- (344.25bp,50.25bp) -- (342.75bp,50.64bp) -- (341.24bp,50.97bp) -- (339.72bp,51.26bp) -- (338.2bp,51.51bp) -- (336.67bp,51.7bp) -- (335.13bp,51.85bp) -- (333.6bp,51.95bp) -- (332.06bp,52.0bp) -- (330.52bp,52.0bp) -- (328.99bp,51.95bp) -- (327.45bp,51.85bp) -- (325.92bp,51.7bp) -- (324.39bp,51.51bp) -- (322.86bp,51.26bp) -- (321.35bp,50.97bp) -- (319.84bp,50.64bp) -- (318.34bp,50.25bp) -- (316.85bp,49.82bp) -- (315.37bp,49.35bp) -- (313.91bp,48.84bp) -- (312.47bp,48.29bp) -- (311.05bp,47.69bp) -- (309.66bp,47.06bp) -- (308.3bp,46.39bp) -- (306.96bp,45.69bp) -- (305.67bp,44.96bp) -- (304.41bp,44.2bp) -- (303.2bp,43.41bp) -- (302.04bp,42.59bp) -- (300.93bp,41.75bp) -- (299.89bp,40.89bp) -- (298.9bp,40.01bp) -- (297.99bp,39.11bp) -- (297.15bp,38.2bp) -- (296.39bp,37.28bp) -- (295.72bp,36.35bp) -- (295.13bp,35.41bp) -- (294.64bp,34.47bp) -- (294.25bp,33.53bp) -- (293.96bp,32.59bp) -- (293.78bp,31.65bp) -- (293.71bp,30.72bp) -- (293.75bp,29.8bp) -- (293.91bp,28.89bp) -- (294.19bp,27.99bp) -- (294.59bp,27.11bp) -- (295.11bp,26.25bp) -- (295.76bp,25.41bp) -- (296.53bp,24.59bp) -- (297.42bp,23.8bp) -- (298.43bp,23.04bp) -- (299.56bp,22.31bp) -- (300.81bp,21.61bp) -- (302.18bp,20.94bp) -- (303.65bp,20.31bp) -- (305.24bp,19.71bp) -- (306.92bp,19.16bp) -- (308.7bp,18.65bp) -- (310.56bp,18.18bp) -- (312.51bp,17.75bp) -- (314.54bp,17.36bp) -- (316.63bp,17.03bp) -- (318.78bp,16.74bp) -- (320.99bp,16.49bp) -- (323.23bp,16.3bp) -- (325.51bp,16.15bp) -- (327.82bp,16.05bp) -- (330.13bp,16.0bp) -- (332.45bp,16.0bp) -- cycle;
+                \draw (331.29bp,34.0bp) node [align=center] {$\top$ \\ {\tiny repeats $0$ - $\infty$}};
+              \end{scope}
+              %
               \end{tikzpicture}}
@@
 We can then use the expanded notation for stared formulas larger than a single proposition, thus navigating a trade-off between small representation and limiting the visual complication.
-Do the back edges in a limited capacity cause confusion between timeline and automata representatins?
-
-\item {\bf What are intuitive representations of star-formulas and do they change depending on the formula?} There are two ways to represent stars in regular expressions \cite{Runming where did you find these?}.
-We can represent a stared formula inside a box \cite{where?} or with a back edge \cite{where?}.
+The criticism of this approach may be that back edges cause confusion between timeline and automata representations, and that with back edges timelines stop being intuitive about linearity of time.
+
+\item {\bf What are intuitive representations of star-formulas and do they change depending on the formula?} Common regular expression visualizers use two ways to represent stars in regular expressions.
+We can represent a stared formula inside a box \cite{B22} with related caption to indicate the repetition (similar to the design decision we made in \tool); or with back edges \cite{A20}.
 Does using the box cause confusion with respect to the LTL $\Box$ operator?
@@
 \end{itemize}
-KYR note: we should include a figure here with the different visual options we brainstormed and reference it in the bullets above.
 

### 2023-02-14 paper/main.tex
updated tllen def

@@
         \tllen(A_1 + A_2)   &= \max(\tllen(A_1), \tllen(A_2))\\
-        \tllen(A^*)         &= 2\tllen(A) + 1
+        \tllen(A^*)         &= \tllen(A) 
     \end{align*}
@@
     \centering
-    \subfloat{{\includegraphics[width=6.5cm]{img/naive-ltl2tl-scatterplot-omit-big-values.png} }}%
+    \subfloat{{\includegraphics[width=6.5cm]{img/tllens-graph.png} }}%
     \quad % [\centering label 1]
-    \subfloat{{\includegraphics[width=6.5cm]{img/star-height-scatter-plot.png}}}
+    \subfloat{{\includegraphics[width=6.5cm]{img/star-height-graph.png}}}
     \caption{Visualization complexity metrics for formulas collected from Acacia \cite{RV10} and NASA's  AAC \cite{GCMTR16}}

### 2023-02-14 src/ltl_regex.py

@@ -76,7 +76,7 @@ def regex_tllen(regex: Regex) -> int:
         case Union(r1, r2):
             return max(regex_tllen(r1), regex_tllen(r2))
         case Star(r):
-            return 2 * regex_tllen(r) + 1
+            return regex_tllen(r) 
         case _:
             raise TypeError(f'Unknown regex type: {type(regex)}')
 

### 2023-06-18 paper/main.tex
something
update figure 11
update paper

@@
-\documentclass[preprint,12pt]{elsarticle}
-\journal{Journal of Computer Languages}
+\documentclass[conference]{IEEEtran}
 \usepackage[x11names, svgnames, rgb]{xcolor}
@@
 
+\tikzset{
+    partial ellipse/.style args={#1:#2:#3}{
+        insert path={+ (#1:#3) arc (#1:#2:#3)}
+    }
+}
+
 \begin{document}
 
-\begin{frontmatter}
 \title{What's in a Name? Linear Temporal Logic Literally Represents Time Lines}
 
-	\author[inst1]{Runming Li\corref{cor1}}
-    \ead{runmingl@andrew.cmu.edu}
-
-	\author[inst1]{Keerthana Gurushankar\corref{cor1}}
-    \ead{kgurusha@andrew.cmu.edu}
-
-    \author[inst1]{Marijn~J.H.~Heule\corref{cor2}}
-    \ead{marijn@cmu.edu}
-
-    \author[inst2]{Kristin~Y.~Rozier}
-    \ead{kyrozier@iastate.edu}
-
-    \affiliation[inst1]{organization={Carnegie Mellon University},%Department and Organization
-                %addressline={5000 Forbes Ave},
-                city={Pittsburgh},
-                %postcode={15213},
-                state={PA},
-                country={USA}}
-
-    \affiliation[inst2]{organization={Iowa State University},%Department and Organization
-                %addressline={Address Two},
-                city={Ames},
-                %postcode={50010},
-                state={IA},
-                country={USA}}
-
-	\cortext[cor1]{These authors contributed equally to this work}
-    \cortext[cor2]{Corresponding author}
+\author{\IEEEauthorblockN{Runming Li}
+\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
+Pittsburgh, USA \\
+runmingl@andrew.cmu.edu}
+\and
+\IEEEauthorblockN{Keerthana Gurushankar}
+\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
+Pittsburgh, USA \\
+kgurusha@andrew.cmu.edu}
+\and
+\IEEEauthorblockN{Marijn~J.H.~Heule}
+\IEEEauthorblockA{\textit{Carnegie Mellon University}\\
+Pittsburgh, USA \\
+marijn@cmu.edu}
+\and
+\IEEEauthorblockN{Kristin~Y.~Rozier}
+\IEEEauthorblockA{\textit{Iowa State University} \\
+Ames, USA \\
+ekyrozier@iastate.edu}
+}
+
+\maketitle
+
+\thispagestyle{plain}
+\pagestyle{plain}
 
 \begin{abstract}
-        Linear Temporal Logic (\ltl) is widely used to specify requirements in safety-critical systems.
+  Linear Temporal Logic (LTL) is widely used to specify requirements in safety-critical systems.
   However, like many formal verification techniques, it is known to be unintuitive and error-prone for human practitioners to specify and validate.
-        In this paper, we provide a new timeline tool for visualizing \ltl-based specifications, which is effective at intuitively representing a wide range of formulas.
-        Our tool generates timeline visualizations by translating \ltl\ formulae to intermediate representations as \Buchi automata and then $\omega$-regular expressions, and finally simplifying and visualizing the expressions.
+  In this paper, we provide a new timeline tool for visualizing LTL-based specifications, which is effective at intuitively representing a wide range of formulas.
+  Our tool generates timeline visualizations by translating LTL formulas to intermediate representations as B\"{u}chi automata and then regular expressions, and finally simplifying and visualizing the expressions.
   We provide an algorithm for this visualization, a theoretical soundness analysis, and an implementation.
@@
 
-    \begin{highlights}
-        \item We transform Linear Temporal Logic (\ltl) formulas to timeline visualizations for the set of satisfying traces.
-        \item We translate \ltl\ formulas to \Buchi automata, then to $\omega$-regular expressions, then simplify them and use graph visualization tools to draw timelines.
-        \item Our algorithm is sound and complete.
-        \item Our tool, \tool, effectively constructs small timeline visualizations for a range of \ltl\ formulas.
-    \end{highlights}
-
-    \begin{keyword}
-        Modal and Temporal Logics
-        \sep Logic and Verification
-        \sep Regular languages
-    \end{keyword}
-\end{frontmatter}
+\begin{IEEEkeywords}
+Modal and Temporal Logics, Logic and Verification, Regular languages
+\end{IEEEkeywords}
+
 \section{Introduction}
-
 Requirement specification is a central step in the development of safety-critical systems.
@@
 \begin{align*}
-    \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \\
-    \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
+    \always & (\texttt{tsafe.TSAFE\_command1} \land \\ & \texttt{controller.CTR\_control\_1} \\
+    \limplies & \nextt (\neg \texttt{controller.CTR\_control\_1}))
 \end{align*}
@@
 
-Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automaton and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of \ltl\ formulas.
+Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automata and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of \ltl\ formulas.
 It would visualize the above air traffic control requirement behavior with the timeline shown in \cref{example:air}.
@@
 
-\subsection{Linear temporal logic (LTL)} \label{sec:ltl}
-
-\begin{definition}[Linear Temporal Logic (LTL)]
+\subsection{Linear temporal logic (\ltl)} \label{sec:ltl}
+
+\begin{definition}[Linear Temporal Logic (\ltl)]
     % cite Kristin's survey paper
@@
     \begin{align*}
-        \Phi ::= p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
+        \Phi ::= & p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \\ & \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
     \end{align*}\label{ltl-defn}
@@
 \begin{definition}[Semantics of \ltl\ formula]
-    The semantics of \ltl\ formula is defined via judgment $\pi, i \models \Phi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step.
+    The semantics of \ltl\ formula is defined via  $\pi, i \models \Phi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step.
 The semantics follows exactly from Rozier~\cite{Roz11}.
@@
         \item an initial or start state called $s\in Q$
-        \item a set of accept states $F \subseteq Q$
+        \item a set of accepting states $F \subseteq Q$
     \end{enumerate}
@@
 \subsection{$\omega$-regular expression}
-\begin{definition}[Regular expression]
+\begin{definition}[Regular expression]\label{def:regex}
     For word $a \in \Sigma$, regular expression is defined by the following grammar:
@@
 \begin{remark}
-    For the purpose of our tool, $\Sigma$ is the set of propositional logic formula defined as
+    For the purpose of our tool, $\Sigma$ is the set of propositional logic formulas defined as
     \[
-    \Psi ::= p \mid \neg \Psi \mid \Psi \land \Psi \mid \Psi \lor \Psi \mid \Psi \limplies \Psi
+    \Psi ::= p \mid \top \mid \bot \mid \neg \Psi \mid \Psi \land \Psi \mid \Psi \lor \Psi \mid \Psi \limplies \Psi
     \]
@@
 
-\begin{definition}[$\omega$-regular expression]
+\begin{definition}[$\omega$-regular expression]\label{def:omega-regex}
     Regular expression concerns only finite-length strings.
@@
     \begin{align*}
-        L_{\omega}(A^{\omega}) & = \{s_1s_2s_3\cdots \mid s_i \in L(A) \text{ and } i \ge 1\} \\
+        L_{\omega}(A^{\omega}) & = \{s_1s_2s_3\cdots \mid s_i \in L(A) \text{ and } i \ge 1\} \tag{$\epsilon
+         \not\in L(A)$} \\
         L_{\omega}(AB) & = \{s_1s_2 \mid s_1 \in L(A) \text{ and } s_2 \in L_{\omega}(B)\} \\
@@
 
-\subsection{Timeline}
+\begin{remark}
+  \Cref{def:regex,def:omega-regex} are the standard definitions of regular expressions and $\omega$-regular expressions, respectively. We include them here for completeness.
+\end{remark}
+
+\subsection{Timeline}\label{sec:timeline}
 We present timelines as graphic visualizations. It contains the following features:
@@
 If $\Psi = 1$, that means all atomic propositions can behave arbitrarily.
-    \item A node in egg shake with a caption ``repeats $0$ - $\infty$'' means to repeat the (one time step) current node for arbitrarily finitely many times.
+    \item A node in egg shape with a caption ``repeats $0$ - $\infty$'' means to repeat the (one time step) current node for arbitrarily finitely many times.
     \item A node with label ``$\cdots$'' means to repeat the pattern prior to it and after it arbitrarily finitely many times.
-    \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its starting point.
+    \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its (left) starting point.
+    \item Timelines can be in parallel, signifying that either of the parallel timeline could happen.
 \end{itemize}
+
+The definition of timeline we use here are specifically what we devised for the purpose of visualizing \ltl\ formulas.
+We show how to construct such timelines from \ltl\ formulas in \cref{sec:correctness-timeline}.
 
@@
         \centering
-        \begin{tikzpicture}
+        \begin{tikzpicture}[scale=0.7, transform shape]
         \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
@@
         \centering
-        \begin{tikzpicture}[>=latex',line join=bevel,]
+        \begin{tikzpicture}[>=latex',line join=bevel, scale=0.7, transform shape]
             \pgfsetlinewidth{1bp}
@@
 \section{Algorithm}
-On a high level, our algorithm of converting \ltl\ formulas into timeline visualization works as follows:
+On a high level, our algorithm of converting \ltl\ formulas into timeline visualizations works as follows:
 \begin{enumerate}
-    \item Convert the given \ltl\ formula to its corresponding \Buchi automata % (as detailed in \cref{ltl2aut})
-    \item Derive the $\omega$-regular expression corresponding to the \Buchi automata % (in \cref{aut2regex})
-    \item Simplify the derived $\omega$-regular expression % (in \cref{regex-simplify})
-    \item Visualize the $\omega$-regular expression according to its structure %(in \cref{regex2timeline})
+    \item Convert the given \ltl\ formula to its corresponding \Buchi automaton. % (as detailed in \cref{ltl2aut})
+    \item Derive the $\omega$-regular expression corresponding to the \Buchi automaton. % (in \cref{aut2regex})
+    \item Simplify the derived $\omega$-regular expression. % (in \cref{regex-simplify})
+    \item Visualize the $\omega$-regular expression according to its structure. %(in \cref{regex2timeline})
 \end{enumerate}
@@
     \centering
-    \includegraphics[width=\textwidth]{img/algorithm_outline.pdf}
+    % \includegraphics[width=\textwidth, scale=0.3]{img/algorithm_outline.pdf}
+    TODO
     \caption{Algorithm outline}
@@
 We have observed multiple patterns in the resulting $\omega$-regular expression that could be simplified.
-For example, an $\omega$-regular expression in the form of $r^*r^{\omega}$ represents the same timeline as $r^{\omega}$, but the latter is more intuitive.
+For example, an $\omega$-regular expression in the form of $r^*r^{\omega}$ represents the same timeline as $r^{\omega}$, but the latter is more intuitive and concise.
 For this purpose, we devised some simplification rules in our tool, based on our observation of common patterns in the generated $\omega$-regular expression.
+
+There is no agreed upon canonical form for regular expression, hence we do not hope to find the simplest regular expression for visualization.
+Regular expression simplification comes down to regular expression equivalence checking, which is computationally hard \cite{MNS04}.
+For purpose of simplification, one could perform a search over equivalent regular expressions and decide which one is simpler to use.
+However, this strategy is expensive in terms of the running time, and for the purpose of visualization, we did not use this strategy in our tool.
+We consider this approach as future work.
 
@@
 Here we show a demonstrating subset of simplification rules we encoded.
+In theory one could add more rules to the tool, so long as they are sound; here we only choose to encode the rules that represent common patterns we have observed in the generated $\omega$-regular expression.
 \begin{alignat*}{2}
@@
 \begin{example}
-    The formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which corresponds to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
-    \begin{figure}[h!]
+    Using our algorithm, the \ltl\ formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which corresponds to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
+    \begin{figure*}[h!]
         \centering
@@
 %        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
-        \caption{Timeline for %un-simplified
+        \caption{Timeline visualization for %un-simplified
         $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
         \label{fig:unsimplified}
-    \end{figure}
-    \begin{figure}[h!]
+    \end{figure*}
+    \begin{figure*}[h!]
         \centering
@@
   %      \includegraphics[scale=0.3]{examples/ex9/ex9.png}
-        \caption{Timeline for simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
+        \caption{Timeline visualization for simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
         \label{fig:simplified}
-    \end{figure}
+    \end{figure*}
 \end{example}
@@
 \]
-where $A_i$ are regular expressions, and $A_{2i-1}$ could be $\epsilon$.
+where $A_i$ are regular expressions, $A_{2i-1}$ could be $\epsilon$, and $\epsilon \not\in L(A_{2i})$.
 On a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input.
@@
 
+\subsection{Correctness of Timeline Visualization}\label{sec:correctness-timeline}
+Inductively, we show how to construct each form of regular and $\omega$-regular expression into a timeline representation.
+\paragraph{Regular expression}
+\begin{enumerate}
+  \item $A = \emptyset$. Visualized as no timeline. An empty regular expression signifies nothing is true at any time.
+  \item $A = \epsilon$. Omitted in the visualization.
+  \item $A = a$. Visualized as a single timeline node with $a$. A regular expression of an propositional logic formula signifies that the atomic proposition is true at the current time step.
+  \item $A = A_1A_2$.
+Visualized as the timeline of $A_1$ followed by the timeline of $A_2$.
+A concatenation of two regular expressions signifies that the first regular expression must be true before the second regular expression can be true in the time step.
+  \item $A = A_1 + A_2$.
+Visualized as the timelines of $A_1$ and $A_2$ in parallel.
+A union of two regular expressions signifies that either of the regular expressions can be true, which is represented by the parallel timelines.
+  \item $A = A_1^*$.
+If $A_1$ is a propositional logic formula, then it is visualized as an egg shape node with caption ``repeats 0 - $\infty$''.
+If $A_1$ is a regular expression involving concatenation, star, etc, then it is visualized as the timeline of $A_1$ followed by a node with label ``$\cdots$'', and that timeline pattern again.
+A Kleene star of a regular expression signifies that the regular expression can be repeated any number of times, including 0 times, which matches the meaning of our representation of egg shape node and ``$\cdots$''  node as described in \cref{sec:timeline}.
+\end{enumerate}
+\paragraph{$\omega$-regular repression}
+\begin{enumerate}
+  \item $B = A^\omega$.
+Visualized as a grey box enclosed with the timeline of $A$.
+An $\omega$ of a regular expression signifies that the regular expression is to be repeated infinitely many times, which matches the meaning of our representation of grey box, because every time it reach the end of the grey box, it must reenter the same grey box again, hence infinite repeat.
+  \item $B = AB$.
+Visualized as the timeline of $A$ followed by the timeline of $B$.
+A concatenation of a regular expression and an $\omega$-regular expression signifies that the first must be true before the second $\omega$-regular expression can be true in the time step.
+  \item $B = B + B$.
+Visualized as the timelines of $B$ and $B$ in parallel.
+A union of two $\omega$-regular expressions signifies that either of the $\omega$-regular expressions can be true, which is represented by the parallel timelines.
+\end{enumerate}
+
 \section{Tool showcase} \label{sec:tool-showcase}
-To demonstrate the result of our tool, we present two examples, one from a real-world model checking example from Zhao and Rozier~\cite{ZR14} and one from a randomly generated \ltl\ formula.
+To demonstrate the result of our tool, we present three examples, one from a real-world model checking example from Zhao and Rozier~\cite{ZR14}, one from a randomly generated \ltl\ formula, and one specifically demonstrates the use of our tool in specification verification.
 
@@
     \begin{align*}
-        \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \\
-        \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
+        \always & (\texttt{tsafe.TSAFE\_command1} \land  \\ & \texttt{controller.CTR\_control\_1} \\
+        \limplies & \nextt (\neg \texttt{controller.CTR\_control\_1}))
     \end{align*}
@@
     For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex14}.
-    \begin{figure}[h!]
+    \begin{figure*}[h!]
         \centering
         \resizebox{\textwidth}{!}{
+%        \begin{tikzpicture}
+%            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) {\!\!\!\!start\!\!\!\!};
+%            \node[shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab1) [right= of s]{\!\!\!\!$a \tand b$\!\!\!\!};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+%            \node (m) at ($(ab1)!0.5!(ab2)$) {};
+%            \node[shape=rectangle, fill=gray!30!white, style={minimum width=4cm, minimum height=3cm}] (g2) [right= -1cm of m] {};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab1) [right= of s]{\!\!\!\!$a \tand b$\!\!\!\!};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab2) [above= 0.6cm of ab1]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+%            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab3) [below= 0.6cm  of ab1]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (b1) [right= 0.75cm  of ab1]{\!\!\!\!\!\!\!\!$\tnot b$\!\!\!\!\!\!\!\!};
+%            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab4) [right= .75cm of ab3]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
+%            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab5) [right= .75cm of ab4]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+%            \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab6) [right= .75cm of ab5]{\!\!\!\!\!\!\!\!$a \tand b$\!\!\!\!\!\!\!\!};
+%            \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=1.3cm}] (g2) [right= 0.6cm of ab6] {};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab7) [right= .75cm of ab6]{\!\!\!\!\!\!\!\!$\tnot b$\!\!\!\!\!\!\!\!};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab8) [right= .75cm of ab7]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab9) [right= .75cm of ab8]{\!\!\!\!\!\!\!\!$\dots$\!\!\!\!\!\!\!\!};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab10) [right= .75cm of ab9]{\!\!\!\!\!\!\!\!$\tnot a\! \tor \! \tnot b$\!\!\!\!\!\!\!\!};
+%            \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (ab11) [right= .75cm of ab10]{\!\!\!\!\!\!\!\!$a \tand b$\!\!\!\!\!\!\!\!};
+%
+%        \draw[thick, line width=1.25] (s) edge[-latex] (ab1) (s) edge[-latex] (ab2) (s) edge[-latex] (ab3) (ab3) edge[-latex] (ab4) (ab4) edge[-latex] (ab5) (ab5) edge[-latex] (ab6) (ab1) edge[-latex] (b1);
+%        \draw[thick, line width=1.25] (ab6) edge[-latex] (ab7) (ab6) edge[-latex] (ab7) (ab7) edge[-latex] (ab8) (ab8) edge[-latex] (ab9) (ab9) edge[-latex] (ab10) (ab10) edge[-latex] (ab11);
+%
+%        \end{tikzpicture}}
+%
+   %    \includegraphics[scale=0.3]{examples/ex14/ex14.png}
+
             \begin{tikzpicture}[>=latex',line join=bevel,]
@@
         \label{fig:ex14}
-    \end{figure}
+    \end{figure*}
 \end{example}
@@
     \[
-    p_2 \land (\eventually \always p_0 \weakrelease \nextt(\always p_1 \land ((p_0 \limplies p_2 \land p_2 \limplies p_0) \stronguntil \eventually p_0)))
+    p_2 \land (\eventually \always p_0 \stronguntil \nextt(\always p_1 \land (((p_0 \limplies p_2) \land (p_2 \limplies p_0)) \stronguntil \eventually p_0)))
     \]
     This formula is reasonably complicated, and hard for human to reason about directly. For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex13}.
-    \begin{figure}[h!]
+    \begin{figure*}[h!]
         \centering
@@
    %     \includegraphics[scale=0.3]{examples/ex13/ex13.png}
-        \caption{Timeline for $p_2 \land (\eventually \always p_0 \weakrelease \nextt(\always p_1 \land ((p_0 \limplies p_2 \land p_2 \limplies p_0) \stronguntil \eventually p_0)))$}
+        \caption{Timeline for $p_2 \land (\eventually \always p_0 \stronguntil \nextt(\always p_1 \land (((p_0 \limplies p_2) \land (p_2 \limplies p_0)) \stronguntil \eventually p_0)))$}
         \label{fig:ex13}
-    \end{figure}
+    \end{figure*}
 \end{example}
@@
 \end{remark}
+
+\begin{example}
+  Suppose we have a specification ``$p$ oscillates every time step''. It is common to come up with the following two \ltl\ formulas to describe this specification.
+  \begin{itemize}
+    \item $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$
+    \item $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$
+  \end{itemize}
+  It may be hard, without rigorous analysis, to distinguish which one is correct for the specification.
+However, our tool can generate the following two timelines for these two formulas as shown in \cref{fig:oscillates1,fig:oscillates2}, which clearly show the first formula is correct and the second formula is equivalent to $\bot$.
+\begin{figure}[!h]
+  \centering
+  \begin{tikzpicture}[scale=0.7, transform shape]
+  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
+  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [below=0.4cm of p1] {\!\!\!$p$\!\!\!};
+  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
+  \node (m) at ($(p1)!0.5!(p2)$) {};
+  \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.25cm}] (g) [right= 1.35cm of m] {};
+
+  \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p4) [right= 1.5cm of m] {\!\!\!$\lnot p$\!\!\!};
+  \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p5) [right= 1cm of p4] {\!\!\!$p$\!\!\!};
+  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 4cm of m] {\!\!\!start\!\!\!};
+  \draw[thick, line width=1.25] (s) edge[-latex] (p1) (s) edge[-latex] (p3) (p3) edge[-latex] (p2) (p1) edge[-latex] (p4) (p2) edge[-latex] (p4) (p4) edge[-latex] (p5);
+
+  \end{tikzpicture}
+%     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
+  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$}
+  \label{fig:oscillates1}
+\end{figure}
+\begin{figure}[!h]
+  \centering
+  \begin{tikzpicture}[>=latex',line join=bevel, scale=0.7, transform shape]
+    \pgfsetlinewidth{1bp}
+  %%
+  \pgfsetcolor{black}
+    % Node: start
+  \begin{scope}
+    \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+    \pgfsetstrokecolor{strokecol}
+    \draw (27.0bp,18.0bp) ellipse (27.0bp and 18.0bp);
+    \draw (27.0bp,18.0bp) node {start};
+  \end{scope}
+  %
+  \end{tikzpicture}
+  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$ (a single ``start'' means every time step is $\bot$)}
+  \label{fig:oscillates2}
+\end{figure}
+\end{example}
 
@@
     \centering
-    \includegraphics[scale=0.6]{img/scale.png}
+    \includegraphics[scale=0.6]{img/binary.png}
     \caption{Scalability measured with binary counter examples from Rozier and Vardi \cite{RV10}}
@@
 \begin{align*}
-    \Phi ::= p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
+    \Phi ::= & p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \\ & \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
 \end{align*}
@@
 %\nocite{*}
-\bibliographystyle{elsarticle-num}
+\bibliographystyle{IEEEtran}
 \bibliography{RelatedWork}

### 2023-06-19 paper/main.tex
Update main.tex
edited abstract

@@
 \begin{abstract}
-  Linear Temporal Logic (LTL) is widely used to specify requirements in safety-critical systems.
-  However, like many formal verification techniques, it is known to be unintuitive and error-prone for human practitioners to specify and validate.
-  In this paper, we provide a new timeline tool for visualizing LTL-based specifications, which is effective at intuitively representing a wide range of formulas.
+  Linear Temporal Logic (LTL) is arguably the most popular specification language for formal verification of safety-critical systems.
+  However, LTL formulas can be unintuitive and error-prone for human practitioners to specify and validate.
+Meanwhile, drawing timelines remains one of the most popular methods for specifying and validating requriements for industrial system designs, such as in aerospace operational concepts.
+  Therefore, we provide a new timeline tool for visualizing LTL specifications as timelines, providing provably-correct, intuitive equivalents between these two specification formats.
   Our tool generates timeline visualizations by translating LTL formulas to intermediate representations as B\"{u}chi automata and then regular expressions, and finally simplifying and visualizing the expressions.

### 2023-06-23 paper/main.tex
dfa to nfa

@@
 
-\author{\IEEEauthorblockN{Runming Li}
+\author{\IEEEauthorblockN{Runming Li\IEEEauthorrefmark{1}}
 \IEEEauthorblockA{\textit{Carnegie Mellon University}\\
@@
 \and
-\IEEEauthorblockN{Keerthana Gurushankar}
+\IEEEauthorblockN{Keerthana Gurushankar\IEEEauthorrefmark{1}}
 \IEEEauthorblockA{\textit{Carnegie Mellon University}\\
@@
 \maketitle
+\begingroup\renewcommand\thefootnote{\textsection}
+\footnotetext{These authors contributed equally to this work}
+\endgroup
 
@@
 \end{enumerate}
-\begin{figure}[!h]
+\begin{figure*}[!t]
     \centering
-    % \includegraphics[width=\textwidth, scale=0.3]{img/algorithm_outline.pdf}
-    TODO
+    \includegraphics[width=\textwidth, scale=0.3]{img/algorithm_outline.pdf}
     \caption{Algorithm outline}
     \label{fig:algo}
-\end{figure}
+\end{figure*}
 
@@
 \begin{algorithm}[h!]
-    \caption{reduce\_dfa}
+    \caption{reduce\_nfa}
     \begin{algorithmic}
-        \Require ($G, v$), a DFA with state $v$ that is not initial or final
+        \Require ($G, v$), an NFA with state $v$ that is not initial or final
         \Ensure Deletes state $v$ from $G$ while ensuring the same language is recognized
@@
 \begin{algorithm}[h!]
-    \caption{dfa2regex}
+    \caption{nfa2regex}
     \begin{algorithmic}
-        \Require ($G, s, f$), a DFA with initial state $s$ and final state $f$
+        \Require ($G, s, f$), an NFA with initial state $s$ and final state $f$
         \Ensure The regular expression corresponding to all paths from $s$ to $f$
@@
         \While{ there exists an interior vertex $v$ }
-            \State reduce\_dfa($G, v$)
+            \State reduce\_nfa($G, v$)
             \State combine multiedges, i.e. $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
@@
 \begin{algorithm}[h!]
-    \caption{dfa2regex\_firstvisit}
+    \caption{nfa2regex\_firstvisit}
     \begin{algorithmic}
-        \Require ($G, s, f$), a DFA with initial state $s$ and final state $f$
+        \Require ($G, s, f$), an NFA with initial state $s$ and final state $f$
         \Ensure The regular expression of all paths from $s$ reaching $f$ for the first time
         \State delete all out edges from $f$ in $G$
-        \State \Return dfa2regex($G, s, f$)
+        \State \Return nfa2regex($G, s, f$)
     \end{algorithmic}
@@
         \Ensure The $\omega$-regular expression recognized by $G$
-        \State \Return $\bigcup_{f \in F}\left(\text{dfa2regex\_firstvisit}(G, s, f)\text{\^{}dfa2regex}(G, f, f) \right) $
+        \State \Return $\bigcup_{f \in F}\left(\text{nfa2regex\_firstvisit}(G, s, f)\text{\^{}nfa2regex}(G, f, f) \right) $
     \end{algorithmic}
@@
 \begin{lemma}
-    % reduce_dfa does its input to output behaviour
-    For any DFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_dfa}$(G, v)$ preserves the regular language accepted by $G$
+    % reduce_nfa does its input to output behaviour
+    For any NFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_nfa}$(G, v)$ preserves the regular language accepted by $G$
 \end{lemma}
 \begin{proof}
-    Let $G'$ be the graph of $G$ post reduction by the application of \textbf{reduce\_dfa}$(G, v)$.
+    Let $G'$ be the graph of $G$ post reduction by the application of \textbf{reduce\_nfa}$(G, v)$.
 We show that the trace of every path accepted by $G$ is also accepted by $G'$.
@@
 \begin{lemma}
-    For any DFA $G$ with start state $s$ and (exactly one) final state $f$, \textbf{dfa2regex}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$ (i.e., the language accepted by $G$)
+    For any NFA $G$ with start state $s$ and (exactly one) final state $f$, \textbf{nfa2regex}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$ (i.e., the language accepted by $G$)
 \end{lemma}
 \begin{proof}
-    The while loop clearly terminates since the number of interior nodes is strictly decreasing, and upon termination, $G$ is a DFA containing only the nodes $s$ and $f$.
+    The while loop clearly terminates since the number of interior nodes is strictly decreasing, and upon termination, $G$ is an NFA containing only the nodes $s$ and $f$.
 Now, every non-terminal visit from $s$ to $f$ and back to $s$, can be replaced by an edge $s\xrightarrow{r_\mathrm{sf}r_\mathrm{ff}^* r_\mathrm{fs}} s$, instead of the edge $f\to s$.
-This DFA yields the regular language $(r_\mathrm{ss}|r_\mathrm{sf}r_\mathrm{ff}^* r_\mathrm{fs})^* r_\mathrm{sf} r_\mathrm{ff}$, as outputted by the algorithm.
+This NFA yields the regular language $(r_\mathrm{ss}|r_\mathrm{sf}r_\mathrm{ff}^* r_\mathrm{fs})^* r_\mathrm{sf} r_\mathrm{ff}$, as outputted by the algorithm.
 \end{proof}
@@
 \begin{lemma}
-    For any DFA $G$ with start state $s$ and (exactly one) final state $f$, \textbf{dfa2regex\_firstvisit}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$, visiting $f$ for the first time.
+    For any NFA $G$ with start state $s$ and (exactly one) final state $f$, \textbf{nfa2regex\_firstvisit}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$, visiting $f$ for the first time.
 \end{lemma}
@@
     \[
-        L = \bigcup_{f\in F} \textbf{dfa2regex}(G, s, f) \verb|^| \left(\textbf{dfa2regex\_firstvisit}(G, f, f)\right)^\omega
+        L = \bigcup_{f\in F} \textbf{nfa2regex}(G, s, f) \verb|^| \left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega
     \]
@@
     First, $L\subseteq L_\omega(G)$ since for every infinite run in $L$, clearly by definition of $L$, there is some $f\in F$ such that passes through $f$ infinitely often.
-The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often, thus the run is in $\textbf{dfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{dfa2regex\_firstvisit}(G, f, f)\right)^\omega$
+The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often, thus the run is in $\textbf{nfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega$
 \end{proof}

### 2023-06-26 paper/main.tex
def 2.4 fn to relation
typos/minor changes

@@
     \item A node with label ``$\cdots$'' means to repeat the pattern prior to it and after it arbitrarily finitely many times.
-    \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its (left) starting point.
+    \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its (left) starting points.
     \item Timelines can be in parallel, signifying that either of the parallel timeline could happen.
@@
 \section{Algorithm}
-On a high level, our algorithm of converting \ltl\ formulas into timeline visualizations works as follows:
+On a high level, our algorithm of converting \ltl\ formulas into timeline visualizations (depicted in \Cref{fig:algo}) works as follows:
 \begin{enumerate}
@@
 \paragraph*{Rule-based simplification}
-Here we show a demonstrating subset of simplification rules we encoded.
-In theory one could add more rules to the tool, so long as they are sound; here we only choose to encode the rules that represent common patterns we have observed in the generated $\omega$-regular expression.
+Here we show a demonstrating subset of the simplification rules we encoded.
+In theory one could add more rules to the tool, so long as they are sound; here we only choose to encode the rules that represent common patterns we have observed in the generated $\omega$-regular expressions.
 \begin{alignat*}{2}
@@
 \paragraph*{Result of simplification}
-Those simplification rules lead to more intuitive representation of timelines. Here we demonstrate their effects using an example.
+These simplification rules lead to more intuitive representation of timelines. Here we demonstrate their effects using an example.
 
 \begin{example}
-    Using our algorithm, the \ltl\ formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which corresponds to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
+    Using our algorithm, the \ltl\ formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
     \begin{figure*}[h!]
@@
 \begin{remark}
-    Both simplified and un-simplified $\omega$-regular expression would generate correct timeline representations.
+    Both simplified and un-simplified $\omega$-regular expressions would generate correct timeline representations.
 Correct as they faithfully represent the set of satisfying traces of the original \ltl\ formula $\Phi$.
@@
 where $A_i$ are regular expressions, $A_{2i-1}$ could be $\epsilon$, and $\epsilon \not\in L(A_{2i})$.
-On a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input.
+At a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input.
 We view each union operator as parallel timelines, and each $A_{2i-1}$ is concatenated with $A_{2i}$ repeated infinitely many times, as represented in the grey box.
@@
 Visualized as the timeline of $A$ followed by the timeline of $B$.
-A concatenation of a regular expression and an $\omega$-regular expression signifies that the first must be true before the second $\omega$-regular expression can be true in the time step.
+A concatenation of a regular expression and an $\omega$-regular expression signifies that the first must be true before the second $\omega$-regular expression can be true in the following timesteps.
   \item $B = B + B$.
@@
     \]
-    This formula is reasonably complicated, and hard for human to reason about directly. For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex13}.
+    This formula is reasonably complicated, and hard for humans to reason about directly. For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex13}.
     \begin{figure*}[h!]

### 2023-06-26 paper/main.tex
typos/minor changes
more typos and reviewer comments

@@
         \item a finite alphabet of input symbols called the alphabet $\Sigma$
-        \item a partial function $\delta : Q\times \Sigma \to Q$, called the transition function
+        \item a relation $\delta \subseteq (Q\times \Sigma) \times Q$, called the transition relation
         \item an initial or start state called $s\in Q$
@@
 \begin{definition}[Regular expression]\label{def:regex}
-    For word $a \in \Sigma$, regular expression is defined by the following grammar:
+    For symbol $a \in \Sigma$, regular expression is defined by the following grammar:
     \begin{align*}
@@
 \begin{definition}[Semantics of regular expression]
-    Let $L(A)$ denote the language accepted by regular expression $A$. Then $L(A)$ is inductively defined as
+    Let $L(A)$ denote the set of propositional formulas accepted by regular expression $A$. Then $L(A)$ is inductively defined as
     \begin{align*}
@@
 \begin{definition}[Semantics of $\omega$-regular expression]\label{def:omega-semantics}
-    Let $\Sigma^{\omega}$ denote the set of infinite-length string over fixed alphabet $\Sigma$.
+    Let $\Sigma^{\omega}$ denote the set of infinite-length strings over fixed alphabet $\Sigma$.
 Let $L_{\omega}(B)$ denote the $\omega$-language accepted by $\omega$-regular expression $B$.
@@
 \begin{remark}
-  \Cref{def:regex,def:omega-regex} are the standard definitions of regular expressions and $\omega$-regular expressions, respectively. We include them here for completeness.
+  \Cref{def:regex,def:omega-regex} are the standard definitions of regular expressions and $\omega$-regular expressions, respectively.
+We include them here for completeness.
+For the remainder of the paper, we denote arbitrary regular expressions using $A$ and $\omega$-regular expressions by $B$.
 \end{remark}
@@
 \subsection{BA to $\omega$-regex} \label{aut2regex}
-We translate \Buchi automata to $\omega$-regular expressions by first finding the regular expressions for paths from the start state to some final state (say $r_\mathrm{sf}$), and for those for paths for looping from the final state back to itself (say $r_\mathrm{ff}$), and finally combining those to form the $\omega$-expression for valid runs ($\bigplus_{f\in F} r_\mathrm{sf}r_\mathrm{ff}^\omega$).
-The regular expressions for finite paths are in turn found by iteratively deleting interior nodes in digraph of the automaton.
+We translate \Buchi automata to $\omega$-regular expressions by first finding the regular expressions for paths from the start state to some final state (say $r_\mathrm{sf}$), and for those for paths looping from the final state back to itself (say $r_\mathrm{ff}$), and finally combining those to form the $\omega$-expression for valid runs ($\bigplus_{f\in F} r_\mathrm{sf}r_\mathrm{ff}^\omega$).
+The regular expressions for finite paths are in turn found by iteratively deleting interior nodes in the digraph of the automaton.
 
@@
         \Ensure The $\omega$-regular expression recognized by $G$
-        \State \Return $\bigcup_{f \in F}\left(\text{nfa2regex\_firstvisit}(G, s, f)\text{\^{}nfa2regex}(G, f, f) \right) $
+        \State \Return $\bigcup_{f \in F}\left(\text{nfa2regex\_firstvisit}(G, s, f)\text{nfa2regex}(G, f, f) \right) $
     \end{algorithmic}
@@
 \section{Theoretical Analyses} \label{sec:analysis}
+In the following section, we prove the correctness of our translation pipeline.
+The currectness of the translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}.
+Below, we prove the correctness of (i) the translation from \Buchi automata to $\omega$-regular expressions, (ii) the ($\omega$-)regular expression rewrite rules we apply, and lastly, we outline the correctness of our timeline visualizations.
 \subsection{Correctness of Regex Translation}

### 2023-06-26 paper/main.tex
typos

@@
   However, LTL formulas can be unintuitive and error-prone for human practitioners to specify and validate.
-Meanwhile, drawing timelines remains one of the most popular methods for specifying and validating requriements for industrial system designs, such as in aerospace operational concepts.
+Meanwhile, drawing timelines remains one of the most popular methods for specifying and validating requirements for industrial system designs, such as in aerospace operational concepts.
   Therefore, we provide a new timeline tool for visualizing LTL specifications as timelines, providing provably-correct, intuitive equivalents between these two specification formats.
@@
 In the following section, we prove the correctness of our translation pipeline.
-The currectness of the translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}.
+The correctness of the translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}.
 Below, we prove the correctness of (i) the translation from \Buchi automata to $\omega$-regular expressions, (ii) the ($\omega$-)regular expression rewrite rules we apply, and lastly, we outline the correctness of our timeline visualizations.
@@
 Visualized as the timeline of $A$ followed by the timeline of $B$.
-A concatenation of a regular expression and an $\omega$-regular expression signifies that the first must be true before the second $\omega$-regular expression can be true in the following timesteps.
+A concatenation of a regular expression and an $\omega$-regular expression signifies that the first must be true before the second $\omega$-regular expression can be true in the following time steps.
   \item $B = B + B$.

### 2023-06-26 paper/main.tex
minor changes
small changes

@@
 As a first step, requirements are typically written in natural language.
-For example, here is a real-world requirement specification from an air traffic control system ~\cite{ZR14}
+For example, here is a real-world requirement specification from an air traffic control system~\cite{ZR14}
 \begin{center}
@@
 \end{align*}
-Several tools have been developed to reason about formal specifications written with such \ltl\ formulas, like R2U2 and FRET \cite{GPMS20}.
+Several tools have been developed to reason about formal specifications written with such \ltl\ formulas, like R2U2 and FRET~\cite{GPMS20}.
 However, these formalized semantics are unintuitive and error-prone for human practitioners, and the tools are much less useful when system designers can't validate input specifications.
@@
 
-We must begin by setting up the prerequisite definitions involved in our work.
+We begin by setting up the prerequisite definitions involved in our work.
 First, we provide the definition and semantics for \ltl.
@@
     The tool we provide in this paper uses a set of concrete syntax to represent those logical connectives, in order to avoid the difficulty of typesetting connectives such as $\always$ and $\eventually$.
-The concrete syntax is defined in \ref{sec:concrete-syntax}.
+The concrete syntax is defined in~\ref{sec:concrete-syntax}.
 \end{remark}
@@
 \subsection{LTL to BA} \label{ltl2aut}
-The automata-theoretic approach \cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} of studying \ltl\ (i.e.
+The automata-theoretic approach~\cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} of studying \ltl\ (i.e.
 reducing \ltl\ formulas to their corresponding \Buchi automata) has been well-studied.
-Many algorithms and optimizations have been studied such as \cite{DGV99, F03}.
+Many algorithms and optimizations have been studied such as~\cite{DGV99, F03}.
 Our tool \tool uses SPOT~\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.} for this step, which provides an implementation of the translation from \ltl\ formulas to \Buchi automata.
@@
             \State reduce\_nfa($G, v$)
-            \State combine multiedges, i.e. $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
+            \State combine multi-edges, i.e. $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
         \EndWhile
@@
 There is no agreed upon canonical form for regular expression, hence we do not hope to find the simplest regular expression for visualization.
-Regular expression simplification comes down to regular expression equivalence checking, which is computationally hard \cite{MNS04}.
+Regular expression simplification comes down to regular expression equivalence checking, which is computationally hard~\cite{MNS04}.
 For purpose of simplification, one could perform a search over equivalent regular expressions and decide which one is simpler to use.
@@
         \centering
-        \resizebox{.8\textwidth}{!}{
+        \resizebox{.55\textwidth}{!}{
             \begin{tikzpicture}[>=latex',line join=bevel,]
@@
 We gather a test suite of 91 formulas used in real-world requirement specification.
-We take $6$ specifications from NASA's Automated Airspace Concept (AAC)\cite{GCMTR16}.
-We also collect formulas from the Acacia suite of examples \cite{RV10}.
+We take $6$ specifications from NASA's Automated Airspace Concept (AAC)~\cite{GCMTR16}.
+We also collect formulas from the Acacia suite of examples~\cite{RV10}.
 We reap $85$ formulas from the suite of $23$ examples, by generating separate visualizations for each line of specification.
@@
     \subfloat{{\includegraphics[width=6.5cm]{img/star-height-graph.png}}}
-    \caption{Visualization complexity metrics for formulas collected from Acacia \cite{RV10} and NASA's  AAC \cite{GCMTR16}}
+    \caption{Visualization complexity metrics for formulas collected from Acacia~\cite{RV10} and NASA's  AAC~\cite{GCMTR16}}
     \label{fig:real-world}
@@
 We measure the scalability of our tool by running it against a set of scalable \ltl\ formulas.
-We define a scalable \ltl\ formula as one that describes an $n$-bit number using a binary counter \cite{RV10}.
+We define a scalable \ltl\ formula as one that describes an $n$-bit number using a binary counter~\cite{RV10}.
 As $n$ gets larger, the \ltl\ formula used to encode the $n$-bit counter scales in size, but it remains practical.
 The result is shown in \cref{fig:scalability}.
-In this analysis, the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi \cite{RV10}.
+In this analysis, the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}.
 
@@
     \centering
-    \includegraphics[scale=0.6]{img/binary.png}
-    \caption{Scalability measured with binary counter examples from Rozier and Vardi \cite{RV10}}
+    \includegraphics[width=6.5cm]{img/binary.png}
+    \caption{Scalability measured with binary counter examples from Rozier and Vardi~\cite{RV10}}
     \label{fig:scalability}
@@
 We can give an example or two here, such as two pictures of timelines for a 2-bit and a 3-bit counter from two different formulas, one with U's and one with X's; one with carry and one without (such as a 2-bit w/carry X formula and a 3-bit no carry U formula).
-The scalable counter formulas are from \cite{RV10}.
+The scalable counter formulas are from~\cite{RV10}.
 
@@
 \begin{itemize}
-    \item Can there be more simplifications methods as described in Section \ref{regex-simplify}?
+    \item Can there be more simplifications methods as described in Section~\ref{regex-simplify}?
 The answer is definitely positive.
@@
 \item {\bf What are intuitive representations of star-formulas and do they change depending on the formula?} Common regular expression visualizers use two ways to represent stars in regular expressions.
-We can represent a stared formula inside a box \cite{B22} with related caption to indicate the repetition (similar to the design decision we made in \tool); or with back edges \cite{A20}.
+We can represent a stared formula inside a box~\cite{B22} with related caption to indicate the repetition (similar to the design decision we made in \tool); or with back edges~\cite{A20}.
 Does using the box cause confusion with respect to the LTL $\Box$ operator?
@@
 The Achilles heel of formal verification is specification; formal methods are only as effective at verification as their specifications are at describing the essential properties to verify.
-Yet, specification remains the biggest bottleneck to the use of formal methods \cite{Roz16}.
-\ltl\ is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway \cite{DBR21}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system \cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS) \cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept \cite{CDRWRWL22} just to name a few.
+Yet, specification remains the biggest bottleneck to the use of formal methods~\cite{Roz16}.
+\ltl\ is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway~\cite{DBR21}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system~\cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS)~\cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept~\cite{CDRWRWL22} just to name a few.
  %
@@
 \section{Concrete Syntax of \tool} \label{sec:concrete-syntax}
-Recall from \ref{ltl-defn} that we define \ltl\ formula as
+Recall from~\ref{ltl-defn} that we define \ltl\ formula as
 \begin{align*}
@@
          &      & \textit{abstract syntax}              & \textit{concrete syntax}                       & \textit{description} \\
-    \Phi & ::=  & p                                     & \texttt{p}                                     & \text{atomic proposition} \\
+    \Phi & ::=  & p                                     & \texttt{p}                                     & \text{atomic prop.} \\
          & \mid & \neg \Phi                             & \texttt{!} \Phi                                & \text{negation} \\
@@
   \hline
-  Design space for NASA's AAC (Automated Airspace Concept) & 20,250 & \cite{GCMTR16} \\
+  Design space for NASA's AAC (Automated Airspace Concept) & 20,250 &~\cite{GCMTR16} \\
   \hline
-  Safety specifications for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
+  Safety specifications for Boeing's AIR6110 wheel brake system & &~\cite{BCFJKPRT15} \\
   \hline
-  Requirements for model checking NASA's AAC high-level architecture & 6 & \cite{ZR14} \\
+  Requirements for model checking NASA's AAC high-level architecture & 6 &~\cite{ZR14} \\
   \hline
-  Real formulas collected from all publicly-available, pre-2011 case studies & 63 & \cite{RV11} \\
+  Real formulas collected from all publicly-available, pre-2011 case studies & 63 &~\cite{RV11} \\
   \hline

### 2023-08-26 paper/main.tex
slightly enlarge text in image

@@
         \centering
-        \begin{tikzpicture}[scale=0.7, transform shape]
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [below=0.4cm of p1] {\!\!\!$p$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
-        \node (m) at ($(p1)!0.5!(p2)$) {};
-        \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.25cm}] (g) [right= 1.35cm of m] {};
-
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p4) [right= 1.5cm of m] {\!\!\!$\lnot p$\!\!\!};
-        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p5) [right= 1cm of p4] {\!\!\!$p$\!\!\!};
-        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 4cm of m] {\!\!\!start\!\!\!};
-        \draw[thick, line width=1.25] (s) edge[-latex] (p1) (s) edge[-latex] (p3) (p3) edge[-latex] (p2) (p1) edge[-latex] (p4) (p2) edge[-latex] (p4) (p4) edge[-latex] (p5);
-
+        \begin{tikzpicture}[>=latex',line join=bevel,scale=0.6, transform shape]
+          \pgfsetlinewidth{1bp}
+        %%
+        \begin{scope}
+          \pgfsetstrokecolor{black}
+          \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+          \pgfsetstrokecolor{strokecol}
+          \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+          \pgfsetfillcolor{fillcol}
+          \filldraw (262.0bp,19.0bp) -- (262.0bp,71.0bp) -- (422.0bp,71.0bp) -- (422.0bp,19.0bp) -- cycle;
+        \end{scope}
+          \pgfsetcolor{black}
+          % Edge: 3 -> 4
+          \draw [->] (324.4bp,45.0bp) .. controls (332.06bp,45.0bp) and (340.57bp,45.0bp)  .. (359.62bp,45.0bp);
+          % Edge: start -> 0
+          \draw [->] (53.503bp,48.868bp) .. controls (83.95bp,53.487bp) and (135.08bp,61.243bp)  .. (180.26bp,68.095bp);
+          % Edge: start -> 1
+          \draw [->] (52.513bp,38.593bp) .. controls (61.307bp,36.295bp) and (71.403bp,33.656bp)  .. (91.313bp,28.452bp);
+          % Edge: 0 -> 3
+          \draw [->] (232.05bp,64.622bp) .. controls (241.17bp,61.824bp) and (251.73bp,58.582bp)  .. (271.98bp,52.369bp);
+          % Edge: 1 -> 2
+          \draw [->] (144.4bp,20.8bp) .. controls (152.06bp,20.452bp) and (160.57bp,20.065bp)  .. (179.62bp,19.199bp);
+          % Edge: 2 -> 3
+          \draw [->] (232.05bp,25.378bp) .. controls (241.17bp,28.176bp) and (251.73bp,31.418bp)  .. (271.98bp,37.631bp);
+          % Node: 3
+        \begin{scope}
+          \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+          \pgfsetstrokecolor{strokecol}
+          \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+          \pgfsetfillcolor{fillcol}
+          \filldraw [opacity=1] (297.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
+          \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+          \pgfsetstrokecolor{strokecol}
+          \draw (297.0bp,45.0bp) node {$\neg \text{p}$};
+        \end{scope}
+          % Node: 4
+        \begin{scope}
+          \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+          \pgfsetstrokecolor{strokecol}
+          \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+          \pgfsetfillcolor{fillcol}
+          \filldraw [opacity=1] (387.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
+          \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+          \pgfsetstrokecolor{strokecol}
+          \draw (387.0bp,45.0bp) node {$\text{p}$};
+        \end{scope}
+          % Node: start
+        \begin{scope}
+          \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+          \pgfsetstrokecolor{strokecol}
+          \draw (27.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
+          \draw (27.0bp,45.0bp) node {start};
+        \end{scope}
+          % Node: 0
+        \begin{scope}
+          \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+          \pgfsetstrokecolor{strokecol}
+          \draw (207.0bp,72.0bp) ellipse (27.0bp and 18.0bp);
+          \draw (207.0bp,72.0bp) node {$\text{p}$};
+        \end{scope}
+          % Node: 1
+        \begin{scope}
+          \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+          \pgfsetstrokecolor{strokecol}
+          \draw (117.0bp,22.0bp) ellipse (27.0bp and 18.0bp);
+          \draw (117.0bp,22.0bp) node {$\neg \text{p}$};
+        \end{scope}
+          % Node: 2
+        \begin{scope}
+          \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+          \pgfsetstrokecolor{strokecol}
+          \draw (207.0bp,18.0bp) ellipse (27.0bp and 18.0bp);
+          \draw (207.0bp,18.0bp) node {$\text{p}$};
+        \end{scope}
+        %
         \end{tikzpicture}
@@
         \centering
-        \begin{tikzpicture}[>=latex',line join=bevel, scale=0.7, transform shape]
+        \begin{tikzpicture}[>=latex',line join=bevel,scale=0.6, transform shape]
           \pgfsetlinewidth{1bp}
@@
           \pgfsetfillcolor{fillcol}
-            \filldraw (287.84bp,8.0bp) -- (287.84bp,60.0bp) -- (357.84bp,60.0bp) -- (357.84bp,8.0bp) -- cycle;
+          \filldraw (301.97bp,8.0bp) -- (301.97bp,60.0bp) -- (371.97bp,60.0bp) -- (371.97bp,8.0bp) -- cycle;
         \end{scope}
@@
           % Edge: start -> 0
-            \draw [->] (54.252bp,34.0bp) .. controls (61.968bp,34.0bp) and (70.673bp,34.0bp)  .. (90.636bp,34.0bp);
+          \draw [->] (54.416bp,34.0bp) .. controls (62.14bp,34.0bp) and (70.893bp,34.0bp)  .. (90.479bp,34.0bp);
           % Edge: 0 -> 1
-            \draw [->] (169.36bp,34.0bp) .. controls (177.45bp,34.0bp) and (185.97bp,34.0bp)  .. (205.41bp,34.0bp);
+          \draw [->] (183.47bp,34.0bp) .. controls (191.95bp,34.0bp) and (200.71bp,34.0bp)  .. (219.63bp,34.0bp);
           % Edge: 1 -> 2
-            \draw [->] (260.25bp,34.0bp) .. controls (267.73bp,34.0bp) and (276.03bp,34.0bp)  .. (295.46bp,34.0bp);
+          \draw [->] (274.37bp,34.0bp) .. controls (282.03bp,34.0bp) and (290.54bp,34.0bp)  .. (309.58bp,34.0bp);
           % Node: 2
@@
           \pgfsetfillcolor{fillcol}
-            \filldraw [opacity=1] (322.84bp,34.0bp) ellipse (27.0bp and 18.0bp);
-            \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
-            \pgfsetstrokecolor{strokecol}
-            \draw (322.84bp,34.0bp) node {$\top$};
+          \filldraw [opacity=1] (336.97bp,34.0bp) ellipse (27.0bp and 18.0bp);
+          \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+          \pgfsetstrokecolor{strokecol}
+          \draw (336.97bp,34.0bp) node {$\top$};
         \end{scope}
@@
           \pgfsetstrokecolor{strokecol}
-            \draw (133.61bp,16.05bp) -- (136.05bp,16.15bp) -- (138.47bp,16.3bp) -- (140.85bp,16.49bp) -- (143.18bp,16.74bp) -- (145.46bp,17.03bp) -- (147.68bp,17.36bp) -- (149.83bp,17.75bp) -- (151.9bp,18.18bp) -- (153.88bp,18.65bp) -- (155.76bp,19.16bp) -- (157.54bp,19.71bp) -- (159.22bp,20.31bp) -- (160.78bp,20.94bp) -- (162.23bp,21.61bp) -- (163.56bp,22.31bp) -- (164.76bp,23.04bp) -- (165.83bp,23.8bp) -- (166.78bp,24.59bp) -- (167.59bp,25.41bp) -- (168.28bp,26.25bp) -- (168.83bp,27.11bp) -- (169.25bp,27.99bp) -- (169.55bp,28.89bp) -- (169.72bp,29.8bp) -- (169.76bp,30.72bp) -- (169.69bp,31.65bp) -- (169.5bp,32.59bp) -- (169.19bp,33.53bp) -- (168.77bp,34.47bp) -- (168.25bp,35.41bp) -- (167.63bp,36.35bp) -- (166.92bp,37.28bp) -- (166.11bp,38.2bp) -- (165.22bp,39.11bp) -- (164.26bp,40.01bp) -- (163.21bp,40.89bp) -- (162.1bp,41.75bp) -- (160.93bp,42.59bp) -- (159.7bp,43.41bp) -- (158.42bp,44.2bp) -- (157.09bp,44.96bp) -- (155.71bp,45.69bp) -- (154.3bp,46.39bp) -- (152.85bp,47.06bp) -- (151.38bp,47.69bp) -- (149.87bp,48.29bp) -- (148.35bp,48.84bp) -- (146.8bp,49.35bp) -- (145.24bp,49.82bp) -- (143.66bp,50.25bp) -- (142.07bp,50.64bp) -- (140.47bp,50.97bp) -- (138.86bp,51.26bp) -- (137.24bp,51.51bp) -- (135.62bp,51.7bp) -- (133.99bp,51.85bp) -- (132.37bp,51.95bp) -- (130.74bp,52.0bp) -- (129.11bp,52.0bp) -- (127.48bp,51.95bp) -- (125.85bp,51.85bp) -- (124.22bp,51.7bp) -- (122.6bp,51.51bp) -- (120.99bp,51.26bp) -- (119.38bp,50.97bp) -- (117.78bp,50.64bp) -- (116.19bp,50.25bp) -- (114.61bp,49.82bp) -- (113.04bp,49.35bp) -- (111.5bp,48.84bp) -- (109.97bp,48.29bp) -- (108.47bp,47.69bp) -- (106.99bp,47.06bp) -- (105.54bp,46.39bp) -- (104.13bp,45.69bp) -- (102.76bp,44.96bp) -- (101.43bp,44.2bp) -- (100.14bp,43.41bp) -- (98.91bp,42.59bp) -- (97.74bp,41.75bp) -- (96.63bp,40.89bp) -- (95.59bp,40.01bp) -- (94.62bp,39.11bp) -- (93.73bp,38.2bp) -- (92.92bp,37.28bp) -- (92.21bp,36.35bp) -- (91.59bp,35.41bp) -- (91.07bp,34.47bp) -- (90.65bp,33.53bp) -- (90.35bp,32.59bp) -- (90.15bp,31.65bp) -- (90.08bp,30.72bp) -- (90.12bp,29.8bp) -- (90.29bp,28.89bp) -- (90.59bp,27.99bp) -- (91.01bp,27.11bp) -- (91.57bp,26.25bp) -- (92.25bp,25.41bp) -- (93.07bp,24.59bp) -- (94.01bp,23.8bp) -- (95.09bp,23.04bp) -- (96.29bp,22.31bp) -- (97.61bp,21.61bp) -- (99.06bp,20.94bp) -- (100.62bp,20.31bp) -- (102.3bp,19.71bp) -- (104.08bp,19.16bp) -- (105.97bp,18.65bp) -- (107.95bp,18.18bp) -- (110.01bp,17.75bp) -- (112.16bp,17.36bp) -- (114.38bp,17.03bp) -- (116.66bp,16.74bp) -- (119.0bp,16.49bp) -- (121.38bp,16.3bp) -- (123.79bp,16.15bp) -- (126.23bp,16.05bp) -- (128.69bp,16.0bp) -- (131.15bp,16.0bp) -- cycle;
-            \draw (129.92bp,34.0bp) node [align=center] {$\neg \text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
+          \draw (141.33bp,16.05bp) -- (144.21bp,16.15bp) -- (147.06bp,16.3bp) -- (149.87bp,16.49bp) -- (152.62bp,16.74bp) -- (155.31bp,17.03bp) -- (157.93bp,17.36bp) -- (160.46bp,17.75bp) -- (162.9bp,18.18bp) -- (165.23bp,18.65bp) -- (167.46bp,19.16bp) -- (169.56bp,19.71bp) -- (171.54bp,20.31bp) -- (173.38bp,20.94bp) -- (175.08bp,21.61bp) -- (176.65bp,22.31bp) -- (178.06bp,23.04bp) -- (179.33bp,23.8bp) -- (180.45bp,24.59bp) -- (181.41bp,25.41bp) -- (182.21bp,26.25bp) -- (182.87bp,27.11bp) -- (183.37bp,27.99bp) -- (183.72bp,28.89bp) -- (183.92bp,29.8bp) -- (183.97bp,30.72bp) -- (183.88bp,31.65bp) -- (183.65bp,32.59bp) -- (183.29bp,33.53bp) -- (182.8bp,34.47bp) -- (182.19bp,35.41bp) -- (181.46bp,36.35bp) -- (180.61bp,37.28bp) -- (179.66bp,38.2bp) -- (178.61bp,39.11bp) -- (177.47bp,40.01bp) -- (176.24bp,40.89bp) -- (174.93bp,41.75bp) -- (173.55bp,42.59bp) -- (172.1bp,43.41bp) -- (170.59bp,44.2bp) -- (169.02bp,44.96bp) -- (167.4bp,45.69bp) -- (165.73bp,46.39bp) -- (164.03bp,47.06bp) -- (162.28bp,47.69bp) -- (160.51bp,48.29bp) -- (158.71bp,48.84bp) -- (156.89bp,49.35bp) -- (155.04bp,49.82bp) -- (153.18bp,50.25bp) -- (151.31bp,50.64bp) -- (149.42bp,50.97bp) -- (147.52bp,51.26bp) -- (145.62bp,51.51bp) -- (143.7bp,51.7bp) -- (141.79bp,51.85bp) -- (139.87bp,51.95bp) -- (137.95bp,52.0bp) -- (136.02bp,52.0bp) -- (134.1bp,51.95bp) -- (132.18bp,51.85bp) -- (130.27bp,51.7bp) -- (128.35bp,51.51bp) -- (126.45bp,51.26bp) -- (124.55bp,50.97bp) -- (122.66bp,50.64bp) -- (120.79bp,50.25bp) -- (118.93bp,49.82bp) -- (117.08bp,49.35bp) -- (115.26bp,48.84bp) -- (113.46bp,48.29bp) -- (111.68bp,47.69bp) -- (109.94bp,47.06bp) -- (108.24bp,46.39bp) -- (106.57bp,45.69bp) -- (104.95bp,44.96bp) -- (103.38bp,44.2bp) -- (101.87bp,43.41bp) -- (100.42bp,42.59bp) -- (99.03bp,41.75bp) -- (97.73bp,40.89bp) -- (96.5bp,40.01bp) -- (95.35bp,39.11bp) -- (94.31bp,38.2bp) -- (93.36bp,37.28bp) -- (92.51bp,36.35bp) -- (91.78bp,35.41bp) -- (91.17bp,34.47bp) -- (90.68bp,33.53bp) -- (90.32bp,32.59bp) -- (90.09bp,31.65bp) -- (90.0bp,30.72bp) -- (90.05bp,29.8bp) -- (90.25bp,28.89bp) -- (90.6bp,27.99bp) -- (91.1bp,27.11bp) -- (91.76bp,26.25bp) -- (92.56bp,25.41bp) -- (93.52bp,24.59bp) -- (94.64bp,23.8bp) -- (95.91bp,23.04bp) -- (97.32bp,22.31bp) -- (98.88bp,21.61bp) -- (100.59bp,20.94bp) -- (102.43bp,20.31bp) -- (104.41bp,19.71bp) -- (106.51bp,19.16bp) -- (108.74bp,18.65bp) -- (111.07bp,18.18bp) -- (113.51bp,17.75bp) -- (116.04bp,17.36bp) -- (118.66bp,17.03bp) -- (121.35bp,16.74bp) -- (124.1bp,16.49bp) -- (126.91bp,16.3bp) -- (129.76bp,16.15bp) -- (132.64bp,16.05bp) -- (135.53bp,16.0bp) -- (138.44bp,16.0bp) -- cycle;
+          \draw (136.98bp,34.0bp) node [align=center] {$\neg \text{a}$ \\ {\small \emph{repeats $0$ - $\infty$}}};
         \end{scope}
@@
           \pgfsetstrokecolor{strokecol}
-            \draw (232.84bp,34.0bp) ellipse (27.0bp and 18.0bp);
-            \draw (232.84bp,34.0bp) node {$\text{a}$};
+          \draw (246.97bp,34.0bp) ellipse (27.0bp and 18.0bp);
+          \draw (246.97bp,34.0bp) node {$\text{a}$};
         \end{scope}
@@
                         \pgfsetstrokecolor{strokecol}
-                        \draw (506.18bp,34.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
+                        \draw (506.18bp,34.0bp) node [align=center] {$\text{a}$ \\ {\small \emph{repeats $0$ - $\infty$}}};
                       \end{scope}
@@
                         \draw (220.15bp,20.05bp) -- (222.41bp,20.15bp) -- (224.65bp,20.3bp) -- (226.86bp,20.49bp) -- (229.03bp,20.74bp) -- (231.14bp,21.03bp) -- (233.2bp,21.36bp) -- (235.19bp,21.75bp) -- (237.11bp,22.18bp) -- (238.95bp,22.65bp) -- (240.7bp,23.16bp) -- (242.35bp,23.71bp) -- (243.9bp,24.31bp) -- (245.35bp,24.94bp) -- (246.7bp,25.61bp) -- (247.93bp,26.31bp) -- (249.04bp,27.04bp) -- (250.04bp,27.8bp) -- (250.91bp,28.59bp) -- (251.67bp,29.41bp) -- (252.3bp,30.25bp) -- (252.82bp,31.11bp) -- (253.21bp,31.99bp) -- (253.49bp,32.89bp) -- (253.64bp,33.8bp) -- (253.68bp,34.72bp) -- (253.61bp,35.65bp) -- (253.44bp,36.59bp) -- (253.15bp,37.53bp) -- (252.77bp,38.47bp) -- (252.28bp,39.41bp) -- (251.71bp,40.35bp) -- (251.04bp,41.28bp) -- (250.3bp,42.2bp) -- (249.47bp,43.11bp) -- (248.57bp,44.01bp) -- (247.61bp,44.89bp) -- (246.58bp,45.75bp) -- (245.49bp,46.59bp) -- (244.35bp,47.41bp) -- (243.16bp,48.2bp) -- (241.92bp,48.96bp) -- (240.65bp,49.69bp) -- (239.34bp,50.39bp) -- (238.0bp,51.06bp) -- (236.63bp,51.69bp) -- (235.23bp,52.29bp) -- (233.82bp,52.84bp) -- (232.38bp,53.35bp) -- (230.93bp,53.82bp) -- (229.47bp,54.25bp) -- (227.99bp,54.64bp) -- (226.51bp,54.97bp) -- (225.02bp,55.26bp) -- (223.52bp,55.51bp) -- (222.01bp,55.7bp) -- (220.51bp,55.85bp) -- (219.0bp,55.95bp) -- (217.48bp,56.0bp) -- (215.97bp,56.0bp) -- (214.46bp,55.95bp) -- (212.95bp,55.85bp) -- (211.44bp,55.7bp) -- (209.94bp,55.51bp) -- (208.44bp,55.26bp) -- (206.95bp,54.97bp) -- (205.46bp,54.64bp) -- (203.99bp,54.25bp) -- (202.52bp,53.82bp) -- (201.07bp,53.35bp) -- (199.64bp,52.84bp) -- (198.22bp,52.29bp) -- (196.83bp,51.69bp) -- (195.46bp,51.06bp) -- (194.12bp,50.39bp) -- (192.81bp,49.69bp) -- (191.53bp,48.96bp) -- (190.3bp,48.2bp) -- (189.11bp,47.41bp) -- (187.97bp,46.59bp) -- (186.88bp,45.75bp) -- (185.85bp,44.89bp) -- (184.88bp,44.01bp) -- (183.98bp,43.11bp) -- (183.16bp,42.2bp) -- (182.41bp,41.28bp) -- (181.75bp,40.35bp) -- (181.17bp,39.41bp) -- (180.69bp,38.47bp) -- (180.3bp,37.53bp) -- (180.02bp,36.59bp) -- (179.84bp,35.65bp) -- (179.77bp,34.72bp) -- (179.81bp,33.8bp) -- (179.97bp,32.89bp) -- (180.24bp,31.99bp) -- (180.64bp,31.11bp) -- (181.15bp,30.25bp) -- (181.79bp,29.41bp) -- (182.54bp,28.59bp) -- (183.42bp,27.8bp) -- (184.42bp,27.04bp) -- (185.53bp,26.31bp) -- (186.76bp,25.61bp) -- (188.1bp,24.94bp) -- (189.55bp,24.31bp) -- (191.11bp,23.71bp) -- (192.76bp,23.16bp) -- (194.51bp,22.65bp) -- (196.34bp,22.18bp) -- (198.26bp,21.75bp) -- (200.25bp,21.36bp) -- (202.31bp,21.03bp) -- (204.43bp,20.74bp) -- (206.59bp,20.49bp) -- (208.8bp,20.3bp) -- (211.04bp,20.15bp) -- (213.31bp,20.05bp) -- (215.59bp,20.0bp) -- (217.87bp,20.0bp) -- cycle;
-                        \draw (216.73bp,38.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
+                        \draw (216.73bp,38.0bp) node [align=center] {$\text{a}$ \\ {\small \emph{repeats $0$ - $\infty$}}};
                       \end{scope}
@@
                 \pgfsetstrokecolor{strokecol}
-                \draw (216.73bp,34.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};
+                \draw (216.73bp,34.0bp) node [align=center] {$\text{a}$ \\ {\small \emph{repeats $0$ - $\infty$}}};
               \end{scope}
@@
                 \pgfsetstrokecolor{strokecol}
-                \draw (462.49bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\tiny repeats $0$ - $\infty$}};
+                \draw (462.49bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\small \emph{repeats $0$ - $\infty$}}};
               \end{scope}
@@
                 \draw (147.01bp,16.05bp) -- (150.21bp,16.15bp) -- (153.39bp,16.3bp) -- (156.51bp,16.49bp) -- (159.58bp,16.74bp) -- (162.58bp,17.03bp) -- (165.49bp,17.36bp) -- (168.31bp,17.75bp) -- (171.03bp,18.18bp) -- (173.63bp,18.65bp) -- (176.1bp,19.16bp) -- (178.44bp,19.71bp) -- (180.64bp,20.31bp) -- (182.7bp,20.94bp) -- (184.6bp,21.61bp) -- (186.34bp,22.31bp) -- (187.92bp,23.04bp) -- (189.33bp,23.8bp) -- (190.57bp,24.59bp) -- (191.64bp,25.41bp) -- (192.54bp,26.25bp) -- (193.26bp,27.11bp) -- (193.82bp,27.99bp) -- (194.21bp,28.89bp) -- (194.43bp,29.8bp) -- (194.49bp,30.72bp) -- (194.39bp,31.65bp) -- (194.14bp,32.59bp) -- (193.74bp,33.53bp) -- (193.19bp,34.47bp) -- (192.51bp,35.41bp) -- (191.69bp,36.35bp) -- (190.75bp,37.28bp) -- (189.7bp,38.2bp) -- (188.53bp,39.11bp) -- (187.26bp,40.01bp) -- (185.89bp,40.89bp) -- (184.43bp,41.75bp) -- (182.89bp,42.59bp) -- (181.27bp,43.41bp) -- (179.59bp,44.2bp) -- (177.84bp,44.96bp) -- (176.04bp,45.69bp) -- (174.18bp,46.39bp) -- (172.28bp,47.06bp) -- (170.34bp,47.69bp) -- (168.37bp,48.29bp) -- (166.36bp,48.84bp) -- (164.33bp,49.35bp) -- (162.28bp,49.82bp) -- (160.2bp,50.25bp) -- (158.12bp,50.64bp) -- (156.01bp,50.97bp) -- (153.9bp,51.26bp) -- (151.78bp,51.51bp) -- (149.65bp,51.7bp) -- (147.51bp,51.85bp) -- (145.37bp,51.95bp) -- (143.23bp,52.0bp) -- (141.09bp,52.0bp) -- (138.95bp,51.95bp) -- (136.82bp,51.85bp) -- (134.68bp,51.7bp) -- (132.55bp,51.51bp) -- (130.43bp,51.26bp) -- (128.32bp,50.97bp) -- (126.21bp,50.64bp) -- (124.12bp,50.25bp) -- (122.05bp,49.82bp) -- (120.0bp,49.35bp) -- (117.97bp,48.84bp) -- (115.96bp,48.29bp) -- (113.99bp,47.69bp) -- (112.05bp,47.06bp) -- (110.15bp,46.39bp) -- (108.29bp,45.69bp) -- (106.49bp,44.96bp) -- (104.74bp,44.2bp) -- (103.05bp,43.41bp) -- (101.44bp,42.59bp) -- (99.9bp,41.75bp) -- (98.44bp,40.89bp) -- (97.07bp,40.01bp) -- (95.8bp,39.11bp) -- (94.63bp,38.2bp) -- (93.57bp,37.28bp) -- (92.63bp,36.35bp) -- (91.82bp,35.41bp) -- (91.14bp,34.47bp) -- (90.59bp,33.53bp) -- (90.19bp,32.59bp) -- (89.93bp,31.65bp) -- (89.84bp,30.72bp) -- (89.9bp,29.8bp) -- (90.12bp,28.89bp) -- (90.51bp,27.99bp) -- (91.06bp,27.11bp) -- (91.79bp,26.25bp) -- (92.69bp,25.41bp) -- (93.76bp,24.59bp) -- (95.0bp,23.8bp) -- (96.41bp,23.04bp) -- (97.99bp,22.31bp) -- (99.73bp,21.61bp) -- (101.63bp,20.94bp) -- (103.68bp,20.31bp) -- (105.89bp,19.71bp) -- (108.23bp,19.16bp) -- (110.7bp,18.65bp) -- (113.3bp,18.18bp) -- (116.02bp,17.75bp) -- (118.84bp,17.36bp) -- (121.75bp,17.03bp) -- (124.75bp,16.74bp) -- (127.82bp,16.49bp) -- (130.94bp,16.3bp) -- (134.12bp,16.15bp) -- (137.32bp,16.05bp) -- (140.55bp,16.0bp) -- (143.78bp,16.0bp) -- cycle;
-                \draw (142.16bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\tiny repeats $0$ - $\infty$}};
+                \draw (142.16bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\small \emph{repeats $0$ - $\infty$}}};
               \end{scope}
@@
                 \draw (336.3bp,70.05bp) -- (339.61bp,70.15bp) -- (342.89bp,70.3bp) -- (346.12bp,70.49bp) -- (349.29bp,70.74bp) -- (352.39bp,71.03bp) -- (355.4bp,71.36bp) -- (358.32bp,71.75bp) -- (361.12bp,72.18bp) -- (363.81bp,72.65bp) -- (366.37bp,73.16bp) -- (368.79bp,73.71bp) -- (371.07bp,74.31bp) -- (373.19bp,74.94bp) -- (375.15bp,75.61bp) -- (376.95bp,76.31bp) -- (378.58bp,77.04bp) -- (380.04bp,77.8bp) -- (381.32bp,78.59bp) -- (382.43bp,79.41bp) -- (383.36bp,80.25bp) -- (384.11bp,81.11bp) -- (384.69bp,81.99bp) -- (385.09bp,82.89bp) -- (385.32bp,83.8bp) -- (385.38bp,84.72bp) -- (385.28bp,85.65bp) -- (385.02bp,86.59bp) -- (384.6bp,87.53bp) -- (384.04bp,88.47bp) -- (383.33bp,89.41bp) -- (382.49bp,90.35bp) -- (381.52bp,91.28bp) -- (380.42bp,92.2bp) -- (379.22bp,93.11bp) -- (377.9bp,94.01bp) -- (376.49bp,94.89bp) -- (374.98bp,95.75bp) -- (373.39bp,96.59bp) -- (371.72bp,97.41bp) -- (369.98bp,98.2bp) -- (368.17bp,98.96bp) -- (366.3bp,99.69bp) -- (364.39bp,100.39bp) -- (362.42bp,101.06bp) -- (360.42bp,101.69bp) -- (358.38bp,102.29bp) -- (356.3bp,102.84bp) -- (354.21bp,103.35bp) -- (352.08bp,103.82bp) -- (349.94bp,104.25bp) -- (347.78bp,104.64bp) -- (345.61bp,104.97bp) -- (343.42bp,105.26bp) -- (341.23bp,105.51bp) -- (339.03bp,105.7bp) -- (336.82bp,105.85bp) -- (334.61bp,105.95bp) -- (332.4bp,106.0bp) -- (330.19bp,106.0bp) -- (327.97bp,105.95bp) -- (325.76bp,105.85bp) -- (323.56bp,105.7bp) -- (321.36bp,105.51bp) -- (319.16bp,105.26bp) -- (316.98bp,104.97bp) -- (314.81bp,104.64bp) -- (312.65bp,104.25bp) -- (310.5bp,103.82bp) -- (308.38bp,103.35bp) -- (306.28bp,102.84bp) -- (304.21bp,102.29bp) -- (302.17bp,101.69bp) -- (300.16bp,101.06bp) -- (298.2bp,100.39bp) -- (296.28bp,99.69bp) -- (294.42bp,98.96bp) -- (292.61bp,98.2bp) -- (290.87bp,97.41bp) -- (289.2bp,96.59bp) -- (287.61bp,95.75bp) -- (286.1bp,94.89bp) -- (284.68bp,94.01bp) -- (283.37bp,93.11bp) -- (282.16bp,92.2bp) -- (281.07bp,91.28bp) -- (280.1bp,90.35bp) -- (279.26bp,89.41bp) -- (278.55bp,88.47bp) -- (277.99bp,87.53bp) -- (277.57bp,86.59bp) -- (277.31bp,85.65bp) -- (277.21bp,84.72bp) -- (277.27bp,83.8bp) -- (277.5bp,82.89bp) -- (277.9bp,81.99bp) -- (278.48bp,81.11bp) -- (279.23bp,80.25bp) -- (280.16bp,79.41bp) -- (281.26bp,78.59bp) -- (282.55bp,77.8bp) -- (284.0bp,77.04bp) -- (285.63bp,76.31bp) -- (287.43bp,75.61bp) -- (289.4bp,74.94bp) -- (291.52bp,74.31bp) -- (293.8bp,73.71bp) -- (296.22bp,73.16bp) -- (298.77bp,72.65bp) -- (301.46bp,72.18bp) -- (304.27bp,71.75bp) -- (307.18bp,71.36bp) -- (310.19bp,71.03bp) -- (313.29bp,70.74bp) -- (316.46bp,70.49bp) -- (319.69bp,70.3bp) -- (322.97bp,70.15bp) -- (326.29bp,70.05bp) -- (329.62bp,70.0bp) -- (332.96bp,70.0bp) -- cycle;
-                \draw (331.29bp,88.0bp) node [align=center] {$\neg \text{p0} \land \text{p1}$ \\ {\tiny repeats $0$ - $\infty$}};
+                \draw (331.29bp,88.0bp) node [align=center] {$\neg \text{p0} \land \text{p1}$ \\ {\small \emph{repeats $0$ - $\infty$}}};
               \end{scope}
@@
                 \draw (334.77bp,16.05bp) -- (337.07bp,16.15bp) -- (339.35bp,16.3bp) -- (341.6bp,16.49bp) -- (343.8bp,16.74bp) -- (345.95bp,17.03bp) -- (348.05bp,17.36bp) -- (350.07bp,17.75bp) -- (352.02bp,18.18bp) -- (353.89bp,18.65bp) -- (355.67bp,19.16bp) -- (357.35bp,19.71bp) -- (358.93bp,20.31bp) -- (360.41bp,20.94bp) -- (361.77bp,21.61bp) -- (363.02bp,22.31bp) -- (364.15bp,23.04bp) -- (365.17bp,23.8bp) -- (366.06bp,24.59bp) -- (366.83bp,25.41bp) -- (367.47bp,26.25bp) -- (368.0bp,27.11bp) -- (368.4bp,27.99bp) -- (368.68bp,28.89bp) -- (368.84bp,29.8bp) -- (368.88bp,30.72bp) -- (368.81bp,31.65bp) -- (368.63bp,32.59bp) -- (368.34bp,33.53bp) -- (367.94bp,34.47bp) -- (367.45bp,35.41bp) -- (366.87bp,36.35bp) -- (366.19bp,37.28bp) -- (365.43bp,38.2bp) -- (364.6bp,39.11bp) -- (363.68bp,40.01bp) -- (362.7bp,40.89bp) -- (361.65bp,41.75bp) -- (360.55bp,42.59bp) -- (359.38bp,43.41bp) -- (358.17bp,44.2bp) -- (356.92bp,44.96bp) -- (355.62bp,45.69bp) -- (354.29bp,46.39bp) -- (352.93bp,47.06bp) -- (351.53bp,47.69bp) -- (350.11bp,48.29bp) -- (348.67bp,48.84bp) -- (347.21bp,49.35bp) -- (345.74bp,49.82bp) -- (344.25bp,50.25bp) -- (342.75bp,50.64bp) -- (341.24bp,50.97bp) -- (339.72bp,51.26bp) -- (338.2bp,51.51bp) -- (336.67bp,51.7bp) -- (335.13bp,51.85bp) -- (333.6bp,51.95bp) -- (332.06bp,52.0bp) -- (330.52bp,52.0bp) -- (328.99bp,51.95bp) -- (327.45bp,51.85bp) -- (325.92bp,51.7bp) -- (324.39bp,51.51bp) -- (322.86bp,51.26bp) -- (321.35bp,50.97bp) -- (319.84bp,50.64bp) -- (318.34bp,50.25bp) -- (316.85bp,49.82bp) -- (315.37bp,49.35bp) -- (313.91bp,48.84bp) -- (312.47bp,48.29bp) -- (311.05bp,47.69bp) -- (309.66bp,47.06bp) -- (308.3bp,46.39bp) -- (306.96bp,45.69bp) -- (305.67bp,44.96bp) -- (304.41bp,44.2bp) -- (303.2bp,43.41bp) -- (302.04bp,42.59bp) -- (300.93bp,41.75bp) -- (299.89bp,40.89bp) -- (298.9bp,40.01bp) -- (297.99bp,39.11bp) -- (297.15bp,38.2bp) -- (296.39bp,37.28bp) -- (295.72bp,36.35bp) -- (295.13bp,35.41bp) -- (294.64bp,34.47bp) -- (294.25bp,33.53bp) -- (293.96bp,32.59bp) -- (293.78bp,31.65bp) -- (293.71bp,30.72bp) -- (293.75bp,29.8bp) -- (293.91bp,28.89bp) -- (294.19bp,27.99bp) -- (294.59bp,27.11bp) -- (295.11bp,26.25bp) -- (295.76bp,25.41bp) -- (296.53bp,24.59bp) -- (297.42bp,23.8bp) -- (298.43bp,23.04bp) -- (299.56bp,22.31bp) -- (300.81bp,21.61bp) -- (302.18bp,20.94bp) -- (303.65bp,20.31bp) -- (305.24bp,19.71bp) -- (306.92bp,19.16bp) -- (308.7bp,18.65bp) -- (310.56bp,18.18bp) -- (312.51bp,17.75bp) -- (314.54bp,17.36bp) -- (316.63bp,17.03bp) -- (318.78bp,16.74bp) -- (320.99bp,16.49bp) -- (323.23bp,16.3bp) -- (325.51bp,16.15bp) -- (327.82bp,16.05bp) -- (330.13bp,16.0bp) -- (332.45bp,16.0bp) -- cycle;
-                \draw (331.29bp,34.0bp) node [align=center] {$\top$ \\ {\tiny repeats $0$ - $\infty$}};
+                \draw (331.29bp,34.0bp) node [align=center] {$\top$ \\ {\small \emph{repeats $0$ - $\infty$}}};
               \end{scope}
@@
   \centering
-  \begin{tikzpicture}[scale=0.7, transform shape]
-  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
-  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [below=0.4cm of p1] {\!\!\!$p$\!\!\!};
-  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
-  \node (m) at ($(p1)!0.5!(p2)$) {};
-  \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.25cm}] (g) [right= 1.35cm of m] {};
-
-  \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p4) [right= 1.5cm of m] {\!\!\!$\lnot p$\!\!\!};
-  \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p5) [right= 1cm of p4] {\!\!\!$p$\!\!\!};
-  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 4cm of m] {\!\!\!start\!\!\!};
-  \draw[thick, line width=1.25] (s) edge[-latex] (p1) (s) edge[-latex] (p3) (p3) edge[-latex] (p2) (p1) edge[-latex] (p4) (p2) edge[-latex] (p4) (p4) edge[-latex] (p5);
-
+  \begin{tikzpicture}[>=latex',line join=bevel,scale=0.6, transform shape]
+    \pgfsetlinewidth{1bp}
+  %%
+  \begin{scope}
+    \pgfsetstrokecolor{black}
+    \definecolor{strokecol}{rgb}{0.83,0.83,0.83};
+    \pgfsetstrokecolor{strokecol}
+    \definecolor{fillcol}{rgb}{0.83,0.83,0.83};
+    \pgfsetfillcolor{fillcol}
+    \filldraw (262.0bp,19.0bp) -- (262.0bp,71.0bp) -- (422.0bp,71.0bp) -- (422.0bp,19.0bp) -- cycle;
+  \end{scope}
+    \pgfsetcolor{black}
+    % Edge: 3 -> 4
+    \draw [->] (324.4bp,45.0bp) .. controls (332.06bp,45.0bp) and (340.57bp,45.0bp)  .. (359.62bp,45.0bp);
+    % Edge: start -> 0
+    \draw [->] (53.503bp,48.868bp) .. controls (83.95bp,53.487bp) and (135.08bp,61.243bp)  .. (180.26bp,68.095bp);
+    % Edge: start -> 1
+    \draw [->] (52.513bp,38.593bp) .. controls (61.307bp,36.295bp) and (71.403bp,33.656bp)  .. (91.313bp,28.452bp);
+    % Edge: 0 -> 3
+    \draw [->] (232.05bp,64.622bp) .. controls (241.17bp,61.824bp) and (251.73bp,58.582bp)  .. (271.98bp,52.369bp);
+    % Edge: 1 -> 2
+    \draw [->] (144.4bp,20.8bp) .. controls (152.06bp,20.452bp) and (160.57bp,20.065bp)  .. (179.62bp,19.199bp);
+    % Edge: 2 -> 3
+    \draw [->] (232.05bp,25.378bp) .. controls (241.17bp,28.176bp) and (251.73bp,31.418bp)  .. (271.98bp,37.631bp);
+    % Node: 3
+  \begin{scope}
+    \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+    \pgfsetstrokecolor{strokecol}
+    \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+    \pgfsetfillcolor{fillcol}
+    \filldraw [opacity=1] (297.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
+    \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+    \pgfsetstrokecolor{strokecol}
+    \draw (297.0bp,45.0bp) node {$\neg \text{p}$};
+  \end{scope}
+    % Node: 4
+  \begin{scope}
+    \definecolor{strokecol}{rgb}{1.0,1.0,1.0};
+    \pgfsetstrokecolor{strokecol}
+    \definecolor{fillcol}{rgb}{1.0,1.0,1.0};
+    \pgfsetfillcolor{fillcol}
+    \filldraw [opacity=1] (387.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
+    \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+    \pgfsetstrokecolor{strokecol}
+    \draw (387.0bp,45.0bp) node {$\text{p}$};
+  \end{scope}
+    % Node: start
+  \begin{scope}
+    \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+    \pgfsetstrokecolor{strokecol}
+    \draw (27.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
+    \draw (27.0bp,45.0bp) node {start};
+  \end{scope}
+    % Node: 0
+  \begin{scope}
+    \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+    \pgfsetstrokecolor{strokecol}
+    \draw (207.0bp,72.0bp) ellipse (27.0bp and 18.0bp);
+    \draw (207.0bp,72.0bp) node {$\text{p}$};
+  \end{scope}
+    % Node: 1
+  \begin{scope}
+    \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+    \pgfsetstrokecolor{strokecol}
+    \draw (117.0bp,22.0bp) ellipse (27.0bp and 18.0bp);
+    \draw (117.0bp,22.0bp) node {$\neg \text{p}$};
+  \end{scope}
+    % Node: 2
+  \begin{scope}
+    \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+    \pgfsetstrokecolor{strokecol}
+    \draw (207.0bp,18.0bp) ellipse (27.0bp and 18.0bp);
+    \draw (207.0bp,18.0bp) node {$\text{p}$};
+  \end{scope}
+  %
   \end{tikzpicture}

### 2023-08-26 src/vis.py

@@ -79,7 +79,7 @@ def make_graph(regex: OmegaRegex, filename: str, format: str) -> Digraph:
                         if latex:
                             tex = parse(s)
                             s1 = s.replace("&", "&amp;")
-                            g.node(node_name, label=f"<{s1}<BR /> <FONT POINT-SIZE=\"10\">repeats 0-∞</FONT>>", texlbl=f"${tex}$ \\\\ {{\\tiny repeats $0$ - $\infty$}}", shape='egg')
+                            g.node(node_name, label=f"<{s1}<BR /> <FONT POINT-SIZE=\"10\">repeats 0-∞</FONT>>", texlbl=f"${tex}$ \\\\ {{\\small \emph{{repeats $0$ - $\infty$}}}}", shape='egg')
                         else:
                             s1 = s.replace("&", "&amp;")
                             g.node(node_name, label=f"<{s1}<BR /> <FONT POINT-SIZE=\"10\">repeats 0-∞</FONT>>", shape='egg')

### 2023-08-26 paper/main.tex
acknowledgements
suppress page number

@@
 
-\newcommand{\tool}{\hspace{0.1cm}\texttt{ltl2timeline}\hspace{0.1cm}}
+%\newcommand{\tool}{\hspace{0.1cm}\texttt{ltl2timeline}\hspace{0.1cm}}
+\newcommand{\tool}{\hspace{0.1cm}\texttt{ltl2timeline}}
 
@@
 
-\title{What's in a Name? Linear Temporal Logic Literally Represents Time Lines}
+\title{What's in a Name? \\ Linear Temporal Logic \\ Literally Represents Time Lines}
 
@@
 \IEEEauthorblockA{\textit{Carnegie Mellon University}\\
-Pittsburgh, USA \\
+Pittsburgh, PA, USA \\
 runmingl@andrew.cmu.edu}
@@
 \IEEEauthorblockA{\textit{Carnegie Mellon University}\\
-Pittsburgh, USA \\
+Pittsburgh, PA, USA \\
 kgurusha@andrew.cmu.edu}
@@
 \IEEEauthorblockA{\textit{Carnegie Mellon University}\\
-Pittsburgh, USA \\
+Pittsburgh, PA, USA \\
 marijn@cmu.edu}
@@
 \IEEEauthorblockA{\textit{Iowa State University} \\
-Ames, USA \\
-ekyrozier@iastate.edu}
+Ames, IA, USA \\
+kyrozier@iastate.edu}
 }
@@
 \pagestyle{plain}
+\pagenumbering{gobble}
 
@@
     \begin{align*}
-        \Phi ::= & p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \\ & \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
+        \varphi ::= & p \mid \neg \varphi \mid \varphi \land \varphi \mid \varphi \lor \varphi \mid \varphi \limplies \varphi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \varphi \mid \varphi \weakrelease \varphi
     \end{align*}\label{ltl-defn}
@@
 \begin{remark}
-    Intuitively, $\always \Phi$ says that formula $\Phi$ is true at every time step; $\eventually \Phi$ says that formula $\Phi$ is true either now or at sometime in the future time step; and $\nextt \Phi$ says formula $\Phi$ is true at the next time step immediately after the current one; $\Phi \stronguntil \Psi$ says that formula $\Phi$ is true \textit{until} such time formula $\Psi$ becomes true; $\Phi \weakrelease \Psi$ says that formula $\Psi$ must be true now and remain true until formula $\Phi$ becomes true, after which point \textit{release} $\Psi$ (if formula $\Phi$ is never true, then formula $\Psi$ must remain true at all time).
+    Intuitively, $\always \varphi$ says that formula $\varphi$ is true at every time step; $\eventually \varphi$ says that formula $\varphi$ is true either now or at sometime in the future time step; and $\nextt \varphi$ says formula $\varphi$ is true at the next time step immediately after the current one; $\varphi \stronguntil \Psi$ says that formula $\varphi$ is true \textit{until} such time formula $\Psi$ becomes true; $\varphi \weakrelease \Psi$ says that formula $\Psi$ must be true now and remain true until formula $\varphi$ becomes true, after which point \textit{release} $\Psi$ (if formula $\varphi$ is never true, then formula $\Psi$ must remain true at all time).
 \end{remark}
@@
 \begin{definition}[Semantics of \ltl\ formula]
-    The semantics of \ltl\ formula is defined via  $\pi, i \models \Phi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step.
+    The semantics of \ltl\ formula is defined via  $\pi, i \models \varphi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step.
 The semantics follows exactly from Rozier~\cite{Roz11}.
@@
 \begin{example}
-    Using our algorithm, the \ltl\ formula $\Phi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
+    Using our algorithm, the \ltl\ formula $\varphi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
     \begin{figure*}[h!]
@@
     Both simplified and un-simplified $\omega$-regular expressions would generate correct timeline representations.
-Correct as they faithfully represent the set of satisfying traces of the original \ltl\ formula $\Phi$.
+Correct as they faithfully represent the set of satisfying traces of the original \ltl\ formula $\varphi$.
 Nonetheless, we, as human users, oftentimes find the simplified version more intuitive to reason about.
@@
     \centering
-    \subfloat{{\includegraphics[width=6.5cm]{img/tllens-graph.png} }}%
+    \subfloat{{\includegraphics[width=0.49\textwidth]{img/tllens-graph.png} }}%
     \quad % [\centering label 1]
-    \subfloat{{\includegraphics[width=6.5cm]{img/star-height-graph.png}}}
+    \subfloat{{\includegraphics[width=0.49\textwidth]{img/star-height-graph.png}}}
     \caption{Visualization complexity metrics for formulas collected from Acacia~\cite{RV10} and NASA's  AAC~\cite{GCMTR16}}
@@
     \centering
-    \includegraphics[width=6.5cm]{img/binary.png}
+    \includegraphics[width=0.49\textwidth]{img/binary.png}
     \caption{Scalability measured with binary counter examples from Rozier and Vardi~\cite{RV10}}
@@
 
+\section*{Acknowledgements}
+
+This work was partially supported by the National Science Foundation (NSF) under grants CCF-2015445, CAREER-1664356, and CCRI-2016592.
+
 \appendix
 \section{Concrete Syntax of \tool} \label{sec:concrete-syntax}
-Recall from~\ref{ltl-defn} that we define \ltl\ formula as
+Recall from~\ref{ltl-defn} that we define an \ltl\ formula as
 \begin{align*}
-    \Phi ::= & p \mid \neg \Phi \mid \Phi \land \Phi \mid \Phi \lor \Phi \mid \Phi \limplies \Phi \mid \always \Phi \mid \eventually \Phi \mid \nextt \Phi \\ & \mid \Phi \stronguntil \Phi \mid \Phi \weakrelease \Phi
+    \varphi ::= & p \mid \neg \varphi \mid \varphi \land \varphi \mid \varphi \lor \varphi \mid \varphi \limplies \varphi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \varphi \mid \varphi \weakrelease \varphi
 \end{align*}
@@
          &      & \textit{abstract syntax}              & \textit{concrete syntax}                       & \textit{description} \\
-    \Phi & ::=  & p                                     & \texttt{p}                                     & \text{atomic prop.} \\
-         & \mid & \neg \Phi                             & \texttt{!} \Phi                                & \text{negation} \\
-         & \mid & \Phi \land \Phi                       & \Phi \texttt{ \& } \Phi                        & \text{conjunction} \\
-         & \mid & \Phi \lor \Phi                        & \Phi \texttt{ | } \Phi                         & \text{disjunction} \\
-         & \mid & \Phi \limplies \Phi                   & \Phi \texttt{ -> } \Phi                        & \text{implication} \\
-         & \mid & \always \Phi                          & \texttt{G} \Phi                                & \text{globally} \\
-         & \mid & \eventually \Phi                      & \texttt{F} \Phi                                & \text{finally} \\
-         & \mid & \nextt \Phi                           & \texttt{X} \Phi                                & \text{next} \\
-         & \mid & \Phi \stronguntil \Phi                & \Phi \texttt{ U } \Phi                         & \text{until} \\
-         & \mid & \Phi \weakrelease \Phi                & \Phi \texttt{ R } \Phi                         & \text{release} \\
+    \varphi & ::=  & p                                     & \texttt{p}                                     & \text{atomic prop.} \\
+         & \mid & \neg \varphi                             & \texttt{!} \varphi                                & \text{negation} \\
+         & \mid & \varphi \land \varphi                       & \varphi \texttt{ \& } \varphi                        & \text{conjunction} \\
+         & \mid & \varphi \lor \varphi                        & \varphi \texttt{ | } \varphi                         & \text{disjunction} \\
+         & \mid & \varphi \limplies \varphi                   & \varphi \texttt{ -> } \varphi                        & \text{implication} \\
+         & \mid & \always \varphi                          & \texttt{G} \varphi                                & \text{globally} \\
+         & \mid & \eventually \varphi                      & \texttt{F} \varphi                                & \text{finally} \\
+         & \mid & \nextt \varphi                           & \texttt{X} \varphi                                & \text{next} \\
+         & \mid & \varphi \stronguntil \varphi                & \varphi \texttt{ U } \varphi                         & \text{until} \\
+         & \mid & \varphi \weakrelease \varphi                & \varphi \texttt{ R } \varphi                         & \text{release} \\
     \end{array}

### 2023-08-26 paper/main.tex
added funding

--- 2023-08-26 paper/main.tex
@@
 Ames, USA \\
-ekyrozier@iastate.edu}
+kyrozier@iastate.edu}
 }
@@
 
+\section*{Acknowledgements}
+
+This work was partially supported by the National Science Foundation (NSF) under grants CCF-2015445, CAREER-1664356, and CCRI-2016592.
+
 \appendix

### 2023-08-27 paper/main.tex
polishes throughout
footnote
revised introduction + added missing related work

--- 2023-08-26 paper/main.tex
@@
 
-\author{\IEEEauthorblockN{Runming Li\IEEEauthorrefmark{1}}
+\author{\IEEEauthorblockN{Runming Li\textsuperscript{\textsection}}
 \IEEEauthorblockA{\textit{Carnegie Mellon University}\\
@@
 \and
-\IEEEauthorblockN{Keerthana Gurushankar\IEEEauthorrefmark{1}}
+\IEEEauthorblockN{Keerthana Gurushankar\textsuperscript{\textsection}}
 \IEEEauthorblockA{\textit{Carnegie Mellon University}\\
@@
 \and
-\IEEEauthorblockN{Kristin~Y.~Rozier}
+\IEEEauthorblockN{Kristin~Yvonne~Rozier}
 \IEEEauthorblockA{\textit{Iowa State University} \\
@@
 \section{Introduction}
-Requirement specification is a central step in the development of safety-critical systems.
-As a first step, requirements are typically written in natural language.
+Requirement specification is a central step in the development of safety-critical systems. %As a first step, requirements are typically written in natural language.
 For example, here is a real-world requirement specification from an air traffic control system~\cite{ZR14}
@@
 \end{center}
-Such natural language requirements are often ambiguous and not amenable to formal analysis, so requirements must often be specified using rigorous formalized semantics for the purpose of verification and validation.
+Such natural language requirements are often ambiguous and not amenable to formal analysis, so we must instead specify such requirements using rigorous formalized semantics for the purpose of verification and validation.
 The above requirement, when translated to Linear Temporal Logic (detailed in \cref{sec:ltl}), may be expressed as follows:
@@
 \end{align*}
-Several tools have been developed to reason about formal specifications written with such \ltl\ formulas, like R2U2 and FRET~\cite{GPMS20}.
-However, these formalized semantics are unintuitive and error-prone for human practitioners, and the tools are much less useful when system designers can't validate input specifications.
+Though, as \cite{ZR14} demonstrates, validating that the resulting formula represents the intended requirement is difficult, even for professionals; in this case study a subtle misconception in the initial formalization of a requirement hid an important safety concern present in the early design-stage requirements.
+Using the play-on-words "Little Tricky Logic," \cite{GSNK22} points to endemic misconceptions in the understanding of LTL.
+
+The need for validation of requirements formalizations has been widely recognized, and tools for several different formalisms have contributed strategies for breaking up the formalisms into patterns and adding GUIs to make validation easier.
+For example, the web-based modeling tool piStar-ext adds a GUI with text, symbols, and diagrams to enable users to better validate iStar-language models \cite{GRMPAC20}.
+Hanfor, a GUI, web-based tool supported formalization of system requirements into an LTL-like structured natural language patterns for several industry projects in the automotive and railway domains \cite{BDHHLPW21}.
+The ForeMoSt framework enables validation of safety assurance cases by translating structured arguments into formal strategies and validating them automatically using the Lean theorem prover \cite{VMDMSC22}.
+AutoTap provides users with a GUI utilizing structured English to write and edit LTL formulas representing Trigger-Action Programs (another form of assume-guarantee contracts) for smart devices and cloud services \cite{ZHMBLU19}.
+
+There has been a recent boom in validation capabilities for the related, but arguably simpler, specification logic Mission-time LTL \cite{LVR19}, which adds finite, integer-bounded, closed intervals to the temporal operators of LTL.
+The runtime verification engine R2U2 includes a web-based GUI enabling specifiers to visualize properties of (sets of) MLTL runtime monitors, such as their shared subformulas and resource usage on embedded systems \cite{JJKRZ23}.
+The FRET tool's GUI color-codes segments of structured natural language to elicit more accurate MLTL formulas from system designers \cite{GPMS20}.
+The WEST tool provides an interactive GUI for MLTL formula validation via regular expressions and truth-table-like visualizations \cite{EGSTWR23}.
+Now we need tools like these for LTL.
+
+The common and intuitive technique of validating LTL formulas via sets of positive and negative examples (i.e., demonstrating traces that both satisfy and violate a given LTL formula) is insufficient for understanding and explainability of LTL specification \cite{NR22}.
 Thus, a significant hurdle remains: how can we convincingly demonstrate to the humans in the loop, from system designers to certifiers, that the analyzed formulas truly represent the desired system requirements?

### 2023-08-27 paper/main.tex
fixed bib file

@@
 Yet, specification remains the biggest bottleneck to the use of formal methods~\cite{Roz16}.
-\ltl\ is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway~\cite{DBR21}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system~\cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS)~\cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept~\cite{CDRWRWL22} just to name a few.
+\ltl\ is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway~\cite{DBR21,DBR23}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system~\cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS)~\cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept~\cite{CDRWRWL22} just to name a few.
  %

### 2023-08-27 paper/main.tex
typo fixes

@@
     Regular expression concerns only finite-length strings.
-However, since \ltl\ formulas reason about events that happen over an infinite-length timeline, we need to model it using infinite regular expressions (i.e.
-$\omega$-regular expression).
+However, since \ltl\ formulas reason about events that happen over an infinite-length timeline, we need to model it using infinite regular expressions (i.e., $\omega$-regular expression).
 $\omega$-regular expression is defined by the following grammar:
@@
 \subsection{LTL to BA} \label{ltl2aut}
-The automata-theoretic approach~\cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} of studying \ltl\ (i.e.
-reducing \ltl\ formulas to their corresponding \Buchi automata) has been well-studied.
+The automata-theoretic approach~\cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} of studying \ltl\ (i.e., reducing \ltl\ formulas to their corresponding \Buchi automata) has been well-studied.
 Many algorithms and optimizations have been studied such as~\cite{DGV99, F03}.
@@
             \State reduce\_nfa($G, v$)
-            \State combine multi-edges, i.e. $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
+            \State combine multi-edges, i.e., $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
         \EndWhile
@@
 \section{Discussion}
-Based on our results, we propose the following questions for discussions and future works:
+Based on our results, we propose the following questions for discussions and future work:
 \begin{itemize}
@@
 On one hand, more rule-based simplifications can be discovered by finding more patterns in the generated $\omega$-regular expressions.
-On the other hand, other simplification are possible: for example, if the generated $\omega$-regular expression is $r_1 + r_2$ where $r_1, r_2$ are not syntactically equivalent (or equivalent up to algebraic rules) $\omega$-regular expressions, but they accepts the same set of infinite-length strings, then we can simplify this down to just $r_1$.
-This reduce the problem to equivalence test on $\omega$-regular expressions, which is decidable.
-In the similar vein, many more simplifications can be used, but the question is how efficient are they?
-In the end, one have to balance trade-off between the efficiency of the tool and the simplicity of the result.
+On the other hand, other simplification are possible: for example, if the generated $\omega$-regular expression is $r_1 + r_2$ where $r_1, r_2$ are not syntactically equivalent (or equivalent up to algebraic rules) $\omega$-regular expressions, but they accept the same set of infinite-length strings, then we can simplify this down to just $r_1$.
+This reduces the problem to equivalence test on $\omega$-regular expressions, which is decidable.
+In a similar vein, many more simplifications may apply, but the question is how \empu{useful} are they?
+In the end, we have to balance the efficiency, simplicity, and understandabillity of the visualization.
     %\item Our tool is effective at translating a wide range of LTL formulas. Even with LTL formulae with complex nesting structure are represented by relatively readable timeline visualizations.
-    \item Can we define timeline more formally so that one can do this process reversely (i.e.
-a tool that converts timeline representation to its corresponding \ltl\ formula)?
+    \item Can we define timeline more formally so that one can do this process reversely (i.e., a tool that converts timeline representation to its corresponding \ltl\ formula)?
 That would be a very useful tool in practice.

### 2023-08-27 paper/main.tex
more typo fixes

@@
 This reduces the problem to equivalence test on $\omega$-regular expressions, which is decidable.
-In a similar vein, many more simplifications may apply, but the question is how \empu{useful} are they?
+In a similar vein, many more simplifications may apply, but the question is how \emph{useful} are they?
 In the end, we have to balance the efficiency, simplicity, and understandabillity of the visualization.
     %\item Our tool is effective at translating a wide range of LTL formulas. Even with LTL formulae with complex nesting structure are represented by relatively readable timeline visualizations.
-    \item Can we define timeline more formally so that one can do this process reversely (i.e., a tool that converts timeline representation to its corresponding \ltl\ formula)?
-That would be a very useful tool in practice.
+    \item Can we define timelines more formally so that one can do this process reversely (i.e., a tool that converts timeline representation to its corresponding \ltl\ formula)?
+That would be very useful in practice.
 However, a direct reverse of the algorithm we presented in this paper may not be viable.
@@
 We can then use the expanded notation for stared formulas larger than a single proposition, thus navigating a trade-off between small representation and limiting the visual complication.
-The criticism of this approach may be that back edges cause confusion between timeline and automata representations, and that with back edges timelines stop being intuitive about linearity of time.
+The criticism of this approach may be that back edges cause confusion between timeline and automata representations, and that with back edges timelines stop being intuitive with respect to the linearity of time.
 
@@
 By our algorithm, we generate parallel lines only when the formulas are not syntactically equivalent, so we would be guaranteed to run the more complex check for logical equivalence.
-In some cases, this could provide a clarifying simplification, with the cost of a repetitive computationally expensive check.
+In some cases, this could provide a clarifying simplification, with the cost of a repetitive computationally-expensive check.
 Would it make sense to offer an ``optimizing'' compilation option to users that takes longer to create a timeline representation but checks for smaller representations via logical equivalence?

### 2023-08-27 paper/main.tex
saw another typo...
typo and section title fixes/polishes

@@
 %\newcommand{\tool}{\hspace{0.1cm}\texttt{ltl2timeline}\hspace{0.1cm}}
-\newcommand{\tool}{\hspace{0.1cm}\texttt{ltl2timeline}}
+\newcommand{\tool}{\texttt{ltl2timeline}}
 
@@
 
-\section{Introduction}
+%\section{Introduction}
+\section{Prologue} %going full Shakespeare on this...
 Requirement specification is a central step in the development of safety-critical systems. %As a first step, requirements are typically written in natural language.
@@
 
-There has been a recent boom in validation capabilities for the related, but arguably simpler, specification logic Mission-time LTL \cite{LVR19}, which adds finite, integer-bounded, closed intervals to the temporal operators of LTL.
+There has been a recent boom in validation capabilities for the related, but arguably simpler, specification logic Mission-time LTL (MLTL) \cite{LVR19}, which adds finite, integer-bounded, closed intervals to the temporal operators of LTL.
 The runtime verification engine R2U2 includes a web-based GUI enabling specifiers to visualize properties of (sets of) MLTL runtime monitors, such as their shared subformulas and resource usage on embedded systems \cite{JJKRZ23}.
@@
 We take a simple idiomatic approach to address this problem.
-As Linear Temporal Logic formulas are temporal information, we devise a tool, \tool, which can draw timelines to depict the satisfying traces of the \ltl\ formula, and thereby represent the specified behavior in a more natural human-intelligible form.
-
-Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automata and regular expression-based intermediate representations, and is surprisingly effective at providing small representations for a range of \ltl\ formulas.
-It would visualize the above air traffic control requirement behavior with the timeline shown in \cref{example:air}.
+Since Linear Temporal Logic formulas differentiate temporal information, we devise a tool, \tool, which can draw timelines to depict the satisfying traces of the \ltl\ formula, and thereby represent the specified behavior in a more natural, human-intelligible form.
+
+Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automata and regular expression-based intermediate representations.
+Yet, it is surprisingly effective at providing small representations for a range of \ltl\ formulas.
+It visualizes the above air traffic control requirement behavior with the timeline shown in \cref{example:air}.
 
@@
     \item We prove correctness in \cref{sec:analysis}. We show that for every \ltl\ formula, the timeline outputted indeed represents the set of satisfying traces.
-    \item We showcase the results of our tool on a range of example formulas in \cref{sec:tool-showcase} and \cref{sec:playing}, including discussing the air traffic example above.
+    \item We showcase the results of our tool on a range of example formulas in \cref{sec:tool-showcase} and \cref{sec:playing}, including discussing the air traffic control example above.
 \end{itemize}
@@
 
-\subsection{Linear temporal logic (\ltl)} \label{sec:ltl}
+\subsection{Linear Temporal Logic (\ltl)} \label{sec:ltl}
 
@@
 
-\section{Algorithm}
+\section{Algorithm: ``Though she be but little, she is fierce$^*$''}
+\begingroup\renewcommand\thefootnote{\textsection}
+\footnotetext{William Shakespeare, \emph{A Midsummer Night's Dream}}
+\endgroup
 On a high level, our algorithm of converting \ltl\ formulas into timeline visualizations (depicted in \Cref{fig:algo}) works as follows:
@@
 
-\section{Theoretical Analyses} \label{sec:analysis}
-In the following section, we prove the correctness of our translation pipeline.
+%\section{Theoretical Analyses} \label{sec:analysis}
+\section{``If we are true to ourselves, we can not be false to anyone$^*$''}
+\label{sec:analysis}
+\begingroup\renewcommand\thefootnote{\textsection}
+\footnotetext{William Shakespeare, \emph{Hamlet}}
+\endgroup
+
+We prove the correctness of our translation pipeline.
 The correctness of the translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}.
@@
 
-\section{Tool showcase} \label{sec:tool-showcase}
+%\section{Tool showcase}
+\section{``Be great in act, as you have been in thought$^*$''}
+\label{sec:tool-showcase}
+\begingroup\renewcommand\thefootnote{\textsection}
+\footnotetext{William Shakespeare, \emph{King John}}
+\endgroup
 To demonstrate the result of our tool, we present three examples, one from a real-world model checking example from Zhao and Rozier~\cite{ZR14}, one from a randomly generated \ltl\ formula, and one specifically demonstrates the use of our tool in specification verification.
@@
 
-\section{Artifact availability}
+\section{Thought is free$^*$: Artifact availability}
+\begingroup\renewcommand\thefootnote{\textsection}
+\footnotetext{William Shakespeare, \emph{The Tempest}}
+\endgroup
 The tool we present in this paper is available at
@@
 
-\section{Discussion}
+\section{Denouement}
 Based on our results, we propose the following questions for discussions and future work:
@@
 In the end, we have to balance the efficiency, simplicity, and understandabillity of the visualization.
-    %\item Our tool is effective at translating a wide range of LTL formulas. Even with LTL formulae with complex nesting structure are represented by relatively readable timeline visualizations.
+    %\item Our tool is effective at translating a wide range of LTL formulas. Even with LTL formulas with complex nesting structure are represented by relatively readable timeline visualizations.
     \item Can we define timelines more formally so that one can do this process reversely (i.e., a tool that converts timeline representation to its corresponding \ltl\ formula)?
@@
 
-\section{Conclusion}
+\section{Epilogue}
 The Achilles heel of formal verification is specification; formal methods are only as effective at verification as their specifications are at describing the essential properties to verify.
@@
 \end{align*}
-where $p \in \AP$. In our tool \tool, we use the following concrete syntax to represent \ltl\ formulae.
+where $p \in \AP$. In our tool \tool, we use the following concrete syntax to represent \ltl\ formulas.
 \[

### 2023-08-27 paper/main.tex
fine-toothed typo corrections: pages 1--2. Moving on to page 3 now...

@@
 \usepackage[capitalise, noabbrev]{cleveref}
+\usepackage{mathrsfs} %for mathscr
 
@@
 \newcommand{\tllen}{\text{tllen}}
+
+\renewcommand{\phi}{\varphi}
+
+\renewcommand{\L}{\mathscr{L}}
 
@@
     \item We prove correctness in \cref{sec:analysis}. We show that for every \ltl\ formula, the timeline outputted indeed represents the set of satisfying traces.
-    \item We showcase the results of our tool on a range of example formulas in \cref{sec:tool-showcase} and \cref{sec:playing}, including discussing the air traffic control example above.
+    \item We showcase the results of our tool on a range of example formulas from real-life industrial verification efforts in \cref{sec:tool-showcase} and \cref{sec:playing}, including discussing the air traffic control example above.
 \end{itemize}
@@
 First, we provide the definition and semantics for \ltl.
-In the following subsections, we define (state-based) \Buchi automata and $\omega$-regular expressions, which are generalizations of the well-known deterministic finite automata (DFAs) and regular expressions, for the case of infinite words.
+In the following subsections, we define (state-based) \Buchi automata and $\omega$-regular expressions, which are generalizations of the well-known deterministic finite automata (DFA) and regular expressions, for the case of infinite words.
 Lastly, we describe the graphic visualizations we will use to depict timelines.
@@
     % cite Kristin's survey paper
-    The syntax of an \ltl\ formula over a set of atomic propositions $\AP$, where $p\in\AP$ is a propositional variable, is given by the following grammar:
+    The syntax of an \ltl\ formula over a set of atomic propositions $\AP$, where $p\in\AP$ is a propositional variable, consists of the following grammar:
     \begin{align*}
-        \varphi ::= & p \mid \neg \varphi \mid \varphi \land \varphi \mid \varphi \lor \varphi \mid \varphi \limplies \varphi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \varphi \mid \varphi \weakrelease \varphi
+        \varphi ::= & p \mid \neg \varphi \mid \varphi \land \psi \mid \varphi \lor \psi \mid \varphi \limplies \psi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \psi \mid \varphi \weakrelease \psi
     \end{align*}\label{ltl-defn}
@@
 \begin{remark}
-    Intuitively, $\always \varphi$ says that formula $\varphi$ is true at every time step; $\eventually \varphi$ says that formula $\varphi$ is true either now or at sometime in the future time step; and $\nextt \varphi$ says formula $\varphi$ is true at the next time step immediately after the current one; $\varphi \stronguntil \Psi$ says that formula $\varphi$ is true \textit{until} such time formula $\Psi$ becomes true; $\varphi \weakrelease \Psi$ says that formula $\Psi$ must be true now and remain true until formula $\varphi$ becomes true, after which point \textit{release} $\Psi$ (if formula $\varphi$ is never true, then formula $\Psi$ must remain true at all time).
+    Intuitively, $\always \varphi$ says that formula $\varphi$ is true at every time step; $\eventually \varphi$ says that formula $\varphi$ is true either now or at some time in the future; $\nextt \varphi$ says formula $\varphi$ is true at the next time step immediately after the current one; $\varphi \stronguntil \psi$ says that formula $\varphi$ is true \textit{until} (strictly before) such time formula $\psi$ becomes true (and $\psi$ is either true now or in the future); and $\varphi \weakrelease \psi$ says that formula $\psi$ must be true now and remain true unless formula $\varphi$ becomes true, after which point we can \textit{release} $\psi$ (if formula $\phi$ is never true, then formula $\psi$ must remain true at all times).
 \end{remark}
@@
 \begin{remark}
-    The tool we provide in this paper uses a set of concrete syntax to represent those logical connectives, in order to avoid the difficulty of typesetting connectives such as $\always$ and $\eventually$.
-The concrete syntax is defined in~\ref{sec:concrete-syntax}.
+    The \tool tool uses a concrete input syntax of ASCII symbols to represent those logical connectives, in order to simplify typesetting connectives such as $\always$ and $\eventually$.
+For reference, the concrete syntax appears in Appendix ~\ref{sec:concrete-syntax}.
 \end{remark}
 
-\begin{definition}[Semantics of \ltl\ formula]
-    The semantics of \ltl\ formula is defined via  $\pi, i \models \varphi$ where $\pi : \omega \rightarrow 2^{\AP}$ is the computation that stores the truthhood and falsehood of every atomic proposition at every time step, and $\omega$ is the set of natural numbers that denote the time step.
-The semantics follows exactly from Rozier~\cite{Roz11}.
+\begin{definition}[Semantics of \ltl\ ]
+    Let $\pi : \omega \rightarrow 2^{\AP}$ be a \emph{computation} or trace that stores the truthhood and falsehood of every atomic proposition at every time step, where $\omega$ is the set of natural numbers that label the time step.
+    Then we say $\pi, i \models \varphi$, that is, computation $\pi$ starting from time $i \in \omega$ models LTL formula $\phi$ whenever the result of this evaluation satisfies $\phi$; see Rozier~\cite{Roz11} for the full LTL semantics.
 \end{definition}
@@
 \begin{definition}[$\omega$-word]
-    An $\omega$-word or infinite run of $\Sigma$, is an infinite string $s = (s_0, s_1, s_2, \dots)$ where each $s_i\in \Sigma$
+    Let $\Sigma$ be an alphabet. An $\omega$-word or infinite run of $\Sigma$, is an infinite string $s = (s_0, s_1, s_2, \dots)$ where each $s_i\in \Sigma$.
 \end{definition}
 \begin{definition}[\Buchi automaton]
-    A \Buchi automaton is a $5$-tuple, $G = (Q, \Sigma, \delta, s, F)$ consisting of
+    A \Buchi automaton is a $5$-tuple, $B = (Q, \Sigma, \delta, s, F)$ consisting of
     \begin{enumerate}
         \item a finite set of states $Q$
-        \item a finite alphabet of input symbols called the alphabet $\Sigma$
-        \item a relation $\delta \subseteq (Q\times \Sigma) \times Q$, called the transition relation
+        \item a finite alphabet of input symbols $\Sigma$
+        \item a transition relation $\delta \subseteq (Q\times \Sigma) \times Q$
         \item an initial or start state called $s\in Q$
@@
     \end{enumerate}
-    $G$ accepts an infinite run iff at least one of its infinitely visited states is in $F$
+    $B$ accepts an infinite run iff at least one of its infinitely visited states is in $F$.
 \end{definition}
 
-\subsection{$\omega$-regular expression}
+\subsection{$\omega$-regular expressions}
 \begin{definition}[Regular expression]\label{def:regex}
-    For symbol $a \in \Sigma$, regular expression is defined by the following grammar:
+    Let $a$ be a symbol in $\Sigma$, $A$ be a regular expression, and $\epsilon$ be the empty expression. We define regular expressions using the following grammar:
     \begin{align*}
@@
 \end{definition}
-\begin{definition}[Semantics of regular expression]
-    Let $L(A)$ denote the set of propositional formulas accepted by regular expression $A$. Then $L(A)$ is inductively defined as
+\begin{definition}[Semantics of regular expressions]
+    Let $\L(A)$ denote the set of propositional formulas accepted by regular expression $A$, also called the language accepted by $A$. We define $\L(A)$, inductively as:
     \begin{align*}
-        L(\emptyset) & = \emptyset \\
-        L(\epsilon) & = \{\epsilon\} \tag{$\epsilon$ denotes the empty string}\\
-        L(a) & = \{a\} \\
-        L(A_1A_2) & = \{s_1s_2 \mid s_1 \in L(A_1) \text{ and } s_2 \in L(A_2)\} \\
-        L(A_1 + A_2) & = L(A_1) \cup L(A_2) \\
-        L^{(0)}(A) & = \{\epsilon\} \\
-        L^{(i + 1)}(A) & = \{s_1s_2 \mid s_1 \in L(A) \text{ and } s_2 \in L^{(i)}(A)\} \\\
-        L(A^*) & = \bigcup_{i \ge 0} L^{(i)}(A)
+        \L(\emptyset) & = \emptyset \\
+        \L(\epsilon) & = \{\epsilon\} \tag{$\epsilon$ denotes the empty string}\\
+        \L(a) & = \{a\} \\
+        \L(A_1A_2) & = \{s_1s_2 \mid s_1 \in L(A_1) \text{ and } s_2 \in L(A_2)\} \\
+        \L(A_1 + A_2) & = L(A_1) \cup L(A_2) \\
+        \L^{(0)}(A) & = \{\epsilon\} \\
+        \L^{(i + 1)}(A) & = \{s_1s_2 \mid s_1 \in L(A) \text{ and } s_2 \in L^{(i)}(A)\} \\\
+        \L(A^*) & = \bigcup_{i \ge 0} L^{(i)}(A)
     \end{align*}
@@
 \begin{remark}
-    For the purpose of our tool, $\Sigma$ is the set of propositional logic formulas defined as
+    For the purpose of our tool, we define $\Sigma$ as the set of propositional logic formulas:
     \[
-    \Psi ::= p \mid \top \mid \bot \mid \neg \Psi \mid \Psi \land \Psi \mid \Psi \lor \Psi \mid \Psi \limplies \Psi
+    a \in \Sigma ::= p \mid \top \mid \bot \mid \neg \phi \mid \phi \land \psi \mid \phi \lor \psi \mid \phi \limplies \psi
     \]
@@
     \item Every timeline starts with a node named ``start''.
-    \item Every node represents one time step, and each node has a propositional logic formula $\Psi$, which specifies the behavior of atomic propositions at that time step.
-The formula $\Psi$ must be true at that time step.
-If $\Psi = 1$, that means all atomic propositions can behave arbitrarily.
+    \item Every node represents one time step, and each node has a propositional logic formula $\psi$, which specifies the behavior of atomic propositions at that time step.
+The formula $\psi$ must be true at that time step.
+If $\psi = 1$, that means all atomic propositions can behave arbitrarily.
     \item A node in egg shape with a caption ``repeats $0$ - $\infty$'' means to repeat the (one time step) current node for arbitrarily finitely many times.
@@
 \begin{align*}
-    \varphi ::= & p \mid \neg \varphi \mid \varphi \land \varphi \mid \varphi \lor \varphi \mid \varphi \limplies \varphi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \varphi \mid \varphi \weakrelease \varphi
+    \varphi ::= & p \mid \neg \varphi \mid \varphi \land \psi \mid \varphi \lor \psi \mid \varphi \limplies \psi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \psi \mid \varphi \weakrelease \psi
 \end{align*}
-where $p \in \AP$. In our tool \tool, we use the following concrete syntax to represent \ltl\ formulas.
+where $p \in \AP$ and $\varphi$ and $\psi$ are LTL formulas. In our tool \tool, we use the following concrete input syntax to represent \ltl\ formulas in ASCII text.
 \[
@@
          & \mid & \neg \varphi                             & \texttt{!} \varphi                                & \text{negation} \\
-         & \mid & \varphi \land \varphi                       & \varphi \texttt{ \& } \varphi                        & \text{conjunction} \\
-         & \mid & \varphi \lor \varphi                        & \varphi \texttt{ | } \varphi                         & \text{disjunction} \\
-         & \mid & \varphi \limplies \varphi                   & \varphi \texttt{ -> } \varphi                        & \text{implication} \\
+         & \mid & \varphi \land \psi                       & \varphi \texttt{ \& } \psi                        & \text{conjunction} \\
+         & \mid & \varphi \lor \psi                        & \varphi \texttt{ | } \psi                         & \text{disjunction} \\
+         & \mid & \varphi \limplies \psi                   & \varphi \texttt{ -> } \psi                        & \text{implication} \\
          & \mid & \always \varphi                          & \texttt{G} \varphi                                & \text{globally} \\
-         & \mid & \eventually \varphi                      & \texttt{F} \varphi                                & \text{finally} \\
+         & \mid & \eventually \varphi                      & \texttt{F} \varphi                                & \text{in the future} \\
          & \mid & \nextt \varphi                           & \texttt{X} \varphi                                & \text{next} \\
-         & \mid & \varphi \stronguntil \varphi                & \varphi \texttt{ U } \varphi                         & \text{until} \\
-         & \mid & \varphi \weakrelease \varphi                & \varphi \texttt{ R } \varphi                         & \text{release} \\
+         & \mid & \varphi \stronguntil \psi                & \varphi \texttt{ U } \psi                         & \text{until} \\
+         & \mid & \varphi \weakrelease \psi                & \varphi \texttt{ R } \psi                         & \text{release} \\
     \end{array}

### 2023-08-27 paper/main.tex
more typo fixes...

@@
     \begin{align*}
-        \varphi ::= & p \mid \neg \varphi \mid \varphi \land \psi \mid \varphi \lor \psi \mid \varphi \limplies \psi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \psi \mid \varphi \weakrelease \psi
+        \varphi = & p \mid \neg \varphi \mid \varphi \land \psi \mid \varphi \lor \psi \mid \varphi \limplies \psi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \psi \mid \varphi \weakrelease \psi
     \end{align*}\label{ltl-defn}
@@
 \end{definition}
-\begin{definition}[\Buchi automaton]
-    A \Buchi automaton is a $5$-tuple, $B = (Q, \Sigma, \delta, s, F)$ consisting of
+\begin{definition}[\Buchi automaton (BA)]
+    A \Buchi automaton is a $5$-tuple, $(Q, \Sigma, \delta, s, F)$ consisting of
     \begin{enumerate}
@@
     \end{enumerate}
-    $B$ accepts an infinite run iff at least one of its infinitely visited states is in $F$.
+    A BA accepts an infinite run iff at least one of its infinitely visited states is in $F$.
 \end{definition}
@@
     \begin{align*}
-        A ::= \emptyset \mid \epsilon \mid a \mid AA \mid A + A \mid A^*
+        A = \emptyset \mid \epsilon \mid a \mid AA \mid A + A \mid A^*
     \end{align*}
@@
     \[
-    a \in \Sigma ::= p \mid \top \mid \bot \mid \neg \phi \mid \phi \land \psi \mid \phi \lor \psi \mid \phi \limplies \psi
+    a \in \Sigma = p \mid \top \mid \bot \mid \neg \phi \mid \phi \land \psi \mid \phi \lor \psi \mid \phi \limplies \psi
     \]
@@
 
-\begin{definition}[$\omega$-regular expression]\label{def:omega-regex}
-    Regular expression concerns only finite-length strings.
-However, since \ltl\ formulas reason about events that happen over an infinite-length timeline, we need to model it using infinite regular expressions (i.e., $\omega$-regular expression).
-$\omega$-regular expression is defined by the following grammar:
+\begin{definition}[$\omega$-regular expressions]\label{def:omega-regex}
+    Our definition \ref{def:regex} of regular expressions concerns only finite-length strings.
+However, since \ltl\ formulas reason about events that happen over an infinite-length timeline, we need to model them using infinite regular expressions (i.e., $\omega$-regular expressions), which we define via the following grammar:
     \begin{align*}
-        B ::= A^{\omega} \mid AB \mid B + B
+        B = A^{\omega} \mid AB \mid B + B
     \end{align*}
 \end{definition}
-\begin{definition}[Semantics of $\omega$-regular expression]\label{def:omega-semantics}
+\begin{definition}[Semantics of $\omega$-regular expressions]\label{def:omega-semantics}
     Let $\Sigma^{\omega}$ denote the set of infinite-length strings over fixed alphabet $\Sigma$.
-Let $L_{\omega}(B)$ denote the $\omega$-language accepted by $\omega$-regular expression $B$.
-Then $L_{\omega}(B)$ is inductively defined as
+Let $\L_{\omega}(B)$ denote the $\omega$-language accepted by $\omega$-regular expression $B$.
+Then $\L_{\omega}(B)$ is inductively defined as
     \begin{align*}
-        L_{\omega}(A^{\omega}) & = \{s_1s_2s_3\cdots \mid s_i \in L(A) \text{ and } i \ge 1\} \tag{$\epsilon
-         \not\in L(A)$} \\
-        L_{\omega}(AB) & = \{s_1s_2 \mid s_1 \in L(A) \text{ and } s_2 \in L_{\omega}(B)\} \\
-        L_{\omega}(B_1 + B_2) &= L_{\omega}(B_1) \cup L_{\omega}(B_2)
+        \L_{\omega}(A^{\omega}) & = \{s_1s_2s_3\cdots \mid s_i \in \L(A) \text{ and } i \ge 1\} \tag{$\epsilon
+         \not\in \L(A)$} \\
+        \L_{\omega}(AB) & = \{s_1s_2 \mid s_1 \in \L(A) \text{ and } s_2 \in \L_{\omega}(B)\} \\
+        \L_{\omega}(B_1 + B_2) &= \L_{\omega}(B_1) \cup \L_{\omega}(B_2)
     \end{align*}
@@
 \]
-where $A_i$ are regular expressions, $A_{2i-1}$ could be $\epsilon$, and $\epsilon \not\in L(A_{2i})$.
+where $A_i$ are regular expressions, $A_{2i-1}$ could be $\epsilon$, and $\epsilon \not\in \L(A_{2i})$.
 At a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input.
@@
 \begin{proof}
-    Let $G'$ be $G$ with all out-edge (including loops) from $f$ deleted. We claim that $L(G')$ is equal to the language $L'$ of all paths from $s$ reaching $f$ for the first time.
-
-    First we show $L(G') \subseteq L'$, i.e., every path accepted by $G'$ starts in $s$ and ends by reaching $f$ for the first time.
+    Let $G'$ be $G$ with all out-edge (including loops) from $f$ deleted. We claim that $\L(G')$ is equal to the language $\L'$ of all paths from $s$ reaching $f$ for the first time.
+
+    First we show $\L(G') \subseteq \L'$, i.e., every path accepted by $G'$ starts in $s$ and ends by reaching $f$ for the first time.
 Since $s$ and $f$ are the initial and final states of $G'$ respectively, clearly every path accepted by $G$ must start in $s$ and end in $f$.
@@
 
-    Also, we show $L' \subseteq L(G')$, i.e., every path starting in $s$ and ending by $f$ reaching $f$ for the first time is accepted by $G'$.
-If a path contains an out-edge of $f$, it cannot be in $L'$ as the trace continues beyond the first time step at $f$.
-Thus, every trace in $L'$ only uses edges in $G'$, and is thus accepted by $G$ iff it is accepted by $G'$.
+    Also, we show $\L' \subseteq \L(G')$, i.e., every path starting in $s$ and ending by $f$ reaching $f$ for the first time is accepted by $G'$.
+If a path contains an out-edge of $f$, it cannot be in $\L'$ as the trace continues beyond the first time step at $f$.
+Thus, every trace in $\L'$ only uses edges in $G'$, and is thus accepted by $G$ iff it is accepted by $G'$.
 \end{proof}
@@
     \[
-        L = \bigcup_{f\in F} \textbf{nfa2regex}(G, s, f) \verb|^| \left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega
+        \L = \bigcup_{f\in F} \textbf{nfa2regex}(G, s, f) \verb|^| \left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega
     \]
-    and the $\omega$-language accepted by $G$, $L_\omega(G)$ are identical.
-
-    First, $L\subseteq L_\omega(G)$ since for every infinite run in $L$, clearly by definition of $L$, there is some $f\in F$ such that passes through $f$ infinitely often.
+    and the $\omega$-language accepted by $G$, $\L_\omega(G)$ are identical.
+
+    First, $\L\subseteq \L_\omega(G)$ since for every infinite run in $\L$, clearly by definition of $\L$, there is some $f\in F$ such that passes through $f$ infinitely often.
 The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often, thus the run is in $\textbf{nfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega$
@@
 \begin{align*}
-    \varphi ::= & p \mid \neg \varphi \mid \varphi \land \psi \mid \varphi \lor \psi \mid \varphi \limplies \psi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \psi \mid \varphi \weakrelease \psi
+    \varphi = & p \mid \neg \varphi \mid \varphi \land \psi \mid \varphi \lor \psi \mid \varphi \limplies \psi \mid \always \varphi \mid \eventually \varphi \mid \nextt \varphi \\ & \mid \varphi \stronguntil \psi \mid \varphi \weakrelease \psi
 \end{align*}
@@
          &      & \textit{abstract syntax}              & \textit{concrete syntax}                       & \textit{description} \\
-    \varphi & ::=  & p                                     & \texttt{p}                                     & \text{atomic prop.} \\
+    \varphi & =  & p                                     & \texttt{p}                                     & \text{atomic prop.} \\
          & \mid & \neg \varphi                             & \texttt{!} \varphi                                & \text{negation} \\

### 2023-08-28 paper/main.tex
fixes through beginning of page 4

@@
 Let $\L_{\omega}(B)$ denote the $\omega$-language accepted by $\omega$-regular expression $B$.
-Then $\L_{\omega}(B)$ is inductively defined as
+Then we define $\L_{\omega}(B)$ inductively as:
     \begin{align*}
@@
 
-\subsection{Timeline}\label{sec:timeline}
-We present timelines as graphic visualizations. It contains the following features:
+\subsection{Timelines}\label{sec:timeline}
+We present timelines as graphic visualizations containing the following features:
 \begin{itemize}
-    \item Every timeline starts with a node named ``start''.
+    \item Every timeline starts with a node named ``start.''
     \item Every node represents one time step, and each node has a propositional logic formula $\psi$, which specifies the behavior of atomic propositions at that time step.
@@
 If $\psi = 1$, that means all atomic propositions can behave arbitrarily.
-    \item A node in egg shape with a caption ``repeats $0$ - $\infty$'' means to repeat the (one time step) current node for arbitrarily finitely many times.
+    \item An egg-shaped node with a caption ``repeats $0$ - $\infty$'' means to repeat the (one time step) current node for arbitrarily finitely many times.
     \item A node with label ``$\cdots$'' means to repeat the pattern prior to it and after it arbitrarily finitely many times.
     \item The grey box means repeat infinitely. Once we reach the end of a timeline in the grey box, we must reenter the same grey box from any of its (left) starting points.
-    \item Timelines can be in parallel, signifying that either of the parallel timeline could happen.
+    \item Timelines can occur in parallel, signifying that any of the parallel timelines could happen.
 \end{itemize}
 
-The definition of timeline we use here are specifically what we devised for the purpose of visualizing \ltl\ formulas.
+The manifestation of timelines we use here is one of possibly many timeline representations that we devised for the purpose of visualizing \ltl\ formulas.
 We show how to construct such timelines from \ltl\ formulas in \cref{sec:correctness-timeline}.
@@
 \begin{example}
-    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $\lnot p$ and one step of $p$.
+    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ holding in the first time step, followed by entering the grey box with one step of $\lnot p$ and one step of $p$.
 Then at the end of the grey box, we reenter the box, with the next time step being $\lnot p$, and so on.
-The lower timeline starts with one step of $\lnot p$ and one step of $p$ outside the grey box, and then enter the infinite run of $\lnot p$ and $p$ repeating.
+The lower timeline starts with one step of $\lnot p$ and one step of $p$ outside the grey box, and then enters the infinite run of $\lnot p$ and $p$ repeating.
     \begin{figure}[!h]
@@
    %     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
-        \caption{Example timeline for specification ``$p$ oscillates every time step''}
+        \caption{Example of one possible timeline for the specification ``$p$ oscillates every time step''}
         \label{fig:ex2}
@@
 \begin{example}
-    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by the second node (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $\top$ (true) in the grey box.
+    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by the second node (note that this could be zero time steps); followed by one node with $a$ that substantiates the specification of ``$a$ is eventually true.'' Once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $\top$ (true) in the grey box.
     \begin{figure}[!h]
@@
     %    \includegraphics[scale=0.4]{examples/ex15/ex15.png}
-        \caption{Example timeline for specification ``$a$ is eventually true''}
+        \caption{Example of a timeline for the specification ``$a$ is eventually true''}
         \label{fig:ex15}
@@
 
-\section{Algorithm: ``Though she be but little, she is fierce$^*$''}
+\section{Algorithm: ``Though she be but little, she is fierce\textsuperscript{\textsection}''}
 \begingroup\renewcommand\thefootnote{\textsection}
@@
 \endgroup
-On a high level, our algorithm of converting \ltl\ formulas into timeline visualizations (depicted in \Cref{fig:algo}) works as follows:
+On a high level, our algorithm for converting \ltl\ formulas into timeline visualizations (depicted in \Cref{fig:algo}) works as follows.
 \begin{enumerate}
@@
     \item Derive the $\omega$-regular expression corresponding to the \Buchi automaton. % (in \cref{aut2regex})
-    \item Simplify the derived $\omega$-regular expression. % (in \cref{regex-simplify})
-    \item Visualize the $\omega$-regular expression according to its structure. %(in \cref{regex2timeline})
+    \item Simplify the derived $\omega$-regular expression. (Note that this step represents a stylistic choice balancing size, complexity, and clarity.) % (in \cref{regex-simplify})
+    \item Visualize the $\omega$-regular expression as a timeline according to its structure. %(in \cref{regex2timeline})
 \end{enumerate}
@@
     \includegraphics[width=\textwidth, scale=0.3]{img/algorithm_outline.pdf}
-    \caption{Algorithm outline}
+    \caption{\tool \ algorithm outline}
     \label{fig:algo}
@@
 \subsection{LTL to BA} \label{ltl2aut}
-The automata-theoretic approach~\cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} of studying \ltl\ (i.e., reducing \ltl\ formulas to their corresponding \Buchi automata) has been well-studied.
-Many algorithms and optimizations have been studied such as~\cite{DGV99, F03}.
-Our tool \tool uses SPOT~\cite{Dur22}\footnote{For our tool, we use SPOT version 2.11.} for this step, which provides an implementation of the translation from \ltl\ formulas to \Buchi automata.
+The automata-theoretic approach~\cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} to evaluating \ltl\ (e.g., via reducing \ltl\ formulas to their corresponding \Buchi automata) has been well-studied \cite{DGV99,F03,RV10,RV11,Dur14}.
+Our tool \tool\ uses SPOT~\cite{Dur22}\footnote{We used SPOT version 2.11.} for this step, which provides a provably-correct implementation of the translation from \ltl\ formulas to minimally-sized \Buchi automata.
 
 \subsection{BA to $\omega$-regex} \label{aut2regex}
-We translate \Buchi automata to $\omega$-regular expressions by first finding the regular expressions for paths from the start state to some final state (say $r_\mathrm{sf}$), and for those for paths looping from the final state back to itself (say $r_\mathrm{ff}$), and finally combining those to form the $\omega$-expression for valid runs ($\bigplus_{f\in F} r_\mathrm{sf}r_\mathrm{ff}^\omega$).
-The regular expressions for finite paths are in turn found by iteratively deleting interior nodes in the digraph of the automaton.
-
+We translate \Buchi automata to $\omega$-regular expressions by first finding the regular expressions for paths from the start state to some final state (say $r_\mathrm{sf}$), and for those for paths looping from the final state back to itself (say $r_\mathrm{ff}$), and finally combining those to form the $\omega$-expression for satisfying runs $\left(\bigplus_{f\in F} r_\mathrm{sf}r_\mathrm{ff}^\omega\right)$.
+Our visualization algorithm finds regular expressions for finite paths by iteratively deleting interior nodes in the digraph of the automaton.
+
+%KYR: FIX THIS!
 The algorithm is outlined below (see Algorithms 1 - 4). %\cref{alg:ba2wregex}
@@
 %\section{Theoretical Analyses} \label{sec:analysis}
-\section{``If we are true to ourselves, we can not be false to anyone$^*$''}
+\section{``If we are true to ourselves, we can not be false to anyone\textsuperscript{\textsection}''}
 \label{sec:analysis}
@@
 %\section{Tool showcase}
-\section{``Be great in act, as you have been in thought$^*$''}
+\section{``Be great in act, as you have been in thought\textsuperscript{\textsection}''}
 \label{sec:tool-showcase}
@@
 
-\section{Thought is free$^*$: Artifact availability}
+\section{Thought is free\textsuperscript{\textsection}: Artifact availability}
 \begingroup\renewcommand\thefootnote{\textsection}

### 2023-08-28 paper/main.tex
edits through end of sectin 3

@@
    %     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
-        \caption{Example of one possible timeline for the specification ``$p$ oscillates every time step''}
+        \caption{Example of one possible timeline for the specification ``$p$ oscillates every time step.''}
         \label{fig:ex2}
@@
     %    \includegraphics[scale=0.4]{examples/ex15/ex15.png}
-        \caption{Example of a timeline for the specification ``$a$ is eventually true''}
+        \caption{Example of a timeline for the specification ``$a$ is eventually true.''}
         \label{fig:ex15}
@@
     \begin{algorithmic}
-        \Require ($G, v$), an NFA with state $v$ that is not initial or final
-        \Ensure Deletes state $v$ from $G$ while ensuring the same language is recognized
+        \Require ($G, v$): NFA $G$ with state $v$ that is not initial or final
+        \Ensure Deletes state $v$ from $G$ while ensuring $\L(G)$ remains unchanged
         \For{ every $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ }
@@
     \begin{algorithmic}
-        \Require ($G, s, f$), an NFA with initial state $s$ and final state $f$
+        \Require ($G, s, f$): NFA $G$ with initial state $s$ and final state $f$
         \Ensure The regular expression corresponding to all paths from $s$ to $f$
@@
             \State reduce\_nfa($G, v$)
-            \State combine multi-edges, i.e., $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
+            \State combine multi-edges, i.e., convert $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
         \EndWhile
@@
     \begin{algorithmic}
-        \Require ($G, s, f$), an NFA with initial state $s$ and final state $f$
+        \Require ($G, s, f$):  NFA $G$ with initial state $s$ and final state $f$
         \Ensure The regular expression of all paths from $s$ reaching $f$ for the first time
@@
 We have observed multiple patterns in the resulting $\omega$-regular expression that could be simplified.
-For example, an $\omega$-regular expression in the form of $r^*r^{\omega}$ represents the same timeline as $r^{\omega}$, but the latter is more intuitive and concise.
-For this purpose, we devised some simplification rules in our tool, based on our observation of common patterns in the generated $\omega$-regular expression.
-
-There is no agreed upon canonical form for regular expression, hence we do not hope to find the simplest regular expression for visualization.
+For example, an $\omega$-regular expression of the form of $r^*r^{\omega}$ represents the same timeline as $r^{\omega}$, but the latter is more intuitive and concise.
+For this purpose, we devised some simplification rules in our tool, based on our observation of common patterns in the generated $\omega$-regular expressions.
+
+There is no agreed-upon canonical form for regular expressions representing \ltl\ formulas, hence we do not hope to find the shortest possible regular expression for visualization.
 Regular expression simplification comes down to regular expression equivalence checking, which is computationally hard~\cite{MNS04}.
@@
 However, this strategy is expensive in terms of the running time, and for the purpose of visualization, we did not use this strategy in our tool.
-We consider this approach as future work.
+We consider simplification for the purpose of finding the most intuitive regular expression for a given \ltl\ formula to be an interesting direction for future work.
 
@@
 \paragraph*{Result of simplification}
-These simplification rules lead to more intuitive representation of timelines. Here we demonstrate their effects using an example.
+These simplification rules lead to more intuitive representations of timelines. Here we demonstrate their effects using an example.
 
 \begin{example}
-    Using our algorithm, the \ltl\ formula $\varphi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.
+    Using our algorithm, the \ltl\ formula $\varphi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}, respectively.
     \begin{figure*}[h!]
@@
         \caption{Timeline visualization for %un-simplified
-        $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
+        $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$.}
         \label{fig:unsimplified}
@@
   %      \includegraphics[scale=0.3]{examples/ex9/ex9.png}
-        \caption{Timeline visualization for simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))^{\omega}$}
+        \caption{Timeline visualization for simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))^{\omega}$.}
         \label{fig:simplified}
@@
 \begin{remark}
-    Both simplified and un-simplified $\omega$-regular expressions would generate correct timeline representations.
-Correct as they faithfully represent the set of satisfying traces of the original \ltl\ formula $\varphi$.
+    Both simplified and un-simplified $\omega$-regular expressions could generate correct timeline representations that faithfully represent the set of satisfying traces of the original \ltl\ formula $\varphi$.
 Nonetheless, we, as human users, oftentimes find the simplified version more intuitive to reason about.
@@
 where $A_i$ are regular expressions, $A_{2i-1}$ could be $\epsilon$, and $\epsilon \not\in \L(A_{2i})$.
-At a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input.
-We view each union operator as parallel timelines, and each $A_{2i-1}$ is concatenated with $A_{2i}$ repeated infinitely many times, as represented in the grey box.
-\cref{fig:timeline} presents a generic timeline resulting from this form of construction.
+At a high level, we visualize each regular expression $A_i$ as a set of accepted inputs.
+We view each union operator as a set of parallel timelines.
+We denote that each $A_{2i-1}$ gets concatenated with $A_{2i}$, which then repeats infinitely many times by surrounding these repeating final nodes with grey boxes.
+\cref{fig:timeline} presents a generic timeline resulting from this construction pattern.
 \begin{figure}[h!]
@@
 %    \includegraphics[scale=0.5]{img/timeline.png}
-    \caption{Generic timeline construction from $A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}$}
+    \caption{Generic timeline construction created from $A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}$.}
     \label{fig:timeline}
@@
  %       \includegraphics[scale=0.75]{img/uvw_dfa.pdf}
-        \caption{A path from $u$ to $w$ in $G$}
+        \caption{A path from $u$ to $w$ in $G$.}
         \label{fig:uvw-dfa}
@@
      %   \includegraphics[scale=0.3]{examples/ex14/ex14.png}
-        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
+        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$.}
         \label{fig:ex14}
@@
    %     \includegraphics[scale=0.3]{examples/ex13/ex13.png}
-        \caption{Timeline for $p_2 \land (\eventually \always p_0 \stronguntil \nextt(\always p_1 \land (((p_0 \limplies p_2) \land (p_2 \limplies p_0)) \stronguntil \eventually p_0)))$}
+        \caption{Timeline for $p_2 \land (\eventually \always p_0 \stronguntil \nextt(\always p_1 \land (((p_0 \limplies p_2) \land (p_2 \limplies p_0)) \stronguntil \eventually p_0)))$.}
         \label{fig:ex13}
@@
 %     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
-  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$}
+  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$.}
   \label{fig:oscillates1}
@@
   \end{tikzpicture}
-  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$ (a single ``start'' means every time step is $\bot$)}
+  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$ (a single ``start'' means every time step is $\bot$).}
   \label{fig:oscillates2}
@@
     \subfloat{{\includegraphics[width=0.49\textwidth]{img/star-height-graph.png}}}
-    \caption{Visualization complexity metrics for formulas collected from Acacia~\cite{RV10} and NASA's  AAC~\cite{GCMTR16}}
+    \caption{Visualization complexity metrics for formulas collected from Acacia~\cite{RV10} and NASA's  AAC~\cite{GCMTR16}.}
     \label{fig:real-world}
@@
     \includegraphics[width=0.49\textwidth]{img/binary.png}
-    \caption{Scalability measured with binary counter examples from Rozier and Vardi~\cite{RV10}}
+    \caption{Scalability measured with binary counter examples from Rozier and Vardi~\cite{RV10}.}
     \label{fig:scalability}

### 2023-08-28 paper/main.tex
edits to sections 6-7

@@
 We prove the correctness of our translation pipeline.
-The correctness of the translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}.
-Below, we prove the correctness of (i) the translation from \Buchi automata to $\omega$-regular expressions, (ii) the ($\omega$-)regular expression rewrite rules we apply, and lastly, we outline the correctness of our timeline visualizations.
+The correctness of the translation from LTL formulas to \Buchi automata stems from using SPOT~\cite{Dur22}.
+Below, we prove the correctness of (i) the translation from \Buchi automata to $\omega$-regular expressions, and (ii) the ($\omega$-)regular expression rewrite rules we apply.
+Lastly, we outline the correctness of our timeline visualizations.
 \subsection{Correctness of Regex Translation}
@@
 \begin{itemize}
-    \item Can there be more simplifications methods as described in Section~\ref{regex-simplify}?
+    \item Can there be more simplification methods as described in Section~\ref{regex-simplify}?
 The answer is definitely positive.
-On one hand, more rule-based simplifications can be discovered by finding more patterns in the generated $\omega$-regular expressions.
-On the other hand, other simplification are possible: for example, if the generated $\omega$-regular expression is $r_1 + r_2$ where $r_1, r_2$ are not syntactically equivalent (or equivalent up to algebraic rules) $\omega$-regular expressions, but they accept the same set of infinite-length strings, then we can simplify this down to just $r_1$.
-This reduces the problem to equivalence test on $\omega$-regular expressions, which is decidable.
+For example, we can add more rule-based simplifications by finding more intuitive patterns in the generated $\omega$-regular expressions.
+Other simplifications are also possible; for example, if the generated $\omega$-regular expression is $r_1 + r_2$ where $r_1, r_2$ are not syntactically equivalent (or equivalent up to algebraic rules) $\omega$-regular expressions, but they accept the same set of infinite-length strings, then we can simplify this down to just $r_1$.
+This reduces the problem to equivalence testing on $\omega$-regular expressions, which is decidable.
 In a similar vein, many more simplifications may apply, but the question is how \emph{useful} are they?
-In the end, we have to balance the efficiency, simplicity, and understandabillity of the visualization.
+In the end, we have to balance the efficiency, simplicity, and understandabillity of each output visualization.
     %\item Our tool is effective at translating a wide range of LTL formulas. Even with LTL formulas with complex nesting structure are represented by relatively readable timeline visualizations.
@@
 
-\item {\bf Can there be back edges in a limited fashion (i.e., to simplify formulas) in timelines?} Most of our formulas have star-height of 1, so if we limit the back-edge representation to only surrounding a single node, that would simplify most formulas.
-We can then use the expanded notation for stared formulas larger than a single proposition, thus navigating a trade-off between small representation and limiting the visual complication.
-The criticism of this approach may be that back edges cause confusion between timeline and automata representations, and that with back edges timelines stop being intuitive with respect to the linearity of time.
+\item {\bf Can there be back edges in a limited fashion (i.e., to simplify formulas) in timelines?} Most of our formulas have a star-height of 1, so if we limit the back-edge representation to only surrounding a single node, that would simplify most formulas.
+We can then use the expanded notation for stared formulas larger than a single proposition, thus navigating the trade-off between having a small representation and limiting the visual complexity.
+One criticism of this approach may be that back edges cause confusion between timeline and automata representations, and that with back edges timelines stop being intuitive with respect to the linearity of time.
 

### 2023-08-28 paper/main.tex
finished edits to sectin 5

@@
 \endgroup
-To demonstrate the result of our tool, we present three examples, one from a real-world model checking example from Zhao and Rozier~\cite{ZR14}, one from a randomly generated \ltl\ formula, and one specifically demonstrates the use of our tool in specification verification.
+To demonstrate using \tool, we present three examples, one from a real-world model checking exercise from Zhao and Rozier~\cite{ZR14}, one from a randomly generated \ltl\ formula, and one that specifically shows the applicability of \tool\ to specification validation.
 
 \begin{example} \label{example:air}
-    Zhao and Rozier~\cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula
+    Zhao and Rozier~\cite{ZR14} presents a model verification specification, ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft,'' which corresponds to the \ltl\ formula
     \begin{align*}
-        \always & (\texttt{tsafe.TSAFE\_command1} \land  \\ & \texttt{controller.CTR\_control\_1} \\
+        \always & (\texttt{tsafe.TSAFE\_command1} \land  \\ & \texttt{controller.CTR\_control\_1}. \\
         \limplies & \nextt (\neg \texttt{controller.CTR\_control\_1}))
@@
     \[
-        \always (a \land b \limplies \nextt (\neg b))
+        \always (a \land b \limplies \nextt (\neg b)).
     \]
-    For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex14}.
+    For this \ltl\ formula, \tool\ generates the timeline representation in \cref{fig:ex14}.
     \begin{figure*}[h!]
@@
 \begin{example}
-    Spot~\cite{SPOT-online} presents command-line tool for random \ltl\ formula generator \texttt{randltl}~\cite{duret.13.atva}. The following \ltl\ formula is generated from this tool.
+    SPOT~\cite{SPOT-online} includes a command-line tool for random \ltl\ formula generation called \texttt{randltl}~\cite{duret.13.atva}. We used it to generate the following \ltl\ formula.
     \[
@@
 \begin{remark}
-    These two examples show that our tool can generate reasonably clear diagrams for both real-world formula and randomly generated formula.
+    These two examples show that our tool can generate reasonably intuitive diagrams for both real-world and randomly-generated formulas.
 \end{remark}
@@
 \begin{example}
-  Suppose we have a specification ``$p$ oscillates every time step''. It is common to come up with the following two \ltl\ formulas to describe this specification.
+  Suppose we have the specification ``$p$ oscillates every time step.'' Human specifiers often write one of the following two \ltl\ formulas to describe this specification.
   \begin{itemize}
@@
   \end{itemize}
-  It may be hard, without rigorous analysis, to distinguish which one is correct for the specification.
-However, our tool can generate the following two timelines for these two formulas as shown in \cref{fig:oscillates1,fig:oscillates2}, which clearly show the first formula is correct and the second formula is equivalent to $\bot$.
+  It may be hard, without rigorous analysis, to distinguish which one faithfully represents the specification.
+However, \tool\ generates the two timelines for these two formulas shown in \cref{fig:oscillates1,fig:oscillates2}, which clearly show the first formula is correct and the second formula is equivalent to $\bot$.
 \begin{figure}[!h]
@@
 
-We quantify the usability and performance of \tool by compiling an extensive set of \ltl\ formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of real-life \ltl\ formulas over those metrics.
+We quantify the usability and performance of \tool\ by compiling an extensive set of \ltl\ formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of real-life \ltl\ formulas over those metrics.
 % We release the set of real-life \ltl\ formulas as a benchmark set for the research community.

### 2023-08-28 paper/main.tex
edits to section 6

@@
 % We release the set of real-life \ltl\ formulas as a benchmark set for the research community.
-Our experimental evaluation conclusively demonstrates that \tool scales to provide helpful visualizations of \ltl\ formulas written by humans.
+Our experimental evaluation conclusively demonstrates that \tool\ scales to provide helpful visualizations of \ltl\ formulas written by humans.
 
@@
 We use two measures of complexity for timeline visualizations: timeline length and star height.
-
-We use timeline length, defined below, to capture the length of our timeline visualization graphs.
+We use timeline length as a proxy for size of our timeline visualization graphs.
 Since Kleene stars are the trickiest operator to depict in timelines, we also use star height, a well-studied measure for the structural complexity of regular expressions, to measure the complexity of our visualizations.
@@
 \begin{definition}[Timeline Length]
-    We define the timeline length of a regular expression $\tllen(A)$ recursively as follows
+    We define the timeline length of a regular expression $\tllen(A)$ recursively as follows.
     \begin{align*}
@@
     \end{align*}
-    We also extend this definition to $\omega$-regular expressions as follows
+    We also extend this definition to $\omega$-regular expressions as follows.
     \begin{align*}
@@
     \end{align*}
-    This quantity $\tllen$ captures the length of the longest path in our timeline graph visualization.
+    Then $\tllen$ captures the length of the longest path in our timeline graph visualization.
 \end{definition}
@@
 \begin{definition}[Star height]
-    We define the star height of regular and $\omega$-regular expressions to be the star-nesting depth in the (unsimplified) expression. Namely,
+    We define the star height of regular and $\omega$-regular expressions to be the star-nesting depth in the (unsimplified) expression. 
     \begin{align*}
@@
 %KYR: Here we nicely show (with pictures as much as possible) all of the individual statistics and results we gathered (note aggregation occurs below).
-\paragraph{Real-world datasets} We study the feasibility of our tool on a benchmark suite of \ltl\ formulas gathered from real world use cases.
-
-We gather a test suite of 91 formulas used in real-world requirement specification.
+%\paragraph{Real-world datasets}
+We study the feasibility of our tool on a benchmark suite of \ltl\ formulas gathered from real world use cases.
+%
+We gather a test suite totalling 91 formulas from two real-world requirement specification applications.
 We take $6$ specifications from NASA's Automated Airspace Concept (AAC)~\cite{GCMTR16}.
@@
 We reap $85$ formulas from the suite of $23$ examples, by generating separate visualizations for each line of specification.
-We choose to visualize each formula specifically, rather than complete specifications, as complete specifications may describe large complex systems, and we only intend the use case of validating individual specification formulas.
+We choose to visualize each formula individually, rather than visualize a complete set of (conjuncted) specifications, as a complete specification set may describe a large, complex system, and we only target the use case of validating individual formulas.
 % We choose to visualize each formula specifically, rather than complete specifications, as
 
-We run \texttt{ltl2regex} on these $91$ examples, the tool completes execution (within timeout of $20$s) on $87$.
+We run \texttt{ltl2regex} on these $91$ examples, \tool\ completes execution (with a timeout of $20$s) on $87$ of the 91 input formulas.
 Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of.
@@
 
-\paragraph{Scalability}
+%\paragraph{Scalability}
+{\bf Scalability.} 
+%KYR: FIX!!!
 We measure the scalability of our tool by running it against a set of scalable \ltl\ formulas.
-We define a scalable \ltl\ formula as one that describes an $n$-bit number using a binary counter~\cite{RV10}.
-As $n$ gets larger, the \ltl\ formula used to encode the $n$-bit counter scales in size, but it remains practical.
-The result is shown in \cref{fig:scalability}.
-In this analysis, the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}.
+We define a scalable \ltl\ formula as one that describes an $n$-bit number using a binary counter, as generated by~\cite{RV10}.
+As $n$ gets larger, the \ltl\ formula required to encode the $n$-bit counter scales in size.
+\cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}.
 
 In \cref{fig:scalability}, the $x$-axis ranges from $1$ to $6$, after which point it hits the $30$ seconds timeout we set, as the timeline length grows exponentially fast.
+
+%KYR: FIX: is timeout 20 seconds or 30 seconds?!?!?
 

### 2023-08-28 paper/main.tex
finished proofreading pass, modulo clarifications

@@
     % reduce_nfa does its input to output behaviour
-    For any NFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_nfa}$(G, v)$ preserves the regular language accepted by $G$
+    For any NFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_nfa}$(G, v)$ preserves the regular language accepted by $G$.
 \end{lemma}
@@
 We show that the trace of every path accepted by $G$ is also accepted by $G'$.
-Suppose a path accepted by $G$ does not pass through $v$, clearly this is true.
-Else, suppose it passes through $v$, since $v$ is an interior node, $v$ cannot be the first or last in the path.
+Suppose a path accepted by $G$ does not pass through $v$, clearly the lemma holds.
+Otherwise, suppose the path passes through $v$; since $v$ is an interior node, $v$ cannot be the first or last in the path.
 Thus, for every pass through $v$, let $u\neq v$ be the last node passed before entering $v$, and likewise $w$ be the first node after exiting $v$.
@@
 If there is a loop edge $r_{vv}$, this edge can be traveled any number of times before exiting $v$, thus the regular expression is $r=r_{uv}r_{vv}^*r_{vw}$.
-This edge $u\xrightarrow{r}w$ is added in $G'$.
+This edge $u\xrightarrow{r}w$ was added to $G'$.
 Thus, for every path accepted by $G$, for every subpath entering and exiting $v$ from some $u$ to $w$, there exists a corresponding subpath from $u$ to $w$ in $G'$, and thus a corresponding path accepted by $G'$.
@@
 \begin{lemma}
-    For any NFA $G$ with start state $s$ and (exactly one) final state $f$, \textbf{nfa2regex}$(G, s, f)$ outputs the regular expression of all paths from $s$ to $f$ (i.e., the language accepted by $G$)
+    For any NFA $G$ with start state $s$ and (exactly one) final state $f$, \textbf{nfa2regex}$(G, s, f)$ outputs the regular expression capturing all paths from $s$ to $f$ (i.e., $\L(G)$, the language accepted by $G$).
 \end{lemma}
 \begin{proof}
-    The while loop clearly terminates since the number of interior nodes is strictly decreasing, and upon termination, $G$ is an NFA containing only the nodes $s$ and $f$.
+    The {\bf while} loop clearly terminates since the number of interior nodes is strictly decreasing, and upon termination, $G$ is an NFA containing only the nodes $s$ and $f$.
 Now, every non-terminal visit from $s$ to $f$ and back to $s$, can be replaced by an edge $s\xrightarrow{r_\mathrm{sf}r_\mathrm{ff}^* r_\mathrm{fs}} s$, instead of the edge $f\to s$.
-This NFA yields the regular language $(r_\mathrm{ss}|r_\mathrm{sf}r_\mathrm{ff}^* r_\mathrm{fs})^* r_\mathrm{sf} r_\mathrm{ff}$, as outputted by the algorithm.
+This NFA yields the regular language $(r_\mathrm{ss}|r_\mathrm{sf}r_\mathrm{ff}^* r_\mathrm{fs})^* r_\mathrm{sf} r_\mathrm{ff}$, as produced by the algorithm.
 \end{proof}
@@
 \begin{proof}
-    Let $G'$ be $G$ with all out-edge (including loops) from $f$ deleted. We claim that $\L(G')$ is equal to the language $\L'$ of all paths from $s$ reaching $f$ for the first time.
+    Let $G'$ be $G$ with all out-edges (including loops) from $f$ deleted. We claim that $\L(G')$ is equal to the language $\L'$ of all paths from $s$ reaching $f$ for the first time.
 
@@
 
-    Also, we show $\L' \subseteq \L(G')$, i.e., every path starting in $s$ and ending by $f$ reaching $f$ for the first time is accepted by $G'$.
+    Also, we show $\L' \subseteq \L(G')$, i.e., every path starting in $s$ and ending by $f$ reaching $f$ for the first time %KYR: FIX!
+    is accepted by $G'$.
 If a path contains an out-edge of $f$, it cannot be in $\L'$ as the trace continues beyond the first time step at $f$.
@@
 \begin{theorem}
-    For any \Buchi automaton $G$ with start state $s$ and final states $F$, \textbf{ba2wregex}$(G)$ outputs the $\omega$-regular language accepted by $G$
+    For any \Buchi automaton $G$ with start state $s$ and final states $F$, \textbf{ba2wregex}$(G)$ outputs the $\omega$-regular language accepted by $G$.
 \end{theorem}
@@
 
-    First, $\L\subseteq \L_\omega(G)$ since for every infinite run in $\L$, clearly by definition of $\L$, there is some $f\in F$ such that passes through $f$ infinitely often.
-The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often, thus the run is in $\textbf{nfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega$
+    First, $\L\subseteq \L_\omega(G)$ since for every infinite run in $\L$, by definition of $\L$, there is some $f\in F$ such that passes through $f$ infinitely often.
+The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often; thus the run is in $\textbf{nfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega$.
 \end{proof}
@@
 
-The soundness of each of these translations can be proven by reasoning about the  semantics detailed in \cref{def:omega-semantics}. A full proof is not provided here.
-
-\subsection{Correctness of Timeline Visualization}\label{sec:correctness-timeline}
-Inductively, we show how to construct each form of regular and $\omega$-regular expression into a timeline representation.
-\paragraph{Regular expression}
+The soundness of each of these translations follows directly from the semantics detailed in \cref{def:omega-semantics}. %A full proof is not provided here.
+
+\subsection{Correctness of Timeline Visualizations}\label{sec:correctness-timeline}
+Inductively, we show how to faithfully capture each form of regular and $\omega$-regular expressions as timeline representations.
+\paragraph{Regular expressions}
 \begin{enumerate}
@@
   \item $A = \epsilon$. Omitted in the visualization.
-  \item $A = a$. Visualized as a single timeline node with $a$. A regular expression of an propositional logic formula signifies that the atomic proposition is true at the current time step.
+  \item $A = a$. Visualized as a single timeline node with $a$. A regular expression of a propositional logic formula signifies that the atomic proposition is true at the current time step.
   \item $A = A_1A_2$.
@@
 Visualized as the timelines of $A_1$ and $A_2$ in parallel.
-A union of two regular expressions signifies that either of the regular expressions can be true, which is represented by the parallel timelines.
+A union of two regular expressions signifies that either of the regular expressions can be true, which \tool\ represents by parallel timelines.
   \item $A = A_1^*$.
-If $A_1$ is a propositional logic formula, then it is visualized as an egg shape node with caption ``repeats 0 - $\infty$''.
-If $A_1$ is a regular expression involving concatenation, star, etc, then it is visualized as the timeline of $A_1$ followed by a node with label ``$\cdots$'', and that timeline pattern again.
-A Kleene star of a regular expression signifies that the regular expression can be repeated any number of times, including 0 times, which matches the meaning of our representation of egg shape node and ``$\cdots$''  node as described in \cref{sec:timeline}.
+If $A_1$ is a propositional logic formula, then its visualization is an egg-shaped node with the caption ``repeats 0 - $\infty$.'' If $A_1$ is a regular expression involving concatenation or a star ($*$) then its visualization is the timeline of $A_1$ followed by a node with label ``$\cdots$,'' and that timeline pattern again.
+A Kleene star of a regular expression signifies that the regular expression can be repeated any number of times, including 0 times, which matches the meaning of our representation of an egg-shaped node and a ``$\cdots$''  node as described in \cref{sec:timeline}.
 \end{enumerate}
-\paragraph{$\omega$-regular repression}
+\paragraph{$\omega$-regular repressions}
 \begin{enumerate}
   \item $B = A^\omega$.
-Visualized as a grey box enclosed with the timeline of $A$.
-An $\omega$ of a regular expression signifies that the regular expression is to be repeated infinitely many times, which matches the meaning of our representation of grey box, because every time it reach the end of the grey box, it must reenter the same grey box again, hence infinite repeat.
+Visualized as a grey box enclosing the timeline of $A$.
+An $\omega$ in a regular (sub-)expression signifies that the regular expression repeats infinitely many times, which matches the meaning of our grey box representation, because every time a timeline traversal reaches the end of the grey box, it must reenter the same grey box again, hence designating an infinite repeat.
   \item $B = AB$.
@@
 A concatenation of a regular expression and an $\omega$-regular expression signifies that the first must be true before the second $\omega$-regular expression can be true in the following time steps.
-  \item $B = B + B$.
-Visualized as the timelines of $B$ and $B$ in parallel.
-A union of two $\omega$-regular expressions signifies that either of the $\omega$-regular expressions can be true, which is represented by the parallel timelines.
+  \item $B = B_1 + B_2$.
+Visualized as the timelines of $B_1$ and $B_2$ in parallel.
+A union of two $\omega$-regular expressions signifies that either of the $\omega$-regular expressions can be true, which we represent by  parallel timelines.
 \end{enumerate}

### 2023-08-28 paper/main.tex
fix minor issues

@@
 We take a simple idiomatic approach to address this problem.
-Since Linear Temporal Logic formulas differentiate temporal information, we devise a tool, \tool, which can draw timelines to depict the satisfying traces of the \ltl\ formula, and thereby represent the specified behavior in a more natural, human-intelligible form.
-
-Our tool, \tool, uses a remarkably simple algorithm: transforming an input \ltl\ formula through a sequence of automata and regular expression-based intermediate representations.
-Yet, it is surprisingly effective at providing small representations for a range of \ltl\ formulas.
+Since Linear Temporal Logic formulas differentiate temporal information, we devise a tool, \tool, which can draw timelines to depict the satisfying traces of the LTL formula, and thereby represent the specified behavior in a more natural, human-intelligible form.
+
+Our tool, \tool, uses a remarkably simple algorithm: transforming an input LTL formula through a sequence of automata and regular expression-based intermediate representations.
+Yet, it is surprisingly effective at providing small representations for a range of LTL formulas.
 It visualizes the above air traffic control requirement behavior with the timeline shown in \cref{example:air}.
@@
 \begin{itemize}
-    \item We provide the tool, \tool, which takes \ltl\ formulas and synthesizes timeline visualizations for them.
-    \item We prove correctness in \cref{sec:analysis}. We show that for every \ltl\ formula, the timeline outputted indeed represents the set of satisfying traces.
+    \item We provide the tool, \tool, which takes LTL formulas and synthesizes timeline visualizations for them.
+    \item We prove correctness in \cref{sec:analysis}. We show that for every LTL formula, the timeline outputted indeed represents the set of satisfying traces.
     \item We showcase the results of our tool on a range of example formulas from real-life industrial verification efforts in \cref{sec:tool-showcase} and \cref{sec:playing}, including discussing the air traffic control example above.
@@
 We begin by setting up the prerequisite definitions involved in our work.
-First, we provide the definition and semantics for \ltl.
+First, we provide the definition and semantics for LTL.
 In the following subsections, we define (state-based) \Buchi automata and $\omega$-regular expressions, which are generalizations of the well-known deterministic finite automata (DFA) and regular expressions, for the case of infinite words.
@@
 
-\subsection{Linear Temporal Logic (\ltl)} \label{sec:ltl}
-
-\begin{definition}[Linear Temporal Logic (\ltl)]
+\subsection{Linear Temporal Logic (LTL)} \label{sec:ltl}
+
+\begin{definition}[Linear Temporal Logic (LTL)]
     % cite Kristin's survey paper
-    The syntax of an \ltl\ formula over a set of atomic propositions $\AP$, where $p\in\AP$ is a propositional variable, consists of the following grammar:
+    The syntax of an LTL formula over a set of atomic propositions $\AP$, where $p\in\AP$ is a propositional variable, consists of the following grammar:
     \begin{align*}
@@
 
-\begin{definition}[Semantics of \ltl\ ]
+\begin{definition}[Semantics of LTL ]
     Let $\pi : \omega \rightarrow 2^{\AP}$ be a \emph{computation} or trace that stores the truthhood and falsehood of every atomic proposition at every time step, where $\omega$ is the set of natural numbers that label the time step.
@@
     Our definition \ref{def:regex} of regular expressions concerns only finite-length strings.
-However, since \ltl\ formulas reason about events that happen over an infinite-length timeline, we need to model them using infinite regular expressions (i.e., $\omega$-regular expressions), which we define via the following grammar:
+However, since LTL formulas reason about events that happen over an infinite-length timeline, we need to model them using infinite regular expressions (i.e., $\omega$-regular expressions), which we define via the following grammar:
     \begin{align*}
@@
 
-The manifestation of timelines we use here is one of possibly many timeline representations that we devised for the purpose of visualizing \ltl\ formulas.
-We show how to construct such timelines from \ltl\ formulas in \cref{sec:correctness-timeline}.
+The manifestation of timelines we use here is one of possibly many timeline representations that we devised for the purpose of visualizing LTL formulas.
+We show how to construct such timelines from LTL formulas in \cref{sec:correctness-timeline}.
 
@@
 \endgroup
-On a high level, our algorithm for converting \ltl\ formulas into timeline visualizations (depicted in \Cref{fig:algo}) works as follows.
+On a high level, our algorithm for converting LTL formulas into timeline visualizations (depicted in \Cref{fig:algo}) works as follows.
 \begin{enumerate}
-    \item Convert the given \ltl\ formula to its corresponding \Buchi automaton. % (as detailed in \cref{ltl2aut})
+    \item Convert the given LTL formula to its corresponding \Buchi automaton. % (as detailed in \cref{ltl2aut})
     \item Derive the $\omega$-regular expression corresponding to the \Buchi automaton. % (in \cref{aut2regex})
@@
 \subsection{LTL to BA} \label{ltl2aut}
-The automata-theoretic approach~\cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} to evaluating \ltl\ (e.g., via reducing \ltl\ formulas to their corresponding \Buchi automata) has been well-studied \cite{DGV99,F03,RV10,RV11,Dur14}.
-Our tool \tool\ uses SPOT~\cite{Dur22}\footnote{We used SPOT version 2.11.} for this step, which provides a provably-correct implementation of the translation from \ltl\ formulas to minimally-sized \Buchi automata.
+The automata-theoretic approach~\cite{ORBi-a8d60ab6-1101-4434-9511-c01ea4e5a15b} to evaluating LTL (e.g., via reducing LTL formulas to their corresponding \Buchi automata) has been well-studied \cite{DGV99,F03,RV10,RV11,Dur14}.
+Our tool \tool\ uses SPOT~\cite{Dur22}\footnote{We used SPOT version 2.11.} for this step, which provides a provably-correct implementation of the translation from LTL formulas to minimally-sized \Buchi automata.
 
@@
 
-There is no agreed-upon canonical form for regular expressions representing \ltl\ formulas, hence we do not hope to find the shortest possible regular expression for visualization.
+There is no agreed-upon canonical form for regular expressions representing LTL formulas, hence we do not hope to find the shortest possible regular expression for visualization.
 Regular expression simplification comes down to regular expression equivalence checking, which is computationally hard~\cite{MNS04}.
@@
 However, this strategy is expensive in terms of the running time, and for the purpose of visualization, we did not use this strategy in our tool.
-We consider simplification for the purpose of finding the most intuitive regular expression for a given \ltl\ formula to be an interesting direction for future work.
+We consider simplification for the purpose of finding the most intuitive regular expression for a given LTL formula to be an interesting direction for future work.
 
@@
 \begin{example}
-    Using our algorithm, the \ltl\ formula $\varphi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}, respectively.
+    Using our algorithm, the LTL formula $\varphi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}, respectively.
     \begin{figure*}[h!]
@@
 \begin{remark}
-    Both simplified and un-simplified $\omega$-regular expressions could generate correct timeline representations that faithfully represent the set of satisfying traces of the original \ltl\ formula $\varphi$.
+    Both simplified and un-simplified $\omega$-regular expressions could generate correct timeline representations that faithfully represent the set of satisfying traces of the original LTL formula $\varphi$.
 Nonetheless, we, as human users, oftentimes find the simplified version more intuitive to reason about.
@@
 \endgroup
-To demonstrate using \tool, we present three examples, one from a real-world model checking exercise from Zhao and Rozier~\cite{ZR14}, one from a randomly generated \ltl\ formula, and one that specifically shows the applicability of \tool\ to specification validation.
+To demonstrate using \tool, we present three examples, one from a real-world model checking exercise from Zhao and Rozier~\cite{ZR14}, one from a randomly generated LTL formula, and one that specifically shows the applicability of \tool\ to specification validation.
 
 \begin{example} \label{example:air}
-    Zhao and Rozier~\cite{ZR14} presents a model verification specification, ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft,'' which corresponds to the \ltl\ formula
+    Zhao and Rozier~\cite{ZR14} presents a model verification specification, ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft,'' which corresponds to the LTL formula
     \begin{align*}
@@
     \]
-    For this \ltl\ formula, \tool\ generates the timeline representation in \cref{fig:ex14}.
+    For this LTL formula, \tool\ generates the timeline representation in \cref{fig:ex14}.
     \begin{figure*}[h!]
@@
 \begin{example}
-    SPOT~\cite{SPOT-online} includes a command-line tool for random \ltl\ formula generation called \texttt{randltl}~\cite{duret.13.atva}. We used it to generate the following \ltl\ formula.
+    SPOT~\cite{SPOT-online} includes a command-line tool for random LTL formula generation called \texttt{randltl}~\cite{duret.13.atva}. We used it to generate the following LTL formula.
     \[
@@
     \]
-    This formula is reasonably complicated, and hard for humans to reason about directly. For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex13}.
+    This formula is reasonably complicated, and hard for humans to reason about directly. For this LTL formula, our tool generates the timeline representation in \cref{fig:ex13}.
     \begin{figure*}[h!]
@@
 \begin{example}
-  Suppose we have the specification ``$p$ oscillates every time step.'' Human specifiers often write one of the following two \ltl\ formulas to describe this specification.
+  Suppose we have the specification ``$p$ oscillates every time step.'' Human specifiers often write one of the following two LTL formulas to describe this specification.
   \begin{itemize}
@@
 
-We quantify the usability and performance of \tool\ by compiling an extensive set of \ltl\ formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of real-life \ltl\ formulas over those metrics.
-% We release the set of real-life \ltl\ formulas as a benchmark set for the research community.
-Our experimental evaluation conclusively demonstrates that \tool\ scales to provide helpful visualizations of \ltl\ formulas written by humans.
+We quantify the usability and performance of \tool\ by compiling an extensive set of LTL formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of real-life LTL formulas over those metrics.
+% We release the set of real-life LTL formulas as a benchmark set for the research community.
+Our experimental evaluation conclusively demonstrates that \tool\ scales to provide helpful visualizations of LTL formulas written by humans.
 
@@
 %\paragraph{Real-world datasets}
-We study the feasibility of our tool on a benchmark suite of \ltl\ formulas gathered from real world use cases.
+We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
 %
@@
 
-We run \texttt{ltl2regex} on these $91$ examples, \tool\ completes execution (with a timeout of $20$s) on $87$ of the 91 input formulas.
+We run \texttt{ltl2regex} on these $91$ examples: $87$ of the $91$ input formulas complete execution within a timeout of $20$s.
 Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of.
@@
 %KYR: FIX!!!
-We measure the scalability of our tool by running it against a set of scalable \ltl\ formulas.
-We define a scalable \ltl\ formula as one that describes an $n$-bit number using a binary counter, as generated by~\cite{RV10}.
-As $n$ gets larger, the \ltl\ formula required to encode the $n$-bit counter scales in size.
+We measure the scalability of our tool by running it against a set of scalable LTL formulas.
+We define a scalable LTL formula as one that describes an $n$-bit number using a binary counter, as generated by~\cite{RV10}.
+As $n$ gets larger, the LTL formula required to encode the $n$-bit counter scales in size.
 \cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}.
@@
 
-% KYR: Here we characterize the size of the timeline as a function of the number of bits of a binary counter for each of the four binary counter \ltl\ formulas.
+% KYR: Here we characterize the size of the timeline as a function of the number of bits of a binary counter for each of the four binary counter LTL formulas.
 The point is that these four are the only (unboundedly) scalable formulas that describe something real (i.e., they describe a binary counter for any number of bits) that have ever been published in the literature.
-These would throw off our metrics about the set of real \ltl\ formulas if we included them in there.
+These would throw off our metrics about the set of real LTL formulas if we included them in there.
 Thus, we analyze them separately, and can define the timeline size as a function of the number of bits for each of the four formulas.
@@
 
-The set of \ltl\ formulas we used to evaluate our tool in \cref{sec:playing} can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas}{here}.
+The set of LTL formulas we used to evaluate our tool in \cref{sec:playing} can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas}{here}.
 
@@
     %\item Our tool is effective at translating a wide range of LTL formulas. Even with LTL formulas with complex nesting structure are represented by relatively readable timeline visualizations.
-    \item Can we define timelines more formally so that one can do this process reversely (i.e., a tool that converts timeline representation to its corresponding \ltl\ formula)?
+    \item Can we define timelines more formally so that one can do this process reversely (i.e., a tool that converts timeline representation to its corresponding LTL formula)?
 That would be very useful in practice.
@@
 Yet, specification remains the biggest bottleneck to the use of formal methods~\cite{Roz16}.
-\ltl\ is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway~\cite{DBR21,DBR23}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system~\cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS)~\cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept~\cite{CDRWRWL22} just to name a few.
+LTL is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway~\cite{DBR21,DBR23}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system~\cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS)~\cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept~\cite{CDRWRWL22} just to name a few.
  %
-Yet the humans that need to use formal verification tools and deeply understand their results struggle to validate that \ltl\ formulas capture the specifications they are meant to capture.
-A major contributor to \ltl's popularity is the propensity of humans to think of requirements in terms of timelines.
-This inspired the creation of \ltl\ in the first place, as a logic that ``intuitively'' represents timelines.
-Our work serves to reinforce that connection, enabling visualization of most realistic \ltl\ formulas as timelines.
-By releasing \tool, we contribute to better validation capabilities for \ltl\ specifications and aid the effort to make formal verification more accessible and wide-spread.
-%We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for \ltl.
+Yet the humans that need to use formal verification tools and deeply understand their results struggle to validate that LTL formulas capture the specifications they are meant to capture.
+A major contributor to LTL's popularity is the propensity of humans to think of requirements in terms of timelines.
+This inspired the creation of LTL in the first place, as a logic that ``intuitively'' represents timelines.
+Our work serves to reinforce that connection, enabling visualization of most realistic LTL formulas as timelines.
+By releasing \tool, we contribute to better validation capabilities for LTL specifications and aid the effort to make formal verification more accessible and wide-spread.
+%We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for LTL.
 
@@
 While we have chosen visual elements that succinctly represent timelines, it would be informative to conduct a study on different possible visualizations and which of the many ways of representing different timeline elements humans find most intuitive.
-It is possible that factors of context, such as the type of requirement an \ltl\ formula describes, change its optimal timeline representation.
+It is possible that factors of context, such as the type of requirement an LTL formula describes, change its optimal timeline representation.
 
@@
 \section{Concrete Syntax of \tool} \label{sec:concrete-syntax}
-Recall from~\ref{ltl-defn} that we define an \ltl\ formula as
+Recall from~\ref{ltl-defn} that we define an LTL formula as
 \begin{align*}
@@
 \end{align*}
-where $p \in \AP$ and $\varphi$ and $\psi$ are LTL formulas. In our tool \tool, we use the following concrete input syntax to represent \ltl\ formulas in ASCII text.
+where $p \in \AP$ and $\varphi$ and $\psi$ are LTL formulas. In our tool \tool, we use the following concrete input syntax to represent LTL formulas in ASCII text.
 \[
@@
 
-We collect the \ltl\ formulas from a covering set of publicly-available case studies that use \ltl\ in the analysis of real-life safety-critical systems.
-As some formulas are redundant (i.e., common properties occur in many different case studies), it is not necessary to include every paper that has ever used \ltl\ in a real setting; we instead opt for the largest and most unique formulas to cover the space of realistic use of \ltl.
-
-Given the tremendous popularity of \ltl\ as a specification language for industrial analysis, surprisingly few real-life system analysis case studies publicly release their \ltl\ formula specifications, largely to protect proprietary system information.
-We purposely avoid using the random or machine-generated formulas from published benchmarks because the purpose of \tool is helping humans understand and validate \ltl\ formulas.
+We collect the LTL formulas from a covering set of publicly-available case studies that use LTL in the analysis of real-life safety-critical systems.
+As some formulas are redundant (i.e., common properties occur in many different case studies), it is not necessary to include every paper that has ever used LTL in a real setting; we instead opt for the largest and most unique formulas to cover the space of realistic use of LTL.
+
+Given the tremendous popularity of LTL as a specification language for industrial analysis, surprisingly few real-life system analysis case studies publicly release their LTL formula specifications, largely to protect proprietary system information.
+We purposely avoid using the random or machine-generated formulas from published benchmarks because the purpose of \tool is helping humans understand and validate LTL formulas.
 Thus, we gather an extensive, representative set of formulas humans have written or needed to understand.
-Our \ltl\ formula collection is as follows.
+Our LTL formula collection is as follows.
 

### 2023-08-28 paper/main.tex
consistency

@@
 %\section{Theoretical Analyses} \label{sec:analysis}
-\section{``If we are true to ourselves, we can not be false to anyone\textsuperscript{\textsection}''}
+\section{Theoretical Analyses: ``If we are true to ourselves, we can not be false to anyone\textsuperscript{\textsection}''}
 \label{sec:analysis}
@@
 %\section{Tool showcase}
-\section{``Be great in act, as you have been in thought\textsuperscript{\textsection}''}
+\section{Tool Showcase: ``Be great in act, as you have been in thought\textsuperscript{\textsection}''}
 \label{sec:tool-showcase}
@@
 
-\section{Thought is free\textsuperscript{\textsection}: Artifact availability}
+\section{Artifact Availability: ``Thought is free\textsuperscript{\textsection}" }
 \begingroup\renewcommand\thefootnote{\textsection}

### 2023-08-28 paper/main.tex
nit

@@
 \begin{remark}
-    The \tool tool uses a concrete input syntax of ASCII symbols to represent those logical connectives, in order to simplify typesetting connectives such as $\always$ and $\eventually$.
+    The \tool\ tool uses a concrete input syntax of ASCII symbols to represent those logical connectives, in order to simplify typesetting connectives such as $\always$ and $\eventually$.
 For reference, the concrete syntax appears in Appendix ~\ref{sec:concrete-syntax}.
@@
 
-\begin{definition}[Semantics of LTL ]
+\begin{definition}[Semantics of LTL]
     Let $\pi : \omega \rightarrow 2^{\AP}$ be a \emph{computation} or trace that stores the truthhood and falsehood of every atomic proposition at every time step, where $\omega$ is the set of natural numbers that label the time step.

### 2023-08-28 paper/main.tex
kristin's pts 7, 8 - fixed typos

@@
 
-    Also, we show $\L' \subseteq \L(G')$, i.e., every path starting in $s$ and ending by $f$ reaching $f$ for the first time %KYR: FIX!
+    Also, we show $\L' \subseteq \L(G')$, i.e., every path starting in $s$ and ending by reaching $f$ for the first time
     is accepted by $G'$.
@@
     \[
-        \L = \bigcup_{f\in F} \textbf{nfa2regex}(G, s, f) \verb|^| \left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega
+        \L = \bigcup_{f\in F} \textbf{nfa2regex}(G, s, f)  \left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega
     \]
@@
     First, $\L\subseteq \L_\omega(G)$ since for every infinite run in $\L$, by definition of $\L$, there is some $f\in F$ such that passes through $f$ infinitely often.
-The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often; thus the run is in $\textbf{nfa2regex}(G, s, f)$ \verb|^| $\left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega$.
+The converse is true as well: for every infinite run $q_0, q_1, \dots$ accepted by $G$, then $q_0 = s$ and by definition of the accepting language, there is some accepting state $f$, passed through infinitely often; thus the run is in $\textbf{nfa2regex}(G, s, f)$ $\left(\textbf{nfa2regex\_firstvisit}(G, f, f)\right)^\omega$.
 \end{proof}

### 2023-08-28 paper/main.tex
clarified fixes...
added FIX label
clarify

@@
 
-%KYR: FIX THIS!
+%KYR: FIX THIS! We need to make it clear the relationship between Algorithms 1..4 and the figure displaying the high-level algorithm.
 The algorithm is outlined below (see Algorithms 1 - 4). %\cref{alg:ba2wregex}
@@
     \begin{align*}
-        \tllen(\emptyset)   &= -\infty\\
+        \tllen(\emptyset)   &= -\infty\\  %KYR:FIX!!!
         \tllen(\epsilon)        &= 0\\
@@
 %\paragraph{Real-world datasets}
+{\bf Feasibility.}
 We study the feasibility of our tool on a benchmark suite of LTL formulas gathered from real world use cases.
@@
 
-We run \texttt{ltl2regex} on these $91$ examples: $87$ of the $91$ input formulas complete execution within a timeout of $20$s.
+We run \texttt{ltl2regex} on these $91$ examples: $87$ of the $91$ input formulas complete execution within a timeout of $20$ seconds for the feasibility tests.
 Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of.
@@
 {\bf Scalability.}
-%KYR: FIX!!!
-We measure the scalability of our tool by running it against a set of scalable LTL formulas.
+%KYR: FIX!!! The description of the exact experiment run is not clear and seems to contradict the points in the above paragraph...
+We measure the scalability of our tool by running it against a set of \emph{scalable} LTL formulas.
 We define a scalable LTL formula as one that describes an $n$-bit number using a binary counter, as generated by~\cite{RV10}.
@@
 
-In \cref{fig:scalability}, the $x$-axis ranges from $1$ to $6$, after which point it hits the $30$ seconds timeout we set, as the timeline length grows exponentially fast.
+In \cref{fig:scalability}, the $x$-axis ranges from $1$ to $6$, after which point it hits the $30$ seconds timeout we set for the scalability tests, as the timeline length grows exponentially fast.
 
 %KYR: FIX: is timeout 20 seconds or 30 seconds?!?!?
+It still sounds like this is the same test as the paragraph above but with a different timeout.
+Please describe the difference in the tests; what was run exactly for a 30 second timeout and why was this different than the 20 second timout?
 
@@
 
-\section{Artifact Availability: ``Thought is free\textsuperscript{\textsection}" }
+\section{Artifact Availability: ``Thought is free\textsuperscript{\textsection}'' }
 \begingroup\renewcommand\thefootnote{\textsection}

### 2023-08-29 paper/main.tex
minor change to timeline length definition
minor change
added small fix
clarification

@@
 %KYR: FIX THIS! We need to make it clear the relationship between Algorithms 1..4 and the figure displaying the high-level algorithm.
-The algorithm is outlined below (see Algorithms 1 - 4). %\cref{alg:ba2wregex}
+The algorithm to convert \Buchi automata to $\omega$-regular expressions \texttt{ba2wregex} combines Algorthms 1--4 below. %\cref{alg:ba2wregex}
 
@@
     \begin{align*}
-        \tllen(\emptyset)   &= -\infty\\  %KYR:FIX!!!
+        \tllen(\emptyset)   & \quad \text{undefined} \\
         \tllen(\epsilon)    &= 0\\
@@
 We take $6$ specifications from NASA's Automated Airspace Concept (AAC)~\cite{GCMTR16}.
-We also collect formulas from the Acacia suite of examples~\cite{RV10}.
-We reap $85$ formulas from the suite of $23$ examples, by generating separate visualizations for each line of specification.
+We also collect formulas from the Acacia suite of examples~\cite{RV10}: $85$ formulas from the suite of $23$ collections of formulas were collected.
 We choose to visualize each formula individually, rather than visualize a complete set of (conjuncted) specifications, as a complete specification set may describe a large, complex system, and we only target the use case of validating individual formulas.
-% We choose to visualize each formula specifically, rather than complete specifications, as
+The set of formulas being tested can be found \href{https://github.com/EULIR/ltl-explainability/blob/main/ltl-formulas/benchmark-ltls.txt}{here}.
 
@@
 \cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}.
+The set of formulas being tested can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas/binary_counter}{here}.
 

### 2023-08-29 paper/main.tex
rewording

@@
 {\bf Scalability.}
-%KYR: FIX!!! The description of the exact experiment run is not clear and seems to contradict the points in the above paragraph...
-We measure the scalability of our tool by running it against a set of \emph{scalable} LTL formulas.
-We define a scalable LTL formula as one that describes an $n$-bit number using a binary counter, as generated by~\cite{RV10}.
-As $n$ gets larger, the LTL formula required to encode the $n$-bit counter scales in size.
+We study the scalability of our tool on a benchmark suite of LTL formulas that scales in size.
+According to Rozier and Vardi~\cite{RV10}, the LTL formula required to encode a $n$-bit binary counter scales in size as $n$ gets larger.
+Therefore the benchmark for scalability consists of LTL formulas that describe $n$-bit counters.
 \cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}.
@@
 In \cref{fig:scalability}, the $x$-axis ranges from $1$ to $6$, after which point it hits the $30$ seconds timeout we set for the scalability tests, as the timeline length grows exponentially fast.
-
-%KYR: FIX: is timeout 20 seconds or 30 seconds?!?!?
-It still sounds like this is the same test as the paragraph above but with a different timeout.
-Please describe the difference in the tests; what was run exactly for a 30 second timeout and why was this different than the 20 second timout?
 

### 2023-08-29 paper/main.tex
replace href with words

@@
 We choose to visualize each formula individually, rather than visualize a complete set of (conjuncted) specifications, as a complete specification set may describe a large, complex system, and we only target the use case of validating individual formulas.
-The set of formulas being tested can be found \href{https://github.com/EULIR/ltl-explainability/blob/main/ltl-formulas/benchmark-ltls.txt}{here}.
 
@@
 \cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}.
-The set of formulas being tested can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas/binary_counter}{here}.
 
@@
 \]
-which comes with two command-line tools, \texttt{ltl2regex} and \tool. The specific usage of the tool can be found  \href{https://github.com/EULIR/ltl-explainability#usage}{here}.
-
-The set of LTL formulas we used to evaluate our tool in \cref{sec:playing} can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas}{here}.
+which comes with two command-line tools, \texttt{ltl2regex} and \tool. The specific usage of the tool can be found in the artifact repository.
+
+The set of LTL formulas we used to evaluate our tool in \cref{sec:playing} can be found in the artifact repository under \texttt{ltl-formulas} directory.
 

### 2023-08-29 paper/main.tex
fixed passive voice

@@
 We take $6$ specifications from NASA's Automated Airspace Concept (AAC)~\cite{GCMTR16}.
-We also collect formulas from the Acacia suite of examples~\cite{RV10}: $85$ formulas from the suite of $23$ collections of formulas were collected.
+We also collect formulas from the Acacia suite of examples~\cite{RV10}: $85$ formulas extracted from the suite of $23$ collections of formulas.
 We choose to visualize each formula individually, rather than visualize a complete set of (conjuncted) specifications, as a complete specification set may describe a large, complex system, and we only target the use case of validating individual formulas.
@@
 We are able to generate tractable visualization on the remaining $85$, or over $93\%$ of benchmarks tested.
-The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.
+The plots of visualization complexity on these formula appear below in \cref{fig:real-world}.
 
